### 2018-01-11 Atomic Spectra/paper.tex
atomic spectra frame

\input{header}
\physics
\begin{document}
\papertitle{Analysis of Atomic Spectra of Various Gases}
\paperauth{A}{Khesin}{Lab Technician}
\paperauth{P}{Zavyalova}{Data Analyst}
\paperdate{January 15, 2018}
\begin{paperabs}
Abstract goes here
\end{paperabs}

\begin{paper}
\papersec{Introduction}

Introduction goes here

\papersec{Method}

Method goes here

\papersec{Data}

Data goes here

\papersec{Analysis}

Analysis goes here

\papersec{Conclusion}

Conclusion goes here
\end{paper}
\end{document}

### 2018-01-11 circuit-elements/thermistor.py
added circuit folder

@@ -1,0 +1,26 @@
+#!/usr/bin/python
+# Plots and fits data for a thermistor w/ varying temperatures
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+# ---------- User-Defined Functions ----------
+
+def f(x, a, b):
+	
+
+# ---------- Main Code ----------
+
+path_to_file = "/home/polina/Documents/3rd_Year/PHY324/circuit-elements/thermistor.txt"
+temp, resist = np.loadtxt(path_to_file, unpack = True)
+
+
+
+plt.plot(temp, resist)
+plt.grid(True)
+plt.xlabel("Temperature (C)")
+plt.ylabel("Resistance (ohms)")
+plt.title("Resistance vs. Temperature for a Thermistor")
+plt.show()

### 2018-01-14 Atomic Spectra/paper.tex
Started introduction
added measurements

@@
 
-Introduction goes here
+In this exercise, a prism spectrometer is calibrated and used to determine the Rydberg constant \( R_H \).
+Further, an ``unknown'' gas is identified by measuring its spectral lines and comparing them with the obtained calibration curve.
 
@@
 
-Data goes here
+(Helium)
+
+\begin{tabular}{|l|c|r|}
+	\hline
+	Vernier & Wavelength (nm) & Color \\ \hline
+	6.66 & 706.5 & red \\ \hline
+	7.06 & 667.8 & red \\ \hline
+	8.31 & 587.6 & yellow \\ \hline
+	11.09 & 501.6 & green \\ \hline
+	11.50 & 492.2 & green \\ \hline
+	12.58 & 471.3 & blue \\ \hline
+	14.19 & 447.1 & blue \\ \hline
+\end{tabular}
+
+(Hydrogen)
+
+\begin{tabular}{|l|r|}
+	\hline
+	Vernier & Color \\ \hline
+	7.26 & red \\ \hline
+	11.80 & blue-green \\ \hline
+	15.15 & violet \\ \hline
+	17.75 & violet \\ \hline
+\end{tabular}
+
+(Unknown \# 7)
+
+\begin{tabular}{|l|r|}
+	\hline
+	Vernier & Color \\ \hline
+	8.44 & orange \\ \hline
+	9.18 & green \\ \hline
+	13.89 & violet \\ \hline
+	15.38 & violet \\ \hline
+\end{tabular}
 

### 2018-01-14 Atomic Spectra/paper.tex
fixed that table
finished the data tables, sort of
finished introduction and observations

--- 2018-01-11 Atomic Spectra/paper.tex
@@
 \begin{paperabs}
-Abstract goes here
+TODO Abstract
 \end{paperabs}
@@
 
-Introduction goes here
+The purpose of this experiment was to use a prism spectrometer to identify
+unknown gases based on their atomic spectra.
+Furthermore, the Rydberg constant ($R_H$) was determined by examining the
+spectral lines of hydrogen.
+The apparatus consisted of a spectrometer, a sodium lamp, a tube of hydrogen
+gas, a tube of helium gas, and two tubes of unknown compounds marked ``Unknown
+\#7'' and ``Unknown \#9''.
 
-\papersec{Method}
+The spectrometer was calibrated by aligning the eyepiece with the lines produced
+by the sodium lamp and the Hartmann relation method was used to determine the
+relation between the observed wavelength and the scale reading on the
+spectrometer.
 
-Method goes here
+By examining the spectral lines of hydrogen, the Rydberg constant was
+determined with the following formula.
 
-\papersec{Data}
+\papereq{Rydberg}{\frac1\lambda=R_H\pars{\frac14-\frac1{n^2}}}{Serbanescu}
+\begin{paperwhere}
+\papervar{\lambda}{observed wavelength}{\meter}
+\papervar{R_H}{Rydberg constant}{\per\meter}
+\papervar{n}{index of spectral line}{}
+\end{paperwhere}
 
-Data goes here
+To determine the relation between the scale reading of the spectrometer and the
+observed wavelength, the Hartmann relation was used.
+
+\papereq{Hartmann}{y=\frac{m}{\lambda-\lambda_0}+b}{Serbanescu}
+\begin{paperwhere}
+\papervar{y}{scale reading}{}
+\papervar{m}{slope of fit}{\meter}
+\papervar{\lambda}{observed wavelength}{\meter}
+\papervar{\lambda_0}{fundamental wavelength of spectrometer}{\meter}
+\papervar{b}{constant of fit}{}
+\end{paperwhere}
+
+For the spectrometer used in the experiment, the value of $\lambda_0$ was
+provided as $(285.2\pm.4)\si{\nano\meter}$.
+
+The experiment was setup as shown.
+\paperfig{Setup}{\pdf{setup}}{The experimental setup.
+The spectrometer (left) is pointing at a tube containing ``Unknown \#7'' (right).}
+\papersec{Observations}
+
+The vernier scale on the spectrometer had a reading error of
+$\pm.02\si{\nano\meter}$.
+The uncertainties in the wavelengths for the spectral lines of helium were
+deemed too small to consider.
+
+The vernier scale readings were recorded for helium, hydrogen, ``Unknown \#7'',
+and ``Unknown \#9''.
+Additionally, the colours of the observed lines and matched wavelengths for the
+spectral lines of helium were recorded.
+
+\paperfig{Helium}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+\paperoline\papertableindexheader&\textsc{Scale}&\textsc{Wavelength}&\multirow{2}{*}{\textsc{Colour}}\\
+\papertablecheaderunit{.02}{\hspace{-0.5ex}}\papertablecheadersymbol{\lambda~(\si{\nano\meter})}&\\\paperiline
+\papertableindex\papertablecval{6.66}\papertablecval{706.5}\papertablecval{Red}\\\paperiline
+\papertableindex\papertablecval{7.06}\papertablecval{667.8}\papertablecval{Red}\\\paperiline
+\papertableindex\papertablecval{8.31}\papertablecval{587.6}\papertablecval{Yellow}\\\paperiline
+\papertableindex\papertablecval{11.09}\papertablecval{501.6}\papertablecval{Green}\\\paperiline
+\papertableindex\papertablecval{11.50}\papertablecval{492.2}\papertablecval{Green}\\\paperiline
+\papertableindex\papertablecval{12.58}\papertablecval{471.3}\papertablecval{Blue}\\\paperiline
+\papertableindex\papertablecval{14.19}\papertablecval{447.1}\papertablecval{Blue}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{The scale readings, matched wavelengths, and colours of the spectral lines of helium.}\vspace{1em}
+
+\paperfig{Hydrogen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
+\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
+\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
+\papertableindex\papertablecval{7.26}\papertablecval{Red}\\\paperiline
+\papertableindex\papertablecval{11.80}\papertablecval{Blue-Green}\\\paperiline
+\papertableindex\papertablecval{15.15}\papertablecval{Violet}\\\paperiline
+\papertableindex\papertablecval{17.75}\papertablecval{Violet}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{The scale readings and colours of the spectral lines of hydrogen.}\vspace{1em}
+
+\paperfig{UnknownSeven}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
+\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
+\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
+\papertableindex\papertablecval{8.44}\papertablecval{Orange}\\\paperiline
+\papertableindex\papertablecval{9.18}\papertablecval{Green}\\\paperiline
+\papertableindex\papertablecval{13.89}\papertablecval{Violet}\\\paperiline
+\papertableindex\papertablecval{15.38}\papertablecval{Violet}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{The scale readings and colours of the spectral lines of ``Unknown \#7''.}\vspace{1em}
+
+\paperfig{UnknownNine}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
+\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
+\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
+\papertableindex\papertablecval{TODO}\papertablecval{Red}\\\paperiline
+\papertableindex\papertablecval{TODO}\papertablecval{Orange}\\\paperiline
+\papertableindex\papertablecval{TODO}\papertablecval{Yellow}\\\paperiline
+\papertableindex\papertablecval{TODO}\papertablecval{Green}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{The scale readings and colours of the spectral lines of ``Unknown \#9''.}
 
@@
 Conclusion goes here
+
+\papersec{Sources}
+
+\papersource{Serbanescu, R., Measuring atomic spectra, 2014}
 \end{paper}

### 2018-01-14 Atomic Spectra/paper.tex
added graph

@@
 
-Analysis goes here
+We start by finding the relationship between the observed wavelength and the
+scale reading on the spectrometer.
+We subtract $\lambda_0$ from all of the values in the wavelength column of
+\figHelium and then take the reciprocals to get the values of our independent
+variable.
+The scale column forms the values for the dependent variable.
+Applying the fit yields a slope of $(2.00\pm.02)\si{\micro\meter}$ and a
+y-intercept of $(1.83\pm.09)$.
+The $R^2$ value for the fit is 0.999489.
+TODO ADD CHI SQUARED AND RESIDUALS\\
+
+\paperfig{ScaleFit}{\begin{tikzpicture}[scale=0.95]
+\begin{axis}[width=\linewidth,
+tick label style={font=\fontsize{10pt}{1em}},
+xlabel={\fontsize{10pt}{1em}\selectfont $\frac{1}{\lambda-\lambda_0}$ ($10^6$ $\si{\per\meter})\rightarrow$},
+ylabel={\fontsize{10pt}{1em}\selectfont $y\rightarrow$},
+\paperaxis{Scale Reading vs. Modified Wavelength}{y}{x}{2}{5}{8}{15}{2}{2}]
+\papergraphoutline{2}{5}{8}{15};
+\addplot [color=black,only marks,mark=o,mark size=1.5,
+error bars/.cd,
+y dir=both,y explicit,
+x dir=both,x explicit
+] coordinates {
+(2.374, 6.66) +- (0.002,0.02)
+(2.614, 7.06) +- (0.003,0.02)
+(3.307, 8.31) +- (0.004,0.02)
+(4.621, 11.09) +- (0.009,0.02)
+(4.831, 11.50) +- (0.009,0.02)
+(5.37, 12.58) +- (0.01,0.02)
+(6.18, 14.19) +- (0.02,0.02)
+};
+\addplot[no marks,
+samples=250,
+domain=2:8]
+{2*x+1.83};
+\end{axis}
+\end{tikzpicture}}
+{The scale readings on the spectrometer plotted against the modified
+wavelengths with the line of best fit.
+The line has a function of $(2.00\pm.02)\text{E-6}x+(1.83\pm.09)$ and an
+\smash{$R^2$} value of 0.999489.
+Error bars were included but were too small to be visible.}
 

### 2018-01-14 Atomic Spectra/paper.tex
added rydberg calculations

@@
 
-\paperfig{Hydrogen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
-\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
-\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
-\papertableindex\papertablecval{7.26}\papertablecval{Red}\\\paperiline
-\papertableindex\papertablecval{11.80}\papertablecval{Blue-Green}\\\paperiline
-\papertableindex\papertablecval{15.15}\papertablecval{Violet}\\\paperiline
-\papertableindex\papertablecval{17.75}\papertablecval{Violet}\\\paperoline
+\paperfig{Hydrogen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+\paperoline\papertableindexheader&\multirow{2}{*}{\textsc{Line Index}}&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
+&\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
+\papertableindex\papertablecval{3}\papertablecval{7.26}\papertablecval{Red}\\\paperiline
+\papertableindex\papertablecval{4}\papertablecval{11.80}\papertablecval{Blue-Green}\\\paperiline
+\papertableindex\papertablecval{5}\papertablecval{15.15}\papertablecval{Violet}\\\paperiline
+\papertableindex\papertablecval{6}\papertablecval{17.75}\papertablecval{Violet}\\\paperoline
 \end{papertable}\vspace{-1.5em}}
-{The scale readings and colours of the spectral lines of hydrogen.}\vspace{1em}
+{The scale readings, indices, and colours of the spectral lines of hydrogen.}\vspace{1em}
 
@@
 
-We start by finding the relationship between the observed wavelength and the
-scale reading on the spectrometer.
-We subtract $\lambda_0$ from all of the values in the wavelength column of
-\figHelium and then take the reciprocals to get the values of our independent
-variable.
-The scale column forms the values for the dependent variable.
-Applying the fit yields a slope of $(2.00\pm.02)\si{\micro\meter}$ and a
+The relationship between the observed wavelength and the
+scale reading on the spectrometer was calculated.
+This was done by subtracting $\lambda_0$ from all of the values in the wavelength column of
+\figHelium and then taking the reciprocals to get the values of the independent
+variables.
+All uncertainties were propagated using the method of quadratures.
+The scale column formed the values for the dependent variable.
+Applying the fit yielded a slope of $(2.00\pm.02)\x\SI{E-6}{\meter}$ and a
 y-intercept of $(1.83\pm.09)$.
-The $R^2$ value for the fit is 0.999489.
+The $R^2$ value for the fit s 0.999489.
 TODO ADD CHI SQUARED AND RESIDUALS\\
@@
 
+Then, \eqHartmann was inverted to convert scale readings into wavelengths.
+
+\papereq{Invert}{\lambda=\frac{m}{y-b}+\lambda_0}{}
+
+By converting all the scale readings from \figHydrogen and plugging the
+wavelengths and the line indices into \eqRydberg, four approximations
+for the Rydberg constant were obtained.
+They were averaged to get the final value for $R_H$, which was
+$(1.097\pm.003)\x\SI{E7}{\per\meter}$, which was well within the range of the
+experimental error from the accepted $\SI{1.09737316E7}{\per\meter}$.
+
 \papersec{Conclusion}

### 2018-01-14 Atomic Spectra/fitting.py
.py fit + residuals

@@ -1,0 +1,65 @@
+#!/usr/bin/python
+# Fits data for helium to the Hartmann relation method
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Functions ----------
+
+# Test function (Hartmann relation, m = a, b = b)
+# (x, a, b) --> (f)
+# (float, float, float) --> (float)
+def f(x, a, b):
+	return a / (x - lambda_0) + b
+
+# ---------- Main Code ----------
+
+unc = 0.02
+lambda_0 = 285.2	# (+- 0.4) nm
+
+# Read .txt file & extract data
+path_to_file = "/home/polina/Documents/3rd_Year/PHY324/Atomic Spectra/atomic-spectra-helium.txt"
+scale, wavelength = np.loadtxt(path_to_file, unpack = True, usecols = (0, 1))
+# Array with uncertainties
+scale_unc = np.empty(scale.size)
+scale_unc.fill(unc)
+# Degrees of freedom
+ddof = np.size(wavelength - 2)
+
+# Fit data
+popt, pcov = curve_fit(f, wavelength, scale, sigma = scale_unc)
+# Calculate chi squared + residuals
+r = scale - f(wavelength, *popt)
+chisq = np.sum(r ** 2 / scale_unc)
+print "Reduced chi squared:", chisq / ddof
+
+print "Parameters:", popt
+
+# Generate data for plotting (using fit parameters)
+x_fit = np.linspace(np.amin(wavelength), np.amax(wavelength), 100)
+y_fit = f(x_fit, *popt)
+
+# Plot data + model with fit parameters
+plt.plot(wavelength, scale, label = "Experiment")
+plt.plot(x_fit, y_fit, label = "Fit")
+plt.legend()
+plt.grid(True)
+plt.xlabel("Wavelength (nm)")
+plt.ylabel("Scale reading")
+plt.title("Scale reading vs. Wavelength for Helium Gas")
+plt.savefig("Hartmann-fit.pdf")
+plt.close()
+
+plt.scatter(wavelength,r)
+plt.plot(np.linspace(np.amin(wavelength) - 100, np.amax(wavelength) + 100, np.size(wavelength)), np.zeros(np.size(wavelength)))
+plt.xlabel("Wavelength (nm)")
+plt.ylabel("Residuals")
[…]

### 2018-01-14 circuit-elements/paper.tex
added photos + introduction

\input{header}
\physics
\begin{document}
\papertitle{Non-linear Circuit Elements}
\paperauth{A}{Khesin}{}
\paperauth{P}{Zavyalova}{}
\paperdate{January 17, 2018}
\begin{paperabs}

	Abstract goes here

\end{paperabs}

\begin{paper}

\papersec{Introduction}

	The purpose of this experiment was to study the relationship between voltage and current for a thermistor and an incandescent lamp. Both of these circuit elements are nonlinear; for a thermistor, the resistance is a function of temperature and obeys the relation

	\papereq{Thermistor}{R = R_0e^{ -\frac{T}{T_0} }}{Serbanescu}
	\begin{paperwhere}
		\papervar{T}{absolute temperature}{\kelvin}
		\papervar{T_0}{constant of device}{\kelvin}
		\papervar{R_0}{constant of device}{\ohm}
	\end{paperwhere}

	The relationship was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown:

	\paperfig{Setup}{\pdf{setup1}}{The experimental setup (thermistor).}

	The temperature of the thermistor was decreased by adding cold water to the thermal flask.

	The tungsten filament in a light bulb follows Ohm's law,

	\papereq{Ohm}{ R = \frac{V}{I} }{Serbanescu}
	\begin{paperwhere}
		\papervar{R}{resistance}{\ohm}
		\papervar{V}{potential}{\volt}
		\papervar{I}{current}{\ampere}
	\end{paperwhere}

	However, as the temperature increases, the resistance of the metal increases and above a certain temperature becomes proportional to the absolute temperature. The actual relationship between \( V \) and \( I \) is investigated in this experiment by fitting obtained measurements of current and potential to

	\papereq{bulb-model}{ V = k I^a }{Serbanescu}
	\begin{paperwhere}
		\papervar{V}{potential}{\volt}
		\papervar{I}{current}{\ampere}
		\papervar{k}{constant}{}
		\papervar{a}{costant}{}
	\end{paperwhere}

	Potential and current are measured using two multimeters, a power supply, a tungsten filament light bulb, and a switch arranged as follows:

	\paperfig{Setup}{\pdf{setup2}}{The experimental setup (light bulb).}

\papersec{Observations}

	\paperfig{Hydrogen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
			\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
			\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
			\papertableindex\papertablecval{7.26}\papertablecval{Red}\\\paperiline
			\papertableindex\papertablecval{11.80}\papertablecval{Blue-Green}\\\paperiline
			\papertableindex\papertablecval{15.15}\papertablecval{Violet}\\\paperiline
			\papertableindex\papertablecval{17.75}\papertablecval{Violet}\\\paperoline
		\end{papertable}\vspace{-1.5em}}
	{The scale readings and colours of the spectral lines of hydrogen.}\vspace{1em}

\papersec{Analysis}

	Analysis

\papersec{Conclusion}

	Conclusion

\papersec{Sources}

	Sources

\papersource{}

\end{paper}

\end{document}

### 2018-01-15 circuit-elements/paper.tex
added observations

@@
 \paperauth{A}{Khesin}{}
-\paperauth{P}{Zavyalova}{}
+\paperauth{P}{Zavyalova}{1002345036}
 \paperdate{January 17, 2018}
@@
 
-	\paperfig{Hydrogen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
-			\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
-			\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
-			\papertableindex\papertablecval{7.26}\papertablecval{Red}\\\paperiline
-			\papertableindex\papertablecval{11.80}\papertablecval{Blue-Green}\\\paperiline
-			\papertableindex\papertablecval{15.15}\papertablecval{Violet}\\\paperiline
-			\papertableindex\papertablecval{17.75}\papertablecval{Violet}\\\paperoline
+	The resistance of the thermistor at various temperatures was obtained and recorded. The uncertainty in resistance is taken to be the last digit increment in the least significant digit displayed.
+
+	\paperfig{Thermistor}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
+			\paperoline\papertableindexheader&\textsc{Temperature}&\multirow{2}{*}{\textsc{Resistance}}\\
+			\papertablecheaderunit{0.5}{\hspace{-0.5ex}}&\\\paperiline
+			\papertableindex\papertablecval{352.5}\papertablecval{6.68}\\\paperiline
+			\papertableindex\papertablecval{349.0}\papertablecval{6.93}\\\paperiline
+			\papertableindex\papertablecval{348.0}\papertablecval{7.54}\\\paperiline
+			\papertableindex\papertablecval{346.0}\papertablecval{8.01}\\\paperiline
+			\papertableindex\papertablecval{340.0}\papertablecval{9.95}\\\paperiline
+			\papertableindex\papertablecval{338.0}\papertablecval{10.33}\\\paperiline
+			\papertableindex\papertablecval{335.0}\papertablecval{11.76}\\\paperiline
+			\papertableindex\papertablecval{334.5}\papertablecval{12.36}\\\paperiline
+			\papertableindex\papertablecval{329.5}\papertablecval{14.45}\\\paperiline
+			\papertableindex\papertablecval{327.5}\papertablecval{15.33}\\\paperiline
+			\papertableindex\papertablecval{324.0}\papertablecval{17.23}\\\paperiline
+			\papertableindex\papertablecval{321.0}\papertablecval{19.51}\\\paperiline
+			\papertableindex\papertablecval{319.0}\papertablecval{21.7}\\\paperiline
+			\papertableindex\papertablecval{317.0}\papertablecval{24.3}\\\paperiline
+			\papertableindex\papertablecval{314.0}\papertablecval{26.1}\\\paperiline
+			\papertableindex\papertablecval{309.5}\papertablecval{31.4}\\\paperiline
+			\papertableindex\papertablecval{308.5}\papertablecval{33.7}\\\paperiline
+			\papertableindex\papertablecval{307.5}\papertablecval{35.5}\\\paperiline
+			\papertableindex\papertablecval{305.0}\papertablecval{38.0}\\\paperiline
+			\papertableindex\papertablecval{304.0}\papertablecval{40.3}\\\paperiline
+			\papertableindex\papertablecval{301.5}\papertablecval{44.3}\\\paperiline
+			\papertableindex\papertablecval{299.5}\papertablecval{47.7}\\\paperiline
+			\papertableindex\papertablecval{298.0}\papertablecval{51.6}\\\paperiline
+			\papertableindex\papertablecval{296.0}\papertablecval{56.3}\\\paperiline
+			\papertableindex\papertablecval{294.0}\papertablecval{61.3}\\\paperiline
+			\papertableindex\papertablecval{292.5}\papertablecval{66.9}\\\paperiline
+			\papertableindex\papertablecval{290.5}\papertablecval{73.8}\\\paperiline
+			\papertableindex\papertablecval{286.0}\papertablecval{92.9}\\\paperiline
+			\papertableindex\papertablecval{283.0}\papertablecval{104.7}\\\paperiline
+			\papertableindex\papertablecval{278.0}\papertablecval{126.2}\\\paperoline
 		\end{papertable}\vspace{-1.5em}}
-	{The scale readings and colours of the spectral lines of hydrogen.}\vspace{1em}
+	{Resistance of thermistor at the given temperatures.}\vspace{1em}
+
+	Further, current and potential for a tungsten filament light bulb were measured and recorded. The uncertainty is again taken to be the last digit increment in the least significant digit displayed.
+
+	\paperfig{Light bulb}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
+			\paperoline\papertableindexheader&\multirow{2}{*}{\textsc{Potential}}&\multirow{2}{*}{\textsc{Current}}\\
+			& \\ \paperiline
+			\papertableindex\papertablecval{0.0222}\papertablecval{0.324}\\\paperiline
+			\papertableindex\papertablecval{0.0776}\papertablecval{1.045}\\\paperiline
+			\papertableindex\papertablecval{0.1122}\papertablecval{1.390}\\\paperiline
+			\papertableindex\papertablecval{0.244}\papertablecval{2.27}\\\paperiline
+			\papertableindex\papertablecval{0.472}\papertablecval{3.40}\\\paperiline
+			\papertableindex\papertablecval{0.541}\papertablecval{3.69}\\\paperiline
+			\papertableindex\papertablecval{0.697}\papertablecval{4.28}\\\paperiline
+			\papertableindex\papertablecval{0.871}\papertablecval{4.89}\\\paperiline
+			\papertableindex\papertablecval{1.128}\papertablecval{5.72}\\\paperiline
+			\papertableindex\papertablecval{1.840}\papertablecval{7.68}\\\paperiline
+			\papertableindex\papertablecval{1.940}\papertablecval{7.93}\\\paperiline
+			\papertableindex\papertablecval{4.01}\papertablecval{12.34}\\\paperiline
+			\papertableindex\papertablecval{6.00}\papertablecval{15.79}\\\paperiline
+			\papertableindex\papertablecval{8.01}\papertablecval{18.83}\\\paperiline
+			\papertableindex\papertablecval{10.24}\papertablecval{21.8}\\\paperiline
+			\papertableindex\papertablecval{12.07}\papertablecval{24.1}\\\paperiline
+			\papertableindex\papertablecval{14.27}\papertablecval{26.6}\\\paperiline
+			\papertableindex\papertablecval{16.01}\papertablecval{28.5}\\\paperiline
+			\papertableindex\papertablecval{17.98}\papertablecval{30.6}\\\paperiline
+			\papertableindex\papertablecval{18.45}\papertablecval{31.1}\\\paperiline
+			\papertableindex\papertablecval{19.86}\papertablecval{31.1}\\\paperiline
+			\papertableindex\papertablecval{19.86}\papertablecval{32.5}\\\paperiline
+			\papertableindex\papertablecval{21.0}\papertablecval{33.6}\\\paperiline
+			\papertableindex\papertablecval{22.1}\papertablecval{34.6}\\\paperiline
+			\papertableindex\papertablecval{22.9}\papertablecval{35.4}\\\paperiline
+			\papertableindex\papertablecval{24.0}\papertablecval{36.4}\\\paperiline
+			\papertableindex\papertablecval{25.1}\papertablecval{37.3}\\\paperoline
+			\end{papertable}\vspace{-1.5em}}
+	{Potential and current through the light bulb.}\vspace{1em}
 

### 2018-01-15 circuit-elements/thermistor.py

@@ -5,18 +5,28 @@
 
 import numpy as np
 import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
 
 # ---------- User-Defined Functions ----------
 
+# Fit function for optimizing; 
 def f(x, a, b):
-	
+	return a * np.exp(- x / b)
 
 # ---------- Main Code ----------
 
 path_to_file = "/home/polina/Documents/3rd_Year/PHY324/circuit-elements/thermistor.txt"
 temp, resist = np.loadtxt(path_to_file, unpack = True)
+temp = temp + 273.0			# Convert temperature to K
 
+print(temp)
+print(resist)
 
+# Arrays w/ uncertainties
+temp_unc = np.full(np.size(temp), 0.5)
+resist_unc = np.concatenate((np.full(12, 0.01), np.full(18, 0.1)))
+
+popt, pcov = curve_fit(f, temp, resist)
 
 plt.plot(temp, resist)
 plt.grid(True)

### 2018-01-15 Atomic Spectra/fitting.py
Fixed .py code

@@ -27,13 +27,13 @@ scale, wavelength = np.loadtxt(path_to_file, unpack = True, usecols = (0, 1))
 scale_unc = np.empty(scale.size)
 scale_unc.fill(unc)
 # Degrees of freedom
-ddof = np.size(wavelength - 2)
+ddof = np.size(wavelength) - 2
 
 # Fit data
 popt, pcov = curve_fit(f, wavelength, scale, sigma = scale_unc)
 # Calculate chi squared + residuals
 r = scale - f(wavelength, *popt)
-chisq = np.sum(r ** 2 / scale_unc)
+chisq = np.sum((r / scale_unc) ** 2)
 print "Reduced chi squared:", chisq / ddof
 
 print "Parameters:", popt

### 2018-01-15 Atomic Spectra/paper.tex
added more data...

@@
 \papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
-\papertableindex\papertablecval{TODO}\papertablecval{Red}\\\paperiline
-\papertableindex\papertablecval{TODO}\papertablecval{Orange}\\\paperiline
-\papertableindex\papertablecval{TODO}\papertablecval{Yellow}\\\paperiline
-\papertableindex\papertablecval{TODO}\papertablecval{Green}\\\paperoline
+\papertableindex\papertablecval{6.61}\papertablecval{Red}\\\paperiline
+\papertableindex\papertablecval{8.05}\papertablecval{Orange}\\\paperiline
+\papertableindex\papertablecval{8.50}\papertablecval{Yellow}\\\paperiline
+\papertableindex\papertablecval{9.65}\papertablecval{Green}\\\paperoline
 \end{papertable}\vspace{-1.5em}}
@@
 tick label style={font=\fontsize{10pt}{1em}},
-xlabel={\fontsize{10pt}{1em}\selectfont $\frac{1}{\lambda-\lambda_0}$ ($10^6$ $\si{\per\meter})\rightarrow$},
+xlabel={\fontsize{10pt}{1em}\selectfont $\frac{1}{\lambda-\lambda_0}$ $(\SI{E6}{\per\meter})\rightarrow$},
 ylabel={\fontsize{10pt}{1em}\selectfont $y\rightarrow$},
@@
 wavelengths with the line of best fit.
-The line has a function of $(2.00\pm.02)\text{E-6}x+(1.83\pm.09)$ and an
+The line has a function of $(2.00\pm.02)\x\SI{E-6}{}x+(1.83\pm.09)$ and an
 \smash{$R^2$} value of 0.999489.
@@
 $(1.097\pm.003)\x\SI{E7}{\per\meter}$, which was well within the range of the
-experimental error from the accepted $\SI{1.09737316E7}{\per\meter}$.
+experimental error from the accepted value of $\SI{1.09737316E7}{\per\meter}$.
+
+The reversed formula was used to compute the wavelengths of the observed
+spectral lines for the two unknown gases.
+The following results were obtained for the two unknown gases.
+
+\paperfig{UnknownSevenResult}{\begin{papertable}{|[outer]I|[inner]U|[inner]C|[outer]}
+\paperoline\papertableindexheader&\multicolumn{2}{c|[inner]}{\textsc{Wavelength}}&\multirow{2}{*}{\textsc{Colour}}\\
+\papertableuheaderunit{\si{\nano\meter}}&\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Orange}\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Green}\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Violet}\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Violet}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{The wavelengths and colours of the spectral lines of ``Unknown \#7''.}\vspace{1em}
+
+\paperfig{UnknownNineResult}{\begin{papertable}{|[outer]I|[inner]U|[inner]C|[outer]}
+\paperoline\papertableindexheader&\multicolumn{2}{c|[inner]}{\textsc{Wavelength}}&\multirow{2}{*}{\textsc{Colour}}\\
+\papertableuheaderunit{\si{\nano\meter}}&\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Red}\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Orange}\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Yellow}\\\paperiline
+\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Green}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{The wavelengths and colours of the spectral lines of ``Unknown \#9''.}
 

### 2018-01-15 Atomic Spectra/paper.tex
added residuals plot

--- 2018-01-14 Atomic Spectra/paper.tex
@@
 The $R^2$ value for the fit s 0.999489.
-TODO ADD CHI SQUARED AND RESIDUALS\\
+The reduced $ \chi^2 $ obtained is $ 12.5827907379 $ with residuals visualized below.
+
+\paperfig{Residuals}{\begin{tikzpicture}[scale = 0.95]
+	\begin{axis}
+		[width=\linewidth,
+		tick label style={font=\fontsize{10pt}{1em}},
+		xlabel={\fontsize{10pt}{1em}\selectfont $\lambda$ (\si{\nm}) $\rightarrow$},
+		ylabel={\fontsize{10pt}{1em}\selectfont $ y - y_{fit} \rightarrow$},
+		\paperaxis{Residuals vs. Wavelength}{y}{x}{450}{-0.15}{750}{0.15}{0}{2}]
+		\papergraphoutline{450}{0}{750}{0};
+		\addplot[color = black, only marks, mark = o, mark size = 1.5, error bars/.cd,
+		y dir = both, y explicit, x dir = both, x explicit] 
+		coordinates {
+			(706.5, 0.0836354) (667.8, 0.00358039) (587.6, -0.13242233)
+			(501.6, 0.01987709) (492.2, 0.01029522) (471.3, 0.00550431)
+			(447.1, 0.00952993)
+		};
+	\end{axis}
+\end{tikzpicture}}{WHAT TO ADD HERE?}
 

### 2018-01-15 Atomic Spectra/fitting.py

@@ -38,6 +38,9 @@ print "Reduced chi squared:", chisq / ddof
 
 print "Parameters:", popt
 
+print "Wavelengths: \n", wavelength
+print "Residuals: \n", r
+
 # Generate data for plotting (using fit parameters)
 x_fit = np.linspace(np.amin(wavelength), np.amax(wavelength), 100)
 y_fit = f(x_fit, *popt)

### 2018-01-15 Atomic Spectra/paper.tex
a a a a

@@
 \begin{paperabs}
-TODO Abstract
+In this experiment a spectrometer was used to study the spectra of various lines, determine the Rydberg constant, and identify several unknown substances.
+The Rydberg constant was computed to be $(1.097\pm.003)\x\SI{E7}{\per\meter}$.
+The gases ``Unknown \#7'' and ``Unknown \#9'' were identified to be krypton and neon respectively.
+a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
 \end{paperabs}
@@
 \papersec{Introduction}
+
+a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
 
@@
 The apparatus consisted of a spectrometer, a sodium lamp, a tube of hydrogen
-gas, a tube of helium gas, and two tubes of unknown compounds marked ``Unknown
+gas, a tube of helium gas, and two tubes marked ``Unknown
 \#7'' and ``Unknown \#9''.
 
-The spectrometer was calibrated by aligning the eyepiece with the lines produced
-by the sodium lamp and the Hartmann relation method was used to determine the
+The spectrometer was calibrated by aligning the eyepiece and the crosshairs with the spectal lines of the sodium lamp and the Hartmann relation method was used to find the
 relation between the observed wavelength and the scale reading on the
@@
 
-To determine the relation between the scale reading of the spectrometer and the
-observed wavelength, the Hartmann relation was used.
+To determine the relation between the scale reading and the
+observed wavelength, the Hartmann relation was used.\columnbreak
 
@@
 \papervar{m}{slope of fit}{\meter}
-\papervar{\lambda}{observed wavelength}{\meter}
 \papervar{\lambda_0}{fundamental wavelength of spectrometer}{\meter}
@@
 The uncertainties in the wavelengths for the spectral lines of helium were
-deemed too small to consider.
+too small to consider.
 
@@
 Additionally, the colours of the observed lines and matched wavelengths for the
-spectral lines of helium were recorded.
+spectral lines of helium were recorded.\pagebreak
 
@@
 \end{papertable}\vspace{-1.5em}}
-{The scale readings, matched wavelengths, and colours of the spectral lines of helium.}\vspace{1em}
+{The scale readings, matched wavelengths, and colours of the spectral lines of helium.}
 
@@
 \end{papertable}\vspace{-1.5em}}
-{The scale readings, indices, and colours of the spectral lines of hydrogen.}\vspace{1em}
+{The scale readings, indices, and colours of the spectral lines of hydrogen.}
 
@@
 \end{papertable}\vspace{-1.5em}}
-{The scale readings and colours of the spectral lines of ``Unknown \#7''.}\vspace{1em}
+{The scale readings and colours of the spectral lines of ``Unknown \#7''.}
 
@@
 y-intercept of $(1.83\pm.09)$.
-The $R^2$ value for the fit s 0.999489.
-The reduced $ \chi^2 $ obtained is $ 12.5827907379 $ with residuals visualized below.
-
-\paperfig{Residuals}{\begin{tikzpicture}[scale = 0.95]
-	\begin{axis}
-		[width=\linewidth,
-		tick label style={font=\fontsize{10pt}{1em}},
-		xlabel={\fontsize{10pt}{1em}\selectfont $\lambda$ (\si{\nm}) $\rightarrow$},
-		ylabel={\fontsize{10pt}{1em}\selectfont $ y - y_{fit} \rightarrow$},
-		\paperaxis{Residuals vs. Wavelength}{y}{x}{450}{-0.15}{750}{0.15}{0}{2}]
-		\papergraphoutline{450}{0}{750}{0};
-		\addplot[color = black, only marks, mark = o, mark size = 1.5, error bars/.cd,
-		y dir = both, y explicit, x dir = both, x explicit] 
-		coordinates {
-			(706.5, 0.0836354) (667.8, 0.00358039) (587.6, -0.13242233)
-			(501.6, 0.01987709) (492.2, 0.01029522) (471.3, 0.00550431)
-			(447.1, 0.00952993)
-		};
-	\end{axis}
-\end{tikzpicture}}{WHAT TO ADD HERE?}
+The $R^2$ value for the fit is 0.999489.
+The reduced $ \chi^2 $ obtained is $12.5828$ with residuals visualized below.
 
@@
 \smash{$R^2$} value of 0.999489.
-Error bars were included but were too small to be visible.}
+Error bars were included but were too small to be visible.}\\
+
+\paperfig{Residuals}{\begin{tikzpicture}[scale = 0.95]
+	\begin{axis}
+		[width=\linewidth,
+		tick label style={font=\fontsize{10pt}{1em}},
+		xlabel={\fontsize{10pt}{1em}\selectfont $\lambda$ (\si{\nm}) $\rightarrow$},
+		ylabel={\fontsize{10pt}{1em}\selectfont $ y - y_\text{fit} \rightarrow$},
+		\paperaxis{Residuals vs. Wavelength}{y}{x}{450}{-0.15}{750}{0.15}{0}{2}]
+		\papergraphoutline{450}{-0.15}{749}{0.15};
+		\addplot[color = black, only marks, mark = o, mark size = 1.5, error bars/.cd,
+		y dir = both, y explicit, x dir = both, x explicit] 
+		coordinates {
+			(706.5, 0.0836354) (667.8, 0.00358039) (587.6, -0.13242233)
+			(501.6, 0.01987709) (492.2, 0.01029522) (471.3, 0.00550431)
+			(447.1, 0.00952993)
+		};
+	\end{axis}
+\end{tikzpicture}}{A plot of the residuals for the fitted data points. The reduced $ \chi^2 $ value for the fit is $12.5828$.}
 
@@
 \papertableuheaderunit{\si{\nano\meter}}&\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Orange}\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Green}\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Violet}\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Violet}\\\paperoline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill588~~}}{\parbox{\widthof{TODO}}{~5}}\papertablecval{Orange}\\\paperiline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill557~~}}{\parbox{\widthof{TODO}}{~4}}\papertablecval{Green}\\\paperiline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill451~~}}{\parbox{\widthof{TODO}}{~2}}\papertablecval{Violet}\\\paperiline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill433~~}}{\parbox{\widthof{TODO}}{~2}}\papertablecval{Violet}\\\paperoline
 \end{papertable}\vspace{-1.5em}}
@@
 \papertableuheaderunit{\si{\nano\meter}}&\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Red}\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Orange}\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Yellow}\\\paperiline
-\papertableindex\papertableuval{TODO}{TODO}\papertablecval{Green}\\\paperoline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill704~~}}{\parbox{\widthof{TODO}}{~9}}\papertablecval{Red}\\\paperiline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill607~~}}{\parbox{\widthof{TODO}}{~6}}\papertablecval{Orange}\\\paperiline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill585~~}}{\parbox{\widthof{TODO}}{~5}}\papertablecval{Yellow}\\\paperiline
+\papertableindex\papertableuval{\parbox{\widthof{TODO}}{\hfill541~~}}{\parbox{\widthof{TODO}}{~4}}\papertablecval{Green}\\\paperoline
 \end{papertable}\vspace{-1.5em}}
-{The wavelengths and colours of the spectral lines of ``Unknown \#9''.}
+{The wavelengths and colours of the spectral lines of ``Unknown \#9''.}\\
+
+The colours of Unknowns 7 and 9 were recorded to be a silvery grey and a bright reddish-orange.
+When this information was combined with the wavelengths of the brightest lines of the spectra for
+various gases (Serbanescu), the identities of the gases could be determined.
+The gas in the tube marked ``Unknown \#7'' was krypton and the gas in the tube marked ``Unknown \#9'' was neon.
+
+For the last part of the experiment, the physical significance of $hcR_H$ was examined where $h$ is Planck's constant,
+$c$ is the speed of light, and $R_H$ is the Rydberg constant.
+The values of these constants were taken to be $h=\SI{6.62607004E-34}{\meter\squared\kilo\gram\per\second}$, $c=\SI{299792458}{\meter\per\second}$, and $R_H=\SI{1.09737316E7}{\per\meter}$.
+This resulted in a value of $hcR_H=\SI{2.17987233E-18}{\joule}$.
+Equivalently, this value was found to be equal to \SI{13.605693}{\electronvolt}.
+This is precisely equal to the ionization energy of atomic hydrogen.
+
+This phenomenon was explained as follows.
+Energy obeys a well known relationship with wavelength.
+
+\papereq{Energy}{E=\frac{hc}\lambda}{}
+\begin{paperwhere}
+\papervar{E}{energy}{\joule}
+\papervar{h}{Planck's constant}{\meter\squared\kilo\gram\per\second}
+\papervar{c}{speed of light}{\meter\per\second}
+\end{paperwhere}
+
+To have enough energy to escape an atom, an electron needs to move from an ``infinitely'' excited state to the ground state.
+This was done by setting the value of $n$, the excited state to $\oo$ in the Lyman series.
+
+\papereq{State}{\frac1\lambda=R_H\pars{1-\frac{1}{n^2}}}{Serbanescu}
+
+By setting $n$ to $\oo$ we get that $\lambda$ is the reciprocal of $R_H$, so we get that $hcR_H=E$.
+This means that $hcR_H$ precisely measures the amount of energy needed to move an electron from any excited state to the ground state, which is the ionization energy of hyrdrogen.
 
@@
 
-Conclusion goes here
+The experiment demonstrated successful use of the spectrometer.
+First the spectrometer was calibrated using a sodium lamp and the scale reading function of the observed wavelength was derived from the spectral lines of helium.
+Then the Rydberg constant was derived from spectral lines of hydrogen.
+
+Two unknown gases were identified and the relationship between the Rydberg constant and the ionization energy of atomic hydrogen was established.
+The main source of error in the experiment was the alignment of the crosshairs on the spectral lines and the reading of the vernier scale.
+
+The derived function was found to be $(2.00\pm.02)\x\SI{E-6}{\meter}\frac{1}{\lambda-\lambda_0}+(1.83\pm.09)$.
+The Rydberg constant was found to be $(1.097\pm.003)\x\SI{E7}{\per\meter}$.
+The gases ``Unknown \#7'' and ``Unknown \#9'' were identified as krypton and neon, respectively.
+Lastly, the value of $hcR_H$ was determined to be the ionization energy of atomic hydrogen.
 

### 2018-01-15 Atomic Spectra/paper.tex
Added to introduction, abstract

@@
 \begin{paperabs}
-In this experiment a spectrometer was used to study the spectra of various lines, determine the Rydberg constant, and identify several unknown substances.
-The Rydberg constant was computed to be $(1.097\pm.003)\x\SI{E7}{\per\meter}$.
+In this experiment a spectrometer was used to study the spectra of various gases, determine the Rydberg constant, and identify several unknown substances.
+The spectrometer was calibrated by performing a least-squares data fitting with the Hartmann relation as the model function.
+Upon calibrating the device, further measurements of the emission spectra of hydrogen and two unknown substances could be perfomed.
+The Rydberg constant was computed to be $(1.097\pm.003)\x\SI{E7}{\per\meter}$, with uncertainty arising from the reading of the vernier scale and the alignment of the crosshairs on the emission lines.
 The gases ``Unknown \#7'' and ``Unknown \#9'' were identified to be krypton and neon respectively. 
-a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
+% a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
 \end{paperabs}
@@
 
-a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
+As an excited atom makes a transition to a lower state, a photon of discrete energy equal to the energy difference between the states is released.
+The collection of all possible transitions and corresponding emission lines makes up an atom's \textit{atomic spectrum}.
+
+% a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
 
 The purpose of this experiment was to use a prism spectrometer to identify
-unknown gases based on their atomic spectra.
+unknown gases based on their atomic spectra. %emission spectra. 
 Furthermore, the Rydberg constant ($R_H$) was determined by examining the
@@
 The $R^2$ value for the fit is 0.999489.
-The reduced $ \chi^2 $ obtained is $12.5828$ with residuals visualized below.
+The reduced $ \chi^2 $ obtained is $12.5828$, mostly due to two outliers, with residuals visualized below.
 
@@
 \end{axis}
-\end{tikzpicture}}
+\end{tikzpicture}\vspace{-1em}}
 {The scale readings on the spectrometer plotted against the modified

### 2018-01-15 circuit-elements/paper.tex
added uncertainties for figure 3
finished figure 4

--- 2018-01-14 circuit-elements/paper.tex
@@
 \papertitle{Non-linear Circuit Elements}
-\paperauth{A}{Khesin}{}
-\paperauth{P}{Zavyalova}{}
+\paperauth{A}{Khesin}{1002442029}
+\paperauth{P}{Zavyalova}{1002345036}
 \paperdate{January 17, 2018}
@@
 
-	\paperfig{Hydrogen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}
-			\paperoline\papertableindexheader&\textsc{Scale}&\multirow{2}{*}{\textsc{Colour}}\\
-			\papertablecheaderunit{.02}{\hspace{-0.5ex}}&\\\paperiline
-			\papertableindex\papertablecval{7.26}\papertablecval{Red}\\\paperiline
-			\papertableindex\papertablecval{11.80}\papertablecval{Blue-Green}\\\paperiline
-			\papertableindex\papertablecval{15.15}\papertablecval{Violet}\\\paperiline
-			\papertableindex\papertablecval{17.75}\papertablecval{Violet}\\\paperoline
+	The resistance of the thermistor at various temperatures was obtained and recorded. The uncertainty in resistance is taken to be the last digit increment in the least significant digit displayed.
+
+	\paperfig{Thermistor}{\begin{papertable}{|[outer]I|[inner]C|[inner]U|[outer]}
+			\paperoline\papertableindexheader&\textsc{Temperature}&\multicolumn{2}{c|[outer]}{\textsc{Resistance}}\\
+			\papertablecheadersymbol{T$ $(\pm0.5$ $\si{\kelvin})}\papertableuheadersymbole{R$ $(\si{\kilo\ohm})}\\\paperiline
+			\papertableindex\papertablecval{352.5}\papertableuval{6.68}{.02}\\\paperiline
+			\papertableindex\papertablecval{349.0}\papertableuval{6.93}{.02}\\\paperiline
+			\papertableindex\papertablecval{348.0}\papertableuval{7.54}{.03}\\\paperiline
+			\papertableindex\papertablecval{346.0}\papertableuval{8.01}{.03}\\\paperiline
+			\papertableindex\papertablecval{340.0}\papertableuval{9.95}{.03}\\\paperiline
+			\papertableindex\papertablecval{338.0}\papertableuval{10.33}{.03}\\\paperiline
+			\papertableindex\papertablecval{335.0}\papertableuval{11.76}{.03}\\\paperiline
+			\papertableindex\papertablecval{334.5}\papertableuval{12.36}{.03}\\\paperiline
+			\papertableindex\papertablecval{329.5}\papertableuval{14.45}{.04}\\\paperiline
+			\papertableindex\papertablecval{327.5}\papertableuval{15.33}{.04}\\\paperiline
+			\papertableindex\papertablecval{324.0}\papertableuval{17.23}{.04}\\\paperiline
+			\papertableindex\papertablecval{321.0}\papertableuval{19.51}{.05}\\\paperiline
+			\papertableindex\papertablecval{319.0}\papertableuval{21.7}{.1}\\\paperiline
+			\papertableindex\papertablecval{317.0}\papertableuval{24.3}{.1}\\\paperiline
+			\papertableindex\papertablecval{314.0}\papertableuval{26.1}{.2}\\\paperiline
+			\papertableindex\papertablecval{309.5}\papertableuval{31.4}{.2}\\\paperiline
+			\papertableindex\papertablecval{308.5}\papertableuval{33.7}{.2}\\\paperiline
+			\papertableindex\papertablecval{307.5}\papertableuval{35.5}{.2}\\\paperiline
+			\papertableindex\papertablecval{305.0}\papertableuval{38.0}{.2}\\\paperiline
+			\papertableindex\papertablecval{304.0}\papertableuval{40.3}{.2}\\\paperiline
+			\papertableindex\papertablecval{301.5}\papertableuval{44.3}{.2}\\\paperiline
+			\papertableindex\papertablecval{299.5}\papertableuval{47.7}{.2}\\\paperiline
+			\papertableindex\papertablecval{298.0}\papertableuval{51.6}{.2}\\\paperiline
+			\papertableindex\papertablecval{296.0}\papertableuval{56.3}{.2}\\\paperiline
+			\papertableindex\papertablecval{294.0}\papertableuval{61.3}{.2}\\\paperiline
+			\papertableindex\papertablecval{292.5}\papertableuval{66.9}{.2}\\\paperiline
+			\papertableindex\papertablecval{290.5}\papertableuval{73.8}{.2}\\\paperiline
+			\papertableindex\papertablecval{286.0}\papertableuval{92.9}{.3}\\\paperiline
+			\papertableindex\papertablecval{283.0}\papertableuval{104.7}{.3}\\\paperiline
+			\papertableindex\papertablecval{278.0}\papertableuval{~126.2}{\parbox{\widthof{126.2~}}{.4}}\\\paperoline
 		\end{papertable}\vspace{-1.5em}}
-	{The scale readings and colours of the spectral lines of hydrogen.}\vspace{1em}
+	{Resistance of thermistor at the given temperatures.}\vspace{1em}
+
+	Further, current and potential for a tungsten filament light bulb were measured and recorded. The uncertainty is again taken to be the last digit increment in the least significant digit displayed.
+
+	\paperfig{Light bulb}{\begin{papertable}{|[outer]I|[inner]U|[inner]U|[outer]}
+			\paperoline\papertableindexheader&\multicolumn{2}{c|[inner]}{\textsc{Potential}}&\multicolumn{2}{c|[outer]}{\textsc{Current}}\\
+			\papertableuheadersymbol{V$ $(\si{\volt})}\papertableuheadersymbole{I$ $(\si{\milli\ampere)}}\\\paperiline
+			\papertableindex\papertableuval{0.0222}{.0002}\papertableuval{0.324}{.003}\\\paperiline
+			\papertableindex\papertableuval{0.0776}{.0003}\papertableuval{1.045}{.009}\\\paperiline
+			\papertableindex\papertableuval{0.1122}{.0004}\papertableuval{1.39}{.01}\\\paperiline
+			\papertableindex\papertableuval{0.244}{.002}\papertableuval{2.27}{.03}\\\paperiline
+			\papertableindex\papertableuval{0.472}{.002}\papertableuval{3.40}{.04}\\\paperiline
+			\papertableindex\papertableuval{0.541}{.002}\papertableuval{3.69}{.04}\\\paperiline
+			\papertableindex\papertableuval{0.697}{.003}\papertableuval{4.28}{.04}\\\paperiline
+			\papertableindex\papertableuval{0.871}{.003}\papertableuval{4.89}{.05}\\\paperiline
+			\papertableindex\papertableuval{1.128}{.004}\papertableuval{5.72}{.05}\\\paperiline
+			\papertableindex\papertableuval{1.840}{.006}\papertableuval{7.68}{.07}\\\paperiline
+			\papertableindex\papertableuval{1.940}{.006}\papertableuval{7.93}{.07}\\\paperiline
+			\papertableindex\papertableuval{4.01}{.02}\papertableuval{12.3}{.1}\\\paperiline
+			\papertableindex\papertableuval{6.00}{.03}\papertableuval{15.8}{.1}\\\paperiline
+			\papertableindex\papertableuval{8.01}{.03}\papertableuval{18.8}{.2}\\\paperiline
+			\papertableindex\papertableuval{10.24}{.04}\papertableuval{21.8}{.3}\\\paperiline
+			\papertableindex\papertableuval{12.07}{.04}\papertableuval{24.1}{.3}\\\paperiline
+			\papertableindex\papertableuval{14.27}{.05}\papertableuval{26.6}{.3}\\\paperiline
+			\papertableindex\papertableuval{16.01}{.05}\papertableuval{28.5}{.3}\\\paperiline
+			\papertableindex\papertableuval{17.98}{.05}\papertableuval{30.6}{.3}\\\paperiline
+			\papertableindex\papertableuval{18.45}{.06}\papertableuval{31.1}{.3}\\\paperiline
+			\papertableindex\papertableuval{19.86}{.06}\papertableuval{32.5}{.3}\\\paperiline
+			\papertableindex\papertableuval{21.0}{.2}\papertableuval{33.6}{.4}\\\paperiline
+			\papertableindex\papertableuval{22.1}{.2}\papertableuval{34.6}{.4}\\\paperiline
+			\papertableindex\papertableuval{22.9}{.2}\papertableuval{35.4}{.4}\\\paperiline
+			\papertableindex\papertableuval{24.0}{.2}\papertableuval{36.4}{.4}\\\paperiline
+			\papertableindex\papertableuval{25.1}{.2}\papertableuval{37.3}{.4}\\\paperoline
+			\end{papertable}\vspace{-1.5em}}
+	{Potential and current through the light bulb.}\vspace{1em}
 

### 2018-01-15 circuit-elements/paper.tex
Some changes to introduction

--- 2018-01-15 circuit-elements/paper.tex
@@
 
-	Potential and current are measured using two multimeters, a power supply, a tungsten filament light bulb, and a switch arranged as follows:
+	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as follows:
 

### 2018-01-15 circuit-elements/thermistor.py
Changed .py for fitting

@@ -9,28 +9,34 @@ from scipy.optimize import curve_fit
 
 # ---------- User-Defined Functions ----------
 
-# Fit function for optimizing; 
+# Fit function for optimizing; a = R_0, b = T_0
+# (x, a, b) --> (f_value)
+# (float, float, float) --> (float)
 def f(x, a, b):
 	return a * np.exp(- x / b)
 
 # ---------- Main Code ----------
 
 path_to_file = "/home/polina/Documents/3rd_Year/PHY324/circuit-elements/thermistor.txt"
-temp, resist = np.loadtxt(path_to_file, unpack = True)
-temp = temp + 273.0			# Convert temperature to K
+# Load data
+temp, temp_unc, resist, resist_unc = np.loadtxt(path_to_file, unpack = True)
+# Convert data to Kelvin, kiloohms
+temp = temp + 273.0
+temp_unc = temp_unc + 273.0
+ddof = np.size(temp) - 2	# degrees of freedom for reduced chi squared
+print(ddof)
 
-print(temp)
-print(resist)
-
-# Arrays w/ uncertainties
-temp_unc = np.full(np.size(temp), 0.5)
-resist_unc = np.concatenate((np.full(12, 0.01), np.full(18, 0.1)))
-
-popt, pcov = curve_fit(f, temp, resist)
+popt, pcov = curve_fit(f, temp, resist, sigma = resist_unc, p0 = [1e6, 10])
+print(popt)
+# Find residuals
+r = temp - f(temp, *popt)
+chisq = np.sum((r / resist_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
 
 plt.plot(temp, resist)
+plt.plot(temp, f(temp, *popt))
 plt.grid(True)
-plt.xlabel("Temperature (C)")
-plt.ylabel("Resistance (ohms)")
+plt.xlabel("Temperature (K)")
+plt.ylabel("Resistance (kiloohms)")
 plt.title("Resistance vs. Temperature for a Thermistor")
 plt.show()

### 2018-01-16 circuit-elements/paper.tex
measurements for lenses lab

@@
 
+	Circuit components may be grouped into linear and nonlinear.
+In linear components, such as resistors, capacitors, and some inductors, the signal obeys the principle of superposition; such components process electronic signals without distorting them.
+Nonlinear circuit components do not have a linear relationship between current and potential, and thus may distort electrical signals.
+
 	The purpose of this experiment was to study the relationship between voltage and current for a thermistor and an incandescent lamp.
@@
 
-	The relationship was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown:
+	The relationship was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown below.
+The temperature of the thermistor was decreased by adding cold water to the thermal flask.
 
 	\paperfig{Setup}{\pdf{setup1}}{The experimental setup (thermistor).}
-
-	The temperature of the thermistor was decreased by adding cold water to the thermal flask.
 

### 2018-01-16 circuit-elements/bulb.py

@@ -1,0 +1,64 @@
+#!/usr/bin/python
+# Plots and fits data for a light bulb w/ varying potentials
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Functions ----------
+
+# Fit function for optimizing
+# (x, k, a) --> (f_value)
+# (float, float, float) --> (float)
+def f(x, k, a):
+	return k * x ** a
+
+# ---------- Main Code ----------
+
+path_to_file = "/home/polina/Documents/3rd_Year/PHY324/circuit-elements/bulb.txt"
+# Load data
+V, V_unc, I, I_unc = np.loadtxt(path_to_file, unpack = True)
+# In text file, potential in V, current in mA
+
+# Use this to exclude the first n points (significantly improves reduced chi squared value)
+n = 0
+V = V[n:]
+V_unc = V_unc[n:]
+I = I[n:]
+I_unc = I_unc[n:]
+
+ddof = np.size(V) - 2	# degrees of freedom for reduced chi squared
+print(ddof)
+
+popt, pcov = curve_fit(f, I, V, sigma = V_unc, p0 = [1, 1])
+print(popt)
+print "k:", popt[0], "+-", np.sqrt(pcov[0, 0])
+print "a:", popt[1], "+-", np.sqrt(pcov[1, 1])
+# Find residuals
+r = V - f(I, *popt)
+chisq = np.sum((r / V_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+
+fig1 = plt.figure(1)
+# Plot data + model
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+plt.scatter(I, V, label = "Data")
+plt.errorbar(I, V, xerr = I_unc, yerr = V_unc, linestyle = "None")
+plt.plot(I, f(I, *popt), label = "Model")
+plt.title("Potential vs. Current of a Light Bulb")
+plt.legend()
+plt.ylabel("Potential (V)")
+# frame1.set_xticklabels([])
+plt.grid(True)
+# Residual plot
+frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
+plt.scatter(V, r)
+plt.grid(True)
+plt.xlabel("Current (mA)")
+plt.ylabel("Residuals")
+# plt.ylim([-2, 9])
+plt.savefig("Bulb.pdf")
+plt.show()
+plt.close()

### 2018-01-16 circuit-elements/thermistor.py

@@ -21,22 +21,46 @@ path_to_file = "/home/polina/Documents/3rd_Year/PHY324/circuit-elements/thermist
 # Load data
 temp, temp_unc, resist, resist_unc = np.loadtxt(path_to_file, unpack = True)
 # Convert data to Kelvin, kiloohms
-temp = temp + 273.0
-temp_unc = temp_unc + 273.0
+temp = temp + 273.15
+temp_unc = temp_unc
+
+# Use this to exclude the first n points (significantly improves reduced chi squared value)
+n = 0
+temp = temp[n:]
+temp_unc = temp_unc[n:]
+resist = resist[n:]
+resist_unc = resist_unc[n:]
+
 ddof = np.size(temp) - 2	# degrees of freedom for reduced chi squared
 print(ddof)
 
 popt, pcov = curve_fit(f, temp, resist, sigma = resist_unc, p0 = [1e6, 10])
 print(popt)
+print "R_0:", popt[0], "+-", np.sqrt(pcov[0, 0])
+print "T_0:", popt[1], "+-", np.sqrt(pcov[1, 1])
 # Find residuals
-r = temp - f(temp, *popt)
+r = resist - f(temp, *popt)
 chisq = np.sum((r / resist_unc) ** 2)
 print "Reduced chi squared:", chisq / ddof
 
-plt.plot(temp, resist)
-plt.plot(temp, f(temp, *popt))
+fig1 = plt.figure(1)
+# Plot data + model
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+plt.scatter(temp, resist, label = "Data")
+plt.errorbar(temp, resist, xerr = temp_unc, yerr = resist_unc, linestyle = "None")
+plt.plot(temp, f(temp, *popt), label = "Model")
+plt.title("Resistance vs. Temperature of a Thermistor")
+plt.legend()
+plt.ylabel("Resistance (kiloohms)")
+# frame1.set_xticklabels([])
+plt.grid(True)
+# Residual plot
+frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
+plt.scatter(temp, r)
 plt.grid(True)
 plt.xlabel("Temperature (K)")
-plt.ylabel("Resistance (kiloohms)")
-plt.title("Resistance vs. Temperature for a Thermistor")
+plt.ylabel("Residuals")
+plt.ylim([-2, 9])
+plt.savefig("Thermistor.pdf")
 plt.show()
+plt.close()

### 2018-01-16 circuit-elements/paper.tex
Started analysis

--- 2018-01-15 circuit-elements/paper.tex
@@
 
+	Circuit components may be classified based on how they process signals as either linear or nonlinear.
+In linear components, such as resistors, capacitors, and some inductors, the signal obeys the principle of superposition; such components process electrical signals without distorting them.
+Nonlinear circuit elements do not have a linear relationship between current and potential, and thus may distort electrical signals.
+
 	The purpose of this experiment was to study the relationship between voltage and current for a thermistor and an incandescent lamp.
@@
 
-	The relationship was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown:
+	As evident from the above expression, the thermistor's resistance decreases with increasing temperature.
+This is unlike the resistance of metals (such as the filament of an incandescent light bulb examined further in the experiment), which exhibit the opposite relationship.
+
+	The relation in (1) was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown below.
+The temperature of the thermistor was decreased by adding cold water to the thermal flask and stirring to ensure uniform temperature in the flask.
 
@@
 
-	The temperature of the thermistor was decreased by adding cold water to the thermal flask.
-
-	The tungsten filament in a light bulb follows Ohm's law,
-
-	\papereq{Ohm}{ R = \frac{V}{I} }{Serbanescu}
-	\begin{paperwhere}
-		\papervar{R}{resistance}{\ohm}
-		\papervar{V}{potential}{\volt}
-		\papervar{I}{current}{\ampere}
-	\end{paperwhere}
-
-	However, as the temperature increases, the resistance of the metal increases and above a certain temperature becomes proportional to the absolute temperature.
+	In general, the tungsten filament in an incandescent light bulb obeys Ohm's law.
+As the temperature increases, however, the resistance of the metal increases and above a certain temperature becomes proportional to the absolute temperature.
 The actual relationship between \( V \) and \( I \) is investigated in this experiment by fitting obtained measurements of current and potential to
@@
 
-	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as follows:
+	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as follows.
 
@@
 
-	The resistance of the thermistor at various temperatures was obtained and recorded. The uncertainty in resistance is taken to be the last digit increment in the least significant digit displayed.
+	The resistance of the thermistor at various temperatures was measured and recorded.
+The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1) $ for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
+The uncertainty in temperature measurements was taken to be $ \pm 0.5 \si{\kelvin} $.
 
@@
 		\end{papertable}\vspace{-1.5em}}
-	{Resistance of thermistor at the given temperatures.}\vspace{1em}
+	{Resistance of thermistor at the given temperatures. As expected, resistance decreased with increasing temperature.}\vspace{1em}
 
-	Further, current and potential for a tungsten filament light bulb were measured and recorded. The uncertainty is again taken to be the last digit increment in the least significant digit displayed.
+	Further, current and potential for a tungsten filament light bulb were measured and recorded.
+As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1) \); current measurements carried an uncertainty of \( \pm (1\% + 3) \).
 
@@
 			\end{papertable}\vspace{-1.5em}}
-	{Potential and current through the light bulb.}\vspace{1em}
+	{Potential and current through the incandescent bulb. Evidently, increased current through the filament led to an increase in potential.} \vspace{1em}
 
@@
 
-	Analysis
+	Using the expression in (1) as the model function, the relationship between the temperature and resistance of a thermistor was calculated.
+Least squares fitting of all data points yielded \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \) as the fit parameters, with a reduced \( \chi ^ 2 \) value of \( 252.1710 \).
+The data, model, and residuals for this fit are shown below.
+
+	\paperfig{Data}{\pdf{Thermistor}}{Resistance of the thermistor plotted against the temperature in the thermal flask, with least squares fit included in blue.
+Error bars on both temperature and resistance were too small to be visible.
+The plot of residuals indicated that the model is a better fit for greater temperatures.} \vspace{1em}
+
+	A visualization of residuals clearly indicated that the data can be better modelled for greater temperatures.
+Indeed, least squares fitting performed without the data points corresponding to three lowest temperatures yielded a reduced \( \chi ^ 2 \) value of \( 181.5543 \).
+Removing the six lower-temperature points led to a model with reduced \( \chi ^ 2 \) value of \( 130.1026 \).
+
+	Further, a least squares fitting was performed on the data obtained for the incandescent light bulb, with the expression in (2) used as a model function.
+The formula was found to hold; the resulting parameters were \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = 1.63 \pm 0.01 \).
+The value of reduced \( \chi ^ 2 \) obtained was \( 176.8952 \).
+The data, model, and residuals for this fit are shown below.
+
+	\paperfig{Data}{\pdf{Bulb}}{Potential of the incandescent light bulb plotted against the current.
+Least squares fit was indicated in blue; residuals visualized below.
+Error bars on the data points were too small to be visible.} \vspace{1em}
 

### 2018-01-16 circuit-elements/bulb.py

@@ -44,21 +44,25 @@ print "Reduced chi squared:", chisq / ddof
 fig1 = plt.figure(1)
 # Plot data + model
 frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
-plt.scatter(I, V, label = "Data")
-plt.errorbar(I, V, xerr = I_unc, yerr = V_unc, linestyle = "None")
+plt.scatter(I, V, label = "Data", s = 10, color = "black")
+plt.errorbar(I, V, xerr = I_unc, yerr = V_unc, linestyle = "None", color = "black")
 plt.plot(I, f(I, *popt), label = "Model")
 plt.title("Potential vs. Current of a Light Bulb")
 plt.legend()
 plt.ylabel("Potential (V)")
+plt.xlim([-5, 45])
+plt.ylim([-4, 29])
+frame1.set_xticklabels([])
 # frame1.set_xticklabels([])
 plt.grid(True)
 # Residual plot
 frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
-plt.scatter(V, r)
+plt.scatter(I, r, s = 10, color = "black")
 plt.grid(True)
 plt.xlabel("Current (mA)")
 plt.ylabel("Residuals")
-# plt.ylim([-2, 9])
+plt.xlim([-5, 45])
+plt.ylim([-0.75, 0.75])
 plt.savefig("Bulb.pdf")
 plt.show()
 plt.close()

### 2018-01-16 circuit-elements/thermistor.py

@@ -24,12 +24,12 @@ temp, temp_unc, resist, resist_unc = np.loadtxt(path_to_file, unpack = True)
 temp = temp + 273.15
 temp_unc = temp_unc
 
-# Use this to exclude the first n points (significantly improves reduced chi squared value)
+# Use this to exclude the last n points (significantly improves reduced chi squared value)
 n = 0
-temp = temp[n:]
-temp_unc = temp_unc[n:]
-resist = resist[n:]
-resist_unc = resist_unc[n:]
+temp = temp[:np.size(temp) - n]
+temp_unc = temp_unc[:np.size(temp_unc) - n]
+resist = resist[:np.size(resist) - n]
+resist_unc = resist_unc[:np.size(resist_unc) - n]
 
 ddof = np.size(temp) - 2	# degrees of freedom for reduced chi squared
 print(ddof)
@@ -46,21 +46,24 @@ print "Reduced chi squared:", chisq / ddof
 fig1 = plt.figure(1)
 # Plot data + model
 frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
-plt.scatter(temp, resist, label = "Data")
-plt.errorbar(temp, resist, xerr = temp_unc, yerr = resist_unc, linestyle = "None")
+plt.scatter(temp, resist, label = "Data", s = 10, color = "black")
+plt.errorbar(temp, resist, xerr = temp_unc, yerr = resist_unc, linestyle = "None", color = "black")
 plt.plot(temp, f(temp, *popt), label = "Model")
 plt.title("Resistance vs. Temperature of a Thermistor")
 plt.legend()
 plt.ylabel("Resistance (kiloohms)")
-# frame1.set_xticklabels([])
+plt.xlim([270, 360])
+# frame1.axes().get_xaxis().set_visible(False)
+frame1.set_xticklabels([])
 plt.grid(True)
 # Residual plot
 frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
-plt.scatter(temp, r)
+plt.scatter(temp, r, s = 10, color = "black")
 plt.grid(True)
 plt.xlabel("Temperature (K)")
 plt.ylabel("Residuals")
-plt.ylim([-2, 9])
+plt.xlim([270, 360])
+plt.ylim([-3, 9])
 plt.savefig("Thermistor.pdf")
 plt.show()
 plt.close()

### 2018-01-16 circuit-elements/paper.tex
analysis w/o 1st question

@@
 
-	Abstract goes here
+	a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
 
@@
 
-	\papereq{Thermistor}{R = R_0e^{ -\frac{T}{T_0} }}{Serbanescu}
+	\papereq{thermistor_model}{R = R_0e^{ -\frac{T}{T_0} }}{Serbanescu}
 	\begin{paperwhere}
@@
 
-	\paperfig{Setup}{\pdf{setup1}}{The experimental setup (thermistor).}
+	\paperfig{setup1}{\pdf{setup1}}{The experimental setup used to measure resistance of a thermistor at varying temperatures.}
 
@@
 	\papereq{bulb-model}{ V = k I^a }{Serbanescu}
-	\begin{paperwhere}
+	\begin{paperwhere}experimental
 		\papervar{V}{potential}{\volt}
@@
 
-	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as follows.
+	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as follows:
 
-	\paperfig{Setup}{\pdf{setup2}}{The experimental setup (light bulb).}
+	\paperfig{setup2}{\pdf{setup2}}{The experimental setup (light bulb).}
+
+	The current-potential data obtained for an incandescent light bulb was further used to determine the value of \( n \) in the Stefan-Boltzmann law,
+
+	\papereq{bulb-model}{ \kappa = \epsilon \sigma T^n }{Serbanescu}
+	\begin{paperwhere}
+		\papervar{\kappa}{power per unit area}{\watt\per\meter\squared}
+		\papervar{\epsilon}{emissivity of radiating body}{}
+		\papervar{\sigma}{Stefan-Boltzmann constant}{\watt\per\meter\squared\per\kelvin\tothe{4}}
+		\papervar{T}{absolute temperature}{K}
+		\papervar{n}{universal constant}{}
+	\end{paperwhere}
+
+	To obtain the value of \( n \), \( \kappa \) and \( T \) were expressed in terms of \( I \) and \( V \) and further in terms of \( I \) (and constants) only with the help of the expression in (2).
+In particular, it was found that
+
+	\papereq{kappa}{ \kappa = \frac{VI}{A} = \frac{k}{A} I^{(a+1)} }{}
+	\begin{paperwhere}
+		\papervar{A}{surface area of filament}{\si{\meter\squared}}
+	\end{paperwhere}
+
+	Further, using  \( R = k'T \), (with \( k' \) being a constant of proportionality) it was shown that
+
+	\papereq{temperature}{ T = \frac{1}{k'} \frac{V}{I} =  \frac{k}{k'} I^{(a-1)}}{}
+
+	Finally, combining the above expressions and setting constants to be equal, the following relationship for \( n \) in terms of \( a \) was obtained.
+
+	\papereq{temperature}{ n = \frac{a+1}{a-1} }{}
 
@@
 The uncertainty in temperature measurements was taken to be $ \pm 0.5 \si{\kelvin} $.
+\vspace{1em}
 
-	\paperfig{Thermistor}{\begin{papertable}{|[outer]I|[inner]C|[inner]U|[outer]}
+	\paperfig{thermistor}{\begin{papertable}{|[outer]I|[inner]C|[inner]U|[outer]}
 			\paperoline\papertableindexheader&\textsc{Temperature}&\multicolumn{2}{c|[outer]}{\textsc{Resistance}}\\
@@
 As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1) \); current measurements carried an uncertainty of \( \pm (1\% + 3) \).
+\vspace{1em}
 
-	\paperfig{Light bulb}{\begin{papertable}{|[outer]I|[inner]U|[inner]U|[outer]}
+	\paperfig{light-bulb}{\begin{papertable}{|[outer]I|[inner]U|[inner]U|[outer]}
 			\paperoline\papertableindexheader&\multicolumn{2}{c|[inner]}{\textsc{Potential}}&\multicolumn{2}{c|[outer]}{\textsc{Current}}\\
@@
 
-	\paperfig{Data}{\pdf{Thermistor}}{Resistance of the thermistor plotted against the temperature in the thermal flask, with least squares fit included in blue.
+	\paperfig{thermistor-plot}{\pdf{Thermistor}}{Resistance of the thermistor plotted against the temperature in the thermal flask, with least squares fit included in blue.
 Error bars on both temperature and resistance were too small to be visible.
@@
 Indeed, least squares fitting performed without the data points corresponding to three lowest temperatures yielded a reduced \( \chi ^ 2 \) value of \( 181.5543 \).
-Removing the six lower-temperature points led to a model with reduced \( \chi ^ 2 \) value of \( 130.1026 \).
+% Removing the six lower-temperature points led to a model with reduced \( \chi ^ 2 \) value of \( 130.1026 \).
 
@@
 
-	\paperfig{Data}{\pdf{Bulb}}{Potential of the incandescent light bulb plotted against the current.
-Least squares fit was indicated in blue; residuals visualized below.
+	\paperfig{bulb-plot}{\pdf{Bulb}}{Potential of the incandescent light bulb plotted against the current.
+Least squares fit was indicated in blue; residuals visualized at the bottom.
 Error bars on the data points were too small to be visible.} \vspace{1em}
+
+	Upon obtaining the value of \( a \), the universal constant \( n \) in Stefan-Boltzmmann law could be approximated.
+Plugging \( a = 1.63 \pm 0.01 \) into (6) yielded \( 4.17 \pm 0.05 \), which was close the actual value of \( n = 4\).
+Another constant appearing in Stefan-Boltzmann law, \( \epsilon \) (emissivity of the radiating body could be determined), differs depending on the material.
+\( \epsilon = 1 \) corresponds to a body that is a perfect absorber and emitter of radiant energy (i.e., a \textit{black body}); \( \epsilon = 0 \) corresponds to a perfect reflector of radiant energy.
 

### 2018-01-17 circuit-elements/paper.tex
abstract + 1st question left

@@
 	The resistance of the thermistor at various temperatures was measured and recorded.
-The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1) $ for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
+The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1 $ LSG) for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
 The uncertainty in temperature measurements was taken to be $ \pm 0.5 \si{\kelvin} $.
@@
 		\end{papertable}\vspace{-1.5em}}
-	{Resistance of thermistor at the given temperatures. As expected, resistance decreased with increasing temperature.}\vspace{1em}
+	{Resistance of thermistor at the given temperatures. All uncertainties were propagated using the method of quadratures.}\vspace{1em}
 
 	Further, current and potential for a tungsten filament light bulb were measured and recorded.
-As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1) \); current measurements carried an uncertainty of \( \pm (1\% + 3) \).
+As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1 \) of last displayed significant digit); current measurements carried an uncertainty of \( \pm (1\% + 3 \) of last displayed significant digit).
 \vspace{1em}
@@
 			\end{papertable}\vspace{-1.5em}}
-	{Potential and current through the incandescent bulb. Evidently, increased current through the filament led to an increase in potential.} \vspace{1em}
+	{Potential and current through the incandescent bulb. All uncertainties were propagated using the method of quadratures.} \vspace{1em}
 
@@
 
-	\paperfig{thermistor-plot}{\pdf{Thermistor}}{Resistance of the thermistor plotted against the temperature in the thermal flask, with least squares fit included in blue.
-Error bars on both temperature and resistance were too small to be visible.
-The plot of residuals indicated that the model is a better fit for greater temperatures.} \vspace{1em}
+	\paperfig{thermistor-plot}{\pdf{Thermistor}}{Resistance and residuals plotted against the temperature in the thermal flask, with least squares fit included in blue.
+Error bars on both temperature and resistance were too small to be visible.} \vspace{1em}
 
@@
 Indeed, least squares fitting performed without the data points corresponding to three lowest temperatures yielded a reduced \( \chi ^ 2 \) value of \( 181.5543 \).
+Removing more lower-temperature data points further improved reduced \( \chi ^ 2 \).
 % Removing the six lower-temperature points led to a model with reduced \( \chi ^ 2 \) value of \( 130.1026 \).
@@
 
+	As evidenced above, thermistors and metal resistors have different variations of resistance with temperatures.
+For metal resistors, resistance increasing with temperature is intuitively explained TODO!
+
 	Upon obtaining the value of \( a \), the universal constant \( n \) in Stefan-Boltzmmann law could be approximated.
-Plugging \( a = 1.63 \pm 0.01 \) into (6) yielded \( 4.17 \pm 0.05 \), which was close the actual value of \( n = 4\).
-Another constant appearing in Stefan-Boltzmann law, \( \epsilon \) (emissivity of the radiating body could be determined), differs depending on the material.
+Plugging \( a = 1.63 \pm 0.01 \) into (6) yielded \( 4.17 \pm 0.05 \) (uncertainty propagated using the method  of quadratures), which was close the actual value of \( n = 4\).
+Another constant appearing in Stefan-Boltzmann law, \( \epsilon \) (emissivity of the radiating body), differs depending on the material.
 \( \epsilon = 1 \) corresponds to a body that is a perfect absorber and emitter of radiant energy (i.e., a \textit{black body}); \( \epsilon = 0 \) corresponds to a perfect reflector of radiant energy.
@@
 
-	Conclusion
+		This experiment has investigated two nonlinear circuit elements, a thermistor and an incandescent tungsten filament light bulb.
+Resistance of the thermistor was found to be a function of the temperature, satisfying the exponential relation in (1) with \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \).
+For the light bulb, the relationship between potential and current was shown to follow a power law introduced in (2), with \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = 1.63 \pm 0.01 \).
+The most significant sources of error arose from potential uneven temperature of water in the thermal flask with the thermistor and inconsistencies in current and potential readings of the multimeter when switching the range of input signal.
+
+		The above value of \( a \) was further used to approximate the power \( n \) of \( T \) in Stefan-Boltzmann law; \( n \) was found to be \( 4.17 \pm 0.05 \), reasonably close to the actual value of \( n = 4 \).
 
@@
 
-	Sources
+	\papersource{Serbanescu, R., Non-linear Circuit Elements, 2015}
 

### 2018-01-17 circuit-elements/paper.tex
Added abstract

@@
 
-	a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
+	% a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
+
+	The relationships between current, potential, resistance, and temperature is of particular interest in nonlinear circuit components as they do not follow the principle of superposition when processing and amplifying signals.
+In this lab, these physical quantities were investigated for a thermistor and an incandescent light bulb.
+For the thermistor, the resistance was found to decrease exponentially as temperature increased.
+The relationship between potential and current of the light bulb was determined to obey a power law.
+Further, the power of temperature in Stefan-Boltzmann law was approximated to be \( 4.17 \pm 0.05 \).
 

### 2018-01-17 circuit-elements/paper.tex
Plots+abstract left

@@
 
-	The relationships between current, potential, resistance, and temperature is of particular interest in nonlinear circuit components as they do not follow the principle of superposition when processing and amplifying signals.
-In this lab, these physical quantities were investigated for a thermistor and an incandescent light bulb.
+	The relationships between current, potential, resistance, and temperature are of particular interest in nonlinear circuit components as they do not follow the principle of superposition when processing and amplifying signals.
+In this experiment, these physical quantities were investigated for a thermistor and an incandescent light bulb.
 For the thermistor, the resistance was found to decrease exponentially as temperature increased.
@@
 
-	\papereq{thermistor_model}{R = R_0e^{ -\frac{T}{T_0} }}{Serbanescu}
+	\papereq{thermistor_model}{R = R_0e^{ -\frac{T}{T_0} } .}{Serbanescu}
 	\begin{paperwhere}
@@
 		\papervar{T_0}{constant of device}{\kelvin}
-		\papervar{R_0}{constant of device}{\ohm}
+		\papervar{R_0}{maximum resistance (device specific)}{\ohm}
 	\end{paperwhere}
@@
 The temperature of the thermistor was decreased by adding cold water to the thermal flask and stirring to ensure uniform temperature in the flask.
+\vspace{-0.8em}
 
-	\paperfig{setup1}{\pdf{setup1}}{The experimental setup used to measure resistance of a thermistor at varying temperatures.}
+	\paperfig{setup1}{\pdf{setup1} \vspace{-2.5em} }{The experimental setup used to measure resistance of a thermistor at varying temperatures. \vspace{0.5em}}
 
@@
 
-	\papereq{bulb-model}{ V = k I^a }{Serbanescu}
-	\begin{paperwhere}experimental
+	\papereq{bulb-model}{ V = k I^a .}{Serbanescu}
+	\begin{paperwhere}
 		\papervar{V}{potential}{\volt}
 		\papervar{I}{current}{\ampere}
-		\papervar{k}{constant}{}
-		\papervar{a}{costant}{}
+		\papervar{k}{proportionality constant}{}
+		\papervar{a}{exponential relational constant}{}
 	\end{paperwhere}
 
-	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as follows:
+	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as shown.
 
-	\paperfig{setup2}{\pdf{setup2}}{The experimental setup (light bulb).}
+	\paperfig{setup2}{\pdf{setup2} \vspace{-2.5em}}{Experimental setup used to obtain potential and current data for the light bulb. \vspace{0.5em}}
 
@@
 
-	\papereq{bulb-model}{ \kappa = \epsilon \sigma T^n }{Serbanescu}
+	\papereq{bulb-model}{ \kappa = \epsilon \sigma T^n. }{Serbanescu}
 	\begin{paperwhere}
@@
 		\papervar{T}{absolute temperature}{K}
-		\papervar{n}{universal constant}{}
+		\papervar{n}{exponential relational constant}{}
 	\end{paperwhere}
 
-	To obtain the value of \( n \), \( \kappa \) and \( T \) were expressed in terms of \( I \) and \( V \) and further in terms of \( I \) (and constants) only with the help of the expression in (2).
-In particular, it was found that
+	Further, the value of \( n \) was obtained.
+Using the expression in (3) and assuming thermal equilibrium, \( \kappa \) and \( T \) were expressed in terms of \( I \) and \( V \).
+Additionally, by expressing \( V \) in terms of \( I \) as shown in (2), \( \kappa \) was written in terms of \( I \) and constants only.
 
-	\papereq{kappa}{ \kappa = \frac{VI}{A} = \frac{k}{A} I^{(a+1)} }{}
+	\papereq{kappa}{ \kappa = \frac{VI}{A} = \frac{k}{A} I^{(a+1)}. }{}
 	\begin{paperwhere}
@@
 
-	\papereq{temperature}{ T = \frac{1}{k'} \frac{V}{I} =  \frac{k}{k'} I^{(a-1)}}{}
+	\papereq{temperature}{ T = \frac{1}{k'} \frac{V}{I} =  \frac{k}{k'} I^{(a-1)}.}{}
 
@@
 	The resistance of the thermistor at various temperatures was measured and recorded.
-The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1 $ LSG) for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
-The uncertainty in temperature measurements was taken to be $ \pm 0.5 \si{\kelvin} $.
-\vspace{1em}
+The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1 $ LSD) for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
+The reading error of the thermometer was taken to be $ \pm 0.5 \si{\kelvin} $.
+\vspace{0.5em}
 
@@
 		\end{papertable}\vspace{-1.5em}}
-	{Resistance of thermistor at the given temperatures. All uncertainties were propagated using the method of quadratures.}\vspace{1em}
+	{Resistance of thermistor at the given temperatures. }\vspace{0.5em}
 
 	Further, current and potential for a tungsten filament light bulb were measured and recorded.
-As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1 \) of last displayed significant digit); current measurements carried an uncertainty of \( \pm (1\% + 3 \) of last displayed significant digit).
-\vspace{1em}
+As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1 \) LSD); current measurements carried an uncertainty of \( \pm (1\% + 3 \) LSD).
+\vspace{0.5em}
 
@@
 			\end{papertable}\vspace{-1.5em}}
-	{Potential and current through the incandescent bulb. All uncertainties were propagated using the method of quadratures.} \vspace{1em}
+	{Potential and current through the incandescent bulb.} %  \vspace{1em}
 
@@
 
-	Using the expression in (1) as the model function, the relationship between the temperature and resistance of a thermistor was calculated.
+	Upon propagating uncertainties in the obtained data using the method of quadratures, the relationship between the temperature and resistance of a thermistor was calculated using the expression in (1) as the model function.
 Least squares fitting of all data points yielded \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \) as the fit parameters, with a reduced \( \chi ^ 2 \) value of \( 252.1710 \).
@@
 	Further, a least squares fitting was performed on the data obtained for the incandescent light bulb, with the expression in (2) used as a model function.
-The formula was found to hold; the resulting parameters were \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = 1.63 \pm 0.01 \).
+The formula was found to hold; the resulting parameters were \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = (1.63 \pm 0.01) \).
 The value of reduced \( \chi ^ 2 \) obtained was \( 176.8952 \).
@@
 	As evidenced above, thermistors and metal resistors have different variations of resistance with temperatures.
-For metal resistors, resistance increasing with temperature is intuitively explained TODO!
+For metal resistors, resistance increasing with temperature is intuitively explained by considering increasing vibrations of electrons in the metal.
+At higher temperatures, electrons will interfere more with free currents and thus the resistance will increase.
+Thermistors, on the other hand, are semiconductors.
+Increasing the temperature increases the number of available electrons, the conductivity increases, and thus the resistance decreases.
 
 	Upon obtaining the value of \( a \), the universal constant \( n \) in Stefan-Boltzmmann law could be approximated.
-Plugging \( a = 1.63 \pm 0.01 \) into (6) yielded \( 4.17 \pm 0.05 \) (uncertainty propagated using the method  of quadratures), which was close the actual value of \( n = 4\).
+Plugging \( a = (1.63 \pm 0.01) \) into (6) yielded \( 4.17 \pm 0.05 \) (uncertainty propagated using the method  of quadratures), which was close the actual value of \( n = 4\).
 Another constant appearing in Stefan-Boltzmann law, \( \epsilon \) (emissivity of the radiating body), differs depending on the material.

### 2018-01-17 circuit-elements/paper.tex
Fixed based on comments

@@
 \begin{document}
-\papertitle{Non-linear Circuit Elements}
+\papertitle{Nonlinear Circuit Elements}
 \paperauth{A}{Khesin}{1002442029}
@@
 
-	The relationships between current, potential, resistance, and temperature are of particular interest in nonlinear circuit components as they do not follow the principle of superposition when processing and amplifying signals.
+	The relationships between current, potential, resistance, and temperature are of particular interest in nonlinear circuit components.
 In this experiment, these physical quantities were investigated for a thermistor and an incandescent light bulb.
-For the thermistor, the resistance was found to decrease exponentially as temperature increased.
-The relationship between potential and current of the light bulb was determined to obey a power law.
-Further, the power of temperature in Stefan-Boltzmann law was approximated to be \( 4.17 \pm 0.05 \).
+For the thermistor, resistance was found to decrease exponentially as temperature increased, following the relation \( R = \pars{1.0 \pm 0.1} \times 10^{13}e^{-T/\pars{24.7 \pm 0.3}} \).
+The relationship between potential and current of the light bulb was determined to obey a power law, \( V = \pars{0.067 \pm 0.002} I^{\pars{1.63 \pm 0.01}} \).
+Further, the exponential relational constant in Stefan-Boltzmann law was approximated to be \( 4.17 \pm 0.05 \).
 
@@
 	As evident from the above expression, the thermistor's resistance decreases with increasing temperature.
-This is unlike the resistance of metals (such as the filament of an incandescent light bulb examined further in the experiment), which exhibit the opposite relationship.
+This is unlike resistance of metals (such as the filament of a light bulb examined further in the experiment), which exhibit the opposite relationship.
 
 	The relation in (1) was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown below.
-The temperature of the thermistor was decreased by adding cold water to the thermal flask and stirring to ensure uniform temperature in the flask.
+Temperature of the thermistor was decreased by adding cold water to the thermal flask and stirring to ensure uniform temperature in the flask.
 \vspace{-0.8em}
@@
 
-	Further, using  \( R = k'T \), (with \( k' \) being a constant of proportionality) it was shown that
+	By using the fact that resistance of a pure metal is directly proportional to its temperature (\( R = k'T \), with \( k' \) being a constant of proportionality) it was shown that
 
@@
 
-	Finally, combining the above expressions and setting constants to be equal, the following relationship for \( n \) in terms of \( a \) was obtained.
+	Finally, combining the above expressions and setting constants to be equal, the following relationship for \( n \) in terms of \( a \) was obtained. \vspace{-0.5em}
 
@@
 
-	The resistance of the thermistor at various temperatures was measured and recorded.
+	The resistance of the thermistor at various temperatures was measured.
 The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1 $ LSD) for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
@@
 		\end{papertable}\vspace{-1.5em}}
-	{Resistance of thermistor at the given temperatures. }\vspace{0.5em}
+	{Thermistor's resistance at given temperatures. }\vspace{0.5em}
 
@@
 			\end{papertable}\vspace{-1.5em}}
-	{Potential and current through the incandescent bulb.} %  \vspace{1em}
+	{Potential and current through the light bulb.}
 
@@
 
-	\paperfig{thermistor-plot}{\pdf{Thermistor}}{Resistance and residuals plotted against the temperature in the thermal flask, with least squares fit included in blue.
-Error bars on both temperature and resistance were too small to be visible.} \vspace{1em}
+	\paperfig{thermistor-plot}{\pdf{Thermistor}}{Resistance and residuals plotted against the temperature in the thermal flask.
+The curve has the function \( (1.0 \pm 0.1) \times 10^{13}e^\frac{T}{\pars{24.7 \pm 0.3}} \) and an \( R^2 \) value of 0.992783.
+Error bars on both temperature and resistance were included but were too small to be visible.} \vspace{1em}
 
@@
 
-	\paperfig{bulb-plot}{\pdf{Bulb}}{Potential of the incandescent light bulb plotted against the current.
-Least squares fit was indicated in blue; residuals visualized at the bottom.
-Error bars on the data points were too small to be visible.} \vspace{1em}
+	\paperfig{bulb-plot}{\pdf{Bulb}}{Potential and residuals plotted against current through the incandescent bulb.
+The curve has the function \( \pars{0.067 \pm 0.002} I^{\pars{1.63 \pm 0.01}} \) with an \( R^2 \) value of \( 0.999532 \).
+Error bars on the data points were included but were too small to be visible.} \vspace{1em}
 
@@
 Another constant appearing in Stefan-Boltzmann law, \( \epsilon \) (emissivity of the radiating body), differs depending on the material.
-\( \epsilon = 1 \) corresponds to a body that is a perfect absorber and emitter of radiant energy (i.e., a \textit{black body}); \( \epsilon = 0 \) corresponds to a perfect reflector of radiant energy.
+\( \epsilon = 1 \) corresponds to a body that is a perfect absorber and emitter of radiant energy (i.e., a black body); \( \epsilon = 0 \) corresponds to a perfect reflector of radiant energy.
 
@@
 Resistance of the thermistor was found to be a function of the temperature, satisfying the exponential relation in (1) with \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \).
-For the light bulb, the relationship between potential and current was shown to follow a power law introduced in (2), with \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = 1.63 \pm 0.01 \).
+For the light bulb, the relationship between potential and current was shown to follow a power law introduced in (2), with \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = \pars{1.63 \pm 0.01} \).
 The most significant sources of error arose from potential uneven temperature of water in the thermal flask with the thermistor and inconsistencies in current and potential readings of the multimeter when switching the range of input signal.

### 2018-01-17 circuit-elements/bulb.py

@@ -17,6 +17,8 @@ def f(x, k, a):
 
 # ---------- Main Code ----------
 
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
 path_to_file = "/home/polina/Documents/3rd_Year/PHY324/circuit-elements/bulb.txt"
 # Load data
 V, V_unc, I, I_unc = np.loadtxt(path_to_file, unpack = True)
@@ -32,6 +34,7 @@ I_unc = I_unc[n:]
 ddof = np.size(V) - 2	# degrees of freedom for reduced chi squared
 print(ddof)
 
+# Fit data to model function
 popt, pcov = curve_fit(f, I, V, sigma = V_unc, p0 = [1, 1])
 print(popt)
 print "k:", popt[0], "+-", np.sqrt(pcov[0, 0])
@@ -41,14 +44,20 @@ r = V - f(I, *popt)
 chisq = np.sum((r / V_unc) ** 2)
 print "Reduced chi squared:", chisq / ddof
 
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((V - np.mean(V)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
 fig1 = plt.figure(1)
 # Plot data + model
 frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
 plt.scatter(I, V, label = "Data", s = 10, color = "black")
 plt.errorbar(I, V, xerr = I_unc, yerr = V_unc, linestyle = "None", color = "black")
-plt.plot(I, f(I, *popt), label = "Model")
+plt.plot(I, f(I, *popt), label = "Model", color = "black")
 plt.title("Potential vs. Current of a Light Bulb")
-plt.legend()
+# plt.legend()
 plt.ylabel("Potential (V)")
 plt.xlim([-5, 45])
 plt.ylim([-4, 29])

### 2018-01-17 circuit-elements/thermistor.py

@@ -17,6 +17,8 @@ def f(x, a, b):
 
 # ---------- Main Code ----------
 
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
 path_to_file = "/home/polina/Documents/3rd_Year/PHY324/circuit-elements/thermistor.txt"
 # Load data
 temp, temp_unc, resist, resist_unc = np.loadtxt(path_to_file, unpack = True)
@@ -32,8 +34,8 @@ resist = resist[:np.size(resist) - n]
 resist_unc = resist_unc[:np.size(resist_unc) - n]
 
 ddof = np.size(temp) - 2	# degrees of freedom for reduced chi squared
-print(ddof)
 
+# Fit data to model function
 popt, pcov = curve_fit(f, temp, resist, sigma = resist_unc, p0 = [1e6, 10])
 print(popt)
 print "R_0:", popt[0], "+-", np.sqrt(pcov[0, 0])
@@ -43,14 +45,20 @@ r = resist - f(temp, *popt)
 chisq = np.sum((r / resist_unc) ** 2)
 print "Reduced chi squared:", chisq / ddof
 
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((resist - np.mean(resist)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
 fig1 = plt.figure(1)
 # Plot data + model
 frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
 plt.scatter(temp, resist, label = "Data", s = 10, color = "black")
 plt.errorbar(temp, resist, xerr = temp_unc, yerr = resist_unc, linestyle = "None", color = "black")
-plt.plot(temp, f(temp, *popt), label = "Model")
+plt.plot(temp, f(temp, *popt), label = "Model", color = "black")
 plt.title("Resistance vs. Temperature of a Thermistor")
-plt.legend()
+# plt.legend()
 plt.ylabel("Resistance (kiloohms)")
 plt.xlim([270, 360])
 # frame1.axes().get_xaxis().set_visible(False)

### 2018-01-17 lenses/paper.tex
Added lenses setup pdf

--- 2018-01-17 circuit-elements/paper.tex
@@
 \begin{document}
-\papertitle{Non-linear Circuit Elements}
+\papertitle{Thick Lenses}
 \paperauth{A}{Khesin}{1002442029}
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{January 17, 2018}
+\paperdate{January 22, 2018}
 \begin{paperabs}
 
-	% a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
-
-	The relationships between current, potential, resistance, and temperature is of particular interest in nonlinear circuit components as they do not follow the principle of superposition when processing and amplifying signals.
-In this lab, these physical quantities were investigated for a thermistor and an incandescent light bulb.
-For the thermistor, the resistance was found to decrease exponentially as temperature increased.
-The relationship between potential and current of the light bulb was determined to obey a power law.
-Further, the power of temperature in Stefan-Boltzmann law was approximated to be \( 4.17 \pm 0.05 \).
+	Abstract
 
@@
 
-	Circuit components may be classified based on how they process signals as either linear or nonlinear.
-In linear components, such as resistors, capacitors, and some inductors, the signal obeys the principle of superposition; such components process electrical signals without distorting them.
-Nonlinear circuit elements do not have a linear relationship between current and potential, and thus may distort electrical signals.
-
-	The purpose of this experiment was to study the relationship between voltage and current for a thermistor and an incandescent lamp.
-Both of these circuit elements are nonlinear; for a thermistor, the resistance is a function of temperature and obeys the relation
-
-	\papereq{thermistor_model}{R = R_0e^{ -\frac{T}{T_0} }}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{T}{absolute temperature}{\kelvin}
-		\papervar{T_0}{constant of device}{\kelvin}
-		\papervar{R_0}{constant of device}{\ohm}
-	\end{paperwhere}
-
-	As evident from the above expression, the thermistor's resistance decreases with increasing temperature.
-This is unlike the resistance of metals (such as the filament of an incandescent light bulb examined further in the experiment), which exhibit the opposite relationship.
-
-	The relation in (1) was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown below.
-The temperature of the thermistor was decreased by adding cold water to the thermal flask and stirring to ensure uniform temperature in the flask.
-
-	\paperfig{setup1}{\pdf{setup1}}{The experimental setup used to measure resistance of a thermistor at varying temperatures.}
-
-	In general, the tungsten filament in an incandescent light bulb obeys Ohm's law.
-As the temperature increases, however, the resistance of the metal increases and above a certain temperature becomes proportional to the absolute temperature.
-The actual relationship between \( V \) and \( I \) is investigated in this experiment by fitting obtained measurements of current and potential to
-
-	\papereq{bulb-model}{ V = k I^a }{Serbanescu}
-	\begin{paperwhere}experimental
-		\papervar{V}{potential}{\volt}
-		\papervar{I}{current}{\ampere}
-		\papervar{k}{constant}{}
-		\papervar{a}{costant}{}
-	\end{paperwhere}
-
-	Potential and current were measured using two multimeters, with one measuring potential and the other current, a power supply, a tungsten filament light bulb, and a switch arranged as follows:
-
-	\paperfig{setup2}{\pdf{setup2}}{The experimental setup (light bulb).}
-
-	The current-potential data obtained for an incandescent light bulb was further used to determine the value of \( n \) in the Stefan-Boltzmann law,
-
-	\papereq{bulb-model}{ \kappa = \epsilon \sigma T^n }{Serbanescu}
-	\begin{paperwhere}
-		\papervar{\kappa}{power per unit area}{\watt\per\meter\squared}
-		\papervar{\epsilon}{emissivity of radiating body}{}
-		\papervar{\sigma}{Stefan-Boltzmann constant}{\watt\per\meter\squared\per\kelvin\tothe{4}}
-		\papervar{T}{absolute temperature}{K}
-		\papervar{n}{universal constant}{}
-	\end{paperwhere}
-
-	To obtain the value of \( n \), \( \kappa \) and \( T \) were expressed in terms of \( I \) and \( V \) and further in terms of \( I \) (and constants) only with the help of the expression in (2).
-In particular, it was found that
-
-	\papereq{kappa}{ \kappa = \frac{VI}{A} = \frac{k}{A} I^{(a+1)} }{}
-	\begin{paperwhere}
-		\papervar{A}{surface area of filament}{\si{\meter\squared}}
-	\end{paperwhere}
-
-	Further, using  \( R = k'T \), (with \( k' \) being a constant of proportionality) it was shown that
-
-	\papereq{temperature}{ T = \frac{1}{k'} \frac{V}{I} =  \frac{k}{k'} I^{(a-1)}}{}
-
-	Finally, combining the above expressions and setting constants to be equal, the following relationship for \( n \) in terms of \( a \) was obtained.
-
-	\papereq{temperature}{ n = \frac{a+1}{a-1} }{}
+	Introduction
 
@@
 
-	The resistance of the thermistor at various temperatures was measured and recorded.
-The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1 $ LSG) for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
-The uncertainty in temperature measurements was taken to be $ \pm 0.5 \si{\kelvin} $.
-\vspace{1em}
-
-	\paperfig{thermistor}{\begin{papertable}{|[outer]I|[inner]C|[inner]U|[outer]}
-			\paperoline\papertableindexheader&\textsc{Temperature}&\multicolumn{2}{c|[outer]}{\textsc{Resistance}}\\
-			\papertablecheadersymbol{T$ $(\pm0.5$ $\si{\kelvin})}\papertableuheadersymbole{R$ $(\si{\kilo\ohm})}\\\paperiline
-			\papertableindex\papertablecval{352.5}\papertableuval{6.68}{.02}\\\paperiline
-			\papertableindex\papertablecval{349.0}\papertableuval{6.93}{.02}\\\paperiline
-			\papertableindex\papertablecval{348.0}\papertableuval{7.54}{.03}\\\paperiline
-			\papertableindex\papertablecval{346.0}\papertableuval{8.01}{.03}\\\paperiline
-			\papertableindex\papertablecval{340.0}\papertableuval{9.95}{.03}\\\paperiline
-			\papertableindex\papertablecval{338.0}\papertableuval{10.33}{.03}\\\paperiline
-			\papertableindex\papertablecval{335.0}\papertableuval{11.76}{.03}\\\paperiline
-			\papertableindex\papertablecval{334.5}\papertableuval{12.36}{.03}\\\paperiline
-			\papertableindex\papertablecval{329.5}\papertableuval{14.45}{.04}\\\paperiline
-			\papertableindex\papertablecval{327.5}\papertableuval{15.33}{.04}\\\paperiline
-			\papertableindex\papertablecval{324.0}\papertableuval{17.23}{.04}\\\paperiline
-			\papertableindex\papertablecval{321.0}\papertableuval{19.51}{.05}\\\paperiline
-			\papertableindex\papertablecval{319.0}\papertableuval{21.7}{.1}\\\paperiline
-			\papertableindex\papertablecval{317.0}\papertableuval{24.3}{.1}\\\paperiline
-			\papertableindex\papertablecval{314.0}\papertableuval{26.1}{.2}\\\paperiline
-			\papertableindex\papertablecval{309.5}\papertableuval{31.4}{.2}\\\paperiline
-			\papertableindex\papertablecval{308.5}\papertableuval{33.7}{.2}\\\paperiline
-			\papertableindex\papertablecval{307.5}\papertableuval{35.5}{.2}\\\paperiline
-			\papertableindex\papertablecval{305.0}\papertableuval{38.0}{.2}\\\paperiline
-			\papertableindex\papertablecval{304.0}\papertableuval{40.3}{.2}\\\paperiline
-			\papertableindex\papertablecval{301.5}\papertableuval{44.3}{.2}\\\paperiline
-			\papertableindex\papertablecval{299.5}\papertableuval{47.7}{.2}\\\paperiline
-			\papertableindex\papertablecval{298.0}\papertableuval{51.6}{.2}\\\paperiline
-			\papertableindex\papertablecval{296.0}\papertableuval{56.3}{.2}\\\paperiline
-			\papertableindex\papertablecval{294.0}\papertableuval{61.3}{.2}\\\paperiline
-			\papertableindex\papertablecval{292.5}\papertableuval{66.9}{.2}\\\paperiline
-			\papertableindex\papertablecval{290.5}\papertableuval{73.8}{.2}\\\paperiline
-			\papertableindex\papertablecval{286.0}\papertableuval{92.9}{.3}\\\paperiline
-			\papertableindex\papertablecval{283.0}\papertableuval{104.7}{.3}\\\paperiline
-			\papertableindex\papertablecval{278.0}\papertableuval{~126.2}{\parbox{\widthof{126.2~}}{.4}}\\\paperoline
-		\end{papertable}\vspace{-1.5em}}
-	{Resistance of thermistor at the given temperatures. All uncertainties were propagated using the method of quadratures.}\vspace{1em}
-
-	Further, current and potential for a tungsten filament light bulb were measured and recorded.
-As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1 \) of last displayed significant digit); current measurements carried an uncertainty of \( \pm (1\% + 3 \) of last displayed significant digit).
-\vspace{1em}
-
-	\paperfig{light-bulb}{\begin{papertable}{|[outer]I|[inner]U|[inner]U|[outer]}
-			\paperoline\papertableindexheader&\multicolumn{2}{c|[inner]}{\textsc{Potential}}&\multicolumn{2}{c|[outer]}{\textsc{Current}}\\
-			\papertableuheadersymbol{V$ $(\si{\volt})}\papertableuheadersymbole{I$ $(\si{\milli\ampere)}}\\\paperiline
-			\papertableindex\papertableuval{0.0222}{.0002}\papertableuval{0.324}{.003}\\\paperiline
-			\papertableindex\papertableuval{0.0776}{.0003}\papertableuval{1.045}{.009}\\\paperiline
-			\papertableindex\papertableuval{0.1122}{.0004}\papertableuval{1.39}{.01}\\\paperiline
-			\papertableindex\papertableuval{0.244}{.002}\papertableuval{2.27}{.03}\\\paperiline
-			\papertableindex\papertableuval{0.472}{.002}\papertableuval{3.40}{.04}\\\paperiline
-			\papertableindex\papertableuval{0.541}{.002}\papertableuval{3.69}{.04}\\\paperiline
-			\papertableindex\papertableuval{0.697}{.003}\papertableuval{4.28}{.04}\\\paperiline
-			\papertableindex\papertableuval{0.871}{.003}\papertableuval{4.89}{.05}\\\paperiline
-			\papertableindex\papertableuval{1.128}{.004}\papertableuval{5.72}{.05}\\\paperiline
-			\papertableindex\papertableuval{1.840}{.006}\papertableuval{7.68}{.07}\\\paperiline
-			\papertableindex\papertableuval{1.940}{.006}\papertableuval{7.93}{.07}\\\paperiline
-			\papertableindex\papertableuval{4.01}{.02}\papertableuval{12.3}{.1}\\\paperiline
-			\papertableindex\papertableuval{6.00}{.03}\papertableuval{15.8}{.1}\\\paperiline
-			\papertableindex\papertableuval{8.01}{.03}\papertableuval{18.8}{.2}\\\paperiline
-			\papertableindex\papertableuval{10.24}{.04}\papertableuval{21.8}{.3}\\\paperiline
-			\papertableindex\papertableuval{12.07}{.04}\papertableuval{24.1}{.3}\\\paperiline
-			\papertableindex\papertableuval{14.27}{.05}\papertableuval{26.6}{.3}\\\paperiline
-			\papertableindex\papertableuval{16.01}{.05}\papertableuval{28.5}{.3}\\\paperiline
-			\papertableindex\papertableuval{17.98}{.05}\papertableuval{30.6}{.3}\\\paperiline
-			\papertableindex\papertableuval{18.45}{.06}\papertableuval{31.1}{.3}\\\paperiline
-			\papertableindex\papertableuval{19.86}{.06}\papertableuval{32.5}{.3}\\\paperiline
-			\papertableindex\papertableuval{21.0}{.2}\papertableuval{33.6}{.4}\\\paperiline
-			\papertableindex\papertableuval{22.1}{.2}\papertableuval{34.6}{.4}\\\paperiline
-			\papertableindex\papertableuval{22.9}{.2}\papertableuval{35.4}{.4}\\\paperiline
-			\papertableindex\papertableuval{24.0}{.2}\papertableuval{36.4}{.4}\\\paperiline
-			\papertableindex\papertableuval{25.1}{.2}\papertableuval{37.3}{.4}\\\paperoline
-			\end{papertable}\vspace{-1.5em}}
-	{Potential and current through the incandescent bulb. All uncertainties were propagated using the method of quadratures.} \vspace{1em}
+	Observations
 
@@
 
-	Using the expression in (1) as the model function, the relationship between the temperature and resistance of a thermistor was calculated.
-Least squares fitting of all data points yielded \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \) as the fit parameters, with a reduced \( \chi ^ 2 \) value of \( 252.1710 \).
-The data, model, and residuals for this fit are shown below.
-
-	\paperfig{thermistor-plot}{\pdf{Thermistor}}{Resistance and residuals plotted against the temperature in the thermal flask, with least squares fit included in blue.
-Error bars on both temperature and resistance were too small to be visible.} \vspace{1em}
-
-	A visualization of residuals clearly indicated that the data can be better modelled for greater temperatures.
-Indeed, least squares fitting performed without the data points corresponding to three lowest temperatures yielded a reduced \( \chi ^ 2 \) value of \( 181.5543 \).
-Removing more lower-temperature data points further improved reduced \( \chi ^ 2 \).
-% Removing the six lower-temperature points led to a model with reduced \( \chi ^ 2 \) value of \( 130.1026 \).
-
-	Further, a least squares fitting was performed on the data obtained for the incandescent light bulb, with the expression in (2) used as a model function.
-The formula was found to hold; the resulting parameters were \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = 1.63 \pm 0.01 \).
-The value of reduced \( \chi ^ 2 \) obtained was \( 176.8952 \).
-The data, model, and residuals for this fit are shown below.
-
-	\paperfig{bulb-plot}{\pdf{Bulb}}{Potential of the incandescent light bulb plotted against the current.
-Least squares fit was indicated in blue; residuals visualized at the bottom.
-Error bars on the data points were too small to be visible.} \vspace{1em}
-
-	As evidenced above, thermistors and metal resistors have different variations of resistance with temperatures.
-For metal resistors, resistance increasing with temperature is intuitively explained TODO!
-
-	Upon obtaining the value of \( a \), the universal constant \( n \) in Stefan-Boltzmmann law could be approximated.
-Plugging \( a = 1.63 \pm 0.01 \) into (6) yielded \( 4.17 \pm 0.05 \) (uncertainty propagated using the method  of quadratures), which was close the actual value of \( n = 4\).
-Another constant appearing in Stefan-Boltzmann law, \( \epsilon \) (emissivity of the radiating body), differs depending on the material.
-\( \epsilon = 1 \) corresponds to a body that is a perfect absorber and emitter of radiant energy (i.e., a \textit{black body}); \( \epsilon = 0 \) corresponds to a perfect reflector of radiant energy.
+	Analysis
 
@@
 
-		This experiment has investigated two nonlinear circuit elements, a thermistor and an incandescent tungsten filament light bulb.
-Resistance of the thermistor was found to be a function of the temperature, satisfying the exponential relation in (1) with \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \).
-For the light bulb, the relationship between potential and current was shown to follow a power law introduced in (2), with \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = 1.63 \pm 0.01 \).
-The most significant sources of error arose from potential uneven temperature of water in the thermal flask with the thermistor and inconsistencies in current and potential readings of the multimeter when switching the range of input signal.
-
-		The above value of \( a \) was further used to approximate the power \( n \) of \( T \) in Stefan-Boltzmann law; \( n \) was found to be \( 4.17 \pm 0.05 \), reasonably close to the actual value of \( n = 4 \).
+		Conclusion
 
@@
 
-	\papersource{Serbanescu, R., Non-linear Circuit Elements, 2015}
-
-\papersource{}
+	Sources
 

### 2018-01-18 thermocouple/calibration.py
.py for fit

@@ -1,0 +1,53 @@
+#!/usr/bin/python
+# 
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Functions ----------
+
+# Fit function for optimizing; a  = S (Seebeck constant)
+# (x, a) --> (f_value)
+# (float, float) --> (float)
+def f(x, a):
+	return a * x
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+path_to_file = "/home/polina/Documents/3rd_Year/PHY324/thermocouple/measurements.txt"
+# Load data
+T1, T1_unc, T2, T2_unc, V, V_unc = np.loadtxt(path_to_file, unpack = True)
+# Convert data to Kelvin
+T1 = T1 + 273.15
+T2 = T2 + 273.15
+T_diff = T2 - T1
+
+ddof = np.size(T_diff) - 1	# degrees of freedom for reduced chi squared
+print ddof
+
+# Fit data to model function
+popt, pcov = curve_fit(f, T_diff, V, sigma = V_unc)
+print(popt)
+print "S:", popt[0], "+-", np.sqrt(pcov[0, 0])
+# Find residuals
+r = V - f(T_diff, *popt)
+chisq = np.sum((r / V_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((V - np.mean(V)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
+plt.plot(T_diff, V)
+plt.show()
+
+#fig1 = plt.figure(1)
+# Plot data + model
+#frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+#plt.scatter(T_diff, V, )

### 2018-01-20 lenses/paper.tex
Lenses introduction

@@
 
-	Abstract
+	a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
 
@@
 
-	Introduction
+	The purpose of this experiment was to determine the index of refraction, \( n \), of a sphere and two hemispheres of different sizes made of a clear plastic.
+In general, refraction of light at a single spherical surface obeys the following relationship.
+	\papereq{SphericalSurfaceRefraction}{\frac{n}{s} + \frac{n'}{s'} = \frac{n' - n}{R}}{Serbanescu}
+	\begin{paperwhere}
+		\papervar{n}{index of refraction of the first medium}{}
+		\papervar{n}{index of refraction of the second medium}{}
+		\papervar{s}{object distance}{\meter}
+		\papervar{s'}{image distance}{\meter}
+		\papervar{R}{radius of curvature}{\meter}
+	\end{paperwhere}
+
+	Applying \eqSphericalSurfaceRefraction to two spherical surfaces sharing a common axis, the Lens Maker's Formula is obtained. 
+	\papereq{LensMakersFormula}{\frac{1}{f} = \pars{n-1}\pars{\frac{1}{R_1} - \frac{1}{R_2} + \frac{\pars{n-1}t}{nR_1R_2}}}{Serbanescu}
+	\begin{paperwhere}
+		\papervar{f}{focal length of lens}{\meter}
+		\papervar{n}{index of refraction of lens}{}
+		\papervar{R_1}{radius of curvature of surface closest to object}{\meter}
+		\papervar{R_2}{radius of curvature of surface closest to image}{\meter}
+		\papervar{t}{axial thickness of lens}{\meter}
+	\end{paperwhere}
+
+	To obtain an expression for the focal length and refractive index of hemispheres and the sphere, \eqLensMakersFormula was used with appropriate radii.
+For a hemisphere with the flat side facing the source, \( R_1 = \infty \) and \( R_2 = R \).
+	\papereq{HemisphereFlatSource}{\frac{1}{f} = \pars{1-n}{\frac{1}{R}}}{}
+
+	To model a hemisphere with the flat side facing away from the source, setting \( R1 = R \) and \( R_2 = \infty \) led to the following expression.
+	\papereq{HemisphereFlatScreen}{\frac{1}{f} = \pars{n-1}{\frac{1}{R}}}{}
+
+	Finally, a sphere with \( R_1 = R_2 = R \) was characterized by the formula below.
+	\papereq{Sphere}{\frac{1}{f} =	\pars{\frac{n-1}{R}}^2\frac{t}{n}}{}
+
+	The experimental setup consisted of an optical bench with a screen, holder for the lenses, a sliding calibrated measuring rod, and a light source mounted as shown.
+	\paperfig{Setup}{\pdf{setup} \vspace{-2.5em}}{The experimental setup with the smaller hemisphere mounted.} \vspace{0.5em}
+
+	The calibrated rod was used to measure the distance between the screen and either the flat side or the vertex of the lens, depending on the orientation with respect to the source.
+Each distance is obtained by finding the difference between the position of the rod holder while in contact with the screen (\figSetup) and with the lens, ensuring to account for screen thickness.
+Before making each measurement, the rod was aligned with the vertex of the lens to attain a more accurate result.
+
+	Of particular interest was the position on the bench where the image on the screen had a magnification \( m = -1 \) (i.e., same size as the source, inverted).
+This position corresponded to \( s_0 = s_i = 2f \), as evident from the Thin Lens Equation below.
+	\papereq{ThinLensEquation}{\frac{1}{s_0} + \frac{1}{s_i} = \frac{1}{f}}{Serbanescu}
+	\begin{paperwhere}
+		\papervar{s_0}{object distance}{\meter}
+		\papervar{s_i}{image distance}{\meter}
+		\papervar{f}{focal length}{\meter}
+	\end{paperwhere}
+
+	While \eqThinLensEquation describes a thin lens in the paraxial region, it can be applied to a lens with nonzero thickness by taking \( s_0 \) to be the distance between the object and the first principle plane and \( s_i \) to be the distance between the image and the second principal plane.
 
@@
 
-	Observations
+	The difference in position of the calibrated rod was measured for two hemispheres and the sphere.
+The error of position readings was taken to be \( \pm 0.05 \si{\cm} \); uncertainty of the difference of positions was propagated using the method of quadratures.
+The difference accounts for the thickness of the screen, which was measured to be \( (1.75 \pm 0.02) \si{\mm} \) using a caliper.
+
+	\paperfig{Helium}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
+			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+			\papertableindex\papertablecval{37.05}\papertablecval{28.95}\papertablecval{}\\\paperiline
+			\papertableindex\papertablecval{36.25}\papertablecval{28.40}\papertablecval{}\\\paperoline
+		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the source.}
 

### 2018-01-22 lenses/paper.tex
Some analysis

@@
 	To obtain an expression for the focal length and refractive index of hemispheres and the sphere, \eqLensMakersFormula was used with appropriate radii.
-For a hemisphere with the flat side facing the source, \( R_1 = \infty \) and \( R_2 = R \).
-	\papereq{HemisphereFlatSource}{\frac{1}{f} = \pars{1-n}{\frac{1}{R}}}{}
+For a hemisphere with the flat side facing the source, \( R_1 = \infty \) and \( R_2 = -R \).
+	\papereq{HemisphereFlatSource}{\frac{1}{f} = \pars{n-1}{\frac{1}{R}}}{}
 
-	To model a hemisphere with the flat side facing away from the source, setting \( R1 = R \) and \( R_2 = \infty \) led to the following expression.
-	\papereq{HemisphereFlatScreen}{\frac{1}{f} = \pars{n-1}{\frac{1}{R}}}{}
+	To model a hemisphere with the flat side facing away from the source, setting \( R1 = R \) and \( R_2 = \infty \) yields \eqHemisphereFlatSource again.
 
 	Finally, a sphere with \( R_1 = R_2 = R \) was characterized by the formula below.
-	\papereq{Sphere}{\frac{1}{f} =	\pars{\frac{n-1}{R}}^2\frac{t}{n}}{}
+	\papereq{Sphere}{\frac{1}{f} =	\pars{\frac{n-1}{R}}^2\frac{t}{n} = \frac{2\pars{n-1}}{nR}}{}
 
 	The experimental setup consisted of an optical bench with a screen, holder for the lenses, a sliding calibrated measuring rod, and a light source mounted as shown.
-	\paperfig{Setup}{\pdf{setup} \vspace{-2.5em}}{The experimental setup with the smaller hemisphere mounted.} \vspace{0.5em}
+	\paperfig{Setup}{\pdf{setup} \vspace{-2.0em}}{The experimental setup with the smaller hemisphere mounted.} \vspace{0.5em}
 
@@
 	The difference in position of the calibrated rod was measured for two hemispheres and the sphere.
-The error of position readings was taken to be \( \pm 0.05 \si{\cm} \); uncertainty of the difference of positions was propagated using the method of quadratures.
-The difference accounts for the thickness of the screen, which was measured to be \( (1.75 \pm 0.02) \si{\mm} \) using a caliper.
+The error of position readings was taken to be \( \pm .05 \si{\cm} \); uncertainty of the difference of positions was propagated using the method of quadratures.
+The difference accounts for the thickness of the screen, which was measured to be \( (1.75 \pm .02) \si{\mm} \) using a caliper.
 
-	\paperfig{Helium}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+	\paperfig{HemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
 			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
@@
 
-	Analysis
+	Principal planes of a hemisphere and a sphere were visualized using the ray diagrams sketched below.
+
+	\paperfig{Hemisphere}{\pdf{hemisphere} \vspace{-1.5em} }{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a hemisphere.}
+
+	If the hemisphere is facing the light source with its curved side, the arrangement in \figHemisphere is mirrored with \( H_2 \) and \( H_1 \) being exchanged.
+This follows naturally from the Principle of Reversibility of light.
+
+	\paperfig{Sphere}{\pdf{sphere} \vspace{-2.0em}}{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a sphere.}
+
+	The measured distance between the screen and the closest vertex for the hemisphere with its flat side facing the light source equalled \( 2f \), as evident by taking \( R1 = \infty \) in the expression for the distance \( h_2 \) between the right vertex and the secondary principal plane.
+	\papereq{VertexToSecondary}{h_2 = -\frac{f\pars{n-1}t}{nR_1}}{Serbanescu}
+
+	Combining \eqVertexToSecondary with the expression for the focal lens of a spherical lens, \( f_{ball} \) provided a way to solve for and calculate the refractive index of the lenses.
+	\papereq{SphereFocalLength}{f_{ball} = \frac{nR}{2\pars{n-1}}}{Serbanescu}
 

### 2018-01-22 thermocouple/calibration.py

@@ -18,6 +18,7 @@ def f(x, a):
 
 # Set desired font
 plt.rc('font', family = 'Times New Roman')
+
 path_to_file = "/home/polina/Documents/3rd_Year/PHY324/thermocouple/measurements.txt"
 # Load data
 T1, T1_unc, T2, T2_unc, V, V_unc = np.loadtxt(path_to_file, unpack = True)
@@ -25,6 +26,8 @@ T1, T1_unc, T2, T2_unc, V, V_unc = np.loadtxt(path_to_file, unpack = True)
 T1 = T1 + 273.15
 T2 = T2 + 273.15
 T_diff = T2 - T1
+T_diff_unc = np.sqrt(T1_unc ** 2 + T2_unc ** 2)
+print(T_diff_unc)
 
 ddof = np.size(T_diff) - 1	# degrees of freedom for reduced chi squared
 print ddof
@@ -44,10 +47,26 @@ ss_tot = np.sum((V - np.mean(V)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
 print "R^2:", r_squared
 
-plt.plot(T_diff, V)
+fig1 = plt.figure(1)
+# Plot data + model
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+plt.scatter(T_diff, V, s = 3, color = "black")
+plt.errorbar(T_diff, V, xerr = T_diff_unc, yerr = V_unc, linestyle = "None", color = "black", linewidth = 0.5)
+plt.plot(T_diff, f(T_diff, *popt), color = "black", linewidth = 0.5)
+plt.title("Potential vs. temperature difference of a thermocouple")
+plt.xlim([-5, 105])
+plt.ylim([-0.5, 4.5])
+plt.ylabel("Potnetial (mV)")
+frame1.set_xticklabels([])
+plt.grid(True)
+# Residual plot
+frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
+plt.scatter(T_diff, r, s = 3, color = "black")
+plt.xlim([-5, 105])
+plt.ylim([-0.19, 0.19])
+plt.xlabel("Temperature difference (K)")
+plt.ylabel("Residuals")
+plt.grid(True)
+plt.savefig("ThermistorCalibration.pdf")
 plt.show()
 
-#fig1 = plt.figure(1)
-# Plot data + model
-#frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
-#plt.scatter(T_diff, V, )

### 2018-01-22 lenses/paper.tex
removed incorrect stuff

@@
 	To obtain an expression for the focal length and refractive index of hemispheres and the sphere, \eqLensMakersFormula was used with appropriate radii.
-For a hemisphere with the flat side facing the source, \( R_1 = \infty \) and \( R_2 = -R \).
+For a hemisphere with the flat side facing the source, \( R_1 = \infty \) and \( R_2 = - R \).
 	\papereq{HemisphereFlatSource}{\frac{1}{f} = \pars{n-1}{\frac{1}{R}}}{}
 
-	To model a hemisphere with the flat side facing away from the source, setting \( R1 = R \) and \( R_2 = \infty \) yields \eqHemisphereFlatSource again.
+	To model a hemisphere with the flat side facing away from the source, setting \( R_1 = -R \) and \( R_2 = - \infty \) yields \eqHemisphereFlatSource again.
 
 	Finally, a sphere with \( R_1 = R_2 = R \) was characterized by the formula below.
-	\papereq{Sphere}{\frac{1}{f} =	\pars{\frac{n-1}{R}}^2\frac{t}{n} = \frac{2\pars{n-1}}{nR}}{}
+	\papereq{Sphere}{\frac{1}{f} =\pars{\frac{n-1}{R}}^2\frac{t}{n} = \frac{2\pars{n-1}}{nR}}{}
 
@@
 
-	The measured distance between the screen and the closest vertex for the hemisphere with its flat side facing the light source equalled \( 2f \), as evident by taking \( R1 = \infty \) in the expression for the distance \( h_2 \) between the right vertex and the secondary principal plane.
-	\papereq{VertexToSecondary}{h_2 = -\frac{f\pars{n-1}t}{nR_1}}{Serbanescu}
-
-	Combining \eqVertexToSecondary with the expression for the focal lens of a spherical lens, \( f_{ball} \) provided a way to solve for and calculate the refractive index of the lenses.
-	\papereq{SphereFocalLength}{f_{ball} = \frac{nR}{2\pars{n-1}}}{Serbanescu}
-
 \papersec{Conclusion}

### 2018-01-22 lenses/paper.tex
Finished analysis

@@
 	The difference in position of the calibrated rod was measured for two hemispheres and the sphere.
-The error of position readings was taken to be \( \pm .05 \si{\cm} \); uncertainty of the difference of positions was propagated using the method of quadratures.
+The error of position readings was taken to be \( \pm .05 \si{\cm} \); uncertainty in the difference of positions was propagated using the method of quadratures.
 The difference accounts for the thickness of the screen, which was measured to be \( (1.75 \pm .02) \si{\mm} \) using a caliper.
 
-	\paperfig{HemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+	\paperfig{SmallHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
 			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
 			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
-			\papertableindex\papertablecval{37.05}\papertablecval{28.95}\papertablecval{}\\\paperiline
-			\papertableindex\papertablecval{36.25}\papertablecval{28.40}\papertablecval{}\\\paperoline
+			\papertableindex\papertablecval{37.05}\papertablecval{28.95}\papertablecval{7.92}\\\paperiline
+			\papertableindex\papertablecval{36.25}\papertablecval{28.40}\papertablecval{7.68}\\\paperoline
 		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the source.}
+
+	\paperfig{SmallHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
+			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+			\papertableindex\papertablecval{36.15}\papertablecval{29.50}\papertablecval{7.48}\\\paperiline
+			\papertableindex\papertablecval{36.10}\papertablecval{29.60}\papertablecval{6.32}\\\paperoline
+		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the screen.}
+
+		\paperfig{LargeHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
+				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+				\papertableindex\papertablecval{41.10}\papertablecval{31.00}\papertablecval{9.92}\\\paperiline
+				\papertableindex\papertablecval{41.75}\papertablecval{31.35}\papertablecval{10.22}\\\paperoline
+			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the large hemisphere, flat surface facing the source.}
+
+		\paperfig{LargeHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
+				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+				\papertableindex\papertablecval{41.85}\papertablecval{32.95}\papertablecval{8.72}\\\paperiline
+				\papertableindex\papertablecval{42.40}\papertablecval{33.15}\papertablecval{9.08}\\\paperoline
+			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the large hemisphere, flat surface facing the screen.}
+
+		\paperfig{SphereData}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
+				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
+				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+				\papertableindex\papertablecval{35.40}\papertablecval{30.40}\papertablecval{4.82}\\\paperiline
+				\papertableindex\papertablecval{35.85}\papertablecval{30.50}\papertablecval{5.18}\\\paperiline
+				\papertableindex\papertablecval{35.95}\papertablecval{30.55}\papertablecval{5.22}\\\paperoline
+			\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the sphere.}
 
@@
 
+	Despite measurements being taken for arrangements where \( s_o = s_i = 2f \), \( \Delta d \) did not always correspond to a constant multiple of the focal length.
+Instead, it was equal to double the focal length minus the distance \( h_2 \) from the right vertex of the lens to the second principal plane.
+In general, \( h_2 \) was given by the following expression.
+	\papereq{VertexToSecondaryPrincipalPlane}{h_2 = - \frac{f\pars{n-1}t}{nR_1}}{Serbanescu}
+
+	By repeatedly applying \eqVertexToSecondaryPrincipalPlane for each orientation and shape of the lens, expressions for \( \Delta d \) in terms of \( R \) and \( n \) were obtained.
+In the case of the sphere,
+	\papereq{SphereData}{\Delta d_{sphere} = \frac{R}{n-1}.}{}
+
+	For a hemisphere with its flat side facing the source, 
+	\papereq{HemisphereFlatSource}{\Delta d_{hemisphere} = 2\frac{R}{n-1}.}{}
+
+	Finally, for a hemisphere with its flat side facing the screen (prime denoting this particular orientation),
+	\papereq{HemisphereFlatScreen}{\Delta d'_{hemisphere} = 2\frac{R}{n\pars{n-1}}.}{}
+
+	To use the measurements obtained for the large sphere and the large hemisphere, expressions in \eqSphereData and \eqHemisphereFlatScreen were rearranged to obtain the following.
+	\papereq{nValueWithSphere}{n= 2 \frac{\Delta d_{sphere}}{\Delta d'_{hemisphere}}}{}
+
+	Upon averaging and plugging in the corresponding measurements for the large sphere and hemisphere, \( n = \pars{1.14 \pm 0.16} \) was obtained, with uncertainty propagated using the method of quadratures.
+Furthermore, by rearranging equations \eqHemisphereFlatSource and \eqHemisphereFlatScreen, the value of \( n \) could be obtained without using the measurements for the sphere, as indicated below.
+	\papereq{nHemisphereOnly}{n = \frac{\Delta d_{hemisphere}}{\Delta d'_{hemisphere}}}{}
+
+	For the large hemisphere, \eqnHemisphereOnly yielded \( n = \pars{1.13 \pm 0.14} \), agreeing with the value obtained using the expression in \eqnValueWithSphere.
+For the small hemisphere, \( n = \pars{1.06 \pm 0.14} \) was obtained.
+
 \papersec{Conclusion}

### 2018-01-22 lenses/paper.tex
Finished abstract

@@
 
-	a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
+	In this experiment, the refractive index of various thick lenses was determined.
+In particular, expressions relating the distance between the image and the right vertex and the index of refraction \( n \) were determined for hemispherical and spherical lenses.
+The refractive index of the spherical and large hemispherical lenses was found to equal \( \pars{1.32 \pm .05} \).
+Further, using the expression for \( n \) in terms of the data for the hemispherical lenses only, \( n \) was calculated again.
+For the large hemisphere, \( n = \pars{1.30 \pm .02} \) was obtained.
+For the small hemisphere, \( n \) was found to equal \( \pars{1.56 \pm .02} \).
 
@@
 			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
-			\papertableindex\papertablecval{36.15}\papertablecval{29.50}\papertablecval{7.48}\\\paperiline
+			\papertableindex\papertablecval{36.15}\papertablecval{29.50}\papertablecval{6.48}\\\paperiline
 			\papertableindex\papertablecval{36.10}\papertablecval{29.60}\papertablecval{6.32}\\\paperoline
@@
 
-	\paperfig{Hemisphere}{\pdf{hemisphere} \vspace{-1.5em} }{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a hemisphere.}
+	\paperfig{Hemisphere}{\pdf{hemisphere} \vspace{-1.5em} }{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a hemisphere.
+Ideally, \( H_2 \) should be tangent to the right vertex of the lens.}
 
@@
 
-	\paperfig{Sphere}{\pdf{sphere} \vspace{-2.0em}}{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a sphere.}
+	\paperfig{Sphere}{\pdf{sphere} \vspace{-2.0em}}{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a sphere.
+Ideally, the two principle planes should coincide at the center of the sphere.}
 
@@
 
-	By repeatedly applying \eqVertexToSecondaryPrincipalPlane for each orientation and shape of the lens, expressions for \( \Delta d \) in terms of \( R \) and \( n \) were obtained.
+	By repeatedly applying \eqVertexToSecondaryPrincipalPlane and \eqLensMakersFormula for each orientation and shape of the lens, expressions for \( \Delta d \) in terms of \( R \) and \( n \) were obtained.
 In the case of the sphere,
@@
 
-	Finally, for a hemisphere with its flat side facing the screen (prime denoting this particular orientation),
-	\papereq{HemisphereFlatScreen}{\Delta d'_{hemisphere} = 2\frac{R}{n\pars{n-1}}.}{}
+	Finally, for a hemisphere with its flat side facing the screen (prime denoting this particular orientation from now on),
+	\papereq{HemisphereFlatScreen}{\Delta d'_{hemisphere} = 2\frac{R\pars{n+1}}{n\pars{n-1}}.}{}
 
 	To use the measurements obtained for the large sphere and the large hemisphere, expressions in \eqSphereData and \eqHemisphereFlatScreen were rearranged to obtain the following.
-	\papereq{nValueWithSphere}{n= 2 \frac{\Delta d_{sphere}}{\Delta d'_{hemisphere}}}{}
+	\papereq{nValueWithSphere}{ n = \pars{\frac{\Delta d'_{hemisphere}}{\Delta d_{sphere}} - 1}^{-1} }{}
 
-	Upon averaging and plugging in the corresponding measurements for the large sphere and hemisphere, \( n = \pars{1.14 \pm 0.16} \) was obtained, with uncertainty propagated using the method of quadratures.
+	Upon averaging and plugging in the corresponding measurements for the large sphere and hemisphere, \( n = \pars{1.32 \pm .05} \) was obtained, with uncertainty propagated using the method of quadratures.
 Furthermore, by rearranging equations \eqHemisphereFlatSource and \eqHemisphereFlatScreen, the value of \( n \) could be obtained without using the measurements for the sphere, as indicated below.
-	\papereq{nHemisphereOnly}{n = \frac{\Delta d_{hemisphere}}{\Delta d'_{hemisphere}}}{}
+	\papereq{nHemisphereOnly}{n = \pars{\frac{2 \Delta d'_{hemisphere}}{\Delta d_{hemisphere}} - 1}^{-1} }{}
 
-	For the large hemisphere, \eqnHemisphereOnly yielded \( n = \pars{1.13 \pm 0.14} \), agreeing with the value obtained using the expression in \eqnValueWithSphere.
-For the small hemisphere, \( n = \pars{1.06 \pm 0.14} \) was obtained.
+	For the large hemisphere, \eqnHemisphereOnly yielded \( n = \pars{1.30 \pm .02} \), agreeing with the value obtained using the expression in \eqnValueWithSphere.
+For the small hemisphere, \( n = \pars{1.56 \pm .02} \) was obtained.
+All uncertainties were propagated using the method of quadratures.
+
+	Possible sources of error in this experiment arose from potential misalignment of the calibrated rod when determining the position of the vertex of the lens and inconsistent focusing of the image.
+Uncertainty of all values of \( n \) could be improved significantly if the optical bench allowed for more accurate measurements of position of the rod.
 
@@
 
-		Conclusion
+		In this experiment, the refractive index of three thick lenses (two hemispheres of different sizes and a sphere) was determined without finding the radius of the lenses.
+It was shown that it is sufficient to determine the separation between the screen and the closest vertex of the lens for the sphere and two orientations of the hemisphere (flat side facing the source and the screen).
+
+		Using the data for the sphere and the large hemisphere, a refractive index of \( n = \pars{1.32 \pm .05} \) was obtained.
+Using the data for two orientations of the large hemisphere only, \( n = \pars{1.30 \pm .02} \) was determined, agreeing with the previous value of \( n \).
+Finally, for the smaller hemisphere, the refractive index was determined to be \( n = \pars{1.56 \pm .02} \).
 
@@
 
-	Sources
+	\papersource{Serbanescu, R., Thick Lenses, 2013}
 

### 2018-01-22 thermocouple/paper.tex
Added paper + setup

--- 2018-01-22 lenses/paper.tex
@@
 \begin{document}
-\papertitle{Thick Lenses}
+\papertitle{The Thermocouple}
 \paperauth{A}{Khesin}{1002442029}
+\paperauth{N}{Rahnamaei}{STUDENT \#}
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{January 22, 2018}
+\paperdate{January 24, 2018}
 \begin{paperabs}
 
-	a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
+	Abstract goes here
 
@@
 
-	The purpose of this experiment was to determine the index of refraction, \( n \), of a sphere and two hemispheres of different sizes made of a clear plastic.
-In general, refraction of light at a single spherical surface obeys the following relationship.
-	\papereq{SphericalSurfaceRefraction}{\frac{n}{s} + \frac{n'}{s'} = \frac{n' - n}{R}}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{n}{index of refraction of the first medium}{}
-		\papervar{n}{index of refraction of the second medium}{}
-		\papervar{s}{object distance}{\meter}
-		\papervar{s'}{image distance}{\meter}
-		\papervar{R}{radius of curvature}{\meter}
-	\end{paperwhere}
-
-	Applying \eqSphericalSurfaceRefraction to two spherical surfaces sharing a common axis, the Lens Maker's Formula is obtained. 
-	\papereq{LensMakersFormula}{\frac{1}{f} = \pars{n-1}\pars{\frac{1}{R_1} - \frac{1}{R_2} + \frac{\pars{n-1}t}{nR_1R_2}}}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{f}{focal length of lens}{\meter}
-		\papervar{n}{index of refraction of lens}{}
-		\papervar{R_1}{radius of curvature of surface closest to object}{\meter}
-		\papervar{R_2}{radius of curvature of surface closest to image}{\meter}
-		\papervar{t}{axial thickness of lens}{\meter}
-	\end{paperwhere}
-
-	To obtain an expression for the focal length and refractive index of hemispheres and the sphere, \eqLensMakersFormula was used with appropriate radii.
-For a hemisphere with the flat side facing the source, \( R_1 = \infty \) and \( R_2 = - R \).
-	\papereq{HemisphereFlatSource}{\frac{1}{f} = \pars{n-1}{\frac{1}{R}}}{}
-
-	To model a hemisphere with the flat side facing away from the source, setting \( R_1 = -R \) and \( R_2 = - \infty \) yields \eqHemisphereFlatSource again.
-
-	Finally, a sphere with \( R_1 = R_2 = R \) was characterized by the formula below.
-	\papereq{Sphere}{\frac{1}{f} =\pars{\frac{n-1}{R}}^2\frac{t}{n} = \frac{2\pars{n-1}}{nR}}{}
-
-	The experimental setup consisted of an optical bench with a screen, holder for the lenses, a sliding calibrated measuring rod, and a light source mounted as shown.
-	\paperfig{Setup}{\pdf{setup} \vspace{-2.0em}}{The experimental setup with the smaller hemisphere mounted.} \vspace{0.5em}
-
-	The calibrated rod was used to measure the distance between the screen and either the flat side or the vertex of the lens, depending on the orientation with respect to the source.
-Each distance is obtained by finding the difference between the position of the rod holder while in contact with the screen (\figSetup) and with the lens, ensuring to account for screen thickness.
-Before making each measurement, the rod was aligned with the vertex of the lens to attain a more accurate result.
-
-	Of particular interest was the position on the bench where the image on the screen had a magnification \( m = -1 \) (i.e., same size as the source, inverted).
-This position corresponded to \( s_0 = s_i = 2f \), as evident from the Thin Lens Equation below.
-	\papereq{ThinLensEquation}{\frac{1}{s_0} + \frac{1}{s_i} = \frac{1}{f}}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{s_0}{object distance}{\meter}
-		\papervar{s_i}{image distance}{\meter}
-		\papervar{f}{focal length}{\meter}
-	\end{paperwhere}
-
-	While \eqThinLensEquation describes a thin lens in the paraxial region, it can be applied to a lens with nonzero thickness by taking \( s_0 \) to be the distance between the object and the first principle plane and \( s_i \) to be the distance between the image and the second principal plane.
+	Introduction goes here
 
@@
 
-	The difference in position of the calibrated rod was measured for two hemispheres and the sphere.
-The error of position readings was taken to be \( \pm .05 \si{\cm} \); uncertainty of the difference of positions was propagated using the method of quadratures.
-The difference accounts for the thickness of the screen, which was measured to be \( (1.75 \pm .02) \si{\mm} \) using a caliper.
-
-	\paperfig{HemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
-			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
-			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
-			\papertableindex\papertablecval{37.05}\papertablecval{28.95}\papertablecval{}\\\paperiline
-			\papertableindex\papertablecval{36.25}\papertablecval{28.40}\papertablecval{}\\\paperoline
-		\end{papertable}\vspace{-1.5em}}{Positions of the rod and the distance between screen and lens for the small hemisphere, flat surface facing the source.}
+	Observations go here
 
@@
 
-	Principal planes of a hemisphere and a sphere were visualized using the ray diagrams sketched below.
-
-	\paperfig{Hemisphere}{\pdf{hemisphere} \vspace{-1.5em} }{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a hemisphere.}
-
-	If the hemisphere is facing the light source with its curved side, the arrangement in \figHemisphere is mirrored with \( H_2 \) and \( H_1 \) being exchanged.
-This follows naturally from the Principle of Reversibility of light.
-
-	\paperfig{Sphere}{\pdf{sphere} \vspace{-2.0em}}{A sketch of locations of primary and secondary principal planes (\( H_1 \) and \( H_2 \) respectively) for a sphere.}
+	Analysis goes here
 
@@
 
-		Conclusion
+	Conclusion goes here
 
@@
 
-	Sources
+	\papersource{Serbanescu, R., The Thermocouple, 2013}
 

### 2018-01-23 lenses/paper.tex
added uncertainty to tables

@@
 \begin{document}
-\papertitle{Thick Lenses}
+\papertitle{Analysis of Refractive Indices of Thick Lenses}
 \paperauth{A}{Khesin}{1002442029}
@@
 		\papervar{n}{index of refraction of the first medium}{}
-		\papervar{n}{index of refraction of the second medium}{}
+		\papervar{n'}{index of refraction of the second medium}{}
 		\papervar{s}{object distance}{\meter}
@@
 		\papervar{n}{index of refraction of lens}{}
-		\papervar{R_1}{radius of curvature of surface closest to object}{\meter}
-		\papervar{R_2}{radius of curvature of surface closest to image}{\meter}
+		\papervar{R_1}{radius of curvature of surface near object}{\meter}
+		\papervar{R_2}{radius of curvature of surface near image}{\meter}
 		\papervar{t}{axial thickness of lens}{\meter}
@@
 	\paperfig{SmallHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
-			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
-			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
+			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
 			\papertableindex\papertablecval{37.05}\papertablecval{28.95}\papertablecval{7.92}\\\paperiline
@@
 	\paperfig{SmallHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
-			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
-			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+			\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
+			\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
 			\papertableindex\papertablecval{36.15}\papertablecval{29.50}\papertablecval{6.48}\\\paperiline
@@
 		\paperfig{LargeHemisphereFlatSource}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
-				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
-				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
+				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
 				\papertableindex\papertablecval{41.10}\papertablecval{31.00}\papertablecval{9.92}\\\paperiline
@@
 		\paperfig{LargeHemisphereFlatScreen}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
-				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
-				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
+				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
 				\papertableindex\papertablecval{41.85}\papertablecval{32.95}\papertablecval{8.72}\\\paperiline
@@
 		\paperfig{SphereData}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[outer]}
-				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\multirow{2}{*}{\textsc{\( \Delta d \)}}\\
-				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}&\\\paperiline
+				\paperoline\papertableindexheader&\textsc{Screen position}&\textsc{Lens position}&\textsc{\( \Delta d \)}\\
+				\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.05 cm}{\hspace{-0.5ex}}\papertablecheaderunit{.07 cm}{\hspace{-0.5ex}}\\\paperiline
 				\papertableindex\papertablecval{35.40}\papertablecval{30.40}\papertablecval{4.82}\\\paperiline

### 2018-01-23 thermocouple/paper.tex
Added calibration curve

@@
 
-	Analysis goes here
+	To calibrate the thermocouple, measured EMF values were plotted against the temperature difference between the junctions.
+Upon fitting the data using least squares method, the Seebeck coefficient was determined to be \( \pars{0.0410 \pm 0.0003} \si{\milli\volt\per\kelvin} \).
+The value of reduced \( \chi ^2 \) for this fit was \( 0.202632 \).
+The calibration curve, fit, and residuals are visualized below.
+
+	\paperfig{CalibrationCurve}{\pdf{ThermocoupleCalibration}}{EMF and residuals plotted against the temperature difference between the junctions.
+The curve has the function \(  \pars{0.0410 \pm 0.0003} \Delta T \) and an \( R^2 \) value of \( 0.998821 \).}
 

### 2018-01-23 thermocouple/calibration.py

@@ -1,5 +1,6 @@
 #!/usr/bin/python
-# 
+# Calibration curve of the thermocouple; estimates Seebeck constant using curve_fit
+
 # ---------- Import Statements ----------
 
 import numpy as np
@@ -56,7 +57,7 @@ plt.plot(T_diff, f(T_diff, *popt), color = "black", linewidth = 0.5)
 plt.title("Potential vs. temperature difference of a thermocouple")
 plt.xlim([-5, 105])
 plt.ylim([-0.5, 4.5])
-plt.ylabel("Potnetial (mV)")
+plt.ylabel("EMF (mV)")
 frame1.set_xticklabels([])
 plt.grid(True)
 # Residual plot
@@ -67,6 +68,6 @@ plt.ylim([-0.19, 0.19])
 plt.xlabel("Temperature difference (K)")
 plt.ylabel("Residuals")
 plt.grid(True)
-plt.savefig("ThermistorCalibration.pdf")
+plt.savefig("ThermocoupleCalibration.pdf")
 plt.show()
 

### 2018-01-25 thermocouple/paper.tex
added circuit diagram
Intro

@@
 
-	Introduction goes here
+	Thermocouples convert a temperature difference into an electromotive force (EMF), and are made of two wires of dissimilar metals which are joined at each end.
+The wires in a temperature gradient will allow the free carriers at the hot end have more kinetic energy and tend to diffuse towards the cold end, which will in turn create an electric field which has a averse tendency the heat flow.
+In this experiment, the temperature difference is measure of an ice bath which stays at constant temperature, and another body of water with temperature which will vary.
 
@@
 
-	Observations go here
+	Observations
 

### 2018-01-25 thermocouple/paper.tex
Stuff
added table

--- 2018-01-23 thermocouple/paper.tex
@@
 
+	The circuit used in the experiment was as follows.
+
+	\paperfig{Circuit}{\center
+	\begin{tikzpicture}[scale=0.7,transform shape]
+	\draw (1,0) to[voltmeter] (3,0) -- (3,1) -- (4,1) -- (4,2) -- (5,2)
+	(4,2) -- (4,3) -- (0,3) -- (0,2) -- (-1,2) -- (0,2) -- (0,1) -- (1,1) -- (1,0);
+	\draw (0.3,1.5) node[right]{$B$};
+	\draw (3.3,1.5) node[right]{$B$};
+	\draw (1.8,2.5) node[right]{$A$};
+	\draw (-1,2) node[left]{$T_1$};
+	\draw (5,2) node[right]{$T_2$};
+	\end{tikzpicture}
+	}{The circuit diagram used in the experiment.
+	The wire marked $A$ was made of Constantan and the wires marked $B$ were made of Copper.
+	The temperature difference was being measured between points $T_1$ and $T_2$.
+	The voltmeter shown at the bottom was used to measure the potential differences in the circuit.}
+
+	The temperature $T_1$ in the ice water bath was kept at a constant $(0.0\pm.5)\degree C$.
+	This value was occasionally remeasured during the experiment to make sure that it was unchanged.
+	The recorded values for the temperatures at $T_2$ and for the potential differences $V$ were recorded in the table below.
+
+	\paperfig{Table}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}\paperoline
+	\papertableindexheader&\multirow{2}{*}{\textsc{Temperature}\vspace{0.5em}}&\multirow{2}{*}{\textsc{Potential}\vspace{0.5em}}\\
+	\papertablecheadersymbol{T_2$ ($\si{\kelvin}$) $(\pm.5\si{\kelvin})}\papertablecheadersymbol{V$ ($\si{\volt}$) $(\pm.1\si{\volt})}\\\paperiline
+	\papertableindex\papertablecval{97.0}\papertablecval{4.0}\\\paperiline
+	\papertableindex\papertablecval{79.5}\papertablecval{3.3}\\\paperiline
+	\papertableindex\papertablecval{70.0}\papertablecval{2.9}\\\paperiline
+	\papertableindex\papertablecval{60.0}\papertablecval{2.4}\\\paperiline
+	\papertableindex\papertablecval{46.5}\papertablecval{1.9}\\\paperiline
+	\papertableindex\papertablecval{38.5}\papertablecval{1.5}\\\paperiline
+	\papertableindex\papertablecval{30.0}\papertablecval{1.2}\\\paperiline
+	\papertableindex\papertablecval{24.5}\papertablecval{1.0}\\\paperiline
+	\papertableindex\papertablecval{17.0}\papertablecval{0.7}\\\paperiline
+	\papertableindex\papertablecval{9.5}\papertablecval{0.3}\\\paperiline
+	\papertableindex\papertablecval{3.0}\papertablecval{0.1}\\\paperiline
+	\papertableindex\papertablecval{0.0}\papertablecval{0.0}\\\paperoline
+	\end{papertable}\vspace{-1em}}{The observations recorded during the experiment of the relationship between $T_2$ and $V$.
+	The value of $T_1$ was not included in the table as it was constant.}
+
 \papersec{Analysis}

### 2018-01-25 thermocouple/paper.tex
fixed degrees
added analysis of questions

@@
 \paperauth{A}{Khesin}{1002442029}
-\paperauth{N}{Rahnamaei}{STUDENT \#}
+\paperauth{N}{Rahnamaei}{1002552686}
 \paperauth{P}{Zavyalova}{1002345036}
@@
 	\papertableindexheader&\multirow{2}{*}{\textsc{Temperature}\vspace{0.5em}}&\multirow{2}{*}{\textsc{Potential}\vspace{0.5em}}\\
-	\papertablecheadersymbol{T_2$ ($\si{\kelvin}$) $(\pm.5\si{\kelvin})}\papertablecheadersymbol{V$ ($\si{\volt}$) $(\pm.1\si{\volt})}\\\paperiline
+	\papertablecheadersymbol{T_2$ ($\si{\celsius}$) $(\pm.5\si{\celsius})}\papertablecheadersymbol{V$ ($\si{\volt}$) $(\pm.1\si{\volt})}\\\paperiline
 	\papertableindex\papertablecval{97.0}\papertablecval{4.0}\\\paperiline
@@
 
+	In this experiment, the output resistance of the thermocouple was measured.
+	The value of this resistance was calculated to be $(1.8\pm.4)\si{\ohm}$.
+
+	The precision of any measurements made in this experiment could have been increased by using several thermocouples in series.
+	Since the differences in temperature between the endpoints of the thermocouples would have added up to the difference between the first and last endpoint, this would have measured the same value of temperature difference, but the fact that the temperature would be measured in many smaller pieces would increase the precision of the measurement.
+	The situation would be identical if a large distance more precisely by measuring many smaller intervals which together add to the longer distance.
+	Thus, there would be a advantage to connecting several thermocouples in series.
+
 \papersec{Conclusion}

### 2018-01-25 thermocouple/paper.tex
Anything

--- 2018-01-25 thermocouple/paper.tex
@@
 The wires in a temperature gradient will allow the free carriers at the hot end have more kinetic energy and tend to diffuse towards the cold end, which will in turn create an electric field which has a averse tendency the heat flow.
-In this experiment, the temperature difference is measure of an ice bath which stays at constant temperature, and another body of water with temperature which will vary.
-
-\papersec{Observations}
-
-	Observations go here
+In this experiment, the temperature difference was established between an ice bath staying at constant temperature, and another body of water with varying temperature.
 
@@
 
+\papersec{Observations}
+
 	The temperature $T_1$ in the ice water bath was kept at a constant $(0.0\pm.5)\degree C$.

### 2018-01-25 thermocouple/paper.tex

--- 2018-01-25 thermocouple/paper.tex
@@
 	The voltmeter shown at the bottom was used to measure the potential differences in the circuit.}
+
+\papersec{Observations}
 

### 2018-01-25 thermocouple/paper.tex
Added abstract

@@
 
-	Abstract goes here
+	In this experiment the EMF across a thermocouple was measured at a variety of temperatures to invesigate the Seebeck Effect.
+Plotting the obtained data on a calibration curve proved the expected linear relationship.
+Upon fitting the temperature differences to the potential using the least squares method, the Seebeck coefficient was determined to be \( \pars{0.0410 \pm 0.0003} \si{\milli\volt\per\kelvin} \).
+Further, the resistance of the thermocouple was measured to be $(1.8\pm.4)\si{\ohm}$.
 
@@
 In this experiment, the temperature difference was established between an ice bath staying at constant temperature, and another body of water with varying temperature.
+
+	EMF generated along the conductor is quantified by the Seebeck Effect, a proportionality law relating the potential and the temperature difference.
+	\papereq{Seebeck}{V = S\pars{T_1 - T_2}}{Serbanescu}
+	\begin{paperwhere}
+		\papervar{S}{Seebeck coefficient}{\volt\per\kelvin}
+		\papervar{T_1}{absolute temperature at first junction}{\kelvin}
+		\papervar{T_2}{absolute temperature at second junction}{\kelvin}
+	\end{paperwhere}
+
+	The experiment setup included a multimeter acting as a voltmeter, two thermal flasks to ensure that the temperature was kept constant and a thermometer all arranged as shown below.
+
+	\paperfig{setup}{\pdf{setup}}{}
 

### 2018-01-25 thermocouple/paper.tex
final version

@@
 
-	In this experiment the EMF across a thermocouple was measured at a variety of temperatures to invesigate the Seebeck Effect.
+	In this experiment the EMF across a thermocouple was measured at a variety of temperatures to investigate the Seebeck Effect.
 Plotting the obtained data on a calibration curve proved the expected linear relationship.
-Upon fitting the temperature differences to the potential using the least squares method, the Seebeck coefficient was determined to be \( \pars{0.0410 \pm 0.0003} \si{\milli\volt\per\kelvin} \).
+Upon fitting the temperature differences to the potential using the least squares method, the Seebeck coefficient was determined to be \( \pars{41.0 \pm .3} \si{\micro\volt\per\kelvin} \).
 Further, the resistance of the thermocouple was measured to be $(1.8\pm.4)\si{\ohm}$.
@@
 	\begin{paperwhere}
+		\papervar{V}{potential difference}{\volt}
 		\papervar{S}{Seebeck coefficient}{\volt\per\kelvin}
@@
 
-	The experiment setup included a multimeter acting as a voltmeter, two thermal flasks to ensure that the temperature was kept constant and a thermometer all arranged as shown below.
+	This equation is convenient as it is linear in both temperature difference and potential.
+	Temperatures were measured in degrees Celsius and compared to freezing, so they were equal to the temperature differences.
 
-	\paperfig{setup}{\pdf{setup}}{}
+	The experiment setup included a voltmeter, two thermal flasks to ensure that the temperature was kept constant and a thermometer all arranged as shown below.
+
+	\paperfig{setup}{\centering\includegraphics[width=0.9\columnwidth]{setup.pdf}}{The setup of the experiment.}
 
@@
 
-	\paperfig{Table}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}\paperoline
+	\paperfig{Table}{\centering\scalebox{0.9}[0.9]{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}\paperoline
 	\papertableindexheader&\multirow{2}{*}{\textsc{Temperature}\vspace{0.5em}}&\multirow{2}{*}{\textsc{Potential}\vspace{0.5em}}\\
@@
 	\papertableindex\papertablecval{0.0}\papertablecval{0.0}\\\paperoline
-	\end{papertable}\vspace{-1em}}{The observations recorded during the experiment of the relationship between $T_2$ and $V$.
+	\end{papertable}}\vspace{-0.5em}}{The observations recorded during the experiment of the relationship between $T_2$ and $V$.
 	The value of $T_1$ was not included in the table as it was constant.}
@@
 	To calibrate the thermocouple, measured EMF values were plotted against the temperature difference between the junctions.
-Upon fitting the data using least squares method, the Seebeck coefficient was determined to be \( \pars{0.0410 \pm 0.0003} \si{\milli\volt\per\kelvin} \).
+Upon fitting the data using least squares method, the Seebeck coefficient was determined to be \( \pars{41.0 \pm .3} \si{\milli\volt\per\kelvin} \).
 The value of reduced \( \chi ^2 \) for this fit was \( 0.202632 \).
@@
 	\paperfig{CalibrationCurve}{\pdf{ThermocoupleCalibration}}{EMF and residuals plotted against the temperature difference between the junctions.
-The curve has the function \(  \pars{0.0410 \pm 0.0003} \Delta T \) and an \( R^2 \) value of \( 0.998821 \).}
+The curve has the function \(  \pars{0.041.0 \pm 0.000.3} \Delta T \) and an \( R^2 \) value of \( 0.998821 \).}\columnbreak
 
@@
 
-	Conclusion goes here
+	The experiment investigated the Seebeck Effect.
+	Although the goodness of the obtained fit was quite high, the experiment was not free from sources of error.
+	In spite of the fact that the ice water bath temperature was occasionally measured, its temperature might have fluctuated during the experiment.
+	Furthermore, the construction and connections in the actual thermocouple itself could have been less than ideal.
+
+	The Seebeck coefficient was determined to be \( \pars{41.0 \pm .3} \si{\micro\volt\per\kelvin} \), close the value for Constantan, -35.
+Note that the sign of the coefficient is not relevant as it is obtained by flipping the poles of the voltmeter.
+Further, the resistance of the thermocouple was measured to be $(1.8\pm.4)\si{\ohm}$.
 

### 2018-01-25 polarization/exercise1.py
Exercise 1, 2 .py

@@ -1,0 +1,101 @@
+#!/usr/bin/python
+# Fits obtained data for two polarizers for Intensity vs. cos(theta) and
+# Intensity vs. (cos(theta)) ** 2
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Functions ----------
+
+# Fit function for optimizing #1
+# Intensity vs. cos(theta), a = I_0, initial intensity
+# (x, a) --> (f_value)
+# (float, float) --> (float)
+def f1(x, a):
+	return a * np.cos(x)
+
+# Fit function for optimizing #2
+# Intensity vs. (cos(theta)) ** 2, a = I_0, initial intensity
+# (x, a) --> (f_value)
+# (float, float) --> (float)
+def f2(x, a):
+	return a * np.cos(x) ** 2
+
+# ---------- Main Code ----------
+
+# Uncertainty in intensity
+I_unc = 0.01
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+path_to_file = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise1-1.txt"
+position, intensity = np.loadtxt(path_to_file, unpack = True)
+intensity_unc = np.full(intensity.size, I_unc)
+
+# Plot raw data
+plt.plot(position, intensity)
+plt.grid(True)
+plt.xlabel("Sensor Position (rad)")
+plt.ylabel("Light Intensity (V)")
+plt.title("Intensity vs. Position for Two Polarizers")
+plt.savefig("exercise1-data.pdf")
+plt.close()
+
+# Number of fit parameters
+num_parameters = 1
+# Find degrees of freedom for redeced chi squared
+ddof = intensity.size - num_parameters
+
+# Fit intensity vs. (cos(theta)) fitting
+print "Fitting to cos(theta)"
+popt, pcov = curve_fit(f1, position, intensity, sigma = intensity_unc)
+print "I_0:", popt[0], "+-", np.sqrt(pcov[0, 0])
+# Find residuals
+r = intensity - f1(position, *popt)
+chisq = np.sum((r / intensity_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
[…]

### 2018-01-25 polarization/exercise2-data.py

@@ -1,0 +1,26 @@
+#!/usr/bin/python
+# Creates a single data file for the three polarizer data (exercise 2)
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+# ---------- User-Defined Functions ----------
+
+# ---------- Main Code ----------
+
+path_to_file_1 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-1.txt"
+path_to_file_2 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-2.txt"
+pos_1, I_1 = np.loadtxt(path_to_file_1,unpack = True)
+pos_2, I_2 = np.loadtxt(path_to_file_2,unpack = True)
+
+# Shift second  
+pos_2 = pos_2 + np.amax(pos_1)
+
+position = np.concatenate((pos_1, pos_2))
+intensity = np.concatenate((I_1, I_2))
+
+plt.plot(position, intensity)
+plt.show()
+

### 2018-01-25 polarization/exercise2.py

@@ -1,0 +1,74 @@
+#!/usr/bin/python
+# Fits obtained data for three polarizers
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Functions ----------
+
+# Function for fitting:
+
+def f(x, a):
+	return (a / 4) * np.sin(2 * (x)) ** 2
+	# return (a / 4) * np.sin(2 * (x + np.pi / 4)) ** 2
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+# Concatenate data files to conver 360 degrees
+path_to_file_1 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-1.txt"
+path_to_file_2 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-2.txt"
+pos_1, I_1 = np.loadtxt(path_to_file_1,unpack = True)
+pos_2, I_2 = np.loadtxt(path_to_file_2,unpack = True)
+# Shift second  
+pos_2 = pos_2 + np.amax(pos_1)
+# Final data arrays
+position = np.concatenate((pos_1, pos_2))
+intensity = np.concatenate((I_1, I_2))
+
+# Uncertainty in intensity
+I_unc = 0.01
+intensity_unc = np.full(intensity.size, I_unc)
+
+# Number of fit parameters
+num_parameters = 1
+# Find degrees of freedom for redeced chi squared
+ddof = intensity.size - num_parameters
+
+# Fit intensity vs. (cos(theta)) fitting
+print "Fitting to sin(2(theta)) ** 2"
+popt, pcov = curve_fit(f, position, intensity, sigma = intensity_unc)
+print "I1:", popt[0], "+-", np.sqrt(pcov[0, 0])
+# Find residuals
+r = intensity - f(position, *popt)
+chisq = np.sum((r / intensity_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
+fig1 = plt.figure(1)
+# Plot data + model
[…]

### 2018-01-25 polarization/exercise3-filter.py
Cleaned up data + attempted to fit

@@ -1,0 +1,70 @@
+#!/bin/python
+# Filters data to get the maxima curve
+# Go back & fit using np.polyfit
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Function ----------
+
+# Fit function (quartic)
+def func(x, a, b, c, d, e): 
+	return a * x ** 4 + b * x ** 3 + c * x ** 2 + d * x + e
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+path_to_file = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-no-polarizer.txt"
+position_raw, intensity_raw = np.loadtxt(path_to_file, unpack = True)
+
+# Filtered arrays
+position = np.array([])
+intensity = np.array([])
+for i in range(0, position_raw.size):
+	# First data point for this position
+	if position_raw[i] not in position:
+		position = np.append(position, position_raw[i])
+		intensity = np.append(intensity, intensity_raw[i])
+	# Position aleready in array
+	else:
+		if intensity_raw[i] >= intensity[ np.where(position == position_raw[i])[0][0] ]:
+			intensity[ np.where(position == position_raw[i])[0][0] ] = intensity_raw[i]
+
+# Uncertainty in intensity
+I_unc = 0.01
+intensity_unc = np.full(intensity.size, I_unc)
+
+# Number of fit parameters
+num_parameters = 5
+# Find degrees of freedom for redeced chi squared
+ddof = intensity.size - num_parameters
+
+print np.sort(position)
+
+# Fit data
+popt, pcov = curve_fit(func, position, intensity, sigma = intensity_unc)
+# Find residuals
+r = intensity - func(position, *popt)
+chisq = np.sum((r / intensity_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
+fig1 = plt.figure(1)
+# Add raw data (all collected intensitites)
+frame1 = fig1.add_subplot(121)
+plt.scatter(position_raw, intensity_raw, s = 5, color = "black")
+plt.title("All data points")
[…]

### 2018-01-29 polarization/paper.tex
Started polarization paper

\input{header}
\physics
\begin{document}
\papertitle{Polarization of Light}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{February 1, 2018}
\begin{paperabs}

	Abstract goes here

\end{paperabs}

\begin{paper}

\papersec{Introduction}

	Classical optics treats light as a transverse electromagnetic wave for which the directions of oscillation of electric and magnetic fields are both orthogonal to the direction of propagation. A light wave is said to be polarized if it has a well-defined, albeit possibly time-dependent, direction of oscillation of the electric field, also commonly referred to as the optical field. Light may be polarized by shining it through a sheet of Polaroid, transmitting only one component of light about a certain direction, coined the transmission axis of the polarizer.

	In this experiment, ...

	The intensity of light passing through two polarizing element can be shown to be a function of the angle between their transmission axes, resulting in an expression known as Malus's law. 
	\papereq{MalusLaw}{I(\theta) = I_0 \cos^2 \pars{\theta}}{Serbanescu}
	\begin{paperwhere}
		\papervar{I_0}{intensity of incident light}{\volt}
		\papervar{\theta}{angle between transmission axes}{\degree}
	\end{paperwhere}

	In a two polarizing element setup, the first element is known as the \textit{polarizer}; the second is referred to as the \textit{analyzer}. As clearly seen from \eqMalusLaw, crossing the polarizer and the analyzer (i.e., \( \theta = 90 \si{\degree}\)) results in no light exiting the arrangement.

	In an extended setup including a third polarizer, with the transmission axes of the first and last polarizers at \( 90 \si{\degree} \), an expression for light intensity may be found by applying \eqMalusLaw twice; now, it is given in terms of \( \phi = 45 \si{\degree} + \Theta \), where \( \Theta \) is the measured angle.
	\papereq{ThreePolarizers}{I_3 = \frac{I_1}{4} \sin^2 \pars{2 \phi} }{}
	\begin{paperwhere}
		\papervar{I_1}{intensity after passing through the first polarizer}{\volt}
		\papervar{\phi}{angle between transmission axes of first and second polarizers}{\degree}
	\end{paperwhere}

	The underlying physical concept behind a Polaroid is dichroism, or selective absorption of light. Other mechanisms involved in polarization of light include scattering, birefringence, and reflection. Of particular interest in this experiment was polarization of light by reflection. For a light beam reflected at an air-glass interface, the Fresnel equations provide the reflection coefficients \( r_{\parallel} \) and \( r_{\perp} \).
	\papereq{ReflectionPerp}{r_{\perp} = \frac{n_1 \cos \theta_1 - n_2 \cos \theta_2}{n_1 \cos \theta_1 + n_2 \cos \theta_2}}{Serbanescu}
	\papereq{ReflectionParallel}{r_{\parallel} = \frac{n_1 \cos \theta_2 - n_2 \cos \theta_1}{n_1 \cos \theta_2 + n_2 \cos \theta_1}}{Serbanescu}
	\begin{paperwhere}
		\papervar{n_1}{refractive index of air}{}
		\papervar{n_2}{refractive index of glass}{}
		\papervar{\theta_1}{angle of incidence}{\degree}
		\papervar{\theta_2}{angle of refraction}{\degree}
	\end{paperwhere}

	The subscripts of the above coefficients reflect the orientation of the optical field of incident ray with respect to the plane of incidence. The reflectances of the rays are defined as the squares of the respective reflection coefficients. 
	\papereq{ReflectancePerp}{R_{\perp} = r_{\perp}^2}{Serbanescu}
	\papereq{ReflectanceParallel}{R_{\parallel} = r_{\parallel}^2}{Serbanescu}

	Finally, the angle of refraction is determined using Snell's law.
	\papereq{SnellsLaw}{n_1 \sin \theta_1 = n_2 \sin \theta_2}{Serbanescu}
	\begin{paperwhere}
		\papervar{n_1}{refractive index of air}{}
		\papervar{n_2}{refractive index of glass}{}
		\papervar{\theta_1}{angle of incidence}{\degree}
		\papervar{\theta_2}{angle of refraction}{\degree}
	\end{paperwhere}

	Reflected light is completely polarized with its optical field perpendicular to the plane of incidence when \( R_{\parallel} = 0 \). In this case, the angle between the reflected and refracted ray is \( 90 \si{\degree} \). The angle of incidence resulting in completely polarized light is known as the Brewster angle, or polarizing angle. An expression for \( \theta_p \) is derived from \eqSnellsLaw by making appropriate angle substitutions.
	\papereq{PolarizingAngle}{\tan \theta_p = \frac{n_2}{n_1}}{Serbanescu}

	This experiment verified Malus's law, \eqMalusLaw, for arrangements of two and three polarizers. In the former case, the laser, two polarizers (one with a rotary motion sensor) and the detector were setup such that maximum amount of light was allowed through without oversaturating the detector. Collecting intensity measurements involved unifromly rotating the polarizer with the rotary motion sensor through \( 180 \si{\degree} \). Data was collected using provided \textit{Polarization of Light} software.

	To verify Malus's law for three polarizers, two polarizers were initially arranged to achieve maximum intensity of transmitted light. Furter, a third polarizer with a rotary motion sensor was inserted between the two initial polarizers and rotated to obtain a minimum in the intensity of transmitted light. Intensity measurements were collected through \( 360 \si{\degree} \) using the provided software.

	The experimental arrangements for investigating polarization of light by reflection involved an acrylic semi-circular lens, a polarizer mounted on the optical bench, a spectrophotometer table with a rotary motion sensor and an optional square polarizer to be mounter on the spectrophotometer table. Furhter, a set of collimating slits was used for focusing the light beam. To calibrate the setup, \textbf{TODO}. The optical benches along with required optical elements are shown below \textbf{TODO}.

\papersec{Observations}

	Intensity of light passing through two polarizers was measured as a function of position. Uncertainties in intensities and positions were found by recording non-changing decimal points in the measurements provided by the software; uncertainty in intensity was determined to be \( \pm .01 \si{\volt} \), uncertainty in position was \( \pm \)\textbf{TODO}. Obtained data is visualized below.
	\paperfig{Exercise1Data}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are included but are too small to be visible.}

	Further, intensity vs. position of the rotary motion sensor of the middle polarizer was measured for three polarizers. Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm \)\textbf{TODO} respectively.
	\paperfig{Exercise2Data}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are not included \textbf{TODO} explain why.}

	Finally, intensity vs. position data was collected for the experimental setup measuring

\papersec{Analysis}

	Analysis goes here

\papersec{Conclusion}

	Conclusion goes here

\papersec{Sources}

	\papersource{Serbanescu, R., The Thermocouple, 2017}

\end{paper}

\end{document}

### 2018-01-29 polarization/exercise1.py

@@ -77,10 +77,22 @@ ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
 print "R^2:", r_squared
 
+# Plot and save raw data only
+plt.scatter(position, intensity, label = "Data", s = 10, color = "black")
+plt.errorbar(position, intensity, yerr = intensity_unc, linestyle = "None", color = "black")
+plt.title("Intensity vs. position for two polarizers")
+plt.xlabel("Sensor Position (rad)")
+plt.ylabel("Light Intensity (V)")
+plt.grid(True)
+plt.title("Intensity vs. position data for two polarizers")
+plt.savefig("exercise1-data.pdf")
+plt.show()
+plt.close()
+
 fig1 = plt.figure(1)
 # Plot data + model
 frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
-plt.scatter(position, intensity, label = "Data", s = 10, color = "black")
+plt.scatter(position, intensity, label = "Data", s = 5, color = "black")
 plt.errorbar(position, intensity, yerr = intensity_unc, linestyle = "None", color = "black")
 plt.plot(position, f2(position, *popt), label = "Model", color = "red")
 plt.title("Intensity vs. position for two polarizers")

### 2018-01-29 polarization/exercise2-data.py

@@ -20,7 +20,16 @@ pos_2 = pos_2 + np.amax(pos_1)
 
 position = np.concatenate((pos_1, pos_2))
 intensity = np.concatenate((I_1, I_2))
+# Uncertainty in intensity
+I_unc = 0.01
+intensity_unc = np.full(intensity.size, I_unc)
 
-plt.plot(position, intensity)
+plt.scatter(position, intensity, s= 5, color = "black")
+# plt.errorbar(position, intensity, yerr = intensity_unc, linestyle = "None", color = "black")
+plt.xlabel("Sensor Position (rad)")
+plt.ylabel("Light Intensity (V)")
+plt.title("Intensity vs. position data for three polarizers")
+plt.grid(True)
+plt.savefig("exercise2-data.pdf")
 plt.show()
 

### 2018-01-29 polarization/exercise3-filter.py

@@ -6,65 +6,70 @@
 
 import numpy as np
 import matplotlib.pyplot as plt
+import matplotlib
 from scipy.optimize import curve_fit
 
 # ---------- User-Defined Function ----------
 
-# Fit function (quartic)
-def func(x, a, b, c, d, e): 
-	return a * x ** 4 + b * x ** 3 + c * x ** 2 + d * x + e
-
 # ---------- Main Code ----------
 
 # Set desired font
-plt.rc('font', family = 'Times New Roman')
+# plt.rc('font', family = 'Times New Roman')
 path_to_file = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-no-polarizer.txt"
 position_raw, intensity_raw = np.loadtxt(path_to_file, unpack = True)
 
-# Filtered arrays
+# Sort the two original arrays
+permutation = position_raw.argsort()
+position_raw = position_raw[permutation]
+intensity_raw = intensity_raw[permutation]
+
 position = np.array([])
 intensity = np.array([])
-for i in range(0, position_raw.size):
-	# First data point for this position
-	if position_raw[i] not in position:
-		position = np.append(position, position_raw[i])
-		intensity = np.append(intensity, intensity_raw[i])
-	# Position aleready in array
+
+# Number of ipoints per interval for selecting max
+pts_per_interval = 300
+for i in range(0, position_raw.size, pts_per_interval):
+	# Check not working w/ last interval:
+	if i < position_raw.size - pts_per_interval:
+		temp_index = np.argmax(intensity_raw[i:i + pts_per_interval])
+		position = np.append(position, position_raw[i:i + pts_per_interval][temp_index])
+		intensity = np.append(intensity, intensity_raw[i:i + pts_per_interval][temp_index])
+	# Last interval
 	else:
-		if intensity_raw[i] >= intensity[ np.where(position == position_raw[i])[0][0] ]:
-			intensity[ np.where(position == position_raw[i])[0][0] ] = intensity_raw[i]
+		temp_index = np.argmax(intensity_raw[i:])
+		position = np.append(position, position_raw[i:][temp_index])
+		intensity = np.append(intensity, intensity_raw[i:][temp_index])
 
-# Uncertainty in intensity
-I_unc = 0.01
-intensity_unc = np.full(intensity.size, I_unc)
[…]

### 2018-01-29 circuit-elements/paper.tex
Added polarization data plots

@@
 \begin{paperabs}
-
-	% a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a a
-
 	The relationships between current, potential, resistance, and temperature are of particular interest in nonlinear circuit components.
 In this experiment, these physical quantities were investigated for a thermistor and an incandescent light bulb.
-For the thermistor, resistance was found to decrease exponentially as temperature increased, following the relation \( R = \pars{1.0 \pm 0.1} \times 10^{13}e^{-T/\pars{24.7 \pm 0.3}} \).
-The relationship between potential and current of the light bulb was determined to obey a power law, \( V = \pars{0.067 \pm 0.002} I^{\pars{1.63 \pm 0.01}} \).
-Further, the exponential relational constant in Stefan-Boltzmann law was approximated to be \( 4.17 \pm 0.05 \).
+For the thermistor, resistance was found to decrease exponentially as temperature increased, following the relation \( R = \pars{1.0 \pm .1} \times 10^{13}e^{-T/\pars{24.7 \pm .3}} \).
+The relationship between potential and current of the light bulb was determined to obey a power law, \( V = \pars{0.067 \pm .002} I^{\pars{1.63 \pm .01}} \).
+Further, the exponential relational constant in Stefan-Boltzmann law was found to be $\pars{4.17\pm.05}$.
 
@@
 	The purpose of this experiment was to study the relationship between voltage and current for a thermistor and an incandescent lamp.
-Both of these circuit elements are nonlinear; for a thermistor, the resistance is a function of temperature and obeys the relation
+These circuit elements are nonlinear; for a thermistor, resistance is a function of temperature and obeys the following relation.
 
@@
 	The relation in (1) was investigated using a multimeter, a thermistor, a thermometer and a thermal flask for maintaining the thermistor at different temperatures, set up as shown below.
-Temperature of the thermistor was decreased by adding cold water to the thermal flask and stirring to ensure uniform temperature in the flask.
+Temperature of the thermistor was decreased by adding cold water to the thermal flask and stirring to ensure it was uniform.
 \vspace{-0.8em}
@@
 As the temperature increases, however, the resistance of the metal increases and above a certain temperature becomes proportional to the absolute temperature.
-The actual relationship between \( V \) and \( I \) is investigated in this experiment by fitting obtained measurements of current and potential to
+The actual relationship between \( V \) and \( I \) was investigated in this experiment by fitting obtained measurements of current and potential to the following.
 
@@
 
-	The current-potential data obtained for an incandescent light bulb was further used to determine the value of \( n \) in the Stefan-Boltzmann law,
+	The current-potential data obtained for an incandescent light bulb was further used to determine the value of \( n \) in the Stefan-Boltzmann law.
 
@@
 
-	Further, the value of \( n \) was obtained.
 	Using the expression in (3) and assuming thermal equilibrium, \( \kappa \) and \( T \) were expressed in terms of \( I \) and \( V \).
@@
 	The resistance of the thermistor at various temperatures was measured.
-The uncertainty, as specified by the manufacturer, was $ \pm (0.2\% + 1 $ LSD) for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
-The reading error of the thermometer was taken to be $ \pm 0.5 \si{\kelvin} $.
+The uncertainty, as specified by the manufacturer, was $ \pm (.2\% + 1 $ LSD) for resistances in the $ (2 \si{\kilo\ohm}, 200 \si{\kilo\ohm}) $ range.
+The reading error of the thermometer was taken to be $ \pm .5 \si{\kelvin} $.
 \vspace{0.5em}
@@
 			\paperoline\papertableindexheader&\textsc{Temperature}&\multicolumn{2}{c|[outer]}{\textsc{Resistance}}\\
-			\papertablecheadersymbol{T$ $(\pm0.5$ $\si{\kelvin})}\papertableuheadersymbole{R$ $(\si{\kilo\ohm})}\\\paperiline
+			\papertablecheadersymbol{T$ $(\pm.5$ $\si{\kelvin})}\papertableuheadersymbole{R$ $(\si{\kilo\ohm})}\\\paperiline
 			\papertableindex\papertablecval{352.5}\papertableuval{6.68}{.02}\\\paperiline
@@
 	Further, current and potential for a tungsten filament light bulb were measured and recorded.
-As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (0.25\% + 1 \) LSD); current measurements carried an uncertainty of \( \pm (1\% + 3 \) LSD).
+As specified by the manufacturer, the uncertainty in potential measurements was taken to be \( \pm (.25\% + 1 \) LSD); current measurements carried an uncertainty of \( \pm (1\% + 3 \) LSD).
 \vspace{0.5em}
@@
 	Upon propagating uncertainties in the obtained data using the method of quadratures, the relationship between the temperature and resistance of a thermistor was calculated using the expression in (1) as the model function.
-Least squares fitting of all data points yielded \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \) as the fit parameters, with a reduced \( \chi ^ 2 \) value of \( 252.1710 \).
-The data, model, and residuals for this fit are shown below.
+Least squares fitting of all data points yielded \( R_0 = (1.0 \pm .1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm .3) \si{\kelvin} \) as the fit parameters, with a reduced \( \chi ^ 2 \) value of \( 252.1710 \).
+The data, fit, and residuals are shown below.
+
+	A visualization of residuals  indicated that the data can be better modeled at higher temperatures.
+Least squares fitting without the data points corresponding to three lowest temperatures yielded a reduced \( \chi ^ 2 \) value of \( 181.5543 \).
+Removing more lower-temperature points improved it further.
 
 	\paperfig{thermistor-plot}{\pdf{Thermistor}}{Resistance and residuals plotted against the temperature in the thermal flask.
-The curve has the function \( (1.0 \pm 0.1) \times 10^{13}e^\frac{T}{\pars{24.7 \pm 0.3}} \) and an \( R^2 \) value of 0.992783.
-Error bars on both temperature and resistance were included but were too small to be visible.} \vspace{1em}
-
-	A visualization of residuals clearly indicated that the data can be better modelled for greater temperatures.
-Indeed, least squares fitting performed without the data points corresponding to three lowest temperatures yielded a reduced \( \chi ^ 2 \) value of \( 181.5543 \).
-Removing more lower-temperature data points further improved reduced \( \chi ^ 2 \).
-	% Removing the six lower-temperature points led to a model with reduced \( \chi ^ 2 \) value of \( 130.1026 \).
+The curve has the function \( (1.0 \pm .1) \times 10^{13}e^{T/\pars{24.7 \pm .3}} \) and an \( R^2 \) value of 0.992783.
+Error bars on both temperature and resistance were included but were too small to be visible.}
 
 	Further, a least squares fitting was performed on the data obtained for the incandescent light bulb, with the expression in (2) used as a model function.
-The formula was found to hold; the resulting parameters were \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = (1.63 \pm 0.01) \).
+The formula was found to hold; the resulting parameters were \( k =  (0.067 \pm .002) \si{\volt\per\ampere} \) and \( a = (1.63 \pm .01) \).
 The value of reduced \( \chi ^ 2 \) obtained was \( 176.8952 \).
@@
 	\paperfig{bulb-plot}{\pdf{Bulb}}{Potential and residuals plotted against current through the incandescent bulb.
-The curve has the function \( \pars{0.067 \pm 0.002} I^{\pars{1.63 \pm 0.01}} \) with an \( R^2 \) value of \( 0.999532 \).
-Error bars on the data points were included but were too small to be visible.} \vspace{1em}
+The curve has the function \( \pars{0.067 \pm .002} I^{\pars{1.63 \pm .01}} \) with an \( R^2 \) value of \( 0.999532 \).
+Error bars on the data points were included but were too small to be visible.}
 
@@
 	Upon obtaining the value of \( a \), the universal constant \( n \) in Stefan-Boltzmmann law could be approximated.
-Plugging \( a = (1.63 \pm 0.01) \) into (6) yielded \( 4.17 \pm 0.05 \) (uncertainty propagated using the method  of quadratures), which was close the actual value of \( n = 4\).
+Plugging \( a = (1.63 \pm .01) \) into (6) yielded $\pars{4.17\pm.05}$ (uncertainty propagated using the method  of quadratures), which was close the actual value of \( n = 4\).
 Another constant appearing in Stefan-Boltzmann law, \( \epsilon \) (emissivity of the radiating body), differs depending on the material.
@@
 
-		This experiment has investigated two nonlinear circuit elements, a thermistor and an incandescent tungsten filament light bulb.
-Resistance of the thermistor was found to be a function of the temperature, satisfying the exponential relation in (1) with \( R_0 = (1.0 \pm 0.1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm 0.3) \si{\kelvin} \).
-For the light bulb, the relationship between potential and current was shown to follow a power law introduced in (2), with \( k =  (0.067 \pm 0.002) \si{\volt\per\ampere} \) and \( a = \pars{1.63 \pm 0.01} \).
-The most significant sources of error arose from potential uneven temperature of water in the thermal flask with the thermistor and inconsistencies in current and potential readings of the multimeter when switching the range of input signal.
+		This experiment has investigated two nonlinear circuit elements, a thermistor and an incandescent tungsten filament light bulb.\vfill\phantom{.}\columnbreak\noindent Resistance of the thermistor was found to be a function of the temperature, satisfying the exponential relation in (1) with \( R_0 = (1.0 \pm .1) \times 10^{13} \si{\ohm} \) and \( T_0 = (24.7 \pm .3) \si{\kelvin} \).
+For the light bulb, the relationship between potential and current was shown to follow a power law introduced in (2), with \( k =  (0.067 \pm .002) \si{\volt\per\ampere} \) and \( a = \pars{1.63 \pm .01} \).
 
-		The above value of \( a \) was further used to approximate the power \( n \) of \( T \) in Stefan-Boltzmann law; \( n \) was found to be \( 4.17 \pm 0.05 \), reasonably close to the actual value of \( n = 4 \).
+		The most significant sources of error arose from potentially uneven temperature of water in the thermal flask with the thermistor where there could have been momentary hot or cold pockets and inconsistencies in current and potential readings of the multimeter when switching the range of input signal on the multimeters.
+
+		The above value of \( a \) was further used to approximate the power \( n \) of \( T \) in Stefan-Boltzmann law; \( n \) was found to be \( 4.17 \pm .05 \), reasonably close to the actual value of \( n = 4 \).
 
@@
 
-\papersource{}
-
 \end{paper}

### 2018-01-29 polarization/paper.tex
Added polarization data plots

@@
 
-	Finally, intensity vs. position data was collected for the experimental setup measuring
+	Finally, intensity vs. position data was collected for the experimental setup investigating polarization by reflection. Uncertainties were taken to be \textbf{TODO}. 
+	\paperfig{Exercise3-Data}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are not included \textbf{TODO} explain why.}
 

### 2018-01-29 polarization/exercise2-data.py

@@ -10,6 +10,8 @@ import matplotlib.pyplot as plt
 
 # ---------- Main Code ----------
 
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
 path_to_file_1 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-1.txt"
 path_to_file_2 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-2.txt"
 pos_1, I_1 = np.loadtxt(path_to_file_1,unpack = True)

### 2018-01-29 polarization/exercise3-filter.py

@@ -14,7 +14,7 @@ from scipy.optimize import curve_fit
 # ---------- Main Code ----------
 
 # Set desired font
-# plt.rc('font', family = 'Times New Roman')
+plt.rc('font', family = 'Times New Roman')
 path_to_file = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-no-polarizer.txt"
 position_raw, intensity_raw = np.loadtxt(path_to_file, unpack = True)
 

### 2018-01-29 polarization/paper.tex
Two polarizer analysis

@@
 
-	In this experiment, ...
+	In this experiment, \textbf{TODO}.
 
@@
 
-	Analysis goes here
+	To begin with, Malus's law was verified using the obtained data for two polarizers.
+Fitting the measured intensity and angles to \( \cos \theta \) using the least squares method yielded a poor fit characterized by a reduced \( \chi ^ 2 \) of \( 48020.4 \) and an \( R^2 \) value of \( -1.53364 \).
+Fitting the data to \eqMalusLaw instead (i.e.
+testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model.
+The fit parameter was determined to be \( I_0 = 3.8269 \pm 0.0008 \).
+A visualization of the fit along with residuals is shown below.
+	\paperfig{Exercise1Fit}{\pdf{exercise1-model}}{Light intensity and and fit residuals plotted against the angular position of the sensor for the two polarizer setup.
+The curve in red has the function \( 3.8269 \pm 0.0008 \cos ^ 2 \theta \).
+Error bars were included but are too small to be visible.}
 

### 2018-01-29 polarization/exercise1.py

@@ -86,7 +86,7 @@ plt.ylabel("Light Intensity (V)")
 plt.grid(True)
 plt.title("Intensity vs. position data for two polarizers")
 plt.savefig("exercise1-data.pdf")
-plt.show()
+# plt.show()
 plt.close()
 
 fig1 = plt.figure(1)

### 2018-01-30 polarization/paper.tex
Fit for three polarizers

@@
 testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model.
-The fit parameter was determined to be \( I_0 = 3.8269 \pm 0.0008 \).
+The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm 0.0008} \).
 A visualization of the fit along with residuals is shown below.
 	\paperfig{Exercise1Fit}{\pdf{exercise1-model}}{Light intensity and and fit residuals plotted against the angular position of the sensor for the two polarizer setup.
-The curve in red has the function \( 3.8269 \pm 0.0008 \cos ^ 2 \theta \).
+The curve in red has the function \( \pars{3.8269 \pm 0.0008} \cos ^ 2 \theta \); \( R ^ 2 \) value of the fit is \( 0.999548 \).
 Error bars were included but are too small to be visible.}
+
+	Further, the data obtained for three polarizers was fit to \eqThreePolarizers using the least squares method.
+The intentensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm 0.002} \si{\volt} \).
+Reduced \( \chi^2 \) was \( 3.422214 \); \( R^2 \) for this fit was \( 0.994677 \).
+	\paperfig{Exercise2Fit}{\pdf{exercise2-model}}{Intensity of light exiting the third polarizer and fit residuals vs.
+the angular position of the second polarizer.
+The curve has the function \( \pars{2.891 \pm 0.002} \sin^2 \pars{2\phi} \).
+\( R^2 \) of this fit was \( 0.994677 \).
+Error bars are not included due to \textbf{TODO}.}
+
+	\textbf{TODO}: questions for exercise 2.
+
+	\textbf{TODO}: discussion for exercise 3 (still need to finish code).
+
+	\textbf{TODO}: include python code using \texttt{texttt}? (Another section?)
 

### 2018-01-30 polarization/exercise2.py

@@ -59,7 +59,7 @@ frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
 plt.scatter(position, intensity, label = "Data", s = 10, color = "black")
 plt.title("Intensity vs. position for three polarizers")
 plt.ylabel("Light Intensity (V)")
-plt.plot(position, f(position, *popt))
+plt.plot(position, f(position, *popt), color = "red")
 frame1.set_xticklabels([])
 plt.grid(True)
 # Residual plot

### 2018-01-31 polarization/paper.tex
More analysis

@@
 Obtained data is visualized below.
-	\paperfig{Exercise1Data}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are included but are too small to be visible.}
+	\paperfig{ExerciseOneData}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are included but are too small to be visible.}
 
@@
 Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm \)\textbf{TODO} respectively.
-	\paperfig{Exercise2Data}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are not included \textbf{TODO} explain why.}
+	\paperfig{ExerciseTwoData}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are not included \textbf{TODO} explain why.}
 
 	Finally, intensity vs. position data was collected for the experimental setup investigating polarization by reflection. Uncertainties were taken to be \textbf{TODO}. 
-	\paperfig{Exercise3-Data}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are not included \textbf{TODO} explain why.}
+	\paperfig{ExerciseThreeData}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are not included \textbf{TODO} explain why.}
 
@@
 
-	\textbf{TODO}: questions for exercise 2.
+	\textbf{TODO} questions for exercise 2.
 
-	\textbf{TODO}: discussion for exercise 3 (still need to finish code).
+	To estimate the value of Brewster's angle \( \theta_p \), given by \eqPolarizingAngle, obtained experimental data for intensity of light vs.
+angular position of the sensor (\figExerciseThreeData) was filtered to include only the maximum intensity data points.
+A least squares fit on the obtained boundary points was then performed with a degree-7 polynomial as the model function.
 
-	\textbf{TODO}: include python code using \texttt{texttt}? (Another section?)
+	\textbf{TODO} include coefficients of polynomial, \( R^2 \), reduced \( \chi^2 \)
+
+	\paperfig{ExerciseThreeFit}{\pdf{exercise3-model}}{Intensity of light vs.
+angular position of the sensor for rays reflected off acrylic semi-circular block.
+Curve in red is a degree-7 polynomial; data was filtered by taking the maximum-intensity data point in 300-point intervals.}
+
+	\textbf{TODO} increase distance between plots to prevent ylabel from overlapping w/ left subplot.
+
+	\textbf{TODO} exercise 3 questions.
 

### 2018-01-31 polarization/paper.tex
various typos and papervar changes

--- 2018-01-30 polarization/paper.tex
@@
 \begin{document}
-\papertitle{Polarization of Light}
+\papertitle{Analysis of Light Intensity with Polarizers}
 \paperauth{A}{Khesin}{1002442029}
@@
 
-	The intensity of light passing through two polarizing element can be shown to be a function of the angle between their transmission axes, resulting in an expression known as Malus's law. 
+	The intensity of light passing through two polarizing elements can be shown to be a function of the angle between their transmission axes, resulting in an expression known as Malus's law. 
 	\papereq{MalusLaw}{I(\theta) = I_0 \cos^2 \pars{\theta}}{Serbanescu}
 	\begin{paperwhere}
-		\papervar{I_0}{intensity of incident light}{\volt}
-		\papervar{\theta}{angle between transmission axes}{\degree}
+		\papervar{I_0}{intensity of incident light}{}
+		\papervar{I}{intensity of transmitted light}{}
+		\papervar{\theta}{angle between transmission axes}{}
 	\end{paperwhere}
@@
 	\begin{paperwhere}
-		\papervar{I_1}{intensity after passing through the first polarizer}{\volt}
-		\papervar{\phi}{angle between transmission axes of first and second polarizers}{\degree}
+		\papervar{I_1}{intensity after first polarizer}{}
+		\papervar{I_3}{intensity of transmitted light}{}
+		\papervar{\phi}{angle between transmission axes of polarizers}{}
 	\end{paperwhere}
@@
 	\begin{paperwhere}
+		\papervar{r_{\perp}}{perpendicular reflection coefficient}{}
+		\papervar{r_{\parallel}}{parallel reflection coefficient}{}
 		\papervar{n_1}{refractive index of air}{}
 		\papervar{n_2}{refractive index of glass}{}
-		\papervar{\theta_1}{angle of incidence}{\degree}
-		\papervar{\theta_2}{angle of refraction}{\degree}
+		\papervar{\theta_1}{angle of incidence}{}
+		\papervar{\theta_2}{angle of refraction}{}
 	\end{paperwhere}
@@
 	\papereq{ReflectanceParallel}{R_{\parallel} = r_{\parallel}^2}{Serbanescu}
+	\begin{paperwhere}
+		\papervar{R_{\perp}}{perpendicular reflectance}{}
+		\papervar{R_{\parallel}}{parallel reflectance}{}
+	\end{paperwhere}
 
@@
 	\papereq{SnellsLaw}{n_1 \sin \theta_1 = n_2 \sin \theta_2}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{n_1}{refractive index of air}{}
-		\papervar{n_2}{refractive index of glass}{}
-		\papervar{\theta_1}{angle of incidence}{\degree}
-		\papervar{\theta_2}{angle of refraction}{\degree}
-	\end{paperwhere}
-
 	Reflected light is completely polarized with its optical field perpendicular to the plane of incidence when \( R_{\parallel} = 0 \).
@@
 
-	\papersource{Serbanescu, R., The Thermocouple, 2017}
+	\papersource{Serbanescu, R., Polarization of Light, 2017}
 
 \end{paper}
-
 \end{document}

### 2018-02-01 polarization/exercise3-filter.py
Reflectances for ex 3

@@ -53,11 +53,20 @@ test = polynomial_fit.deriv(2)(r_crit)
 # Find local minima (excluding endpoints)
 x_min = r_crit[test > 0]
 y_min = polynomial_fit(x_min)
+# Brewster's angle
 print "Minimum angle (Brewster angle):", x_min[0] / 2
 n1 = 1.00 	# Index of refraction of intial medium (air)
+# Determine refractive index of acrylic
 p_angle = x_min[0] / 2 * np.pi / 180.0
 n2 = n1 * np.tan(p_angle)
 print "Refractive index of acrylic:", n2
+
+# Determine reflection coefficients & reflectances
+theta_t = np.arcsin(n1 * np.sin(p_angle) / n2)		# Refracted angle
+r_perp = (n1 * np.cos(p_angle) - n2 * np.cos(theta_t)) / (n1 * np.cos(p_angle) + n2 * np.cos(theta_t))
+r_parallel = (n1 * np.cos(theta_t) - n2 * np.cos(p_angle)) / (n1 * np.cos(theta_t) + n2 * np.cos(p_angle))
+print "Normal reflectance:", r_perp ** 2
+print "Parallel reflectance:", r_parallel ** 2
 
 plt.scatter(position_raw, intensity_raw, s = 5, color = "black")
 plt.xlabel("Sensor Position (degrees)")

### 2018-02-01 polarization/exercise3-filter.py
Horizontal/vertical I plots

@@ -98,5 +98,30 @@ plt.xlim([94, 121])
 plt.ylim([0, 1.2])
 plt.gca().set_title('Filtered data')
 plt.savefig("exercise3-model.pdf")
-plt.show()
+plt.close()
 
+position_hor, intensity_hor = np.loadtxt("/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-horizontal.txt", unpack = True)
+position_vert, intensity_vert = np.loadtxt("/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-vertical.txt", unpack = True)
+
+position_hor = 120.0 - np.abs(180.0 - position_hor)
+position_vert = 120.0 - np.abs(180.0 - position_vert)
+
+# Plot horizontal polarizer intensity
+plt.scatter(position_hor, intensity_hor, s = 5, color = "black")
+plt.xlabel("Sensor Position (degrees)")
+plt.ylabel("Light Intentisty (V)")
+plt.title("Intensity vs. angluar position for horizontal polarizer")
+plt.grid(True)
+plt.savefig("exercise3-horizontal.pdf")
+plt.show()
+plt.close()
+
+# Plot horizontal polarizer intensity
+plt.scatter(position_vert, intensity_vert, s = 5, color = "black")
+plt.xlabel("Sensor Position (degrees)")
+plt.ylabel("Light Intentisty (V)")
+plt.title("Intensity vs. angluar position for vertical polarizer")
+plt.grid(True)
+plt.savefig("exercise3-vertical.pdf")
+plt.show()
+plt.close()

### 2018-02-01 polarization/paper.tex
very little left

@@
 
-	Abstract goes here
+	TODO Abstract
 
@@
 Light may be polarized by shining it through a sheet of Polaroid, transmitting only one component of light about a certain direction, coined the transmission axis of the polarizer.
-
-	In this experiment, \textbf{TODO}.
 
@@
 In the former case, the laser, two polarizers (one with a rotary motion sensor) and the detector were setup such that maximum amount of light was allowed through without oversaturating the detector.
-Collecting intensity measurements involved unifromly rotating the polarizer with the rotary motion sensor through \( 180 \si{\degree} \).
+Collecting intensity measurements involved uniformly rotating the polarizer with the rotary motion sensor through \( 180 \si{\degree} \).
 Data was collected using provided \textit{Polarization of Light} software.
@@
 	To verify Malus's law for three polarizers, two polarizers were initially arranged to achieve maximum intensity of transmitted light.
-Furter, a third polarizer with a rotary motion sensor was inserted between the two initial polarizers and rotated to obtain a minimum in the intensity of transmitted light.
+Further, a third polarizer with a rotary motion sensor was inserted between the two initial polarizers and rotated to obtain a minimum in the intensity of transmitted light.
 Intensity measurements were collected through \( 360 \si{\degree} \) using the provided software.
 
-	The experimental arrangements for investigating polarization of light by reflection involved an acrylic semi-circular lens, a polarizer mounted on the optical bench, a spectrophotometer table with a rotary motion sensor and an optional square polarizer to be mounter on the spectrophotometer table.
-Furhter, a set of collimating slits was used for focusing the light beam.
-To calibrate the setup, \textbf{TODO}.
-The optical benches along with required optical elements are shown below \textbf{TODO}.
+	The experimental arrangements for investigating polarization of light by reflection involved an acrylic D-lens, a polarizer mounted on the optical bench, a spectrophotometer table with a rotary motion sensor and an optional square polarizer to be mounter on the spectrophotometer table.
+Further, a set of collimating slits was used for focusing the light beam.
+To calibrate the setup, the polarizers were carefully rotated to ensure that their alignment was exactly as required, in addition to comparing the values listed on the outside (such as aligning a polarizer with the label 0, in the case of a vertical polarizer).
+The optical benches along with required optical elements are shown below.
+The experiment was carried out by rotating the platform with the detector while simultaneously rotating the D-lens to keep the reflected beam aligned with the detector.
+
+	\paperfig{Setup}{\pdf{setup}}{The setup used in the experiments.
+	Along the top track are the three polarizers used in the second part of the experiment.
+For the first part of the experiment, the middle polarizer was removed.
+For the first two experiments, a light source was placed on the left of the top track, which shone into the light detector on the right of the top track.
+For the Brewster's angle experiment, the bottom track was used.
+The light source (bottom right corner) shone through a polarizer (bottom right), collimating slits (bottom middle), reflected off of the D-lens (bottom left), and was detected by the detector (middle left).}
 
@@
 	Intensity of light passing through two polarizers was measured as a function of position.
-Uncertainties in intensities and positions were found by recording non-changing decimal points in the measurements provided by the software; uncertainty in intensity was determined to be \( \pm .01 \si{\volt} \), uncertainty in position was \( \pm \)\textbf{TODO}.
+Uncertainties in intensities and positions were found by recording non-changing decimal points in the measurements provided by the software; uncertainty in intensity was determined to be \( \pm .01 \si{\volt} \), uncertainty in position was \( \pm .02\).
 Obtained data is visualized below.
-	\paperfig{ExerciseOneData}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are included but are too small to be visible.}
+	\paperfig{ExerciseOneData}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are 3included but are too small to be visible.}
 
@@
 position of the rotary motion sensor of the middle polarizer was measured for three polarizers.
-Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm \)\textbf{TODO} respectively.
-	\paperfig{ExerciseTwoData}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are not included \textbf{TODO} explain why.}
+Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm .02\) respectively.
+	\paperfig{ExerciseTwoData}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are included but are too small to be visible.}
 
-	Finally, intensity vs. position data was collected for the experimental setup investigating polarization by reflection. Uncertainties were taken to be \textbf{TODO}. 
-	\paperfig{ExerciseThreeData}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are not included \textbf{TODO} explain why.}
+	Finally, intensity vs.
+position data was collected for the experimental setup investigating polarization by reflection.
+Uncertainties were taken to be \( \pm .01 \si{\volt} \) in intensity and \( \pm .02\) in position.
+	\paperfig{ExerciseThreeData}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are included but are too small to be visible.}
 
@@
 	To begin with, Malus's law was verified using the obtained data for two polarizers.
-Fitting the measured intensity and angles to \( \cos \theta \) using the least squares method yielded a poor fit characterized by a reduced \( \chi ^ 2 \) of \( 48020.4 \) and an \( R^2 \) value of \( -1.53364 \).
+Fitting the measured intensity and angles to \( \cos (\theta )\) using the least squares method yielded a poor fit characterized by a reduced \( \chi ^ 2 \) of \( 48020.4 \) and an \( R^2 \) value of \( -1.53364 \).
 Fitting the data to \eqMalusLaw instead (i.e.
 testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model.
-The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm 0.0008} \).
+The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm .0008} \).
 A visualization of the fit along with residuals is shown below.
-	\paperfig{Exercise1Fit}{\pdf{exercise1-model}}{Light intensity and and fit residuals plotted against the angular position of the sensor for the two polarizer setup.
-The curve in red has the function \( \pars{3.8269 \pm 0.0008} \cos ^ 2 \theta \); \( R ^ 2 \) value of the fit is \( 0.999548 \).
+	\paperfig{ExerciseOneFit}{\pdf{exercise1-model}}{Light intensity and fit residuals plotted against the angular position of the sensor for the two polarizer setup.
+The curve in red has the function \( \pars{3.8269 \pm .0008} \cos ^ 2( \theta )\); \( R ^ 2 \) value of the fit is \( 0.999548 \).
 Error bars were included but are too small to be visible.}
@@
 	Further, the data obtained for three polarizers was fit to \eqThreePolarizers using the least squares method.
-The intentensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm 0.002} \si{\volt} \).
+The intentensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm .002} \si{\volt} \).
 Reduced \( \chi^2 \) was \( 3.422214 \); \( R^2 \) for this fit was \( 0.994677 \).
-	\paperfig{Exercise2Fit}{\pdf{exercise2-model}}{Intensity of light exiting the third polarizer and fit residuals vs.
+	\paperfig{ExerciseTwoFit}{\pdf{exercise2-model}}{Intensity of light exiting the third polarizer and fit residuals vs.
 the angular position of the second polarizer.
-The curve has the function \( \pars{2.891 \pm 0.002} \sin^2 \pars{2\phi} \).
+The curve has the function \( \pars{2.891 \pm .002} \sin^2 \pars{2\phi} \).
 \( R^2 \) of this fit was \( 0.994677 \).
-Error bars are not included due to \textbf{TODO}.}
+Error bars are included but are too small to be visible.}
 
-	\textbf{TODO} questions for exercise 2.
+	The graph in \figExerciseTwoFit differs from the one in \figExerciseOneFit in two major ways.
+The first is that it has a frequency equal to double of the one in \figExerciseOneFit.
+The second is that it starts from a peak and descends, while the graph in \figExerciseOneFit does the opposite, by starting from a minimum.
 
+	The maximum transmission through the three polarizers can be calculated by maximizing \eqThreePolarizers.
+The peak is attained when the first and middle polarizer are $\SI{45}{\degree}$ apart.
+From the same equation, it can be seen that the minimum transmission is obtained when the first and middle polarizers are either $\SI{0}{\degree}$ or $\SI{90}{\degree}$ apart.
+
+	In the Brewster's angle experiment, the data was very noisy due to the fact that it is near impossible to rotate both the lens and the detector slowly while keeping the reflected light beam aligned with the detector.
 To estimate the value of Brewster's angle \( \theta_p \), given by \eqPolarizingAngle, obtained experimental data for intensity of light vs.
-angular position of the sensor (\figExerciseThreeData) was filtered to include only the maximum intensity data points.
-A least squares fit on the obtained boundary points was then performed with a degree-7 polynomial as the model function.
+angular position of the sensor (\figExerciseThreeData) was filtered to include only the maximum intensity data points, as those represented when the light beam was perfectly aligned with the detector.
+A least squares fit on the obtained boundary points was then performed with a cubic polynomial as the model function, which was deemed a good function to approximate the peak intensities of the data.
 
-	\textbf{TODO} include coefficients of polynomial, \( R^2 \), reduced \( \chi^2 \)
+	This function was chosen not to model the curve, but to find the minimum of the dip.
+The fit was deemed a good approximation as it had a reduced $\chi^2$ value of 2.00305 and an $R^2$ value of 0.983524.
+By taking the minimum of the polynomial, Brewster's angle was found to be $54.0\pm.5$, which resulted in a refractive index of $1.38\pm.01$ for acrylic.
+All uncertainties were propagated using the method of quadratures.
 
-	\paperfig{ExerciseThreeFit}{\pdf{exercise3-model}}{Intensity of light vs.
-angular position of the sensor for rays reflected off acrylic semi-circular block.
-Curve in red is a degree-7 polynomial; data was filtered by taking the maximum-intensity data point in 300-point intervals.}
-
-	\textbf{TODO} increase distance between plots to prevent ylabel from overlapping w/ left subplot.
+	\paperfig{ExerciseThreeFit}{\hspace{-4ex}\scalebox{1.2}[1.2]{\pdf{exercise3-model}}}{Intensity of light vs sensor position for rays reflected off acrylic D-lens.
+Curve in red is a cubic polynomial; data was filtered by taking the maximum-intensity data point in 300-point intervals.
+The fit had an $R^2$ value of 0.983524.
+Error bars were included but were too small to be visible.}
 
@@
 
-	Conclusion goes here
+	TODO Conclusion
 
@@
 \end{paper}
+
+TODO PYTHON CODE
 \end{document}

### 2018-02-01 polarization/exercise3-filter.py

@@ -15,7 +15,7 @@ from scipy.optimize import curve_fit
 
 # Set desired font
 plt.rc('font', family = 'Times New Roman')
-path_to_file = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-no-polarizer.txt"
+path_to_file = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise3-no-polarizer.txt"
 position_raw, intensity_raw = np.loadtxt(path_to_file, unpack = True)
 
 # Sort the two original arrays
@@ -41,8 +41,10 @@ for i in range(0, position_raw.size, pts_per_interval):
 		position = np.append(position, position_raw[i:][temp_index])
 		intensity = np.append(intensity, intensity_raw[i:][temp_index])
 
+position = position[1:]
+intensity = intensity[1:]
 # Fit filtered data to a polynomial
-coeffs =  np.polyfit(position, intensity, 7, full = False)
+coeffs =  np.polyfit(position, intensity, 3, full = False)
 polynomial_fit = np.poly1d(coeffs)
 intensity_fit = polynomial_fit(position)
 
@@ -53,11 +55,21 @@ test = polynomial_fit.deriv(2)(r_crit)
 # Find local minima (excluding endpoints)
 x_min = r_crit[test > 0]
 y_min = polynomial_fit(x_min)
-print "Minimum angle (Brewster angle):", x_min[0] / 2
+print("Coefficients:", coeffs)
+# Find residuals
+r = intensity - intensity_fit
+chisq = np.sum((r / 0.01) ** 2)
+print("Reduced chi squared:", chisq / (intensity.size - 4))
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print("R^2:", r_squared)
+print("Minimum angle (Brewster angle):", x_min[0] / 2)
 n1 = 1.00 	# Index of refraction of intial medium (air)
 p_angle = x_min[0] / 2 * np.pi / 180.0
 n2 = n1 * np.tan(p_angle)
-print "Refractive index of acrylic:", n2
+print("Refractive index of acrylic:", n2)
 
 plt.scatter(position_raw, intensity_raw, s = 5, color = "black")
 plt.xlabel("Sensor Position (degrees)")

### 2018-02-01 polarization/paper.tex
all done

@@
 \input{header}
+\usepackage{listings}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=Python,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true,
+  tabsize=3
+}
 \physics
@@
 
-	TODO Abstract
+	This experiment studied the effects of polarized light with two polarizers,three polarizers, and an acrylic D-lens.
+This experiment used a light source paired with a detector to make these measurements.
+Lastly this experiment determined the amplitudes of the curves with two polarizers and with three polarizers, as well as Brewster's angle, the index of refraction, the perpendicular reflectance and the parallel reflectance for an acrylic D-lens.
+The values for these were determined to be $(3.8269 \pm .0008)\si{\volt}$, $(2.891 \pm .002) \si{\volt}$, $(54.0\pm.5)\si{\degree}$, $(1.38\pm.03)$, $(0.1\pm.01)$, and $(0\pm8)\si{E-6}$, respectively.
 
@@
 
-	The intensity of light passing through two polarizing elements can be shown to be a function of the angle between their transmission axes, resulting in an expression known as Malus's law. 
+	The intensity of light passing through two polarizers is a function of the angle between their transmission axes, resulting in an expression known as Malus's law. 
 	\papereq{MalusLaw}{I(\theta) = I_0 \cos^2 \pars{\theta}}{Serbanescu}
 	\begin{paperwhere}
-		\papervar{I_0}{intensity of incident light}{}
-		\papervar{I}{intensity of transmitted light}{}
+		\papervar{I_0}{intensity of incident light}{\volt}
+		\papervar{I}{intensity of transmitted light}{\volt}
 		\papervar{\theta}{angle between transmission axes}{}
@@
 	In an extended setup including a third polarizer, with the transmission axes of the first and last polarizers at \( 90 \si{\degree} \), an expression for light intensity may be found by applying \eqMalusLaw twice; now, it is given in terms of \( \phi = 45 \si{\degree} + \Theta \), where \( \Theta \) is the measured angle.
+
 	\papereq{ThreePolarizers}{I_3 = \frac{I_1}{4} \sin^2 \pars{2 \phi} }{}
 	\begin{paperwhere}
-		\papervar{I_1}{intensity after first polarizer}{}
-		\papervar{I_3}{intensity of transmitted light}{}
+		\papervar{I_1}{intensity after first polarizer}{\volt}
+		\papervar{I_3}{intensity of transmitted light}{\volt}
 		\papervar{\phi}{angle between transmission axes of polarizers}{}
@@
 Of particular interest in this experiment was polarization of light by reflection.
-For a light beam reflected at an air-glass interface, the Fresnel equations provide the reflection coefficients \( r_{\parallel} \) and \( r_{\perp} \).
+For a light beam reflected at an air-glass interface, the Fresnel equations provide the values for the reflection coefficients \( r_{\parallel} \) and \( r_{\perp} \).
+
 	\papereq{ReflectionPerp}{r_{\perp} = \frac{n_1 \cos \theta_1 - n_2 \cos \theta_2}{n_1 \cos \theta_1 + n_2 \cos \theta_2}}{Serbanescu}
@@
 The reflectances of the rays are defined as the squares of the respective reflection coefficients.
-	\papereq{ReflectancePerp}{R_{\perp} = r_{\perp}^2}{Serbanescu}
+	\papereq{ReflectancePerp}{R_{\perp} = r_{\perp}^2}{Serbanescu}\vspace{-1em}
 	\papereq{ReflectanceParallel}{R_{\parallel} = r_{\parallel}^2}{Serbanescu}
@@
 The experiment was carried out by rotating the platform with the detector while simultaneously rotating the D-lens to keep the reflected beam aligned with the detector.
-
-	\paperfig{Setup}{\pdf{setup}}{The setup used in the experiments.
+	\paperfig{Setup}{\vspace{-1em}\pdf{setup}\vspace{-2em}}{The setup used in the experiments.
 	Along the top track are the three polarizers used in the second part of the experiment.
@@
 	Intensity of light passing through two polarizers was measured as a function of position.
-Uncertainties in intensities and positions were found by recording non-changing decimal points in the measurements provided by the software; uncertainty in intensity was determined to be \( \pm .01 \si{\volt} \), uncertainty in position was \( \pm .02\).
-Obtained data is visualized below.
-	\paperfig{ExerciseOneData}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are 3included but are too small to be visible.}
+Uncertainties were detemined to be \( \pm .01 \si{\volt} \) in intensity and \( \pm .02\si{\degree}\) in position.
+
+	\paperfig{ExerciseOneData}{\pdf{exercise1-data}\vspace{-1em}}{Intensity of light as a function of rotary sensor position for two polarizers.
+Error bars are 3included but are too small to be visible.}\pagebreak
 
@@
 position of the rotary motion sensor of the middle polarizer was measured for three polarizers.
-Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm .02\) respectively.
+Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm .02\si{degree}\) respectively.
 	\paperfig{ExerciseTwoData}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are included but are too small to be visible.}
 
-	Finally, intensity vs.
-position data was collected for the experimental setup investigating polarization by reflection.
-Uncertainties were taken to be \( \pm .01 \si{\volt} \) in intensity and \( \pm .02\) in position.
+	Finally, intensity vs position data was collected for the experimental setup investigating polarization by reflection.
+Uncertainties were taken to be \( \pm .01 \si{\volt} \) in intensity and \( \pm .02\si{degree}\) in position.
 	\paperfig{ExerciseThreeData}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are included but are too small to be visible.}
 
+	The same data was also collected with a square polarizer in front of the detector.
+This allowed for the values of $I_{\perp}$ (when the polarizer was aligned vertically) and $I_{\parallel}$ (when the polarizer was aligned horizontally) to be measured.
+	\paperfig{Vertical}{\pdf{exercise3-vertical}}{Perpendicular intensity of reflected ray ($I_{\perp}$) as a function of position of the rotary motion sensor.
+Error bars are included but are too small to be visible.}
+	\paperfig{Horizontal}{\pdf{exercise3-horizontal}}{Parallel intensity of reflected ray ($I_{\parallel}$) as a function of position of the rotary motion sensor.
+Error bars are included but are too small to be visible.}
+
 \papersec{Analysis}
+
+	All Python programs used for analysis of data were appended at the end of this paper.
 
@@
 testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model.
-The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm .0008} \).
-A visualization of the fit along with residuals is shown below.
+The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm .0008} \si{\volt}\).
+A visualization of the fit along with residuals is shown below.\pagebreak
+
 	\paperfig{ExerciseOneFit}{\pdf{exercise1-model}}{Light intensity and fit residuals plotted against the angular position of the sensor for the two polarizer setup.
@@
 	Further, the data obtained for three polarizers was fit to \eqThreePolarizers using the least squares method.
-The intentensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm .002} \si{\volt} \).
+The intensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm .002} \si{\volt} \).
 Reduced \( \chi^2 \) was \( 3.422214 \); \( R^2 \) for this fit was \( 0.994677 \).
@@
 
-	This function was chosen not to model the curve, but to find the minimum of the dip.
-The fit was deemed a good approximation as it had a reduced $\chi^2$ value of 2.00305 and an $R^2$ value of 0.983524.
-By taking the minimum of the polynomial, Brewster's angle was found to be $54.0\pm.5$, which resulted in a refractive index of $1.38\pm.01$ for acrylic.
-All uncertainties were propagated using the method of quadratures.
-
 	\paperfig{ExerciseThreeFit}{\hspace{-4ex}\scalebox{1.2}[1.2]{\pdf{exercise3-model}}}{Intensity of light vs sensor position for rays reflected off acrylic D-lens.
@@
 
-	\textbf{TODO} exercise 3 questions.
+	This function was chosen not to model the curve, but to find the minimum of the dip.
+The fit was deemed a good approximation as it had a reduced $\chi^2$ value of 2.00305 and an $R^2$ value of 0.983524.
+By taking the minimum of the polynomial, Brewster's angle was found to be $(54.0\pm.5)\si{\degree}$, which resulted in a refractive index of $(1.38\pm.03)$ for acrylic through \eqPolarizingAngle.
+All uncertainties were propagated using the method of quadratures.
+
+	With \eqReflectionPerp, \eqReflectionParallel, \eqReflectancePerp, and \eqReflectanceParallel, the values of $R_{\perp}$ and $R_{\parallel}$ were derived to be $(0.1\pm.01)$ and $(0\pm8)\SI{E-6}{}$, respectively.
+These values are reasonable as $R_{\parallel}$ is indeed expected to be 0 at Brewster's angle.
+All uncertainties were propagated using the method of quadratures.
+
+	The refraction index of water is slightly lower than the obtained value for acrylic so if the light was reflecting off of water, Brewster's angle would be slightly smaller as per \eqPolarizingAngle.
+The data for an arrangement with a vertical square polarizer was recorded and shown above in \figVertical.
+The mechanism examined in this experiment demonstrates how polarized sunglasses reduce glare, which can come from polarized reflecting off of something like a pool of water.
+The polarization in the glasses is vertical, which keeps out a very large fraction of the incoming light.
+This can be checked by tilting one's head until the polarization in their sunglasses becomes parallel to the ground and seeing the glare from reflected light increase.
 
@@
 
-	TODO Conclusion
+	The experiment was successful in demonstrating the effects of light polarization.
+However, it was not free from sources of error.
+The most error-prone section was ensuring that the light beam was shining directly into the detector.
+This was especially noticeable for the experiment measuring Brewster's angle, where both the D-lens and the detector had to be constantly moved at different rates, meaning that a lot of data was recorded where the light beam was not shining directly at the detector.
+This was mitigated by using a program to only record the highest point of intervals of fixed width.
+
+	In conclusion, the experiment determined the value of $I_0$ in Malus's law for two polarizers to be $(3.8269 \pm .0008)\si{\volt}$.
+The experiment also determined the value of $I_1$ in \eqThreePolarizers to be $(2.891 \pm .002) \si{\volt}$.
+Finally, the experiment determined Brewster's angle, the index of refraction, the perpendicular reflectance and the parallel reflectance.
+The values for these were determined to be $(54.0\pm.5)\si{\degree}$, $(1.38\pm.03)$, $(0.1\pm.01)$, and $(0\pm8)\si{E-6}$, respectively.
 
@@
 \end{paper}
+\section*{Experiment 1 Code}
+\begin{lstlisting}
+#!/usr/bin/python
+# Fits obtained data for two polarizers for Intensity vs. cos(theta) and
+# Intensity vs. (cos(theta)) ** 2
 
-TODO PYTHON CODE
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Functions ----------
+
+# Fit function for optimizing #1
+# Intensity vs. cos(theta), a = I_0, initial intensity
+# (x, a) --> (f_value)
+# (float, float) --> (float)
+def f1(x, a):
+        return a * np.cos(x)
+
+# Fit function for optimizing #2
+# Intensity vs. (cos(theta)) ** 2, a = I_0, initial intensity
+# (x, a) --> (f_value)
+# (float, float) --> (float)
+def f2(x, a):
+        return a * np.cos(x) ** 2
+
+# ---------- Main Code ----------
+
+# Uncertainty in intensity
+I_unc = 0.01
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+path_to_file = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise1-1.txt"
+position, intensity = np.loadtxt(path_to_file, unpack = True)
+intensity_unc = np.full(intensity.size, I_unc)
+
+# Plot raw data
+plt.plot(position, intensity)
+plt.grid(True)
+plt.xlabel("Sensor Position (rad)")
+plt.ylabel("Light Intensity (V)")
+plt.title("Intensity vs. Position for Two Polarizers")
+plt.savefig("exercise1-data.pdf")
+plt.close()
+
+# Number of fit parameters
+num_parameters = 1
+# Find degrees of freedom for redeced chi squared
+ddof = intensity.size - num_parameters
+
+# Fit intensity vs. (cos(theta)) fitting
+print("Fitting to cos(theta)")
+popt, pcov = curve_fit(f1, position, intensity, sigma = intensity_unc)
+print("I_0:", popt[0], "+-", np.sqrt(pcov[0, 0]))
+# Find residuals
+r = intensity - f1(position, *popt)
+chisq = np.sum((r / intensity_unc) ** 2)
+print("Reduced chi squared:", chisq / ddof)
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print("R^2:", r_squared)
+
+# Fit intensity vs. (cos(theta)) ** 2 fitting
+print("Fitting to cos(theta) ** 2")
+popt, pcov = curve_fit(f2, position, intensity, sigma = intensity_unc)
+print("I_0:", popt[0], "+-", np.sqrt(pcov[0, 0]))
+# Find residuals
+r = intensity - f2(position, *popt)
+chisq = np.sum((r / intensity_unc) ** 2)
+print("Reduced chi squared:", chisq / ddof)
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print("R^2:", r_squared)
+
+# Plot and save raw data only
+plt.scatter(position, intensity, label = "Data", s = 10, color = "black")
+plt.errorbar(position, intensity, yerr = intensity_unc, linestyle = "None", color = "black")
+plt.title("Intensity vs. position for two polarizers")
+plt.xlabel("Sensor Position (rad)")
+plt.ylabel("Light Intensity (V)")
+plt.grid(True)
+plt.title("Intensity vs. position data for two polarizers")
+plt.savefig("exercise1-data.pdf")
+# plt.show()
+plt.close()
+
+fig1 = plt.figure(1)
+# Plot data + model
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+plt.scatter(position, intensity, label = "Data", s = 5, color = "black")
+plt.errorbar(position, intensity, yerr = intensity_unc, linestyle = "None", color = "black")
+plt.plot(position, f2(position, *popt), label = "Model", color = "red")
+plt.title("Intensity vs. position for two polarizers")
+plt.ylabel("Light Intensity (V)")
+#plt.xlim([-0.2, 3.2])
+frame1.set_xticklabels([])
+plt.grid(True)
+# Residual plot
+frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
+plt.scatter(position, r, s = 10, color = "black")
+plt.grid(True)
+plt.xlabel("Sensor Position (rad)")
+plt.ylabel("Residuals")
+#plt.xlim([-0.2, 3.2])
+#plt.ylim([-3, 9])
+plt.savefig("exercise1-model.pdf")
+plt.show()
+plt.close()
+\end{lstlisting}
+
+\subsection*{Code Output}
+\begin{lstlisting}
+Fitting to cos(theta)
+I_0: 1.57477106402 +- 0.0499865567274
+Reduced chi squared: 48020.3665806
+R^2: -1.53364393683
+Fitting to cos(theta) ** 2
+I_0: 3.82685141159 +- 0.000757737807859
+Reduced chi squared: 8.56035764563
+R^2: 0.999548339594
+\end{lstlisting}\vfill\pagebreak
+\section*{Experiment 2 Code}
+\begin{lstlisting}
+#!/usr/bin/python
+# Fits obtained data for three polarizers
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Functions ----------
+
+# Function for fitting:
+
+def f(x, a):
+        return (a / 4) * np.sin(2 * (x)) ** 2
+        # return (a / 4) * np.sin(2 * (x + np.pi / 4)) ** 2
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+# Concatenate data files to conver 360 degrees
+path_to_file_1 = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise2-1.txt"
+path_to_file_2 = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise2-2.txt"
+pos_1, I_1 = np.loadtxt(path_to_file_1,unpack = True)
+pos_2, I_2 = np.loadtxt(path_to_file_2,unpack = True)
+# Shift second
+pos_2 = pos_2 + np.amax(pos_1)
+# Final data arrays
+position = np.concatenate((pos_1, pos_2))
+intensity = np.concatenate((I_1, I_2))
+
+# Uncertainty in intensity
+I_unc = 0.01
+intensity_unc = np.full(intensity.size, I_unc)
+
+# Number of fit parameters
+num_parameters = 1
+# Find degrees of freedom for redeced chi squared
+ddof = intensity.size - num_parameters
+
+# Fit intensity vs. (cos(theta)) fitting
+print("Fitting to sin(2(theta)) ** 2")
+popt, pcov = curve_fit(f, position, intensity, sigma = intensity_unc)
+print("I1:", popt[0], "+-", np.sqrt(pcov[0, 0]))
+# Find residuals
+r = intensity - f(position, *popt)
+chisq = np.sum((r / intensity_unc) ** 2)
+print("Reduced chi squared:", chisq / ddof)
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print("R^2:", r_squared)
+
+fig1 = plt.figure(1)
+# Plot data + model
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+plt.scatter(position, intensity, label = "Data", s = 10, color = "black")
+plt.title("Intensity vs. position for three polarizers")
+plt.ylabel("Light Intensity (V)")
+plt.plot(position, f(position, *popt), color = "red")
+frame1.set_xticklabels([])
+plt.grid(True)
+# Residual plot
+frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
+plt.scatter(position, r, s = 10, color = "black")
+plt.grid(True)
+plt.xlabel("Sensor Position (rad)")
+plt.ylabel("Residuals")
+plt.savefig("exercise2-model.pdf")
+plt.show()
+plt.close()
+\end{lstlisting}
+
+\subsection*{Code Output}
+\begin{lstlisting}
+Fitting to sin(2(theta)) ** 2
+I1: 2.89097142639 +- 0.00168062019253
+Reduced chi squared: 3.42221396661
+R^2: 0.994676784893
+\end{lstlisting}\vfill\pagebreak
+\section*{Experiment 3 Code}
+\begin{lstlisting}
+#!/bin/python
+# Filters data to get the maxima curve
+# Go back & relabel angles --> software took them incorrectly
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Function ----------
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+path_to_file = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise3-no-polarizer.txt"
+position_raw, intensity_raw = np.loadtxt(path_to_file, unpack = True)
+
+# Sort the two original arrays
+permutation = position_raw.argsort()
+position_raw = position_raw[permutation]
+intensity_raw = intensity_raw[permutation]
+position_raw = 120.0 - np.abs(180.0 - position_raw)
+
+position = np.array([])
+intensity = np.array([])
+
+# Number of ipoints per interval for selecting max
+pts_per_interval = 300
+for i in range(0, position_raw.size, pts_per_interval):
+        # Check not working w/ last interval:
+        if i < position_raw.size - pts_per_interval:
+                temp_index = np.argmax(intensity_raw[i:i + pts_per_interval])
+                position = np.append(position, position_raw[i:i + pts_per_interval][temp_index])
+                intensity = np.append(intensity, intensity_raw[i:i + pts_per_interval][temp_index])
+        # Last interval
+        else:
+                temp_index = np.argmax(intensity_raw[i:])
+                position = np.append(position, position_raw[i:][temp_index])
+                intensity = np.append(intensity, intensity_raw[i:][temp_index])
+
+position = position[1:]
+intensity = intensity[1:]
+# Fit filtered data to a polynomial
+coeffs =  np.polyfit(position, intensity, 3, full = False)
+polynomial_fit = np.poly1d(coeffs)
+intensity_fit = polynomial_fit(position)
+
+# Find the local minima
+crit = polynomial_fit.deriv().r
+r_crit = crit[crit.imag==0].real
+test = polynomial_fit.deriv(2)(r_crit)
+# Find local minima (excluding endpoints)
+x_min = r_crit[test > 0]
+y_min = polynomial_fit(x_min)
+print("Coefficients:", coeffs)
+# Find residuals
+r = intensity - intensity_fit
+chisq = np.sum((r / 0.01) ** 2)
+print("Reduced chi squared:", chisq / (intensity.size - 4))
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print("R^2:", r_squared)
+# Brewster's angle
+print("Minimum angle (Brewster angle):", x_min[0] / 2)
+n1 = 1.00       # Index of refraction of intial medium (air)
+# Determine refractive index of acrylic
+p_angle = x_min[0] / 2 * np.pi / 180.0
+n2 = n1 * np.tan(p_angle)
+print("Refractive index of acrylic:", n2)
+
+# Determine reflection coefficients & reflectances
+theta_t = np.arcsin(n1 * np.sin(p_angle) / n2)          # Refracted angle
+r_perp = (n1 * np.cos(p_angle) - n2 * np.cos(theta_t)) / (n1 * np.cos(p_angle) + n2 * np.cos(theta_t))
+r_parallel = (n1 * np.cos(theta_t) - n2 * np.cos(p_angle)) / (n1 * np.cos(theta_t) + n2 * np.cos(p_angle))
+print("Normal reflectance:", r_perp ** 2)
+print("Parallel reflectance:", r_parallel ** 2)
+
+plt.scatter(position_raw, intensity_raw, s = 5, color = "black")
+plt.xlabel("Sensor Position (degrees)")
+plt.ylabel("Light Intentisty (V)")
+plt.ylim([0, 1.2])
+plt.title("Intensity vs. position, polarization by refraction")
+plt.grid()
+plt.savefig("exercise3-data.pdf")
+plt.show()
+plt.close()
+
+# Plot original (collected data)
+plt.subplot(121)
+plt.scatter(position_raw, intensity_raw, s = 5, color = "black")
+plt.plot(position, intensity_fit, color = "red")
+plt.xlabel("Sensor Position (degrees)")
+plt.ylabel("Light Intentisty (V)")
+plt.xlim([94, 121])
+plt.ylim([0, 1.2])
+plt.gca().set_title('Collected data')
+# Plot filtered data
+plt.subplot(122)
+plt.scatter(position, intensity, s = 5, color = "black")
+# plt.plot(x_min, y_min, "o")
+# plt.plot(position, intensity_fit, color = "red")
+plt.xlabel("Sensor Position (degrees)")
+plt.ylabel("Light Intensity (V)")
+plt.xlim([94, 121])
+plt.ylim([0, 1.2])
+plt.gca().set_title('Filtered data')
+plt.savefig("exercise3-model.pdf")
+plt.close()
+
+position_hor, intensity_hor = np.loadtxt("C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise3-horizontal.txt", unpack = True)
+position_vert, intensity_vert = np.loadtxt("C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise3-vertical.txt", unpack = True)
+
+position_hor = 120.0 - np.abs(180.0 - position_hor)
+position_vert = 120.0 - np.abs(180.0 - position_vert)
+
+# Plot horizontal polarizer intensity
+plt.scatter(position_hor, intensity_hor, s = 5, color = "black")
+plt.xlabel("Sensor Position (degrees)")
+plt.ylabel("Light Intentisty (V)")
+plt.title("Intensity vs. angluar position for horizontal polarizer")
+plt.grid(True)
+plt.savefig("exercise3-horizontal.pdf")
+plt.show()
+plt.close()
+
+# Plot horizontal polarizer intensity
+plt.scatter(position_vert, intensity_vert, s = 5, color = "black")
+plt.xlabel("Sensor Position (degrees)")
+plt.ylabel("Light Intentisty (V)")
+plt.title("Intensity vs. angluar position for vertical polarizer")
+plt.grid(True)
+plt.savefig("exercise3-vertical.pdf")
+plt.show()
+plt.close()
+\end{lstlisting}
+
+\subsection*{Code Output}
+\begin{lstlisting}
+Coefficients: [  7.78927076e-05  -2.35896116e-02   2.36977631e+00  -7.81328762e+01
+]
+Reduced chi squared: 2.00305497198
+R^2: 0.983523761927
+Minimum angle (Brewster angle): 53.9936461819
+Refractive index of acrylic: 1.37606099182
+Normal reflectance: 0.0953611776688
+Parallel reflectance: 4.708853396e-33
+\end{lstlisting}
 \end{document}

### 2018-02-01 polarization/exercise1.py

@@ -31,7 +31,7 @@ I_unc = 0.01
 
 # Set desired font
 plt.rc('font', family = 'Times New Roman')
-path_to_file = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise1-1.txt"
+path_to_file = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise1-1.txt"
 position, intensity = np.loadtxt(path_to_file, unpack = True)
 intensity_unc = np.full(intensity.size, I_unc)
 
@@ -50,32 +50,32 @@ num_parameters = 1
 ddof = intensity.size - num_parameters
 
 # Fit intensity vs. (cos(theta)) fitting
-print "Fitting to cos(theta)"
+print("Fitting to cos(theta)")
 popt, pcov = curve_fit(f1, position, intensity, sigma = intensity_unc)
-print "I_0:", popt[0], "+-", np.sqrt(pcov[0, 0])
+print("I_0:", popt[0], "+-", np.sqrt(pcov[0, 0]))
 # Find residuals
 r = intensity - f1(position, *popt)
 chisq = np.sum((r / intensity_unc) ** 2)
-print "Reduced chi squared:", chisq / ddof
+print("Reduced chi squared:", chisq / ddof)
 # Calculate and print R^2
 ss_res = np.sum(r ** 2)
 ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
-print "R^2:", r_squared
+print("R^2:", r_squared)
 
 # Fit intensity vs. (cos(theta)) ** 2 fitting
-print "Fitting to cos(theta) ** 2"
+print("Fitting to cos(theta) ** 2")
 popt, pcov = curve_fit(f2, position, intensity, sigma = intensity_unc)
-print "I_0:", popt[0], "+-", np.sqrt(pcov[0, 0])
+print("I_0:", popt[0], "+-", np.sqrt(pcov[0, 0]))
 # Find residuals
 r = intensity - f2(position, *popt)
 chisq = np.sum((r / intensity_unc) ** 2)
-print "Reduced chi squared:", chisq / ddof
+print("Reduced chi squared:", chisq / ddof)
 # Calculate and print R^2
 ss_res = np.sum(r ** 2)
 ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
-print "R^2:", r_squared
[…]

### 2018-02-01 polarization/exercise2.py

@@ -20,8 +20,8 @@ def f(x, a):
 # Set desired font
 plt.rc('font', family = 'Times New Roman')
 # Concatenate data files to conver 360 degrees
-path_to_file_1 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-1.txt"
-path_to_file_2 = "/home/polina/Documents/3rd_Year/PHY324/polarization/exercise2-2.txt"
+path_to_file_1 = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise2-1.txt"
+path_to_file_2 = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise2-2.txt"
 pos_1, I_1 = np.loadtxt(path_to_file_1,unpack = True)
 pos_2, I_2 = np.loadtxt(path_to_file_2,unpack = True)
 # Shift second  
@@ -40,18 +40,18 @@ num_parameters = 1
 ddof = intensity.size - num_parameters
 
 # Fit intensity vs. (cos(theta)) fitting
-print "Fitting to sin(2(theta)) ** 2"
+print("Fitting to sin(2(theta)) ** 2")
 popt, pcov = curve_fit(f, position, intensity, sigma = intensity_unc)
-print "I1:", popt[0], "+-", np.sqrt(pcov[0, 0])
+print("I1:", popt[0], "+-", np.sqrt(pcov[0, 0]))
 # Find residuals
 r = intensity - f(position, *popt)
 chisq = np.sum((r / intensity_unc) ** 2)
-print "Reduced chi squared:", chisq / ddof
+print("Reduced chi squared:", chisq / ddof)
 # Calculate and print R^2
 ss_res = np.sum(r ** 2)
 ss_tot = np.sum((intensity - np.mean(intensity)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
-print "R^2:", r_squared
+print("R^2:", r_squared)
 
 fig1 = plt.figure(1)
 # Plot data + model

### 2018-02-01 polarization/exercise3-filter.py

@@ -77,8 +77,8 @@ print("Refractive index of acrylic:", n2)
 theta_t = np.arcsin(n1 * np.sin(p_angle) / n2)		# Refracted angle
 r_perp = (n1 * np.cos(p_angle) - n2 * np.cos(theta_t)) / (n1 * np.cos(p_angle) + n2 * np.cos(theta_t))
 r_parallel = (n1 * np.cos(theta_t) - n2 * np.cos(p_angle)) / (n1 * np.cos(theta_t) + n2 * np.cos(p_angle))
-print "Normal reflectance:", r_perp ** 2
-print "Parallel reflectance:", r_parallel ** 2
+print("Normal reflectance:", r_perp ** 2)
+print("Parallel reflectance:", r_parallel ** 2)
 
 plt.scatter(position_raw, intensity_raw, s = 5, color = "black")
 plt.xlabel("Sensor Position (degrees)")
@@ -112,8 +112,8 @@ plt.gca().set_title('Filtered data')
 plt.savefig("exercise3-model.pdf")
 plt.close()
 
-position_hor, intensity_hor = np.loadtxt("/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-horizontal.txt", unpack = True)
-position_vert, intensity_vert = np.loadtxt("/home/polina/Documents/3rd_Year/PHY324/polarization/exercise3-vertical.txt", unpack = True)
+position_hor, intensity_hor = np.loadtxt("C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise3-horizontal.txt", unpack = True)
+position_vert, intensity_vert = np.loadtxt("C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise3-vertical.txt", unpack = True)
 
 position_hor = 120.0 - np.abs(180.0 - position_hor)
 position_vert = 120.0 - np.abs(180.0 - position_vert)

### 2018-02-06 thermoelectricity/paper.tex

--- 2018-01-31 polarization/paper.tex
@@
 \input{header}
+
 \physics
 \begin{document}
-\papertitle{Analysis of Light Intensity with Polarizers}
+\papertitle{Thermoelectricity}
 \paperauth{A}{Khesin}{1002442029}
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{February 1, 2018}
+\paperdate{February 12, 2018, Completed February 6, 2018}
 \begin{paperabs}
@@
 
-	Classical optics treats light as a transverse electromagnetic wave for which the directions of oscillation of electric and magnetic fields are both orthogonal to the direction of propagation.
-A light wave is said to be polarized if it has a well-defined, albeit possibly time-dependent, direction of oscillation of the electric field, also commonly referred to as the optical field.
-Light may be polarized by shining it through a sheet of Polaroid, transmitting only one component of light about a certain direction, coined the transmission axis of the polarizer.
-
-	In this experiment, \textbf{TODO}.
-
-	The intensity of light passing through two polarizing elements can be shown to be a function of the angle between their transmission axes, resulting in an expression known as Malus's law. 
-	\papereq{MalusLaw}{I(\theta) = I_0 \cos^2 \pars{\theta}}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{I_0}{intensity of incident light}{}
-		\papervar{I}{intensity of transmitted light}{}
-		\papervar{\theta}{angle between transmission axes}{}
-	\end{paperwhere}
-
-	In a two polarizing element setup, the first element is known as the \textit{polarizer}; the second is referred to as the \textit{analyzer}.
-As clearly seen from \eqMalusLaw, crossing the polarizer and the analyzer (i.e., \( \theta = 90 \si{\degree}\)) results in no light exiting the arrangement.
-
-	In an extended setup including a third polarizer, with the transmission axes of the first and last polarizers at \( 90 \si{\degree} \), an expression for light intensity may be found by applying \eqMalusLaw twice; now, it is given in terms of \( \phi = 45 \si{\degree} + \Theta \), where \( \Theta \) is the measured angle.
-	\papereq{ThreePolarizers}{I_3 = \frac{I_1}{4} \sin^2 \pars{2 \phi} }{}
-	\begin{paperwhere}
-		\papervar{I_1}{intensity after first polarizer}{}
-		\papervar{I_3}{intensity of transmitted light}{}
-		\papervar{\phi}{angle between transmission axes of polarizers}{}
-	\end{paperwhere}
-
-	The underlying physical concept behind a Polaroid is dichroism, or selective absorption of light.
-Other mechanisms involved in polarization of light include scattering, birefringence, and reflection.
-Of particular interest in this experiment was polarization of light by reflection.
-For a light beam reflected at an air-glass interface, the Fresnel equations provide the reflection coefficients \( r_{\parallel} \) and \( r_{\perp} \).
-	\papereq{ReflectionPerp}{r_{\perp} = \frac{n_1 \cos \theta_1 - n_2 \cos \theta_2}{n_1 \cos \theta_1 + n_2 \cos \theta_2}}{Serbanescu}
-	\papereq{ReflectionParallel}{r_{\parallel} = \frac{n_1 \cos \theta_2 - n_2 \cos \theta_1}{n_1 \cos \theta_2 + n_2 \cos \theta_1}}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{r_{\perp}}{perpendicular reflection coefficient}{}
-		\papervar{r_{\parallel}}{parallel reflection coefficient}{}
-		\papervar{n_1}{refractive index of air}{}
-		\papervar{n_2}{refractive index of glass}{}
-		\papervar{\theta_1}{angle of incidence}{}
-		\papervar{\theta_2}{angle of refraction}{}
-	\end{paperwhere}
-
-	The subscripts of the above coefficients reflect the orientation of the optical field of incident ray with respect to the plane of incidence.
-The reflectances of the rays are defined as the squares of the respective reflection coefficients.
-	\papereq{ReflectancePerp}{R_{\perp} = r_{\perp}^2}{Serbanescu}
-	\papereq{ReflectanceParallel}{R_{\parallel} = r_{\parallel}^2}{Serbanescu}
-	\begin{paperwhere}
-		\papervar{R_{\perp}}{perpendicular reflectance}{}
-		\papervar{R_{\parallel}}{parallel reflectance}{}
-	\end{paperwhere}
-
-	Finally, the angle of refraction is determined using Snell's law.
-	\papereq{SnellsLaw}{n_1 \sin \theta_1 = n_2 \sin \theta_2}{Serbanescu}
-	Reflected light is completely polarized with its optical field perpendicular to the plane of incidence when \( R_{\parallel} = 0 \).
-In this case, the angle between the reflected and refracted ray is \( 90 \si{\degree} \).
-The angle of incidence resulting in completely polarized light is known as the Brewster angle, or polarizing angle.
-An expression for \( \theta_p \) is derived from \eqSnellsLaw by making appropriate angle substitutions.
-	\papereq{PolarizingAngle}{\tan \theta_p = \frac{n_2}{n_1}}{Serbanescu}
-
-	This experiment verified Malus's law, \eqMalusLaw, for arrangements of two and three polarizers.
-In the former case, the laser, two polarizers (one with a rotary motion sensor) and the detector were setup such that maximum amount of light was allowed through without oversaturating the detector.
-Collecting intensity measurements involved unifromly rotating the polarizer with the rotary motion sensor through \( 180 \si{\degree} \).
-Data was collected using provided \textit{Polarization of Light} software.
-
-	To verify Malus's law for three polarizers, two polarizers were initially arranged to achieve maximum intensity of transmitted light.
-Furter, a third polarizer with a rotary motion sensor was inserted between the two initial polarizers and rotated to obtain a minimum in the intensity of transmitted light.
-Intensity measurements were collected through \( 360 \si{\degree} \) using the provided software.
-
-	The experimental arrangements for investigating polarization of light by reflection involved an acrylic semi-circular lens, a polarizer mounted on the optical bench, a spectrophotometer table with a rotary motion sensor and an optional square polarizer to be mounter on the spectrophotometer table.
-Furhter, a set of collimating slits was used for focusing the light beam.
-To calibrate the setup, \textbf{TODO}.
-The optical benches along with required optical elements are shown below \textbf{TODO}.
+	Introduction goes here
 
@@
 
-	Intensity of light passing through two polarizers was measured as a function of position.
-Uncertainties in intensities and positions were found by recording non-changing decimal points in the measurements provided by the software; uncertainty in intensity was determined to be \( \pm .01 \si{\volt} \), uncertainty in position was \( \pm \)\textbf{TODO}.
-Obtained data is visualized below.
-	\paperfig{ExerciseOneData}{\pdf{exercise1-data}}{Intensity of light as a function of rotary sensor position for two polarizers. Error bars are included but are too small to be visible.}
-
-	Further, intensity vs.
-position of the rotary motion sensor of the middle polarizer was measured for three polarizers.
-Uncertainties in intensity and position were again determined to be \( \pm .01 \si{\volt} \) and \( \pm \)\textbf{TODO} respectively.
-	\paperfig{ExerciseTwoData}{\pdf{exercise2-data}}{Intensity of light as a function of rotary sensor position for three polarizers. Error bars are not included \textbf{TODO} explain why.}
-
-	Finally, intensity vs. position data was collected for the experimental setup investigating polarization by reflection. Uncertainties were taken to be \textbf{TODO}. 
-	\paperfig{ExerciseThreeData}{\pdf{exercise3-data}}{Intensity of reflected ray as a function of position of the rotary motion sensor. Error bars are not included \textbf{TODO} explain why.}
+	Observations go here
 
@@
 
-	To begin with, Malus's law was verified using the obtained data for two polarizers.
-Fitting the measured intensity and angles to \( \cos \theta \) using the least squares method yielded a poor fit characterized by a reduced \( \chi ^ 2 \) of \( 48020.4 \) and an \( R^2 \) value of \( -1.53364 \).
-Fitting the data to \eqMalusLaw instead (i.e.
-testing a dependence on cosine squared) yielded a better fit characterized by a reduced \( \chi ^ 2 \)	of \( 8.56036 \) and an \( R ^ 2 \) value of \( 0.999548 \), indicating that the data obeys the theoretical model.
-The fit parameter was determined to be \( I_0 = \pars{3.8269 \pm 0.0008} \).
-A visualization of the fit along with residuals is shown below.
-	\paperfig{Exercise1Fit}{\pdf{exercise1-model}}{Light intensity and and fit residuals plotted against the angular position of the sensor for the two polarizer setup.
-The curve in red has the function \( \pars{3.8269 \pm 0.0008} \cos ^ 2 \theta \); \( R ^ 2 \) value of the fit is \( 0.999548 \).
-Error bars were included but are too small to be visible.}
-
-	Further, the data obtained for three polarizers was fit to \eqThreePolarizers using the least squares method.
-The intentensity of light through the first polarizer, \( I_0 \), was determined to be \( \pars{2.891 \pm 0.002} \si{\volt} \).
-Reduced \( \chi^2 \) was \( 3.422214 \); \( R^2 \) for this fit was \( 0.994677 \).
-	\paperfig{Exercise2Fit}{\pdf{exercise2-model}}{Intensity of light exiting the third polarizer and fit residuals vs.
-the angular position of the second polarizer.
-The curve has the function \( \pars{2.891 \pm 0.002} \sin^2 \pars{2\phi} \).
-\( R^2 \) of this fit was \( 0.994677 \).
-Error bars are not included due to \textbf{TODO}.}
-
-	\textbf{TODO} questions for exercise 2.
-
-	To estimate the value of Brewster's angle \( \theta_p \), given by \eqPolarizingAngle, obtained experimental data for intensity of light vs.
-angular position of the sensor (\figExerciseThreeData) was filtered to include only the maximum intensity data points.
-A least squares fit on the obtained boundary points was then performed with a degree-7 polynomial as the model function.
-
-	\textbf{TODO} include coefficients of polynomial, \( R^2 \), reduced \( \chi^2 \)
-
-	\paperfig{ExerciseThreeFit}{\pdf{exercise3-model}}{Intensity of light vs.
-angular position of the sensor for rays reflected off acrylic semi-circular block.
-Curve in red is a degree-7 polynomial; data was filtered by taking the maximum-intensity data point in 300-point intervals.}
-
-	\textbf{TODO} increase distance between plots to prevent ylabel from overlapping w/ left subplot.
-
-	\textbf{TODO} exercise 3 questions.
+	Analysis goes here
 
@@
 
-	\papersource{Serbanescu, R., Polarization of Light, 2017}
+	\papersource{Albanelli, P., Fomichev, S., Thermoelectricity, 2014}
 

### 2018-02-06 thermoelectricity/2a.py
2a, 2b plots

@@ -1,0 +1,41 @@
+#!/bin/python
+# Plots temperature change and electrical power input versus time
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Function ----------
+
+# ---------- Main Code ----------
+
+plt.rc('font', family = 'Times New Roman')
+# path_to_file = "/home/polina/Documents/3rd_Year/PHY324/thermoelectricity/part2a.txt"
+path_to_file = "part2a.txt"
+V, I, T1, T2 = np.loadtxt(path_to_file, unpack = True)
+
+P = V * I
+delta_T = T1 - T2
+
+plt.figure(num = None, figsize = (10, 6), dpi = 80, facecolor = 'w')
+# Plot power
+plt.subplot(121)
+plt.plot(P, color = "red", label = "Power (W)")
+plt.grid(True)
+plt.gca().set_title("Power input")
+plt.xticks([], [])
+plt.ylabel("Power (W)")
+# Plot temperature difference
+plt.subplot(122)
+plt.plot(delta_T, color = "blue", label = "Temperature difference (K)")
+plt.gca().set_title("Temperature change")
+plt.xticks([], [])
+plt.grid(True)
+plt.ylabel("Temperature difference (K)")
+plt.suptitle("TEC data, Varniac autotransformer turned off")
+plt.savefig("part2a-data.pdf")
+plt.show()
+

### 2018-02-06 thermoelectricity/2b.py

@@ -1,0 +1,50 @@
+#!/bin/python
+# Plots temperature change and electrical power input versus time
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Function ----------
+
+# ---------- Main Code ----------
+
+plt.rc('font', family = 'Times New Roman')
+# path_to_file = "/home/polina/Documents/3rd_Year/PHY324/thermoelectricity/part2b.txt"
+path_to_file = "part2b.txt"
+V_s, V_d, I_d, T1, T2, V_in, I_in = np.loadtxt(path_to_file, unpack = True)
+
+P_in = V_in * I_in
+delta_T = T1 - T2
+P_d = V_d * I_d
+
+# Plot data
+plt. figure(num = None, figsize = (14, 8), dpi = 80, facecolor = 'w')
+# Temperature difference
+plt.subplot(131)
+plt.plot(P_in, delta_T)
+plt.grid(True)
+plt.xlabel("P_in (W)")
+plt.ylabel("Temperature difference (K)")
+plt.title("Temperature difference vs. input power")
+# P_d
+plt.subplot(132)
+plt.plot(P_in, P_d)
+plt.grid(True)
+plt.xlabel("P_in (W)")
+plt.ylabel("P_d (W)")
+plt.title("Total electrical power vs. input power")
+# V_d
+plt.subplot(133)
+plt.plot(P_in, V_d)
+plt.grid(True)
+plt.xlabel("P_in (W)")
+plt.ylabel("V_d (V)")
+plt.title("Total voltage across TEC vs. input power")
+# Show plots
+plt.suptitle("TEC data, Varniac autotransformer turned on")
+plt.savefig("part2b-data.pdf")
+plt.show()

### 2018-02-10 thermoelectricity/paper.tex
started on circuit... long way to go
finished circuit

@@
 
+\paperfig{Circuit}
+{\begin{tikzpicture}[scale=1.5]
+\draw
+(0,0) rectangle (2,1)
+(1,0.5) node{\LARGE TEC}
+(4.5,0.75) rectangle (5,1.25)
+(4.75,1) node{CB}
+(4.75,1.25) -- (4.75,1.5)
+(4.5,1.5) rectangle (5,2)
+(4.75,1.75) node{VT}
+(0,1.5) rectangle (0.5,2)
+(0.25,1.75) node{TS}
+(0.17,1) -- (0.17,1.5)
+(0.33,1) -- (0.33,1.5)
+(0.25,1) node[below]{\small $T_1~T_2$}
+(4.5,0.92) -| (4.25,0.33)
+(4.5,1.08) -| (4.25,1.67)
+(2,0.33) to[ammeter] (3.75,0.33) -- (4.25,0.33)
+(2,0.33) node[left]{\small R}
+(4.25,1.67) -- (3.75,1.67) to[voltmeter] (3.67,0.33)
+(3.75,1.67) -| (2.5,0.67) -- (2,0.67) node[left]{\small R}
+(1,1.5) rectangle (1.5,2)
+(1.25,1.75) node{WO}
+(1.25,1.5) -- (1.25,1)
+(1.5,1.75) -- (4.5,1.75)
+(0.25,0) -- (0.25,-1.5) to[ammeter] (1.75,-1.5) to[voltmeter] (3.75,-1.5) to[capacitor] (5,-1.5)
+(0.25,0) node[above]{\small +}
+(3.75,-1.5) -- (3.75,-0.5) to[capacitor] (5,-0.5) -- (5,-1.5)
+(3.75,-0.5) -| (1.75,0) node[above]{\small \_}
+(1.75,-1.5) -- (1.75,-1) -| (1,0) node[above]{\small +}
+(0.25,-1.5) |- (5,-2) -- (5,-1.5)
+(0.5,-1.5) node[above]{\small +}
+(1.5,-1.5) node[above]{\small $-$}
+(2.25,-1.5) node[above]{\small +}
+(3.25,-1.5) node[above]{\small $-$}
+(4,-0.5) node[above]{\small $-$}
+(4.75,-0.5) node[above]{\small +}
+(4,-1.5) node[above]{\small $-$}
+(4.75,-1.5) node[above]{\small +};
+\end{tikzpicture}}
+{The circuit used in the experiment.
+The lower ammeter and voltmeter are set to DC.
+The upper ammeter and voltmeter are set to AC.
+TEC is the thermo-electric cooler.
+TS is the temperature sensor.
+WO is the wall outlet.
+VT is the Variac transformer.
+CB is the current balance.
+The filter capacitors are shown on the bottom right.
+The points $T_1$ and $T_2$ are the temperature of the heat sink, $T_\text{out}$, and the temperature of the reservoir, $T_\text{in}$, respectively.
+The two positive ports and the negative port of the TEC are indicated with pluses and a minus, respectively.
+The resistor ports of the TEC are indicated with the letter R.
+Positive and negative terminals were not shown on the upper ammeter and voltmeter as they do not affect the results by more than a sign.}
+
 \papersec{Observations}

### 2018-02-12 thermoelectricity/paper.tex
Thermoelectricity introduction

--- 2018-02-06 thermoelectricity/paper.tex
@@
 
-	Introduction goes here
+	A thermo-electric cooler (TEC) is a device that exploits Peltier and Seebeck effects to act as a solid-state heat pump.
+Composed of a set of metal-to-semiconductor thermocouple junctions, the TEC is capable of transferring heat from a cold environment to a warmer one, essentially acting as a reverse heat engine.
+
+	The Seebeck effect refers to the process of a temperature difference being converted into electricity.
+Given a circular loop composed of two different metals, it is evident that when maintained at the same temperature, the wires have different electron densities.
+As electrons move in the loop to correct the electron imbalance, net electric fields are created at the junctions.
+Further, introducing a temperature difference by keeping one junction at a constant temperature and increasing the temperature of the other gives electrons more kinetic energy and thus resulting in charge imbalances being corrected faster at the warmer junction.
+A net electric field is created in the loop; an electric potential difference and a current flow are established in the loop.
+
+	The inverse of the Seebeck effect is referred to as the Peltier effect.
+As electric current passes through a loop made of two different junctions, a temperature difference between the two junctions is established.
+The junction where electron flow opposed the net electric field is being heated up as work is done by the electrons; at the other junction electron flow coincides with the direction of the net electric field and thus the junction is being cooled down.
+
+	On top of the above two effects underlying the functionality of a TEC, a variety of other processes are observed in the device.
+A significant example is ohmic heating, or the process of a circuit element with nonzero resistance being heated up as current flows through it.
+The process is simply described using the relationship below.
+
+	\papereq{OhmicHeating}{P = I ^ 2 R}{\textbf{TODO}}
+	\begin{paperwhere}
+		\papervar{P}{heat production per unit time}{\watt}
+		\papervar{I}{current}{\ampere}
+		\papervar{R}{resistance}{\ohm}
+	\end{paperwhere}
+
+	In this experiment, the above physical principles were used to connect various aspects of TEC's performance.
+In steady-state operation of the TEC, the three elements to be examined were an ideal Peltier reversible heat pump, Ohmic resistive heating, and non-electronic heat flow from from the hot output port of the TEC to the cold input port.
+
+	The experimental setup included the TEC, \textbf{four} multimeters, current balance, Variac transformer, filter capacitors to filter out noise produced by the TEC, and a \textbf{thermometer}, all arranged as shown below.
+
+	\paperfig{Setup}{\pdf{setup}}{}
+
+\noindent\begin{tikzpicture}
+\draw
+(0,0) rectangle (2,1)
+(3,1.5) rectangle (3.5,2)
+(3.5,1.75) -- (4.5,1.75)
+(4.5,1.5) rectangle (5,2)
+(0,1.5) rectangle (0.5,2)
+(0.17,1) -- (0.17,1.5)
+(0.33,1) -- (0.33,1.5)
+(1,1) -- (1,1.75) to[ammeter] (3,1.75)
+(2,0.67) -| (2.67,1.75)
+(2,0.33) -| (3.83,1.75)
+(2.67,1) to[voltmeter] (3.83,1)
+;
+\end{tikzpicture}
 

### 2018-02-12 interfer/linfit.py

@@ -1,0 +1,25 @@
+#!/bin/python
+# Linear fit of micrometer reading vs. num of fringes
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Function ----------
+
+# Linear fit function
+def func(x, a, b):
+	return a * x + b
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+path_to_file = "measurements.txt"
+num, reading = np.loadtxt(path_to_file, unpack = True)
+
+plt.plot(num, reading)
+plt.show()

### 2018-02-12 thermoelectricity/paper.tex

@@
 
-\noindent\begin{tikzpicture}
+\paperfig{Circuit}
+{\begin{tikzpicture}[scale=1.5]
 \draw
 (0,0) rectangle (2,1)
-(3,1.5) rectangle (3.5,2)
-(3.5,1.75) -- (4.5,1.75)
+(1,0.5) node{\LARGE TEC}
+(4.5,0.75) rectangle (5,1.25)
+(4.75,1) node{CB}
+(4.75,1.25) -- (4.75,1.5)
 (4.5,1.5) rectangle (5,2)
+(4.75,1.75) node{VT}
 (0,1.5) rectangle (0.5,2)
+(0.25,1.75) node{TS}
 (0.17,1) -- (0.17,1.5)
 (0.33,1) -- (0.33,1.5)
-(1,1) -- (1,1.75) to[ammeter] (3,1.75)
-(2,0.67) -| (2.67,1.75)
-(2,0.33) -| (3.83,1.75)
-(2.67,1) to[voltmeter] (3.83,1)
-;
-\end{tikzpicture}
+(0.25,1) node[below]{\small $T_1~T_2$}
+(4.5,0.92) -| (4.25,0.33)
+(4.5,1.08) -| (4.25,1.67)
+(2,0.33) to[ammeter] (3.75,0.33) -- (4.25,0.33)
+(2,0.33) node[left]{\small R}
+(4.25,1.67) -- (3.75,1.67) to[voltmeter] (3.67,0.33)
+(3.75,1.67) -| (2.5,0.67) -- (2,0.67) node[left]{\small R}
+(1,1.5) rectangle (1.5,2)
+(1.25,1.75) node{WO}
+(1.25,1.5) -- (1.25,1)
+(1.5,1.75) -- (4.5,1.75)
+(0.25,0) -- (0.25,-1.5) to[ammeter] (1.75,-1.5) to[voltmeter] (3.75,-1.5) to[capacitor] (5,-1.5)
+(0.25,0) node[above]{\small +}
+(3.75,-1.5) -- (3.75,-0.5) to[capacitor] (5,-0.5) -- (5,-1.5)
+(3.75,-0.5) -| (1.75,0) node[above]{\small \_}
+(1.75,-1.5) -- (1.75,-1) -| (1,0) node[above]{\small +}
+(0.25,-1.5) |- (5,-2) -- (5,-1.5)
+(0.5,-1.5) node[above]{\small +}
+(1.5,-1.5) node[above]{\small $-$}
+(2.25,-1.5) node[above]{\small +}
+(3.25,-1.5) node[above]{\small $-$}
+(4,-0.5) node[above]{\small $-$}
+(4.75,-0.5) node[above]{\small +}
+(4,-1.5) node[above]{\small $-$}
+(4.75,-1.5) node[above]{\small +};
+\end{tikzpicture}}
+{The circuit used in the experiment.
+The lower ammeter and voltmeter are set to DC.
+The upper ammeter and voltmeter are set to AC.
+TEC is the thermo-electric cooler.
+TS is the temperature sensor.
+WO is the wall outlet.
+VT is the Variac transformer.
+CB is the current balance.
+The filter capacitors are shown on the bottom right.
+The points $T_1$ and $T_2$ are the temperature of the heat sink, $T_\text{out}$, and the temperature of the reservoir, $T_\text{in}$, respectively.
+The two positive ports and the negative port of the TEC are indicated with pluses and a minus, respectively.
+The resistor ports of the TEC are indicated with the letter R.
+Positive and negative terminals were not shown on the upper ammeter and voltmeter as they do not affect the results by more than a sign.}
 

### 2018-02-13 thermoelectricity/paper.tex
Procedure

@@
 
-	Observations go here
+	To begin with, the temperatures of the input and output reservoirs and the ambient air were measured for several values of input power.
+To make the measurements, the terminals were open-circuited (obtained by unplugging one of the chords connecting the TEC to the DC ammeter).
+The ambient temperature was determined to be \( \pars{22.1 \pm 0.1} \si{\celsius} \), and was found to remain constant throughout the obtaining of the measurements.
+
+	Further, after allowing the system to cool off, the TEC was operated with an approximately fixed current supplied from the built-in power supply.
+The Variac transformer was turned off; measurements of voltage across the TEC and the current supplied to it, as well as the temperatures of the output and the input reservoir were taken.
+
+	Finally, after reaching a \( 30 \si{\celsius} \) temperature difference, the Variac transformer was turned on to supply various power inputs to the system.
+Allowing the system to reach a semi-stable state (waiting roughly two minutes after changing the power), reservoir temperatures, input and output power, and the Seebeck voltage were measured.
+The Seebeck voltage was obtained by turning off the TEC and recording the highest reading of continuously running-off potential.
 
 \papersec{Analysis}
-
-	Analysis goes here
 

### 2018-02-13 thermoelectricity/paper.tex
added first table

--- 2018-02-12 thermoelectricity/paper.tex
@@
 
+	\paperfig{TableOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
+	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_{in}}\papertableuheadersymbole{V_{in}}\\
+	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
+\papertableindex\papertablecval{23.0}\papertablecval{31.8}\papertableuval{1.541}{.01}\papertableuval{3.197}{.005}\\\paperiline
+\papertableindex\papertablecval{22.9}\papertablecval{31.4}\papertableuval{1.386}{.01}\papertableuval{2.884}{.004}\\\paperiline
+\papertableindex\papertablecval{22.9}\papertablecval{30.2}\papertableuval{1.197}{.01}\papertableuval{2.488}{.004}\\\paperiline
+\papertableindex\papertablecval{22.7}\papertablecval{27.4}\papertableuval{0.982}{.01}\papertableuval{2.044}{.004}\\\paperiline
+\papertableindex\papertablecval{22.5}\papertablecval{25.3}\papertableuval{0.693}{.008}\papertableuval{1.441}{.004}\\\paperiline
+\papertableindex\papertablecval{22.3}\papertablecval{23.3}\papertableuval{0.006}{.005}\papertableuval{0.014}{.003}\\\paperoline
+\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $I_{in}$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the experiment.}
+
 \papersec{Analysis}

### 2018-02-13 thermoelectricity/paper.tex

@@
 
-	Observations go here
+	To begin with, the temperatures of the input and output reservoirs and the ambient air were measured for several values of input power.
+To make the measurements, the terminals were open-circuited (obtained by unplugging one of the chords connecting the TEC to the DC ammeter).
+The ambient temperature was determined to be \( \pars{22.1 \pm 0.1} \si{\celsius} \), and was found to remain constant throughout the obtaining of the measurements.
+
+	Further, after allowing the system to cool off, the TEC was operated with an approximately fixed current supplied from the built-in power supply.
+The Variac transformer was turned off; measurements of voltage across the TEC and the current supplied to it, as well as the temperatures of the output and the input reservoir were taken.
+
+	Finally, after reaching a \( 30 \si{\celsius} \) temperature difference, the Variac transformer was turned on to supply various power inputs to the system.
+Allowing the system to reach a semi-stable state (waiting roughly two minutes after changing the power), reservoir temperatures, input and output power, and the Seebeck voltage were measured.
+The Seebeck voltage was obtained by turning off the TEC and recording the highest reading of continuously running-off potential.
 
@@
 
-	Analysis goes here
-
 \papersec{Conclusion}

### 2018-02-13 thermoelectricity/paper.tex
1 plot

@@
 
+	\paperfig{TableOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
+			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_{in}}\papertableuheadersymbole{V_{in}}\\
+			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
+			\papertableindex\papertablecval{23.0}\papertablecval{31.8}\papertableuval{1.54}{.01}\papertableuval{3.197}{.005}\\\paperiline
+			\papertableindex\papertablecval{22.9}\papertablecval{31.4}\papertableuval{1.39}{.01}\papertableuval{2.884}{.004}\\\paperiline
+			\papertableindex\papertablecval{22.9}\papertablecval{30.2}\papertableuval{1.20}{.01}\papertableuval{2.488}{.004}\\\paperiline
+			\papertableindex\papertablecval{22.7}\papertablecval{27.4}\papertableuval{0.98}{.01}\papertableuval{2.044}{.004}\\\paperiline
+			\papertableindex\papertablecval{22.5}\papertablecval{25.3}\papertableuval{0.693}{.008}\papertableuval{1.441}{.004}\\\paperiline
+			\papertableindex\papertablecval{22.3}\papertablecval{23.3}\papertableuval{0.006}{.005}\papertableuval{0.014}{.003}\\\paperoline
+	\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $I_{in}$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the experiment.}
+
 	Further, after allowing the system to cool off, the TEC was operated with an approximately fixed current supplied from the built-in power supply.
@@
 
-	\paperfig{TableOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
-	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_{in}}\papertableuheadersymbole{V_{in}}\\
-	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
-\papertableindex\papertablecval{23.0}\papertablecval{31.8}\papertableuval{1.541}{.01}\papertableuval{3.197}{.005}\\\paperiline
-\papertableindex\papertablecval{22.9}\papertablecval{31.4}\papertableuval{1.386}{.01}\papertableuval{2.884}{.004}\\\paperiline
-\papertableindex\papertablecval{22.9}\papertablecval{30.2}\papertableuval{1.197}{.01}\papertableuval{2.488}{.004}\\\paperiline
-\papertableindex\papertablecval{22.7}\papertablecval{27.4}\papertableuval{0.982}{.01}\papertableuval{2.044}{.004}\\\paperiline
-\papertableindex\papertablecval{22.5}\papertablecval{25.3}\papertableuval{0.693}{.008}\papertableuval{1.441}{.004}\\\paperiline
-\papertableindex\papertablecval{22.3}\papertablecval{23.3}\papertableuval{0.006}{.005}\papertableuval{0.014}{.003}\\\paperoline
-\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $I_{in}$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the experiment.}
+\papersec{Analysis}
 
-\papersec{Analysis}
+	To visualize the data with the open-circuited terminals, temperature difference was plotted against the input power. Uncertainties were propagated using the method of quadratures.
+
+	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but are too small to be visible.}
+
+	To visualize the results for the
 

### 2018-02-13 thermoelectricity/paper.tex
second table

--- 2018-02-13 thermoelectricity/paper.tex
@@
 
+	\bgroup\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
+	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_d}\papertableuheadersymbole{V_d}\\
+	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
+\papertableindex\papertablecval{22.2}\papertablecval{20.6}\papertableuval{2.68}{.07}\papertableuval{9.77}{.03}\\\paperiline
+\papertableindex\papertablecval{24.7}\papertablecval{16.7}\papertableuval{2.72}{.07}\papertableuval{9.72}{.03}\\\paperiline
+\papertableindex\papertablecval{25.7}\papertablecval{15.0}\papertableuval{2.70}{.07}\papertableuval{9.47}{.02}\\\paperiline
+\papertableindex\papertablecval{26.4}\papertablecval{13.4}\papertableuval{2.69}{.07}\papertableuval{9.49}{.02}\\\paperiline
+\papertableindex\papertablecval{27.1}\papertablecval{11.3}\papertableuval{2.65}{.07}\papertableuval{9.29}{.02}\\\paperiline
+\papertableindex\papertablecval{27.3}\papertablecval{10.4}\papertableuval{2.63}{.07}\papertableuval{9.21}{.02}\\\paperiline
+\papertableindex\papertablecval{27.6}\papertablecval{9.1}\papertableuval{2.62}{.07}\papertableuval{9.16}{.02}\\\paperiline
+\papertableindex\papertablecval{27.8}\papertablecval{8.0}\papertableuval{2.65}{.07}\papertableuval{9.22}{.02}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{6.8}\papertableuval{2.59}{.07}\papertableuval{9.00}{.02}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{5.9}\papertableuval{2.75}{.08}\papertableuval{9.57}{.02}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{4.8}\papertableuval{2.78}{.08}\papertableuval{9.65}{.03}\\\paperiline
+\papertableindex\papertablecval{28.4}\papertablecval{4.0}\papertableuval{2.78}{.08}\papertableuval{9.62}{.03}\\\paperiline
+\papertableindex\papertablecval{28.4}\papertablecval{3.1}\papertableuval{2.79}{.08}\papertableuval{9.65}{.03}\\\paperiline
+\papertableindex\papertablecval{28.5}\papertablecval{2.3}\papertableuval{2.79}{.08}\papertableuval{9.66}{.03}\\\paperiline
+\papertableindex\papertablecval{28.5}\papertablecval{1.5}\papertableuval{2.80}{.08}\papertableuval{9.68}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{0.7}\papertableuval{2.80}{.08}\papertableuval{9.69}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{0.1}\papertableuval{2.80}{.08}\papertableuval{9.67}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-0.4}\papertableuval{2.80}{.08}\papertableuval{9.67}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-1.1}\papertableuval{2.81}{.08}\papertableuval{9.71}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-1.7}\papertableuval{2.81}{.08}\papertableuval{9.71}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-2.7}\papertableuval{2.81}{.08}\papertableuval{9.69}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-3.3}\papertableuval{2.82}{.08}\papertableuval{9.73}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-3.7}\papertableuval{2.81}{.08}\papertableuval{9.68}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-4.2}\papertableuval{2.80}{.08}\papertableuval{9.67}{.03}\\\paperiline
+\papertableindex\papertablecval{28.5}\papertablecval{-4.7}\papertableuval{2.74}{.07}\papertableuval{9.41}{.02}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-5.2}\papertableuval{2.73}{.07}\papertableuval{9.34}{.02}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{-5.5}\papertableuval{2.70}{.07}\papertableuval{9.28}{.02}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{-5.7}\papertableuval{2.70}{.07}\papertableuval{9.29}{.02}\\\paperoline\end{papertable}\egroup
+
+\paperfig{PartTwoA}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
+	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_d}\papertableuheadersymbole{V_d}\\
+	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
+\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\papertableindex\papertablecval{28.1}\papertablecval{-5.9}\papertableuval{2.71}{.07}\papertableuval{9.33}{.02}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-6.2}\papertableuval{2.63}{.07}\papertableuval{9.21}{.02}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-6.3}\papertableuval{2.67}{.07}\papertableuval{9.21}{.02}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{-6.5}\papertableuval{2.68}{.07}\papertableuval{9.20}{.02}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{-6.7}\papertableuval{2.71}{.07}\papertableuval{9.34}{.02}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-6.9}\papertableuval{2.80}{.08}\papertableuval{9.72}{.03}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.1}\papertableuval{2.66}{.07}\papertableuval{9.21}{.02}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.2}\papertableuval{2.65}{.07}\papertableuval{9.15}{.02}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.4}\papertableuval{2.63}{.07}\papertableuval{9.14}{.02}\\\paperiline
+\papertableindex\papertablecval{27.8}\papertablecval{-7.4}\papertableuval{2.85}{.08}\papertableuval{9.98}{.03}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.6}\papertableuval{2.86}{.08}\papertableuval{10.05}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-7.9}\papertableuval{2.86}{.08}\papertableuval{10.05}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-8.1}\papertableuval{2.87}{.08}\papertableuval{10.07}{.03}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{-8.2}\papertableuval{2.84}{.08}\papertableuval{9.99}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.3}\papertableuval{2.87}{.08}\papertableuval{10.13}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.5}\papertableuval{2.87}{.08}\papertableuval{10.14}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.6}\papertableuval{2.87}{.08}\papertableuval{10.15}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.7}\papertableuval{2.88}{.08}\papertableuval{10.21}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.7}\papertableuval{2.87}{.08}\papertableuval{10.21}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.6}\papertableuval{2.84}{.08}\papertableuval{10.09}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.8}\papertableuval{2.72}{.07}\papertableuval{9.69}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.9}\papertableuval{2.75}{.08}\papertableuval{9.79}{.03}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{-8.9}\papertableuval{2.71}{.07}\papertableuval{9.66}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-8.9}\papertableuval{2.83}{.08}\papertableuval{10.17}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-8.9}\papertableuval{2.83}{.08}\papertableuval{10.19}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-9.0}\papertableuval{2.84}{.08}\papertableuval{10.25}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-9.0}\papertableuval{2.84}{.08}\papertableuval{10.27}{.03}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{-9.1}\papertableuval{2.85}{.08}\papertableuval{10.31}{.03}\\\paperoline
+\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_d$ ($\si{\celsius}$), $I_d$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the second part of the experiment.}
+
 \papersec{Analysis}

### 2018-02-13 thermoelectricity/paper.tex

@@
 The Seebeck voltage was obtained by turning off the TEC and recording the highest reading of continuously running-off potential.
-
-	\paperfig{TableOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
-	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_{in}}\papertableuheadersymbole{V_{in}}\\
-	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
-\papertableindex\papertablecval{23.0}\papertablecval{31.8}\papertableuval{1.541}{.01}\papertableuval{3.197}{.005}\\\paperiline
-\papertableindex\papertablecval{22.9}\papertablecval{31.4}\papertableuval{1.386}{.01}\papertableuval{2.884}{.004}\\\paperiline
-\papertableindex\papertablecval{22.9}\papertablecval{30.2}\papertableuval{1.197}{.01}\papertableuval{2.488}{.004}\\\paperiline
-\papertableindex\papertablecval{22.7}\papertablecval{27.4}\papertableuval{0.982}{.01}\papertableuval{2.044}{.004}\\\paperiline
-\papertableindex\papertablecval{22.5}\papertablecval{25.3}\papertableuval{0.693}{.008}\papertableuval{1.441}{.004}\\\paperiline
-\papertableindex\papertablecval{22.3}\papertablecval{23.3}\papertableuval{0.006}{.005}\papertableuval{0.014}{.003}\\\paperoline
-\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $I_{in}$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the experiment.}
 
@@
 
+	To visualize the data with the open-circuited terminals, temperature difference was plotted against the input power. Uncertainties were propagated using the method of quadratures.
+
+	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but are too small to be visible.}
+
+	To visualize the results for the
+
 \papersec{Conclusion}

### 2018-02-13 thermoelectricity/paper.tex
All plots

@@
 
-	\papereq{OhmicHeating}{P = I ^ 2 R}{\textbf{TODO}}
+	\papereq{OhmicHeating}{P = I ^ 2 R}{AF, 2014}
 	\begin{paperwhere}
@@
 
-	Finally, after reaching a \( 30 \si{\celsius} \) temperature difference, the Variac transformer was turned on to supply various power inputs to the system.
-Allowing the system to reach a semi-stable state (waiting roughly two minutes after changing the power), reservoir temperatures, input and output power, and the Seebeck voltage were measured.
-The Seebeck voltage was obtained by turning off the TEC and recording the highest reading of continuously running-off potential.
-
 	\bgroup\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
@@
 
+	Finally, after reaching a \( 30 \si{\celsius} \) temperature difference, the Variac transformer was turned on to supply various power inputs to the system.
+Allowing the system to reach a semi-stable state (waiting roughly two minutes after changing the power), reservoir temperatures, input and output power, and the Seebeck voltage were measured.
+The Seebeck voltage was obtained by turning off the TEC and recording the highest reading of continuously running-off potential.
+
 \papersec{Analysis}
@@
 
-	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but are too small to be visible.}
+	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but were too small to be visible.}
 
-	To visualize the results for the
+	To visualize the results for the fixed current setup supplied by the built-in power supply, temperature difference and the electrical power input were plotted against time.
+All uncertainties were propagates using the method of quadratures.
+
+	\paperfig{part2a}{\pdf{part2a-data}}{Power and temperature difference plotted against time. Uncertainties were included but were too small to be visible.}
+
+	To visualize the results for various power inputs supplied by the Variac transformer, reservoir temperatures, power, and the Seebeck voltage were plotted versus the input power.
+All uncertainties were propagates using the method of quadratures.
+
+	\paperfig{part2b}{\pdf{part2b-data}}{Temperature vs.
+input power (left), total electrical power vs.
+input power (middle) and total voltage across the TEC vs.
+input power (right).
+Uncertainties were included but were too small to be visible.}
 

### 2018-02-13 thermoelectricity/paper.tex
second to last table

--- 2018-02-13 thermoelectricity/paper.tex
@@
 	\paperfig{TableOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
-			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_{in}}\papertableuheadersymbole{V_{in}}\\
-			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
-			\papertableindex\papertablecval{23.0}\papertablecval{31.8}\papertableuval{1.54}{.01}\papertableuval{3.197}{.005}\\\paperiline
-			\papertableindex\papertablecval{22.9}\papertablecval{31.4}\papertableuval{1.39}{.01}\papertableuval{2.884}{.004}\\\paperiline
-			\papertableindex\papertablecval{22.9}\papertablecval{30.2}\papertableuval{1.20}{.01}\papertableuval{2.488}{.004}\\\paperiline
-			\papertableindex\papertablecval{22.7}\papertablecval{27.4}\papertableuval{0.98}{.01}\papertableuval{2.044}{.004}\\\paperiline
-			\papertableindex\papertablecval{22.5}\papertablecval{25.3}\papertableuval{0.693}{.008}\papertableuval{1.441}{.004}\\\paperiline
-			\papertableindex\papertablecval{22.3}\papertablecval{23.3}\papertableuval{0.006}{.005}\papertableuval{0.014}{.003}\\\paperoline
+			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{V_{in}}\papertableuheadersymbole{I_{in}}\\
+			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\volt}}\papertableuheaderunite{\si{\ampere}}\\\paperiline
+			\papertableindex\papertablecval{23.0}\papertablecval{31.8}\papertableuval{3.197}{.005}\papertableuval{1.54}{.01}\\\paperiline
+			\papertableindex\papertablecval{22.9}\papertablecval{31.4}\papertableuval{2.884}{.004}\papertableuval{1.39}{.01}\\\paperiline
+			\papertableindex\papertablecval{22.9}\papertablecval{30.2}\papertableuval{2.488}{.004}\papertableuval{1.20}{.01}\\\paperiline
+			\papertableindex\papertablecval{22.7}\papertablecval{27.4}\papertableuval{2.044}{.004}\papertableuval{0.98}{.01}\\\paperiline
+			\papertableindex\papertablecval{22.5}\papertablecval{25.3}\papertableuval{1.441}{.004}\papertableuval{0.693}{.008}\\\paperiline
+			\papertableindex\papertablecval{22.3}\papertablecval{23.3}\papertableuval{0.014}{.003}\papertableuval{0.006}{.005}\\\paperoline
 	\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $I_{in}$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the experiment.}
@@
 	\bgroup\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
-	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_d}\papertableuheadersymbole{V_d}\\
-	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
+	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{V_d}\papertableuheadersymbole{I_d}\\
+	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\volt}}\papertableuheaderunite{\si{\ampere}}\\\paperiline
 \papertableindex\papertablecval{22.2}\papertablecval{20.6}\papertableuval{2.68}{.07}\papertableuval{9.77}{.03}\\\paperiline
-\papertableindex\papertablecval{24.7}\papertablecval{16.7}\papertableuval{2.72}{.07}\papertableuval{9.72}{.03}\\\paperiline
-\papertableindex\papertablecval{25.7}\papertablecval{15.0}\papertableuval{2.70}{.07}\papertableuval{9.47}{.02}\\\paperiline
+\papertableindex\papertablecval{24.7}\papertablecval{16.7}\papertableuval{2.72}{.07}\papertableuval{9.73}{.03}\\\paperiline
+\papertableindex\papertablecval{25.7}\papertablecval{15.0}\papertableuval{2.71}{.07}\papertableuval{9.47}{.02}\\\paperiline
 \papertableindex\papertablecval{26.4}\papertablecval{13.4}\papertableuval{2.69}{.07}\papertableuval{9.49}{.02}\\\paperiline
-\papertableindex\papertablecval{27.1}\papertablecval{11.3}\papertableuval{2.65}{.07}\papertableuval{9.29}{.02}\\\paperiline
+\papertableindex\papertablecval{27.1}\papertablecval{11.3}\papertableuval{2.66}{.07}\papertableuval{9.29}{.02}\\\paperiline
 \papertableindex\papertablecval{27.3}\papertablecval{10.4}\papertableuval{2.63}{.07}\papertableuval{9.21}{.02}\\\paperiline
-\papertableindex\papertablecval{27.6}\papertablecval{9.1}\papertableuval{2.62}{.07}\papertableuval{9.16}{.02}\\\paperiline
-\papertableindex\papertablecval{27.8}\papertablecval{8.0}\papertableuval{2.65}{.07}\papertableuval{9.22}{.02}\\\paperiline
-\papertableindex\papertablecval{28.0}\papertablecval{6.8}\papertableuval{2.59}{.07}\papertableuval{9.00}{.02}\\\paperiline
+\papertableindex\papertablecval{27.6}\papertablecval{9.1}\papertableuval{2.63}{.07}\papertableuval{9.17}{.02}\\\paperiline
+\papertableindex\papertablecval{27.8}\papertablecval{8.0}\papertableuval{2.66}{.07}\papertableuval{9.22}{.02}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{6.8}\papertableuval{2.60}{.07}\papertableuval{9.01}{.02}\\\paperiline
 \papertableindex\papertablecval{28.1}\papertablecval{5.9}\papertableuval{2.75}{.08}\papertableuval{9.57}{.02}\\\paperiline
 \papertableindex\papertablecval{28.2}\papertablecval{4.8}\papertableuval{2.78}{.08}\papertableuval{9.65}{.03}\\\paperiline
-\papertableindex\papertablecval{28.4}\papertablecval{4.0}\papertableuval{2.78}{.08}\papertableuval{9.62}{.03}\\\paperiline
+\papertableindex\papertablecval{28.4}\papertablecval{4.0}\papertableuval{2.78}{.08}\papertableuval{9.63}{.03}\\\paperiline
 \papertableindex\papertablecval{28.4}\papertablecval{3.1}\papertableuval{2.79}{.08}\papertableuval{9.65}{.03}\\\paperiline
-\papertableindex\papertablecval{28.5}\papertablecval{2.3}\papertableuval{2.79}{.08}\papertableuval{9.66}{.03}\\\paperiline
+\papertableindex\papertablecval{28.5}\papertablecval{2.3}\papertableuval{2.80}{.08}\papertableuval{9.67}{.03}\\\paperiline
 \papertableindex\papertablecval{28.5}\papertablecval{1.5}\papertableuval{2.80}{.08}\papertableuval{9.68}{.03}\\\paperiline
-\papertableindex\papertablecval{28.6}\papertablecval{0.7}\papertableuval{2.80}{.08}\papertableuval{9.69}{.03}\\\paperiline
-\papertableindex\papertablecval{28.6}\papertablecval{0.1}\papertableuval{2.80}{.08}\papertableuval{9.67}{.03}\\\paperiline
-\papertableindex\papertablecval{28.6}\papertablecval{-0.4}\papertableuval{2.80}{.08}\papertableuval{9.67}{.03}\\\paperiline
-\papertableindex\papertablecval{28.6}\papertablecval{-1.1}\papertableuval{2.81}{.08}\papertableuval{9.71}{.03}\\\paperiline
-\papertableindex\papertablecval{28.6}\papertablecval{-1.7}\papertableuval{2.81}{.08}\papertableuval{9.71}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{0.7}\papertableuval{2.81}{.08}\papertableuval{9.70}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{0.1}\papertableuval{2.80}{.08}\papertableuval{9.68}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-0.4}\papertableuval{2.80}{.08}\papertableuval{9.68}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-1.1}\papertableuval{2.82}{.08}\papertableuval{9.71}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-1.7}\papertableuval{2.82}{.08}\papertableuval{9.71}{.03}\\\paperiline
 \papertableindex\papertablecval{28.6}\papertablecval{-2.7}\papertableuval{2.81}{.08}\papertableuval{9.69}{.03}\\\paperiline
-\papertableindex\papertablecval{28.6}\papertablecval{-3.3}\papertableuval{2.82}{.08}\papertableuval{9.73}{.03}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-3.3}\papertableuval{2.83}{.08}\papertableuval{9.74}{.03}\\\paperiline
 \papertableindex\papertablecval{28.6}\papertablecval{-3.7}\papertableuval{2.81}{.08}\papertableuval{9.68}{.03}\\\paperiline
-\papertableindex\papertablecval{28.6}\papertablecval{-4.2}\papertableuval{2.80}{.08}\papertableuval{9.67}{.03}\\\paperiline
-\papertableindex\papertablecval{28.5}\papertablecval{-4.7}\papertableuval{2.74}{.07}\papertableuval{9.41}{.02}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-5.2}\papertableuval{2.73}{.07}\papertableuval{9.34}{.02}\\\paperiline
+\papertableindex\papertablecval{28.6}\papertablecval{-4.2}\papertableuval{2.81}{.08}\papertableuval{9.67}{.03}\\\paperiline
+\papertableindex\papertablecval{28.5}\papertablecval{-4.7}\papertableuval{2.74}{.07}\papertableuval{9.42}{.02}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-5.2}\papertableuval{2.73}{.07}\papertableuval{9.35}{.02}\\\paperiline
 \papertableindex\papertablecval{28.2}\papertablecval{-5.5}\papertableuval{2.70}{.07}\papertableuval{9.28}{.02}\\\paperiline
-\papertableindex\papertablecval{28.2}\papertablecval{-5.7}\papertableuval{2.70}{.07}\papertableuval{9.29}{.02}\\\paperoline\end{papertable}\egroup
+\papertableindex\papertablecval{28.2}\papertablecval{-5.7}\papertableuval{2.71}{.07}\papertableuval{9.30}{.02}\\\paperoline\end{papertable}\egroup
 
 \paperfig{PartTwoA}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]U|[inner]U|[outer]}\paperoline
-	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{I_d}\papertableuheadersymbole{V_d}\\
-	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\ampere}}\papertableuheaderunite{\si{\volt}}\\\paperiline
+	\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertableuheadersymbol{V_d}\papertableuheadersymbole{I_d}\\
+	\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertableuheaderunit{\si{\volt}}\papertableuheaderunite{\si{\ampere}}\\\paperiline
 \stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\stepcounter{papertableindexcounter}\papertableindex\papertablecval{28.1}\papertablecval{-5.9}\papertableuval{2.71}{.07}\papertableuval{9.33}{.02}\\\paperiline
-\papertableindex\papertablecval{28.1}\papertablecval{-6.2}\papertableuval{2.63}{.07}\papertableuval{9.21}{.02}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-6.2}\papertableuval{2.64}{.07}\papertableuval{9.22}{.02}\\\paperiline
 \papertableindex\papertablecval{28.1}\papertablecval{-6.3}\papertableuval{2.67}{.07}\papertableuval{9.21}{.02}\\\paperiline
-\papertableindex\papertablecval{28.0}\papertablecval{-6.5}\papertableuval{2.68}{.07}\papertableuval{9.20}{.02}\\\paperiline
-\papertableindex\papertablecval{28.0}\papertablecval{-6.7}\papertableuval{2.71}{.07}\papertableuval{9.34}{.02}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{-6.5}\papertableuval{2.68}{.07}\papertableuval{9.21}{.02}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{-6.7}\papertableuval{2.72}{.07}\papertableuval{9.34}{.02}\\\paperiline
 \papertableindex\papertablecval{27.9}\papertablecval{-6.9}\papertableuval{2.80}{.08}\papertableuval{9.72}{.03}\\\paperiline
-\papertableindex\papertablecval{27.9}\papertablecval{-7.1}\papertableuval{2.66}{.07}\papertableuval{9.21}{.02}\\\paperiline
-\papertableindex\papertablecval{27.9}\papertablecval{-7.2}\papertableuval{2.65}{.07}\papertableuval{9.15}{.02}\\\paperiline
-\papertableindex\papertablecval{27.9}\papertablecval{-7.4}\papertableuval{2.63}{.07}\papertableuval{9.14}{.02}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.1}\papertableuval{2.67}{.07}\papertableuval{9.21}{.02}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.2}\papertableuval{2.65}{.07}\papertableuval{9.16}{.02}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.4}\papertableuval{2.64}{.07}\papertableuval{9.15}{.02}\\\paperiline
 \papertableindex\papertablecval{27.8}\papertablecval{-7.4}\papertableuval{2.85}{.08}\papertableuval{9.98}{.03}\\\paperiline
-\papertableindex\papertablecval{27.9}\papertablecval{-7.6}\papertableuval{2.86}{.08}\papertableuval{10.05}{.03}\\\paperiline
-\papertableindex\papertablecval{28.1}\papertablecval{-7.9}\papertableuval{2.86}{.08}\papertableuval{10.05}{.03}\\\paperiline
-\papertableindex\papertablecval{28.1}\papertablecval{-8.1}\papertableuval{2.87}{.08}\papertableuval{10.07}{.03}\\\paperiline
-\papertableindex\papertablecval{28.2}\papertablecval{-8.2}\papertableuval{2.84}{.08}\papertableuval{9.99}{.03}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.6}\papertableuval{2.87}{.08}\papertableuval{10.06}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-7.9}\papertableuval{2.87}{.08}\papertableuval{10.05}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-8.1}\papertableuval{2.87}{.08}\papertableuval{10.08}{.03}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{-8.2}\papertableuval{2.85}{.08}\papertableuval{10.00}{.03}\\\paperiline
 \papertableindex\papertablecval{28.3}\papertablecval{-8.3}\papertableuval{2.87}{.08}\papertableuval{10.13}{.03}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-8.5}\papertableuval{2.87}{.08}\papertableuval{10.14}{.03}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-8.6}\papertableuval{2.87}{.08}\papertableuval{10.15}{.03}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-8.7}\papertableuval{2.88}{.08}\papertableuval{10.21}{.03}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-8.7}\papertableuval{2.87}{.08}\papertableuval{10.21}{.03}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-8.6}\papertableuval{2.84}{.08}\papertableuval{10.09}{.03}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-8.8}\papertableuval{2.72}{.07}\papertableuval{9.69}{.03}\\\paperiline
-\papertableindex\papertablecval{28.3}\papertablecval{-8.9}\papertableuval{2.75}{.08}\papertableuval{9.79}{.03}\\\paperiline
-\papertableindex\papertablecval{28.2}\papertablecval{-8.9}\papertableuval{2.71}{.07}\papertableuval{9.66}{.03}\\\paperiline
-\papertableindex\papertablecval{28.1}\papertablecval{-8.9}\papertableuval{2.83}{.08}\papertableuval{10.17}{.03}\\\paperiline
-\papertableindex\papertablecval{28.1}\papertablecval{-8.9}\papertableuval{2.83}{.08}\papertableuval{10.19}{.03}\\\paperiline
-\papertableindex\papertablecval{28.1}\papertablecval{-9.0}\papertableuval{2.84}{.08}\papertableuval{10.25}{.03}\\\paperiline
-\papertableindex\papertablecval{28.1}\papertablecval{-9.0}\papertableuval{2.84}{.08}\papertableuval{10.27}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.5}\papertableuval{2.88}{.08}\papertableuval{10.14}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.6}\papertableuval{2.87}{.08}\papertableuval{10.16}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.7}\papertableuval{2.88}{.08}\papertableuval{10.22}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.7}\papertableuval{2.88}{.08}\papertableuval{10.22}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.6}\papertableuval{2.85}{.08}\papertableuval{10.09}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.8}\papertableuval{2.72}{.07}\papertableuval{9.70}{.03}\\\paperiline
+\papertableindex\papertablecval{28.3}\papertablecval{-8.9}\papertableuval{2.76}{.08}\papertableuval{9.79}{.03}\\\paperiline
+\papertableindex\papertablecval{28.2}\papertablecval{-8.9}\papertableuval{2.72}{.07}\papertableuval{9.66}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-8.9}\papertableuval{2.84}{.08}\papertableuval{10.17}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-8.9}\papertableuval{2.84}{.08}\papertableuval{10.20}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-9.0}\papertableuval{2.85}{.08}\papertableuval{10.25}{.03}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-9.0}\papertableuval{2.85}{.08}\papertableuval{10.27}{.03}\\\paperiline
 \papertableindex\papertablecval{28.2}\papertablecval{-9.1}\papertableuval{2.85}{.08}\papertableuval{10.31}{.03}\\\paperoline
-\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_d$ ($\si{\celsius}$), $I_d$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the second part of the experiment.}
+\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_d$ ($\si{\celsius}$), $V_d$ ($\si{\volt}$), and $I_d$ ($\si{\ampere}$) for the first part of the second part of the experiment.}
+
+	\paperfig{TableTwoB}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[inner]C|[outer]}\paperoline
+			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertablecheadersymbol{V_d~(\si{\volt})}\papertablecheadersymbol{I_d~(\si{\ampere})}\\
+			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertablecheaderunit{.004}{$\si{\volt}$}\papertablecheaderunit{.3}{$\si{\ampere}$}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-7.0}\papertablecval{2.573}\papertablecval{12.1}\\\paperiline
+\papertableindex\papertablecval{27.9}\papertablecval{-6.6}\papertablecval{2.603}\papertablecval{12.6}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{-5.3}\papertablecval{2.524}\papertablecval{12.4}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{-3.9}\papertablecval{2.535}\papertablecval{12.8}\\\paperiline
+\papertableindex\papertablecval{28.0}\papertablecval{-2.7}\papertablecval{2.510}\papertablecval{12.8}\\\paperiline
+\papertableindex\papertablecval{28.1}\papertablecval{-1.4}\papertablecval{2.479}\papertablecval{12.9}\\\paperiline
+\papertableindex\papertablecval{28.9}\papertablecval{-0.3}\papertablecval{2.752}\papertablecval{14.8}\\\paperiline
+\papertableindex\papertablecval{29.4}\papertablecval{0.4}\papertablecval{2.742}\papertablecval{15.0}\\\paperiline
+\papertableindex\papertablecval{28.9}\papertablecval{2.2}\papertablecval{2.447}\papertablecval{13.6}\\\paperiline
+\papertableindex\papertablecval{28.5}\papertablecval{4.0}\papertablecval{2.512}\papertablecval{14.3}\\\paperiline
+\papertableindex\papertablecval{28.7}\papertablecval{5.4}\papertablecval{2.542}\papertablecval{14.8}\\\paperoline
+	\end{papertable}\vspace{-0.5em}}{TODO}
 

### 2018-02-13 thermoelectricity/paper.tex
done tables

@@
 
-	\paperfig{TableTwoB}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[inner]C|[outer]}\paperoline
+	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[inner]C|[outer]}\paperoline
 			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertablecheadersymbol{V_d~(\si{\volt})}\papertablecheadersymbol{I_d~(\si{\ampere})}\\
@@
 \papertableindex\papertablecval{28.7}\papertablecval{5.4}\papertablecval{2.542}\papertablecval{14.8}\\\paperoline
+	\end{papertable}\vspace{-0.5em}}{TODO}
+
+	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]U|[inner]U|[inner]C|[outer]}\paperoline
+			\papertableindexheader\papertableuheadersymbol{V_{in}}\papertableuheadersymbol{I_{in}}\papertablecheadersymbol{V_s}\\
+			\papertableuheadersymbol{(\si{\volt})}\papertableuheadersymbol{(\si{\ampere})}\papertablecheadersymbol{(\si{\volt})}\\\paperiline
+\papertableindex\papertableuval{0.00}{.02}\papertableuval{0.00}{.01}\papertablecval{0.408}\\\paperiline
+\papertableindex\papertableuval{0.67}{.03}\papertableuval{1.50}{.05}\papertablecval{0.396}\\\paperiline
+\papertableindex\papertableuval{0.95}{.04}\papertableuval{2.12}{.06}\papertablecval{0.392}\\\paperiline
+\papertableindex\papertableuval{1.16}{.04}\papertableuval{2.57}{.07}\papertablecval{0.367}\\\paperiline
+\papertableindex\papertableuval{1.34}{.05}\papertableuval{2.99}{.08}\papertablecval{0.353}\\\paperiline
+\papertableindex\papertableuval{1.50}{.05}\papertableuval{3.33}{.09}\papertablecval{0.336}\\\paperiline
+\papertableindex\papertableuval{1.66}{.05}\papertableuval{3.6}{.1}\papertablecval{0.339}\\\paperiline
+\papertableindex\papertableuval{1.78}{.06}\papertableuval{3.9}{.1}\papertablecval{0.337}\\\paperiline
+\papertableindex\papertableuval{1.90}{.06}\papertableuval{4.2}{.1}\papertablecval{0.304}\\\paperiline
+\papertableindex\papertableuval{2.03}{.06}\papertableuval{4.4}{.1}\papertablecval{0.281}\\\paperiline
+\papertableindex\papertableuval{2.13}{.06}\papertableuval{4.7}{.1}\papertablecval{0.273}\\\paperoline
 	\end{papertable}\vspace{-0.5em}}{TODO}

### 2018-02-13 thermoelectricity/1.py
Fit results

@@ -10,6 +10,9 @@ from scipy.optimize import curve_fit
 
 # ---------- User-Defined Function ----------
 
+def func(x, a, b):
+	return a * x + b
+
 # ---------- Main Code ----------
 
 plt.rc('font', family = 'Times New Roman')
@@ -22,12 +25,48 @@ T0_unc = 0.1
 P = V * I
 P_unc = np.abs(P) * np.sqrt((I_unc / I) ** 2 + (V_unc / V) ** 2)
 T_unc = np.sqrt(2 * T1_unc ** 2)
-print(P_unc)
+
+ddof = T1.size - 2
+
+print "T_in - T_out"
+popt1, pcov1 = curve_fit(func, P, T2 - T1)
+print "a:", popt1[0], "+-", np.sqrt(pcov1[0, 0])
+print "b:", popt1[1], "+-", np.sqrt(pcov1[1, 1])
+# Find residuals
+r = (T2 - T1) - func(P, *popt1)
+chisq = np.sum((r / T_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((T2 - T1 - np.mean(T2 - T1)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
+print "\n K_d", 1 / popt1[0], "+-", np.sqrt(pcov1[0, 0]) / (popt1[0] ** 2), "\n"
+
+print "T_out - T_0"
+popt2, pcov2 = curve_fit(func, P, T1 - T0)
+print "a:", popt2[0], "+-", np.sqrt(pcov2[0, 0])
+print "b:", popt2[1], "+-", np.sqrt(pcov2[1, 1])
+
+# Find residuals
+r = (T1 - T0) - func(P, *popt2)
+chisq = np.sum((r / T_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((T1 - T0 - np.mean(T1 - T0)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
+print "\n K_hs", 1 / popt2[0], "+-", np.sqrt(pcov2[0, 0]) / (popt2[0] ** 2), "\n"
 
 plt.plot(P, T2 - T1, label = "T_in - T_out", color = "red")
[…]

### 2018-02-13 thermoelectricity/2a.py

@@ -10,6 +10,9 @@ from scipy.optimize import curve_fit
 
 # ---------- User-Defined Function ----------
 
+def func(x, a, b, c):
+	return a + b * np.exp(c * x)
+
 # ---------- Main Code ----------
 
 plt.rc('font', family = 'Times New Roman')
@@ -19,6 +22,27 @@ V, I, T1, T2 = np.loadtxt(path_to_file, unpack = True)
 
 P = V * I
 delta_T = T1 - T2
+delta_T_unc = np.full((1, delta_T.size), np.sqrt(2) * 0.1)[0]
+
+ddof = delta_T.size - 3
+
+# Time array
+t = np.arange(0, 1.0 * delta_T.size, 1.0)
+
+popt, pcov = curve_fit(func, t, delta_T, p0 = [37, -37, -1/14])
+print "a:", popt[0], "+-", np.sqrt(pcov[0, 0])
+print "b:", popt[1], "+-", np.sqrt(pcov[1, 1])
+print "c:", popt[2], "+-", np.sqrt(pcov[2, 2])
+# Find residuals
+r = delta_T - func(t, *popt)
+chisq = np.sum((r / delta_T_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((delta_T - np.mean(delta_T)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
 
 plt.figure(num = None, figsize = (10, 6), dpi = 80, facecolor = 'w')
 # Plot power
@@ -30,7 +54,8 @@ plt.xticks([], [])
 plt.ylabel("Power (W)")
 # Plot temperature difference
 plt.subplot(122)
-plt.plot(delta_T, color = "blue", label = "Temperature difference (K)")
+plt.plot(t, delta_T, color = "blue", label = "Temperature difference (K)")
+plt.plot(t, func(t, *popt))
 plt.gca().set_title("Temperature change")
 plt.xticks([], [])
 plt.grid(True)

### 2018-02-13 thermoelectricity/2b.py

@@ -21,6 +21,16 @@ P_in = V_in * I_in
 delta_T = T1 - T2
 P_d = V_d * I_d
 
+K_d = 0.58858351619
+K_d_unc = 0.0582914163177 
+
+# S_d = (V_in * I_in + 0.5 * V_d * I_d + K_d * (T1 - T2)) / (T2 * I_d)
+S_d = V_s / (T1 - T2)
+print "S_d:", np.mean(S_d), "+-", np.std(S_d)
+
+R_d = V_d / I_d
+print "R_d:", np.mean(R_d), "+-", np.std(R_d)
+
 # Plot data
 plt. figure(num = None, figsize = (14, 8), dpi = 80, facecolor = 'w')
 # Temperature difference

### 2018-02-13 thermoelectricity/paper.tex
stuff
everything except five and six

@@
 
-	Abstract goes here
+	This experiment investigated the properties of thermoelectric cooling. This
+process is based on the Peltier and Seeback effects to use energy to pump heat.
+This experiment measured various properties of the thermoelectric cooler.
+The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$.
+The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
+The Seebeck coefficient for the system, $S_d$, was determined to be $(11.6\pm.1)\si{\milli\volt\per\kelvin}$.
+The internal resistance of the thermoelectric cooler, $R_d$, was determined to be $(0.19\pm.01)\si{\ohm}$.
+The lowest achievable temperature at the thermal reservoir with no heat input was determined to be $(-9.1\pm.2)\si{\kelvin}$.
+The optimum drive current for the system was determined to be TODO.
+The lowest achievable temperature with the optimum input current was determined to be TODO.
 
@@
 
-	The experimental setup included the TEC, \textbf{four} multimeters, current balance, Variac transformer, filter capacitors to filter out noise produced by the TEC, and a \textbf{thermometer}, all arranged as shown below.
+	The experimental setup included the TEC, four multimeters, current balance, Variac transformer, filter capacitors to filter out noise produced by the TEC, and a temperature sensor, all arranged as shown below.
 
@@
 To make the measurements, the terminals were open-circuited (obtained by unplugging one of the chords connecting the TEC to the DC ammeter).
+
 	The ambient temperature was determined to be \( \pars{22.1 \pm 0.1} \si{\celsius} \), and was found to remain constant throughout the obtaining of the measurements.
+
+	The following are measured values of the temperatures of the input reservoir, the heat sink, the input potential and the input current.
 
@@
 	\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $I_{in}$ ($\si{\ampere}$), and $V_{in}$ ($\si{\volt}$) for the first part of the experiment.}
-
-	Further, after allowing the system to cool off, the TEC was operated with an approximately fixed current supplied from the built-in power supply.
-The Variac transformer was turned off; measurements of voltage across the TEC and the current supplied to it, as well as the temperatures of the output and the input reservoir were taken.
 
@@
 \papertableindex\papertablecval{28.2}\papertablecval{-9.1}\papertableuval{2.85}{.08}\papertableuval{10.31}{.03}\\\paperoline
-\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_d$ ($\si{\celsius}$), $V_d$ ($\si{\volt}$), and $I_d$ ($\si{\ampere}$) for the first part of the second part of the experiment.}
+\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $V_d$ ($\si{\volt}$), and $I_d$ ($\si{\ampere}$) for the first part of the second part of the experiment.}
+
+	Further, after allowing the system to cool off, the TEC was operated with an approximately fixed current supplied from the built-in power supply.
+The Variac transformer was turned off; measurements of voltage across the TEC and the current supplied to it, as well as the temperatures of the output and the input reservoir were taken (see \figPartTwoA).
+
+	One of the main sources of error in the experiment was the non-constant potential of the current balance, which seemed to always be smaller than the marked potential of 6 volts.
+For this reason, a fourth multimeter was used in the data collection to account for this.
 
@@
 \papertableindex\papertablecval{28.7}\papertablecval{5.4}\papertablecval{2.542}\papertablecval{14.8}\\\paperoline
-	\end{papertable}\vspace{-0.5em}}{TODO}
+	\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_d$ ($\si{\celsius}$), $V_d$ ($\si{\volt}$), and $I_d$ ($\si{\ampere}$) for the second part of the second part of the experiment.}\vspace{2em}
 
@@
 \papertableindex\papertableuval{2.13}{.06}\papertableuval{4.7}{.1}\papertablecval{0.273}\\\paperoline
-	\end{papertable}\vspace{-0.5em}}{TODO}
+	\end{papertable}\vspace{-0.5em}}{Measurements of $V_{in}$ ($\si{\volt}$), $I_{in}$ ($\si{\ampere}$), and $V_s$ ($\si{\volt}$) for the second part of the second part of the experiment.}\vspace{2em}
 
@@
 
-	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but were too small to be visible.}
+	\paperfig{PartOne}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals.
+The error bars were included but were too small to be visible.
+Linear functions were fitted to the two curves in the graph.
+The reciprocals of their slopes are the thermal conductances between the relevant materials.
+The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$.
+This fit had a reduced $\chi^2$ of 24.2124 and an $R^2$ value of 0.962248.
+The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
+This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316.}
 
@@
 
-	\paperfig{part2a}{\pdf{part2a-data}}{Power and temperature difference plotted against time. Uncertainties were included but were too small to be visible.}
+	The thermal conductance between the input and the output reservoirs, $K_d$, obeys the following relation.
+
+	\papereq{Kd}{P_K=K_d\Delta T}{AF, 2014}
+
+	The thermal conductance between the output heat sink and the ambient air, $K_{hs}$, obeys a similar relation.
+Thus, the values of $K_d$ and $K_{hs}$ were computed by fitting linear functions to the curves in \figPartOne and taking the reciprocals of the obtained values.
+The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$.
+The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
+
+	\paperfig{partTwoa}{\pdf{part2a-data}}{Power and temperature difference plotted against time.
+Uncertainties were included but were too small to be visible.
+An increasing exponential function with a plateau was fit to the temperature difference.
+The plateau was determined to have a height of $(37.3\pm.2)\si{\kelvin}$.
+This fit had a reduced $\chi^2$ of 20.3006 and an $R^2$ value of 0.994558.}
+
+	An overall linear increase in the power input as a function of time was observed except for the rapid decreases that could be attributed to noise in the circuit.
+
+	The TEC model was used to predict the lowest achievable temperature with no heat input.
+This was done by modeling the graph in \figpartTwoa as an increasing exponential function with a plateau.
+This resulted in the largest possible temperature difference, which was compared against the existing data in \figPartTwoA.
+As a result, the lowest achievable temperature at the thermal reservoir with no heat input was determined to be $(-9.1\pm.2)\si{\kelvin}$.
 
@@
 
-	Conclusion goes here
+	Although most of the values obtained in this experiment had high precision, the experiment was not free from sources of error.
+The primary source of error was the fluctuating potential of the current balance.
+An attempt was made to mitigate this by adding a fourth multimeter to the data collection.
+
+	A secondary source of error came from the fact that both the input thermal reservoir and the heat sink were both in contact with the surrounding air, in which eddies and other current were free to exchange heat, thereby introducing uncertainty into the measurements in this experiment.
+
+	Aside from the sources of error, the experiment was successful in determining the key values in question. These were determined to be the following.
+The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$.
+The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
+The Seebeck coefficient for the system, $S_d$, was determined to be $(11.6\pm.1)\si{\milli\volt\per\kelvin}$.
+The internal resistance of the thermoelectric cooler, $R_d$, was determined to be $(0.19\pm.01)\si{\ohm}$.
+The lowest achievable temperature at the thermal reservoir with no heat input was determined to be $(-9.1\pm.2)\si{\kelvin}$.
+The optimum drive current for the system was determined to be TODO.
+The lowest achievable temperature with the optimum input current was determined to be TODO.
 

### 2018-02-13 thermoelectricity/paper.tex
should be done. just need residuals

@@
 The lowest achievable temperature at the thermal reservoir with no heat input was determined to be $(-9.1\pm.2)\si{\kelvin}$.
-The optimum drive current for the system was determined to be TODO.
-The lowest achievable temperature with the optimum input current was determined to be TODO.
+The optimum drive current for the system was determined to be $(17.0\pm.9)\si{\ampere}$.
+The lowest achievable temperature with the optimum input current was determined to be $(-18.4\pm.3)\si{\celsius}$.
 
@@
 
-	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]U|[inner]U|[inner]C|[outer]}\paperoline
+	\paperfig{TableTwoBTwo}{\centering\begin{papertable}{|[outer]I|[inner]U|[inner]U|[inner]C|[outer]}\paperoline
 			\papertableindexheader\papertableuheadersymbol{V_{in}}\papertableuheadersymbol{I_{in}}\papertablecheadersymbol{V_s}\\
@@
 The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
-This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316.}
+This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316.}\vspace{2em}
 
@@
 	\papereq{Kd}{P_K=K_d\Delta T}{AF, 2014}
+	\begin{paperwhere}
+	\papervar{P_K}{power}{\watt}
+	\papervar{K_d}{thermal conductance}{\watt\per\kelvin}
+	\papervar{\Delta T}{temperature difference}{\kelvin}
+	\end{paperwhere}
 
@@
 input power (right).
-Uncertainties were included but were too small to be visible.}
+Uncertainties were included but were too small to be visible.}\vspace{2em}
+
+	The internal resistance of the thermoelectric cooler, $R_d$, was determined using Ohm's law.
+
+	\papereq{OhmAgain}{R_d=\frac{V_d}{I_d}}{AF, 2014}
+	\begin{paperwhere}
+	\papervar{R_d}{TEC resistance}{\ohm}
+	\papervar{V_d}{TEC potential}{\volt}
+	\papervar{I_d}{TEC current}{\ampere}
+	\end{paperwhere}
+
+	By combining \eqOhmAgain with data from \figTableTwoBOne, the internal resistance of the thermoelectric cooler, $R_d$, was determined to be $(0.19\pm.01)\si{\ohm}$.
+
+	By a similar process, the Seebeck coefficient was determined by using the model for the TEC.
+
+	\papereq{Seebeck}{S_d=\frac{V_s}{\Delta T}}{AF, 2014}
+	\begin{paperwhere}
+	\papervar{S_d}{Seebeck coefficient}{\volt\per\kelvin}
+	\papervar{V_s}{Seebeck potential}{\volt}
+	\papervar{\Delta T}{temperature difference}{\kelvin}
+	\end{paperwhere}
+
+	By combining \eqSeebeck with data from \figTableTwoBOne and \figTableTwoBTwo, the Seebeck coefficient for the system, $S_d$, was determined to be $(11.6\pm.1)\si{\milli\volt\per\kelvin}$.
+
+	By examining the derivative of $P_{in}$ with an output temperature of $\SI{35}{\celsius}$ and an input temperature not exceeding $\SI{5}{\celsius}$, the optimum input current was determined using the TEC model.
+It is known that $P_{in}$ obeys the following relation.
+
+	\papereq{Pin}{\fontsize{10pt}{10pt}\selectfont P_{in}=(T_{out}-\Delta T)S_dI_d-\frac12R_dI^2_d-K_d\Delta T}{AF, 2014}
+	\begin{paperwhere}
+	\papervar{P_{in}}{input power}{\watt}
+	\papervar{T_{out}}{output temperature}{\kelvin}
+	\papervar{\Delta T}{temperature difference}{\kelvin}
+	\papervar{S_d}{Seebeck coefficient}{\volt\per\kelvin}
+	\papervar{I_d}{TEC current}{\ampere}
+	\papervar{R_d}{TEC resistance}{\ohm}
+	\papervar{K_d}{thermal conductance}{\watt\per\kelvin}
+	\end{paperwhere}
+
+	When differentiated and set to zero to find the maximum, the optimal input current was shown to be equal to the following.
+
+	\papereq{Diff}{I_d=\frac{(T_{out}-\Delta T)S_d}{R_d}}{}
+	\begin{paperwhere}
+	\papervar{T_{out}}{output temperature}{\kelvin}
+	\papervar{\Delta T}{temperature difference}{\kelvin}
+	\papervar{S_d}{Seebeck coefficient}{\volt\per\kelvin}
+	\papervar{I_d}{TEC current}{\ampere}
+	\papervar{R_d}{TEC resistance}{\ohm}
+	\end{paperwhere}
+
+	The optimal current was thus found to be $(17.0\pm.9)\si{\ampere}$.
+
+	If no heat were admitted to the reservoir, $P_{in}$ is set to 0.
+By using the value for the optimal current and rearranging \eqPin to solve for $T_{in}$, the lowest input temperature was shown to be $(-18.4\pm.3)\si{\celsius}$.
+
+	Lastly, to have a dynamic model, the PID stabilization algorithm could be used.
+This could be done in combination with the well known heat equation to create a model for the spread of heat through the system.
+These partial differential equations could be solved with numerical methods for modeling the transition of heat between the boundaries of the TEC elements.
 

### 2018-02-13 thermoelectricity/1.py
Residuals

@@ -33,11 +33,11 @@ popt1, pcov1 = curve_fit(func, P, T2 - T1)
 print "a:", popt1[0], "+-", np.sqrt(pcov1[0, 0])
 print "b:", popt1[1], "+-", np.sqrt(pcov1[1, 1])
 # Find residuals
-r = (T2 - T1) - func(P, *popt1)
-chisq = np.sum((r / T_unc) ** 2)
+r1 = (T2 - T1) - func(P, *popt1)
+chisq = np.sum((r1 / T_unc) ** 2)
 print "Reduced chi squared:", chisq / ddof
 # Calculate and print R^2
-ss_res = np.sum(r ** 2)
+ss_res = np.sum(r1 ** 2)
 ss_tot = np.sum((T2 - T1 - np.mean(T2 - T1)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
 print "R^2:", r_squared
@@ -50,17 +50,19 @@ print "a:", popt2[0], "+-", np.sqrt(pcov2[0, 0])
 print "b:", popt2[1], "+-", np.sqrt(pcov2[1, 1])
 
 # Find residuals
-r = (T1 - T0) - func(P, *popt2)
-chisq = np.sum((r / T_unc) ** 2)
+r2 = (T1 - T0) - func(P, *popt2)
+chisq = np.sum((r2 / T_unc) ** 2)
 print "Reduced chi squared:", chisq / ddof
 # Calculate and print R^2
-ss_res = np.sum(r ** 2)
+ss_res = np.sum(r2 ** 2)
 ss_tot = np.sum((T1 - T0 - np.mean(T1 - T0)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
 print "R^2:", r_squared
 
 print "\n K_hs", 1 / popt2[0], "+-", np.sqrt(pcov2[0, 0]) / (popt2[0] ** 2), "\n"
 
+fig1 = plt.figure(1)
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
 plt.plot(P, T2 - T1, label = "T_in - T_out", color = "red")
 plt.errorbar(P, T2 - T1, xerr = P_unc, yerr = T_unc, linestyle = "None", color = "black")
 plt.plot(P, func(P, *popt1))
@@ -69,8 +71,15 @@ plt.errorbar(P, T1 - T0, xerr = P_unc, yerr = T_unc, linestyle = "None", color =
[…]

### 2018-02-13 thermoelectricity/2a.py

@@ -44,16 +44,16 @@ ss_tot = np.sum((delta_T - np.mean(delta_T)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
 print "R^2:", r_squared
 
-plt.figure(num = None, figsize = (10, 6), dpi = 80, facecolor = 'w')
+figure = plt.figure(num = None, figsize = (10, 6), dpi = 80, facecolor = 'w')
 # Plot power
-plt.subplot(121)
+ax1 = figure.add_subplot(221)
 plt.plot(P, color = "red", label = "Power (W)")
 plt.grid(True)
 plt.gca().set_title("Power input")
 plt.xticks([], [])
 plt.ylabel("Power (W)")
 # Plot temperature difference
-plt.subplot(122)
+ax2 = figure.add_subplot(222)
 plt.plot(t, delta_T, color = "blue", label = "Temperature difference (K)")
 plt.plot(t, func(t, *popt))
 plt.gca().set_title("Temperature change")
@@ -62,5 +62,13 @@ plt.grid(True)
 plt.ylabel("Temperature difference (K)")
 plt.suptitle("TEC data, Varniac autotransformer turned off")
 plt.savefig("part2a-data.pdf")
+ax3 = figure.add_subplot(313)
+plt.scatter(t, r)
+plt.grid(True)
+plt.xlabel("Time")
+plt.xticks([], [])
+plt.ylabel("Residuals")
+ax3.title.set_text("Temperature difference vs. time fit residuals")
+plt.title("")
 plt.show()
 

### 2018-02-13 thermoelectricity/2a.py
Residuals better

@@ -61,7 +61,6 @@ plt.xticks([], [])
 plt.grid(True)
 plt.ylabel("Temperature difference (K)")
 plt.suptitle("TEC data, Varniac autotransformer turned off")
-plt.savefig("part2a-data.pdf")
 ax3 = figure.add_subplot(313)
 plt.scatter(t, r)
 plt.grid(True)
@@ -69,6 +68,6 @@ plt.xlabel("Time")
 plt.xticks([], [])
 plt.ylabel("Residuals")
 ax3.title.set_text("Temperature difference vs. time fit residuals")
-plt.title("")
+plt.savefig("part2a-data.pdf")
 plt.show()
 

### 2018-02-13 thermoelectricity/paper.tex
final version

@@
 
-	To visualize the data with the open-circuited terminals, temperature difference was plotted against the input power. Uncertainties were propagated using the method of quadratures.
+	To visualize the data with the open-circuited terminals, temperature difference was plotted against the input power. Uncertainties were propagated using the method of quadratures.\\
 
@@
 The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
-This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316.}\vspace{2em}
+This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316.
+Residuals for the fits are shown below the plot.}\vspace{2em}
 
@@
 The plateau was determined to have a height of $(37.3\pm.2)\si{\kelvin}$.
-This fit had a reduced $\chi^2$ of 20.3006 and an $R^2$ value of 0.994558.}
+This fit had a reduced $\chi^2$ of 20.3006 and an $R^2$ value of 0.994558.
+Residuals for the fit are shown below the plot.}
 
@@
 	By examining the derivative of $P_{in}$ with an output temperature of $\SI{35}{\celsius}$ and an input temperature not exceeding $\SI{5}{\celsius}$, the optimum input current was determined using the TEC model.
-It is known that $P_{in}$ obeys the following relation.
+It is known that $P_{in}$ obeys the following relation.\columnbreak
 

### 2018-02-22 interfer/paper.tex
Added interferometry folder
Started interferometers paper

--- 2018-02-06 thermoelectricity/paper.tex
@@
 \input{header}
+\usepackage{tikz}
+\usetikzlibrary{optics}
 
@@
 \begin{document}
-\papertitle{Thermoelectricity}
+\papertitle{Interferometers}
 \paperauth{A}{Khesin}{1002442029}
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{February 12, 2018, Completed February 6, 2018}
+\paperdate{}
 \begin{paperabs}
@@
 
-	Introduction goes here
+	Interference patterns produced by various light sources may be studied using interferometers, which operate by dividing either the wavefront or the amplitude of the original light beam.
+In this experiment, an amplitude-splitting interferometer, the Michelson interferometer, was used extensively to determine the indexes of refraction of a transparent solid and a gas after being calibrated using a sodium light.
+
+	\paperfig{MichelsonInterferometer}{% Still need to figure out labels (esp. the slide location)
+	\begin{tikzpicture}[use optics]
+		\node[thick optics element] at (-2.5, 0) {};
+		\node[thick optics element, rotate = -45] at (0, 0) {};
+		\node[generic optics io, io body aspect ratio = 1] at (-4.0, 0) {};
+		\node[mirror] at (3.0, 0) {};
+		\node[mirror, rotate = 90] at (0, 3.0) {};
+		\node[thick optics element, rotate = -45] at (1.5, -0.5) {};
+		\draw[->-] (-3.38, 0) -- (-0.15, 0);
+		\draw[->-] (-0.15, 0) -- (-0.15, 3.0);
+		\draw[->-] (0, 3.0) -- (0, 0.15);
+		\draw[] (0, 0.15) -- (0.15, 0);
+		\draw[->-] (0.15, 0) -- (0.15, -3.0);
+		\draw[] (-0.15, 0) -- (0, -0.15);
+		\draw[->-] (0, -0.15) -- (1.7, -0.15);
+		\draw[] (1.7, -0.15) -- (1.85, -0.3);
+		\draw[->-] (1.85, -0.3) -- (3.0, -0.3);
+		\draw[->-] (3.0, -0.45) -- (1.70, -0.45);
+		\draw[] (1.70, -0.45) -- (1.55, -0.3);
+		\draw[->-] (1.55, -0.3) -- (-0.15, -0.3);
+		\draw[->-] (-0.15, -0.3) -- (-0.15, -3.0);
+		\node[sensor line, rotate = -90] at (0, -3.2) {};	% May switch this to another element
+		\node[thin optics element, rotate = 90] at (0, 2.25) {};
+	\end{tikzpicture}}{Schematic diagram of the Michelson interferometer.}
+
+	Prior to making any measurements, the Michelson interferometer was calibrated against a sodium lamp with an assumed mean wavelength value of \( \lambda = 598.3 \) \si{nm}.
+The calibration curve itself was obtained by moving the carriage toward the observer, counting the number of fringes disappearing from the middle of the field of view and plotting the results.
+
+	Once the interferometer was calibrated, the setup could be used to determine the index of refraction of various materials.
+For instance, the index of refraction of a transparent solid---a microscope slide---was found.
+In general, the index of refraction of a solid can be shown to obey the following relation.
+
+	\papereq{SolidRefractiveIndex}{\mu = \frac{m \lambda}{2d} + 1}{\textbf{TODO}}
+	\begin{paperwhere}
+		\papervar{\mu}{index of refraction}{}
+		\papervar{m}{number of fringes displaced}{}
+		\papervar{\lambda}{wavelength of light}{\meter}
+		\papervar{d}{thickness of the solid}{\meter}
+	\end{paperwhere}
+
+	As seen from \eqSolidRefractiveIndex, inserting a transparent solid into the optical path of the beam results in a displacement of the interference pattern produced by the light source.
 
@@
 
-	\papersource{Albanelli, P., Fomichev, S., Thermoelectricity, 2014}
+	\papersource{}
 

### 2018-02-22 interfer/linfit.py

@@ -18,8 +18,54 @@ def func(x, a, b):
 
 # Set desired font
 plt.rc('font', family = 'Times New Roman')
-path_to_file = "measurements.txt"
+path_to_file = "calibration.txt"
 num, reading = np.loadtxt(path_to_file, unpack = True)
+reading_unc = np.full((1, reading.size), 0.005)[0]
+ddof = reading.size - 2
 
+wavelength = 589.3e-9	# m
+
+# Plot micrometer reading vs, fringe count
 plt.plot(num, reading)
+plt.grid(True)
+plt.xlabel("Fringe count")
+plt.ylabel("Micrometer reading")
+plt.title("Micrometer reading vs. fringe count for sodium lamp")
+plt.savefig("calibration1.pdf")
+plt.close()
+
+dist = num * wavelength / 2		# m
+
+popt, pcov = curve_fit(func, dist, reading, sigma = reading_unc)
+print "a:", popt[0], "+-", np.sqrt(pcov[0, 0]), "(slope)"
+print "b:", popt[1], "+-", np.sqrt(pcov[1, 1])
+# Calculate chi squared + residuals
+r = reading - func(dist, *popt)
+chisq = np.sum((r / reading_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((reading - np.mean(reading)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
+print "\n", "Inverse slope:", 1 / popt[0], "<-- f value used for calibration"
+
+# Plot micrometer reading vs. carriage displacement
+fig1 = plt.figure(1)
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+plt.scatter(dist, reading, color = "black", s = 10)
+plt.plot(dist, func(dist, *popt), color = "black")
+plt.grid(True)
+plt.ylabel("Micrometer reading")
+plt.xlim([-0.3e-4, 3.3e-4])
+frame1.set_xticklabels([])
+plt.title("Micrometer reading vs. carriage displacement for sodium lamp")
+frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
+plt.scatter(dist, r, color = "black", s = 10)
+plt.ylabel("Residuals")
[…]

### 2018-02-22 polarization/exercise2.py

@@ -20,8 +20,8 @@ def f(x, a):
 # Set desired font
 plt.rc('font', family = 'Times New Roman')
 # Concatenate data files to conver 360 degrees
-path_to_file_1 = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise2-1.txt"
-path_to_file_2 = "C:\\Users\\Andrey\\Documents\\PHY324\\polarization\\exercise2-2.txt"
+path_to_file_1 = "exercise2-1.txt"
+path_to_file_2 = "exercise2-2.txt"
 pos_1, I_1 = np.loadtxt(path_to_file_1,unpack = True)
 pos_2, I_2 = np.loadtxt(path_to_file_2,unpack = True)
 # Shift second  

### 2018-03-04 interfer/paper.tex
Fabry measurements

@@
 \input{header}
-\usepackage{tikz}
-\usetikzlibrary{optics}
-
 \physics
@@
 	Interference patterns produced by various light sources may be studied using interferometers, which operate by dividing either the wavefront or the amplitude of the original light beam.
-In this experiment, an amplitude-splitting interferometer, the Michelson interferometer, was used extensively to determine the indexes of refraction of a transparent solid and a gas after being calibrated using a sodium light.
+In this experiment, the Michelson interferometer was used extensively to determine the indexes of refraction of a transparent solid and a gas after being calibrated using a sodium light.
+As seen from the schematic below, the Michelson interferometer operates by splitting the amplitude of the incident beam.
 
@@
 		\draw[->-] (-0.15, -0.3) -- (-0.15, -3.0);
-		\node[sensor line, rotate = -90] at (0, -3.2) {};	% May switch this to another element
+		\node[thin optics element, rotate = -90] at (0, -3.0) {};
 		\node[thin optics element, rotate = 90] at (0, 2.25) {};
-	\end{tikzpicture}}{Schematic diagram of the Michelson interferometer.}
+	\end{tikzpicture}}{\textbf{TODO}}
 

### 2018-03-06 interfer/paper.tex
Final interferometer paper

--- 2018-02-22 interfer/paper.tex
@@
 \begin{document}
-\papertitle{Interferometers}
+\papertitle{Analysis of Interferometer Properties}
 \paperauth{A}{Khesin}{1002442029}
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{}
+\paperdate{March 5, 2018, Completed February 27, 2018}
 \begin{paperabs}
 
-	Abstract goes here
+	This experiment investigated various uses of inteferometers for determining unknown constants.
+The experiment produced results that were consistent with the current ones.
+The calibration curve for the Michelson interferometer was fit with the function \( \pars{5770 \pm 30 } x + \pars{19.991 \pm .006} \), a $\chi^2$ value of 7.9231, and an \( R^2 \) value of \( 0.9993 \).
+	The refractive index for the microscope slide was determined to be $(1.480\pm.03)$, which was close to the accepted value of 1.5251.
+	The pressure as a function of the number of fringes was found to be \( \pars{16.39 \pm 0.04}x \), with a $\chi^2$ value of 1.5654, and an \( R^2 \) value of \( 0.9992 \).
+	The refractive index for air was determined to be $(1.00029\pm.00001)$, which was close to the accepted value of 1.000277.
+	The Fabry-Per\'ot interferometer calibration curve was found to be \( \pars{5390 \pm 30} x + \pars{12.146 \pm .005 } \), with a $\chi^2$ value of 6.6118, and an \( R^2 \) value of \( 0.9994 \).
+	The sodium doublet wavelength separation was found to be $(0.60\pm.03)\si{\nano\meter}$, which is close to the accepted value of \SI{0.5974}{\nano\meter}.
 
@@
 		\node[thin optics element, rotate = 90] at (0, 2.25) {};
-	\end{tikzpicture}}{Schematic diagram of the Michelson interferometer.}
+	\end{tikzpicture}}{Schematic diagram of the Michelson interferometer.
+The light source comes in from the left, and splits by reflecting up and refracting to the right, when the beams are recombined in the middle, they proceed towards the observer at the bottom, and since the top mirror can be moved, small changes in path difference can make the waves from the light interfere constructively or destructively.}
 
-	Prior to making any measurements, the Michelson interferometer was calibrated against a sodium lamp with an assumed mean wavelength value of \( \lambda = 598.3 \) \si{nm}.
-The calibration curve itself was obtained by moving the carriage toward the observer, counting the number of fringes disappearing from the middle of the field of view and plotting the results.
+	\paperfig{SetupM}{\scalebox{1}[0.7]{\pdf{setup1}}}{The experimental setup of the Michelson interferometer.}
+
+	Prior to making any measurements, the Michelson interferometer was setup as in \figSetupM and calibrated against a sodium lamp with an assumed mean wavelength value of $\lambda = \SI{598.3}{\nano\meter}$.
+The calibration curve itself was obtained by moving the carriage toward the observer, counting the number of fringes disappearing from the middle of the field of view and plotting the results to determine the relation between the micrometer screw reading and the movement of the carriage, 50 fringes at a time.
 
 	Once the interferometer was calibrated, the setup could be used to determine the index of refraction of various materials.
-For instance, the index of refraction of a transparent solid---a microscope slide---was found.
-In general, the index of refraction of a solid can be shown to obey the following relation.
+For instance, the index of refraction of a transparent solid---a microscope slide---was found by measuring the difference between the peaks of the white light fringes both with and without the microscope slide.
+In general, the index of refraction of a solid obeys the following relation.
 
-	\papereq{SolidRefractiveIndex}{\mu = \frac{m \lambda}{2d} + 1}{\textbf{TODO}}
+	\papereq{SolidRefractiveIndex}{\mu = \frac{m \lambda}{2d} + 1}{AF, 2014}
 	\begin{paperwhere}
@@
 
+	Additionally, a derivation from the ideal gas law shows that if instead of a solid, a gas was inserted into the path of the beam, then the refractive index of the gas can be obtained.
+
+	\papereq{GasRefractiveIndex}{n=1+\frac{\d N}{\d P}\frac{\lambda}{2l}\frac{760T}{273.15}}{AF, 2014}
+	\begin{paperwhere}
+	    \papervar{n}{refractive index of gas}{}
+	    \papervar{N}{number of fringes counted}{}
+	    \papervar{P}{pressure inside gas chamber}{mmHg}
+	    \papervar{l}{thickness of gas chamber}{\meter}
+	    \papervar{T}{temperature}{\kelvin}
+	\end{paperwhere}
+
+	\paperfig{SetupF}{\scalebox{1}[0.7]{\pdf{setup2}}}{The experimental setup of the Fabry-Per\'ot interferometer.}
+
+	Lastly, a Fabry-Per\'ot was used to find the wavelength separation of the doublet of sodium spectral lines.
+
+	\papereq{Doublet}{\Delta\lambda=\frac{\overline{\lambda}^2}{2fM}}{AF, 2014}
+	\begin{paperwhere}
+	    \papervar{\Delta\lambda}{sodium doublet separation}{\meter}
+	    \papervar{\overline{\lambda}}{wavelength of sodium}{\meter}
+	    \papervar{f}{conversion factor}{}
+	    \papervar{M}{micrometer screw reading}{\meter}
+	\end{paperwhere}
+
+	With \eqDoublet, the separation of the doublet could be determined.
+
 \papersec{Observations}
 
-	Observations go here
+	The calibration curve for the Michelson interferometer was obtained by first counting the number of fringes that went by and writing down the micrometer screw readings for each fringe that went by.\pagebreak
+
+	\paperfig{CalibrationCurve}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}\paperoline
+	    \papertableindexheader&\multirow{2}{*}{\textsc{Fringes}}&\textsc{Reading}\\
+	    &\papertablecheadersymbol{(\pm.005)}\\\paperiline
+	    \papertableindex\papertablecval{0}\papertablecval{20.000}\\\paperiline
+	    \papertableindex\papertablecval{50}\papertablecval{20.085}\\\paperiline
+	    \papertableindex\papertablecval{100}\papertablecval{20.160}\\\paperiline
+	    \papertableindex\papertablecval{150}\papertablecval{20.245}\\\paperiline
+	    \papertableindex\papertablecval{200}\papertablecval{20.320}\\\paperiline
+	    \papertableindex\papertablecval{250}\papertablecval{20.410}\\\paperiline
+	    \papertableindex\papertablecval{300}\papertablecval{20.485}\\\paperiline
+	    \papertableindex\papertablecval{350}\papertablecval{20.570}\\\paperiline
+	    \papertableindex\papertablecval{400}\papertablecval{20.670}\\\paperiline
+	    \papertableindex\papertablecval{450}\papertablecval{20.775}\\\paperiline
+	    \papertableindex\papertablecval{500}\papertablecval{20.865}\\\paperiline
+	    \papertableindex\papertablecval{550}\papertablecval{20.950}\\\paperiline
+	    \papertableindex\papertablecval{600}\papertablecval{21.010}\\\paperiline
+	    \papertableindex\papertablecval{650}\papertablecval{21.090}\\\paperiline
+	    \papertableindex\papertablecval{700}\papertablecval{21.165}\\\paperiline
+	    \papertableindex\papertablecval{750}\papertablecval{21.250}\\\paperiline
+	    \papertableindex\papertablecval{800}\papertablecval{21.335}\\\paperiline
+	    \papertableindex\papertablecval{850}\papertablecval{21.420}\\\paperiline
+	    \papertableindex\papertablecval{900}\papertablecval{21.530}\\\paperiline
+	    \papertableindex\papertablecval{950}\papertablecval{21.620}\\\paperiline
+	    \papertableindex\papertablecval{1000}\papertablecval{21.700}\\\paperoline
+	\end{papertable}\vspace{-1.5em}}{A table showing the reading of the micrometer screw for each interval at intervals in which 50 fringes disappear in the field of view.}
+
+	In \figCalibrationCurve, the results for the first part of the experiment are shown.
+	The micrometer screw readings are shown which were taken in intervals of 50 fringes.
+
+	In the second part of the experiment, the thickness of the microscope slide was measured using a caliper and was found to be $(.95\pm.05)\si{\milli\meter}$.
+	Next, the positions on the micrometer screw where the white light fringes were observed without the slide, and where they were observed with the slide, was recorded.\\
+
+	\paperfig{WLF}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}\paperoline
+	\papertableindexheader&\textsc{With Slide}&\textsc{Without Slide}\\
+	\papertablecheadersymbol{(\pm.005\si{\micro\meter})}\papertablecheadersymbol{(\pm.005\si{\micro\meter})}\\\paperiline
+	\papertableindex\papertablecval{10.005}\papertablecval{12.650}\\\paperiline
+	\papertableindex\papertablecval{9.995}\papertablecval{12.605}\\\paperiline
+	\papertableindex\papertablecval{9.970}\papertablecval{12.595}\\\paperiline
+	\papertableindex\papertablecval{9.975}\papertablecval{12.590}\\\paperiline
+	\papertableindex\papertablecval{9.970}\papertablecval{12.590}\\\paperoline
+	\end{papertable}\vspace{-1.5em}}{A table of the readings of the micrometer screw at the position of the white light fringes both with a slide and without.
+The difference between the two readings is $(2.63\pm.03)\si{\micro\meter}$.}\\
+
+	Shown in \figWLF are the micrometer screw readings for the positions of the white light fringes both with the microscope slide and without it.
+	The difference between the two readings is $(2.63\pm.03)\si{\micro\meter}$.
+
+	In the third part of the experiment, the number of fringes that went by was recorded as the pressure in a gas chamber was decreased.
+The thickness of the gas chamber with both of its glass covers removed was measured with a caliper to be $(49.95\pm.05)\si{\milli\meter}$.
+
+	\paperfig{Pressure}{\scalebox{1}[0.92]{\begin{papertable}{|[outer]I|[inner]C|[outer]}\paperoline
+	\papertableindexheader&\textsc{Pressure}\\
+	\papertablecheadersymbol{P$ $(\pm\SI{5}{mmHg})}\\\paperiline
+\papertableindex\papertablecval{20}\\\paperiline
+\papertableindex\papertablecval{40}\\\paperiline
+\papertableindex\papertablecval{50}\\\paperiline
+\papertableindex\papertablecval{60}\\\paperiline
+\papertableindex\papertablecval{80}\\\paperiline
+\papertableindex\papertablecval{100}\\\paperiline
+\papertableindex\papertablecval{120}\\\paperiline
+\papertableindex\papertablecval{130}\\\paperiline
+\papertableindex\papertablecval{150}\\\paperiline
+\papertableindex\papertablecval{170}\\\paperiline
+\papertableindex\papertablecval{190}\\\paperiline
+\papertableindex\papertablecval{210}\\\paperiline
+\papertableindex\papertablecval{220}\\\paperiline
+\papertableindex\papertablecval{230}\\\paperiline
+\papertableindex\papertablecval{250}\\\paperiline
+\papertableindex\papertablecval{270}\\\paperiline
+\papertableindex\papertablecval{290}\\\paperiline
+\papertableindex\papertablecval{300}\\\paperiline
+\papertableindex\papertablecval{320}\\\paperiline
+\papertableindex\papertablecval{330}\\\paperiline
+\papertableindex\papertablecval{350}\\\paperiline
+\papertableindex\papertablecval{370}\\\paperiline
+\papertableindex\papertablecval{390}\\\paperiline
+\papertableindex\papertablecval{400}\\\paperiline
+\papertableindex\papertablecval{420}\\\paperiline
+\papertableindex\papertablecval{440}\\\paperiline
+\papertableindex\papertablecval{460}\\\paperiline
+\papertableindex\papertablecval{470}\\\paperiline
+\papertableindex\papertablecval{480}\\\paperiline
+\papertableindex\papertablecval{500}\\\paperiline
+\papertableindex\papertablecval{520}\\\paperiline
+\papertableindex\papertablecval{540}\\\paperiline
+\papertableindex\papertablecval{550}\\\paperiline
+\papertableindex\papertablecval{560}\\\paperiline
+\papertableindex\papertablecval{580}\\\paperiline
+\papertableindex\papertablecval{600}\\\paperiline
+\papertableindex\papertablecval{620}\\\paperiline
+\papertableindex\papertablecval{640}\\\paperiline
+\papertableindex\papertablecval{660}\\\paperiline
+\papertableindex\papertablecval{670}\\\paperiline
+\papertableindex\papertablecval{680}\\\paperiline
+\papertableindex\papertablecval{690}\\\paperiline
+\papertableindex\papertablecval{710}\\\paperiline
+\papertableindex\papertablecval{720}\\\paperiline
+\papertableindex\papertablecval{730}\\\paperiline
+\papertableindex\papertablecval{750}\\\paperoline
+	\end{papertable}}\vspace{-0.5em}}{Table of measurements of pressure as a function of fringe index.}
+
+	The measurements in \figPressure show the pressure in the chamber for each passing fringe, as seen in the interferometer.
+
+	In the last part of the experiment, the Fabry-Per\'ot interferometer was used to measure the wavelength difference of the sodium doublet.
+
+	\paperfig{FP}{\begin{papertable}{|[outer]I|[inner]C|[inner]C|[outer]}\paperoline
+	    \papertableindexheader&\multirow{2}{*}{\textsc{Fringes}}&\textsc{Reading}\\
+	    &\papertablecheadersymbol{(\pm.005)}\\\paperiline
+	    \papertableindex\papertablecval{0}\papertablecval{12.120}\\\paperiline
+	    \papertableindex\papertablecval{50}\papertablecval{12.205}\\\paperiline
+	    \papertableindex\papertablecval{100}\papertablecval{12.295}\\\paperiline
+	    \papertableindex\papertablecval{150}\papertablecval{12.380}\\\paperiline
+	    \papertableindex\papertablecval{200}\papertablecval{12.475}\\\paperiline
+	    \papertableindex\papertablecval{250}\papertablecval{12.560}\\\paperiline
+	    \papertableindex\papertablecval{300}\papertablecval{12.640}\\\paperiline
+	    \papertableindex\papertablecval{350}\papertablecval{12.725}\\\paperiline
+	    \papertableindex\papertablecval{400}\papertablecval{12.795}\\\paperiline
+	    \papertableindex\papertablecval{450}\papertablecval{12.870}\\\paperiline
+	    \papertableindex\papertablecval{500}\papertablecval{12.950}\\\paperiline
+	    \papertableindex\papertablecval{550}\papertablecval{13.020}\\\paperiline
+	    \papertableindex\papertablecval{600}\papertablecval{13.100}\\\paperiline
+	    \papertableindex\papertablecval{650}\papertablecval{13.180}\\\paperiline
+	    \papertableindex\papertablecval{700}\papertablecval{13.250}\\\paperiline
+	    \papertableindex\papertablecval{750}\papertablecval{13.325}\\\paperiline
+	    \papertableindex\papertablecval{800}\papertablecval{13.410}\\\paperiline
+	    \papertableindex\papertablecval{850}\papertablecval{13.500}\\\paperiline
+	    \papertableindex\papertablecval{900}\papertablecval{13.575}\\\paperiline
+	    \papertableindex\papertablecval{950}\papertablecval{13.650}\\\paperiline
+	    \papertableindex\papertablecval{1000}\papertablecval{13.730}\\\paperoline
+	\end{papertable}\vspace{-1.5em}}{A table showing the readings of the micrometer screw for each interval of 50 fringes disappearing in the field of view of the Fabry-Per\'ot interferometer.}
+
+	The Fabry-Per\'ot interferometer was calibrated using the same procedure as the Michelson interferometer using the measurements in \figFP, which recorded the readings of the micrometer screw every time 50 fringes disappeared in the field of view.
+
+	\paperfig{Doublet}{\begin{papertable}{|[outer]I|[inner]C|[outer]}\paperoline
+	\papertableindexheader&\textsc{Micrometer Screw Reading}\\
+	\papertablecheadersymbol{(\pm.005)}\\\paperiline
+	\papertableindex\papertablecval{13.530}\\\paperiline
+	\papertableindex\papertablecval{15.095}\\\paperiline
+	\papertableindex\papertablecval{16.645}\\\paperiline
+	\papertableindex\papertablecval{18.210}\\\paperiline
+	\papertableindex\papertablecval{19.770}\\\paperiline
+	\papertableindex\papertablecval{21.335}\\\paperoline
+	\end{papertable}\vspace{-1em}}{The micrometer screw readings for instances of coincidence between the sodium doublet lines.}
+
+	The measurements in \figDoublet were taken every time the sodium doublet lines were in coincidence. The average difference between a pair of readings was $(1.56\pm.01)$.
 
@@
 
-	Analysis goes here
+	To begin with, a calibration curve was built for a Michelson interferometer with a sodium lamp by rotating the micrometer screw, recording its reading every 50 disappearing fringes.
+The following linear plot of micrometer screw reading vs.
+the number of fringes was obtained by plotting the data in \figCalibrationCurve.
+
+	\paperfig{MichelsonReadingCount}{\pdf{calibration1}\vspace{-1em}}{Micrometer reading vs. fringe count calibration curve for a Michelson interferometer with sodium light.}
+
+	One can relate the distance moved by the carriage to the number of fringes by applying the following relation.
+
+	\papereq{DistanceNumberFringes}{2d = m\lambda}{AF, 2014}
+	\begin{paperwhere}
+	    \papervar{d}{distance moved by the carriage}{m}
+	    \papervar{m}{number of fringes}{}
+	    \papervar{\lambda}{wavelength of light}{m}
+    \end{paperwhere}
+
+    Upon converting the number of fringes to the distance moved by the carriage and fitting the data using the least squares method, the following fit was obtained.
+Reduced \( \chi^2 \) value for this fit was \( 7.9231 \); \( R^2 \) was determined to be \( 0.9993 \).
+
+    \paperfig{MichelsonCalibration}{\pdf{calibration2}\vspace{-1em}}{Micrometer reading and fit residuals plotted against the carriage displacement of the interferometer.
+The linear relation has the function \( \pars{5770 \pm 30 } x + \pars{19.991 \pm .006} \).
+\( R^2 \) of the fit is \( 0.9993 \).
+Error bars were included but were too small to be visible.}
+
+	The slope of the fit was used in the following parts of the experiment to convert micrometer readings to distances moved by the mirror carriage.
+The visible linearity of the curve as well as reduced \( \chi^2 \) and \( R^2 \) values of the fit suggest that the micrometer screw is fairly uniform when the mirror carriage is moved towards the observer.
+The conversion factor, $f$, becomes the reciprocal of the slope, so it is $(1.733\pm.009)\SI{E-4}{}$.
+
+	\papereq{Index}{\mu=\frac{Mf}{t}+1}{AF, 2014}
+	\begin{paperwhere}
+	\papervar{\mu}{refractive index}{}
+	\papervar{M}{micrometer screw reading}{\meter}
+	\papervar{f}{conversion factor}{}
+	\papervar{t}{thickness of solid}{\meter}
+	\end{paperwhere}
+
+	By using the average displacement between the values in \figWLF, \eqIndex was used to find the refractive index to be $(1.480\pm.03)$.
+This was close to the actual refractive index of low-iron sodaglass, which microscope slides are made of.
+This material typically has a refractive index of 1.5251 and 1.5230.
+
+	The Michelson interferometer was further used to determine the refractive index of a gas.
+By counting and recording the number of passing fringes at various pressures, a curve of pressure vs.
+number of fringes was obtained.
+Additionally, a least-squares fit was performed on the obtained data using a linear model.
+The reduced \( \chi ^ 2 \) value was determined to be \( 1.5654 \); \( R ^ 2 \) was \( 0.9992 \).
+
+	\paperfig{GasLinearFit}{\pdf{gas-fit}}{Pressure vs.
+number of fringes passed the field of view of a Michelson interferometer.
+The linear function followed the relation \( \pars{16.39 \pm 0.04}x \).
+\( R^2 \) of the fit was \( 0.9992 \).
+Error bars were included but were too small to be visible.}
+
+	Using the slope obtained from the fit above, the thickness of the chamber, and the mean wavelength of sodium the refractive index of the gas could be found with \eqGasRefractiveIndex.
+The result is that the refractive index of air is $(1.00029\pm.00001)$.
+The very high precision of the value comes from the fact that a small value with a reasonable uncertainty was added to 1.
+
+	At various pressures, the length of the cell was measured with the caps on, and the measurement was found to be constant with pressure.
+Thus, it was determined that the pressure does not affect the length of the cell.
+The relative humidity of the cell was not deemed as a significant source of error, as the experiment was conducted slowly so that the humidity in the cell could settle on the walls, thereby minimising its change to the refractive index in the interior of the cell.
+
+	Prior to using the Fabry-Per\'ot interferometer, a calibration curve similar to the one prior in the experiment was built.
+By counting the number of fringes passing the field of view as the micrometer screw is rotated, a linear curve is obtained.
+The data was further fit using the least-squares method, yielding a reduced \( \chi ^ 2  \) value of \( 6.6118 \) and an \( R ^ 2 \) value of \( 0.9994 \).
+
+	\paperfig{FabryPerotCalibration}{\pdf{calibration3}}{Micrometer screw reading vs.
+the number of fringes passed the field of view for a Fabry-Per\'ot interferometer.
+The linear function followed the relation \( \pars{5390 \pm 30} x + \pars{12.146 \pm .005 } \).
+\( R^2 \) of the fit was \( 0.9994 \).
+Error bars were included but were too small to be visible.
+}
+
+	The reciprocal of the slope in \figFabryPerotCalibration was used as the conversion factor between the micrometer reading and the carriage displacement.
+Together with \eqDoublet, and with the displacements between doublet coincidences from \figDoublet, the wavelength separation of the sodium doublet was obtained to be $(0.60\pm.03)\si{\nano\meter}$, which is within range of the accepted \SI{0.5974}{\nano\meter}.
 
@@
 
-	Conclusion goes here
+	Although the experiment was highly accurate, it was not free from sources of error.
+The main sources of error were the counting of the fringes, which relied on human accuracy to view a faint interference pattern.
+If the micrometer screw was turned too quickly or too slowly, it was difficult to maintain an accurate count.
+Since the resulting fit was very accurate, it is improbable that this significantly affected the results of the experiment.
+
+	The portion of the experiment which involved the white light fringes and the microscope slide had a lot of benchmarks and was relatively free from sources of error.
+However, no procedure was found that would mitigate the humidity of the gas inside the cell, which resulted in another source of error.
+
+	Lastly, the positions of the coincidences were hard to see and were determined as best as possible, but not in a manner that was free from sources of error.
+
+The calibration curve for the Michelson interferometer was fit with the function \( \pars{5770 \pm 30 } x + \pars{19.991 \pm .006} \), a $\chi^2$ value of 7.9231, and an \( R^2 \) value of \( 0.9993 \).
+	The refractive index for the microscope slide was determined to be $(1.480\pm.03)$, which was close to the accepted value of 1.5251.
+	The pressure as a function of the number of fringes was found to be \( \pars{16.39 \pm 0.04}x \), with a $\chi^2$ value of 1.5654, and an \( R^2 \) value of \( 0.9992 \).
+	The refractive index for air was determined to be $(1.00029\pm.00001)$, which was close to the accepted value of 1.
+	The Fabry-Per\'ot interferometer calibration curve was found to be \( \pars{5390 \pm 30} x + \pars{12.146 \pm .005 } \), with a $\chi^2$ value of 6.6118, and an \( R^2 \) value of \( 0.9994 \).
+	The sodium doublet wavelength separation was found to be $(0.60\pm.03)\si{\nano\meter}$, which is close to the accepted value of \SI{0.5974}{\nano\meter}.
 
@@
 
-	\papersource{}
+	\papersource{P. Albanelli, S. Fomichev, Interferometry, 2014}
 

### 2018-03-06 interfer/fabry-fit.py

@@ -1,5 +1,5 @@
 #!/bin/python
-# Linear fit of micrometer reading vs. num of fringes
+# Calibration curve for the Fabry interferometer
 
 # ---------- Import Statements ----------
 
@@ -13,29 +13,21 @@ from scipy.optimize import curve_fit
 # Linear fit function
 def func(x, a, b):
 	return a * x + b
-
+	# return a * x
+	
 # ---------- Main Code ----------
 
 # Set desired font
 plt.rc('font', family = 'Times New Roman')
-path_to_file = "calibration.txt"
+path_to_file = "fabry-measurements.txt"
 num, reading = np.loadtxt(path_to_file, unpack = True)
 reading_unc = np.full((1, reading.size), 0.005)[0]
+num = np.flip(num, 0)
 ddof = reading.size - 2
 
 wavelength = 589.3e-9	# m
 
-# Plot micrometer reading vs, fringe count
-plt.scatter(np.flip(num, 0), reading, color = "black", s = 5)
-plt.grid(True)
-plt.xlabel("Fringe count")
-plt.ylabel("Micrometer reading")
-plt.title("Micrometer reading vs. fringe count for sodium lamp")
-plt.savefig("calibration1.pdf")
-plt.close()
-
 dist = num * wavelength / 2		# m
-dist = np.flip(dist, 0)
 
 popt, pcov = curve_fit(func, dist, reading, sigma = reading_unc)
 print "a:", popt[0], "+-", np.sqrt(pcov[0, 0]), "(slope)"
@@ -50,23 +42,24 @@ ss_tot = np.sum((reading - np.mean(reading)) ** 2)
 r_squared = 1 - (ss_res / ss_tot)
 print "R^2:", r_squared
 
-print "\n", "Inverse slope:", 1 / popt[0], "<-- f value used for calibration"
-
-# Plot micrometer reading vs. carriage displacement
+# Plot micrometer reading vs. fringe count
 fig1 = plt.figure(1)
 frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
-plt.scatter(dist, reading, color = "black", s = 10)
+plt.scatter(dist, reading, color = "black", s = 5)
 plt.plot(dist, func(dist, *popt), color = "black")
 plt.grid(True)
 plt.ylabel("Micrometer reading")
-plt.xlim([-0.3e-4, 3.3e-4])
[…]

### 2018-03-06 interfer/gas-fit.py

@@ -1,0 +1,61 @@
+#!/bin/python
+# Linear fit of pressure vs. num of fringes passed the fied of view
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib
+from scipy.optimize import curve_fit
+
+# ---------- User-Defined Function ----------
+
+# Linear fit function
+def func(x, a):
+	# return a * x + b
+	return a * x
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+path_to_file = "gas.txt"
+pressure = np.loadtxt(path_to_file, unpack = True)
+num_fringes = np.arange(0, pressure.size)
+pressure_unc = np.full((1, pressure.size), 5)[0]
+# Degrees freedom in the fit
+ddof = pressure.size - 1
+
+# Fit the data
+popt, pcov = curve_fit(func, num_fringes, pressure, sigma = pressure_unc)
+print "a:", popt[0], "+-", np.sqrt(pcov[0, 0]), "(slope)"
+# print "b:", popt[1], "+-", np.sqrt(pcov[1, 1])
+# Calculate chi squared + residuals
+r = pressure - func(num_fringes, *popt)
+chisq = np.sum((r / pressure_unc) ** 2)
+print "Reduced chi squared:", chisq / ddof
+# Calculate and print R^2
+ss_res = np.sum(r ** 2)
+ss_tot = np.sum((pressure - np.mean(pressure)) ** 2)
+r_squared = 1 - (ss_res / ss_tot)
+print "R^2:", r_squared
+
+# Plot micrometer reading vs. carriage displacement
+fig1 = plt.figure(1)
+frame1 = fig1.add_axes((0.1, 0.3, 0.8, 0.6))
+plt.scatter(num_fringes, pressure, color = "black", s = 10)
+plt.plot(num_fringes, func(num_fringes, *popt), color = "black")
+plt.grid(True)
+plt.ylabel("Pressure (mm Hg)")
+plt.xlim([-2, 48])
+frame1.set_xticklabels([])
+plt.title("Pressure vs. number of fringes passing the field of view")
+frame2 = fig1.add_axes((0.1, 0.1, 0.8, 0.2))
+plt.scatter(num_fringes, r, color = "black", s = 10)
+plt.ylabel("Residuals")
+plt.xlabel("Number of fringes")
[…]

### 2018-03-12 two_terminal/paper.tex
Paper + characteristic curves

--- 2018-02-22 interfer/paper.tex
@@
 \begin{document}
-\papertitle{Interferometers}
+\papertitle{Two-Terminal Devices}
 \paperauth{A}{Khesin}{1002442029}
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{}
+\paperdate{March 19, 2018, Completed March 13, 2018}
 \begin{paperabs}
@@
 
-	Interference patterns produced by various light sources may be studied using interferometers, which operate by dividing either the wavefront or the amplitude of the original light beam.
-In this experiment, an amplitude-splitting interferometer, the Michelson interferometer, was used extensively to determine the indexes of refraction of a transparent solid and a gas after being calibrated using a sodium light.
-
-	\paperfig{MichelsonInterferometer}{% Still need to figure out labels (esp. the slide location)
-	\begin{tikzpicture}[use optics]
-		\node[thick optics element] at (-2.5, 0) {};
-		\node[thick optics element, rotate = -45] at (0, 0) {};
-		\node[generic optics io, io body aspect ratio = 1] at (-4.0, 0) {};
-		\node[mirror] at (3.0, 0) {};
-		\node[mirror, rotate = 90] at (0, 3.0) {};
-		\node[thick optics element, rotate = -45] at (1.5, -0.5) {};
-		\draw[->-] (-3.38, 0) -- (-0.15, 0);
-		\draw[->-] (-0.15, 0) -- (-0.15, 3.0);
-		\draw[->-] (0, 3.0) -- (0, 0.15);
-		\draw[] (0, 0.15) -- (0.15, 0);
-		\draw[->-] (0.15, 0) -- (0.15, -3.0);
-		\draw[] (-0.15, 0) -- (0, -0.15);
-		\draw[->-] (0, -0.15) -- (1.7, -0.15);
-		\draw[] (1.7, -0.15) -- (1.85, -0.3);
-		\draw[->-] (1.85, -0.3) -- (3.0, -0.3);
-		\draw[->-] (3.0, -0.45) -- (1.70, -0.45);
-		\draw[] (1.70, -0.45) -- (1.55, -0.3);
-		\draw[->-] (1.55, -0.3) -- (-0.15, -0.3);
-		\draw[->-] (-0.15, -0.3) -- (-0.15, -3.0);
-		\node[sensor line, rotate = -90] at (0, -3.2) {};	% May switch this to another element
-		\node[thin optics element, rotate = 90] at (0, 2.25) {};
-	\end{tikzpicture}}{Schematic diagram of the Michelson interferometer.}
-
-	Prior to making any measurements, the Michelson interferometer was calibrated against a sodium lamp with an assumed mean wavelength value of \( \lambda = 598.3 \) \si{nm}.
-The calibration curve itself was obtained by moving the carriage toward the observer, counting the number of fringes disappearing from the middle of the field of view and plotting the results.
-
-	Once the interferometer was calibrated, the setup could be used to determine the index of refraction of various materials.
-For instance, the index of refraction of a transparent solid---a microscope slide---was found.
-In general, the index of refraction of a solid can be shown to obey the following relation.
-
-	\papereq{SolidRefractiveIndex}{\mu = \frac{m \lambda}{2d} + 1}{\textbf{TODO}}
-	\begin{paperwhere}
-		\papervar{\mu}{index of refraction}{}
-		\papervar{m}{number of fringes displaced}{}
-		\papervar{\lambda}{wavelength of light}{\meter}
-		\papervar{d}{thickness of the solid}{\meter}
-	\end{paperwhere}
-
-	As seen from \eqSolidRefractiveIndex, inserting a transparent solid into the optical path of the beam results in a displacement of the interference pattern produced by the light source.
+	Introduction goes here
 
@@
 
-	\papersource{}
+	\papersource{J.V., R.M.S., Two-terminal devices, 2010}
 

### 2018-03-12 two_terminal/plot_master.py

@@ -1,0 +1,47 @@
+#!/bin/python
+# Reads .csv files (oscilloscope's) output for channels 1 and 2 and graphs the corresponding XY plot
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+# ---------- User-defined Functions ----------
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+
+directories = np.genfromtxt("plot_titles.txt", dtype = "str", delimiter = "\t")
+print directories
+
+for line in directories:
+		
+	ch1_file = "data/" + line[0] + "/F00" + line[2] + "CH1.CSV"
+	ch2_file = "data/" + line[0] + "/F00" + line[2] + "CH2.CSV"
+
+
+	# Import channel 1, channel 2 data
+	ch1_data = np.genfromtxt(ch1_file, delimiter = ",")
+	ch2_data = np.genfromtxt(ch2_file, delimiter = ",")
+
+	t = ch1_data[:, 3]
+	ch1_data = ch1_data[:, 4]
+	ch2_data = ch2_data[:, 4]
+
+	# Determine left & right bounds of the plot (want fixed to visualize the slope)
+	left_bound = np.min([np.min(ch1_data), np.min(ch2_data)])
+	right_bound = np.max([np.max(ch1_data), np.max(ch2_data)])
+	left_bound -= (right_bound - left_bound) / 10
+	right_bound += (right_bound - left_bound) / 10
+
+	# Graph XY graph
+	plt.plot(ch2_data, ch1_data, color = "black")
+	# plt.xlim([left_bound, right_bound])
+	# plt.ylim([left_bound, right_bound])
+	plt.xlabel("Channel 2 potential (V)")
+	plt.ylabel("Channel 1 potential (V)")
+	plt.title(line[1])
+	plt.savefig("char_curves/" + line[0] + ".pdf")
+	plt.close()

### 2018-03-13 two_terminal/plot_master.py
Changed master plot

@@ -16,19 +16,21 @@ plt.rc('font', family = 'Times New Roman')
 directories = np.genfromtxt("plot_titles.txt", dtype = "str", delimiter = "\t")
 print directories
 
+R = 4.7	# ohms
+
 for line in directories:
 		
 	ch1_file = "data/" + line[0] + "/F00" + line[2] + "CH1.CSV"
 	ch2_file = "data/" + line[0] + "/F00" + line[2] + "CH2.CSV"
 
-
 	# Import channel 1, channel 2 data
 	ch1_data = np.genfromtxt(ch1_file, delimiter = ",")
 	ch2_data = np.genfromtxt(ch2_file, delimiter = ",")
 
+	# Extract the t, potential data only
 	t = ch1_data[:, 3]
 	ch1_data = ch1_data[:, 4]
-	ch2_data = ch2_data[:, 4]
+	ch2_data = ch2_data[:, 4] / R
 
 	# Determine left & right bounds of the plot (want fixed to visualize the slope)
 	left_bound = np.min([np.min(ch1_data), np.min(ch2_data)])
@@ -37,7 +39,7 @@ for line in directories:
 	right_bound += (right_bound - left_bound) / 10
 
 	# Graph XY graph
-	plt.plot(ch2_data, ch1_data, color = "black")
+	plt.plot(ch1_data, ch2_data, color = "black")
 	# plt.xlim([left_bound, right_bound])
 	# plt.ylim([left_bound, right_bound])
 	plt.xlabel("Channel 2 potential (V)")

### 2018-03-13 two_terminal/plot_master.py
fixed minuses

@@ -1,4 +1,3 @@
-#!/bin/python
 # Reads .csv files (oscilloscope's) output for channels 1 and 2 and graphs the corresponding XY plot
 
 # ---------- Import Statements ----------
@@ -14,14 +13,14 @@ import matplotlib.pyplot as plt
 plt.rc('font', family = 'Times New Roman')
 
 directories = np.genfromtxt("plot_titles.txt", dtype = "str", delimiter = "\t")
-print directories
+print(directories)
 
 R = 4.7	# ohms
 
 for line in directories:
 		
-	ch1_file = "data/" + line[0] + "/F00" + line[2] + "CH1.CSV"
-	ch2_file = "data/" + line[0] + "/F00" + line[2] + "CH2.CSV"
+	ch1_file = "data\\" + line[0] + "\\F00" + line[2] + "CH1.CSV"
+	ch2_file = "data\\" + line[0] + "\\F00" + line[2] + "CH2.CSV"
 
 	# Import channel 1, channel 2 data
 	ch1_data = np.genfromtxt(ch1_file, delimiter = ",")

### 2018-03-13 two_terminal/plot_master.py
fixed plot titles

@@ -41,8 +41,8 @@ for line in directories:
 	plt.plot(ch1_data, ch2_data, color = "black")
 	# plt.xlim([left_bound, right_bound])
 	# plt.ylim([left_bound, right_bound])
-	plt.xlabel("Channel 2 potential (V)")
-	plt.ylabel("Channel 1 potential (V)")
+	plt.xlabel("Device Potential (V)")
+	plt.ylabel("Device Current (I)")
 	plt.title(line[1])
 	plt.savefig("char_curves/" + line[0] + ".pdf")
 	plt.close()

### 2018-03-15 two_terminal/plot_master.py
FH data

@@ -39,7 +39,7 @@ for line in directories:
 	right_bound += (right_bound - left_bound) / 10
 
 	# Graph XY graph
-	plt.plot(ch1_data, ch2_data, color = "black")
+	plt.scatter(ch1_data, ch2_data, color = "black", s = 5)
 	# plt.xlim([left_bound, right_bound])
 	# plt.ylim([left_bound, right_bound])
 	plt.xlabel("Channel 2 potential (V)")

### 2018-03-19 two_terminal/paper.tex
made resistance table

@@
 \input{header}
-\usepackage{tikz}
-\usetikzlibrary{optics}
 
@@
 
+\paperfig{Resistances}{\begin{papertable}{|[outer]I|[inner]C|[inner]U|[outer]}\paperoline
+\papertableindexheader&\multirow{2}{*}{\textsc{Device}}\papertableuheadersymbole{\textsc{Resistance}}\\
+&\papertableuheadersymbole{R$ $(\si{\ohm})}\\\paperiline
+\papertableindex\papertablecval{Short Circuit}\papertableuval{0.0}{.3}\\\paperiline
+\papertableindex\papertablecval{\SI{47}{\ohm} Resistor}\papertableuval{47.0}{.8}\\\paperiline
+\papertableindex\papertablecval{\SI{1}{\kilo\ohm} Resistor}\papertableuval{990}{10}\\\paperiline
+\papertableindex\papertablecval{With Cell (+/-)}\papertableuval{(5.21}{.04)\SI{E6}{}}\\\paperiline
+\papertableindex\papertablecval{Ge (+ Cathode)}\papertableuval{2830}{30}\\\paperiline
+\papertableindex\papertablecval{Ge (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
+\papertableindex\papertablecval{Si (+ Cathode)}\papertableuval{(3.33}{.03)\SI{E6}{}}\\\paperiline
+\papertableindex\papertablecval{Si (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
+\papertableindex\papertablecval{Se (+ Cathode)}\papertableuval{(18.4}{.2)\SI{E3}{}}\\\paperiline
+\papertableindex\papertablecval{Se (+ Anode)}\papertableuval{(61.4}{.5)\SI{E3}{}}\\\paperiline
+\papertableindex\papertablecval{Tube (+ Cathode)}\papertableuval{7020}{60}\\\paperiline
+\papertableindex\papertablecval{Tube (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
+\papertableindex\papertablecval{Zener (+ Cathode)}\papertableuval{(25.2}{.2)\SI{E6}{}}\\\paperiline
+\papertableindex\papertablecval{Zener (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
+\papertableindex\papertablecval{Thermistor}\papertableuval{1150}{10}\\\paperiline
+\papertableindex\papertablecval{\SI{68.6}{\milli\henry} Inductor}\papertableuval{0.3}{.3}\\\paperiline
+\papertableindex\papertablecval{\SI{1.68}{\milli\henry} Inductor}\papertableuval{0.0}{.3}\\\paperiline
+\papertableindex\papertablecval{\SI{1.0}{\micro\farad} Capacitor}\papertableuval{$\infty$}{?}\\\paperiline
+\papertableindex\papertablecval{\SI{22}{\nano\farad} Capacitor}\papertableuval{$\infty$}{?}\\\paperiline
+\papertableindex\papertablecval{\SI{0.1}{\micro\farad} Capacitor}\papertableuval{$\infty$}{?}\\\paperiline
+\papertableindex\papertablecval{5-\SI{50}{\ohm} Pot.}\papertableuval{5.0}{.3}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{A table of the resistances of various devices used in the experiment.
+For each device, the resistance was measured in both directions, if it was found to be the same, it was recorded in a single line,
+otherwise, it was recorded with a note indicating if the positive lead of the multimeter was at the cathode or the anode of the device.
+In cases where the resistance was so large that it could not be accurately measured by the multimeter, or in the cases where it was oscillating between large and small values and was not stabilising, $(\infty\pm?)$ was recorded.
+The entries in the table are for the following devices: a short circuit, a \SI{47}{\ohm} resistor, a \SI{1}{\kilo\ohm} resistor, a \SI{47}{\ohm} resistor in series with a \SI{1.5}{\volt} battery in both directions, a germanium diode, a silicon diode, one section of a selenium rectifier, a diode vacuum tube, a zener diode, a thermistor, a \SI{68.6}{\milli\henry} inductor, a \SI{1.68}{\milli\henry} inductor, a \SI{1.0}{\micro\farad} capacitor, a \SI{22}{\nano\farad} capacitor, a \SI{0.1}{\micro\farad} capacitor, and a a $5-\SI{50}{\ohm}$ potentiometer which was set to its lowest setting.}
+
 \papersec{Analysis}

### 2018-03-19 two_terminal/paper.tex
added circuit diagram

@@
 \input{header}
-
 \physics
@@
 	Introduction goes here
+
+\paperfig{Circuit}{\begin{center}
+\begin{tikzpicture}
+\draw
+(2,2) rectangle (3,3)
+(2.5,2) |- (5,1.5)
+(2.5,1.5) to[resistor] (2.5,0)
+(1,0) -- (5,0)
+(2.5,3) |- (5,3.5)
+(2.5,3.5) to[resistor] (1,3.5) -- (1,2.1)
+(-0.05,2.1) node[transformer core]{}
+(4,0) node[ground]{}
+(5,0) node[above]{\small Ground}
+(5,1.5) node[above]{\small Y Input}
+(5,3.5) node[below]{\small X Input}
+(2.5,2.5) node[]{\small Device}
+(2.7,0.9) node[right]{\small $R_2$}
+(2.7,0.6) node[right]{\small\SI{4.7}{\ohm}}
+(1.75,3.4) node[below]{\small $R_1$}
+(0.5,1.3) node[right]{\small \SI{6.3}{\volt}}
+(0.5,1) node[right]{\small RMS}
+(0.5,0.7) node[right]{\small A. C.}
+(-0.5,0.85) node[left]{\small A. C.}
+(-0.5,1.15) node[left]{\small \SI{60}{\hertz}}
+;
+\end{tikzpicture}\end{center}}
+{The circuit used in the experiment.
+The value of $R_1$ was varied depending on what was used for the Device.
+The $X$ and $Y$ nodes were connected to an oscilloscope.}
 

### 2018-03-19 two_terminal/paper.tex
stuff

--- 2018-03-12 two_terminal/paper.tex
@@
 \usetikzlibrary{optics}
+
+\usepackage{verbatim}
 
@@
 
-	Introduction goes here
+	The operation of a two-terminal device may be completely described by providing a relationship between the current through the device and the voltage across it.
+In this lab, the latter relation was determined for a variety of circuit elements, including resistors, a resistor in series with a dry cell, several diodes, a thermistor, and a section of a rectifier.
+
+	\textbf{TODO}: circuit diagram + description.
+
+	Prior to wiring the circuit as displayed above, vertical and horizontal sensitivities of the oscilloscope along with its zeros were set.
+The desired I vs.
+V curves were displayed in the Y vs.
+X mode of the oscilloscope; to obtain current as opposed to potential on the dependent axes, the Y voltage was divided by \( R_2 = 4.7 \si{\ohm} \) before plotting.
+The final experimental setup looked as shown below.
+
+	\paperfig{SetupMain}{\pdf{setup_main}}{Experimental setup used to determine I vs. V plots for a variety of provided circuit components, with the diode vacuum tube specifically investigated here.}
+
+	To further interpret the obtained I vs. V curves, a multimeter was used to measure the resistance of each component, with the connections made in both possible directions.
+
+	Additionally, I vs. V graphs of several capacitors, inductors, and a potentiometer were obtained. The same circuit as in \textbf{TODO} was used, resulting in the following setup.
+
+	\paperfig{SetupAdditional}{\pdf{setup_additional}}{Experimental setup used to determine I vs. V curves of additional circuit components, with a \( 100 \si{\kilo\ohm} \) connected here.}
 
@@
 
-	Observations go here
+	To obtain I vs.
+V plots for the circuit components investigated, measurements were first saved using the \textit{Save} function of the oscilloscope.
+Dividing the channel two voltage by the resistance as described above, the desired plots were obtained.
+Note that \( R_1 \) in \textbf{TODO} varied for each circuit component.
+
+	% \begin{comment}
+	\paperfig{ShortCircuit}{\pdf{char_curves/1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
+	\paperfig{Resistor47}{\pdf{char_curves/2-47}}{I vs. V curve for a \( 47 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
+	\paperfig{Resistor1000}{\pdf{char_curves/3-1000}}{I vs. V curve for a \( 1000 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
+	\paperfig{CellUp}{\pdf{char_curves/4a-cell-up}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{positive direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{CellDown}{\pdf{char_curves/4b-cell-down}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{negative direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Germanium}{\pdf{char_curves/5-germanium}}{I vs. V curve for a germanium diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Silicon}{\pdf{char_curves/6-silicon}}{I vs. V curve for a silicon diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Selenium}{\pdf{char_curves/7-selenium}}{I vs. V curve for a one section of a selenium rectifier. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Vacuum}{\pdf{char_curves/8-vacuum}}{I vs. V curve for a diode vacuum tube. Here, \( R_1 \) of \( 0 \si{\ohm} \) was used.}
+	\paperfig{Zener}{\pdf{char_curves/9-zener}}{I vs. V curve for a zener diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Thermistor}{\pdf{char_curves/10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
+	% \end{comment}
+
+	\begin{comment}
+	\paperfig{ShortCircuit}{\pdf{char_curves\\1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
+	\paperfig{ShortCircuit}{\pdf{char_curves\\2-47}}{I vs. V curve for a \( 47 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}
+	\paperfig{Resistor1000}{\pdf{char_curves\\3-1000}}{I vs. V curve for a \( 1000 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
+	\paperfig{CellUp}{\pdf{char_curves\\4a-cell-up}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{positive direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{CellDown}{\pdf{char_curves\\4b-cell-down}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{negative direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Germanium}{\pdf{char_curves\\5-germanium}}{I vs. V curve for a germanium diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Silicon}{\pdf{char_curves\\6-silicon}}{I vs. V curve for a silicon diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	paperfig{Selenium}{\pdf{char_curves\\7-selenium}}{I vs. V curve for a one section of a selenium rectifier. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Vacuum}{\pdf{char_curves\\8-vacuum}}{I vs. V curve for a diode vacuum tube. Here, \( R_1 \) of \( 0 \si{\ohm} \) was used.}
+	\paperfig{Zener}{\pdf{char_curves\\9-zener}}{I vs. V curve for a zener diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Thermistor}{\pdf{char_curves\\10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
+	\end{comment}
 
 \papersec{Analysis}
-
-	Analysis goes here
 

### 2018-03-19 two_terminal/plot_master.py

@@ -4,8 +4,13 @@
 
 import numpy as np
 import matplotlib.pyplot as plt
+from scipy.optimize import curve_fit
 
 # ---------- User-defined Functions ----------
+
+# Linear model function used for fitting
+def func(x, a, b):
+	return a * x + b
 
 # ---------- Main Code ----------
 
@@ -13,14 +18,16 @@ import matplotlib.pyplot as plt
 plt.rc('font', family = 'Times New Roman')
 
 directories = np.genfromtxt("plot_titles.txt", dtype = "str", delimiter = "\t")
-print(directories)
 
 R = 4.7	# ohms
 
 for line in directories:
 		
-	ch1_file = "data\\" + line[0] + "\\F00" + line[2] + "CH1.CSV"
-	ch2_file = "data\\" + line[0] + "\\F00" + line[2] + "CH2.CSV"
+	ch1_file = "data/" + line[0] + "/F00" + line[2] + "CH1.CSV"
+	ch2_file = "data/" + line[0] + "/F00" + line[2] + "CH2.CSV"
+		
+	# ch1_file = "data\\" + line[0] + "\\F00" + line[2] + "CH1.CSV"
+	# ch2_file = "data\\" + line[0] + "\\F00" + line[2] + "CH2.CSV"
 
 	# Import channel 1, channel 2 data
 	ch1_data = np.genfromtxt(ch1_file, delimiter = ",")
@@ -29,7 +36,30 @@ for line in directories:
 	# Extract the t, potential data only
 	t = ch1_data[:, 3]
 	ch1_data = ch1_data[:, 4]
-	ch2_data = ch2_data[:, 4] / R
+	ch2_data = (ch2_data[:, 4] / R)
+
+	# Index of elements whose i vs. v is linear (can fit for slope)
+	need_slope = np.array(["1", "2", "2", "4a", "4b", "10"])
+
+	print line
+	'''
+	unc_ch1 = ch1_data * 0.04
+	unc_ch2 = ch2_data * 0.04
+	ddof = 2
+	# Print slope of the relation (if linear)
+	if line[0][ : (line[0]).find("-") ] in need_slope:
+		popt, pcov = curve_fit(func, ch1_data, ch2_data, sigma = unc_ch2)
+		print "Slope:", popt[0], "+-", np.sqrt(pcov[0, 0])
+		# Find residuals
+		r1 = ch2_data - func(ch1_data, *popt)
+		chisq = np.sum((r1 / unc_ch2) ** 2)
[…]

### 2018-03-19 two_terminal/paper.tex
fixed conflict

--- 2018-03-19 two_terminal/paper.tex
@@
 
-	Introduction goes here
+	The operation of a two-terminal device may be completely described by providing a relationship between the current through the device and the voltage across it.
+In this lab, the latter relation was determined for a variety of circuit elements, including resistors, a resistor in series with a dry cell, several diodes, a thermistor, and a section of a rectifier.
 
@@
 
+	Prior to wiring the circuit as displayed above, vertical and horizontal sensitivities of the oscilloscope along with its zeros were set.
+The desired I vs.
+V curves were displayed in the Y vs.
+X mode of the oscilloscope; to obtain current as opposed to potential on the dependent axes, the Y voltage was divided by \( R_2 = 4.7 \si{\ohm} \) before plotting.
+The final experimental setup looked as shown below.
+
+	\paperfig{SetupMain}{\pdf{setup_main}}{Experimental setup used to determine I vs. V plots for a variety of provided circuit components, with the diode vacuum tube specifically investigated here.}
+
+	To further interpret the obtained I vs. V curves, a multimeter was used to measure the resistance of each component, with the connections made in both possible directions.
+
+	Additionally, I vs. V graphs of several capacitors, inductors, and a potentiometer were obtained. The same circuit as in \textbf{TODO} was used, resulting in the following setup.
+
+	\paperfig{SetupAdditional}{\pdf{setup_additional}}{Experimental setup used to determine I vs. V curves of additional circuit components, with a \( 100 \si{\kilo\ohm} \) connected here.}
+
 \papersec{Observations}
 
-	Observations go here
+	To obtain I vs.
+V plots for the circuit components investigated, measurements were first saved using the \textit{Save} function of the oscilloscope.
+Dividing the channel two voltage by the resistance as described above, the desired plots were obtained.
+Note that \( R_1 \) in \textbf{TODO} varied for each circuit component.
+
+	% \begin{comment}
+	\paperfig{ShortCircuit}{\pdf{char_curves/1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
+	\paperfig{Resistor47}{\pdf{char_curves/2-47}}{I vs. V curve for a \( 47 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
+	\paperfig{Resistor1000}{\pdf{char_curves/3-1000}}{I vs. V curve for a \( 1000 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
+	\paperfig{CellUp}{\pdf{char_curves/4a-cell-up}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{positive direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{CellDown}{\pdf{char_curves/4b-cell-down}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{negative direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Germanium}{\pdf{char_curves/5-germanium}}{I vs. V curve for a germanium diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Silicon}{\pdf{char_curves/6-silicon}}{I vs. V curve for a silicon diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Selenium}{\pdf{char_curves/7-selenium}}{I vs. V curve for a one section of a selenium rectifier. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Vacuum}{\pdf{char_curves/8-vacuum}}{I vs. V curve for a diode vacuum tube. Here, \( R_1 \) of \( 0 \si{\ohm} \) was used.}
+	\paperfig{Zener}{\pdf{char_curves/9-zener}}{I vs. V curve for a zener diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Thermistor}{\pdf{char_curves/10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
+	% \end{comment}
+
+	\comment{
+	\paperfig{ShortCircuit}{\pdf{char_curves\\1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
+	\paperfig{ShortCircuit}{\pdf{char_curves\\2-47}}{I vs. V curve for a \( 47 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}
+	\paperfig{Resistor1000}{\pdf{char_curves\\3-1000}}{I vs. V curve for a \( 1000 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
+	\paperfig{CellUp}{\pdf{char_curves\\4a-cell-up}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{positive direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{CellDown}{\pdf{char_curves\\4b-cell-down}}{I vs.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{negative direction???}.
+Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Germanium}{\pdf{char_curves\\5-germanium}}{I vs. V curve for a germanium diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Silicon}{\pdf{char_curves\\6-silicon}}{I vs. V curve for a silicon diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	paperfig{Selenium}{\pdf{char_curves\\7-selenium}}{I vs. V curve for a one section of a selenium rectifier. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Vacuum}{\pdf{char_curves\\8-vacuum}}{I vs. V curve for a diode vacuum tube. Here, \( R_1 \) of \( 0 \si{\ohm} \) was used.}
+	\paperfig{Zener}{\pdf{char_curves\\9-zener}}{I vs. V curve for a zener diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
+	\paperfig{Thermistor}{\pdf{char_curves\\10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
+}
 

### 2018-03-19 two_terminal/paper.tex
Started analysis

@@
 \input{header}
+\usepackage{tikz}
+\usetikzlibrary{optics}
+
+\usepackage{verbatim}
+
 \physics
@@
 
+	Introduction goes here
+
 \papersec{Observations}
@@
 
-	\comment{
+	\begin{comment}
 	\paperfig{ShortCircuit}{\pdf{char_curves\\1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
@@
 	\paperfig{Thermistor}{\pdf{char_curves\\10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
-}
+	\end{comment}
 
@@
 
+	As stated in the introduction, the I vs.
+V curve provides a complete description of the functionality of an electrical component.
+Here, slopes, intercepts, and points of bending of the curves were examined where applicable and compared to the results available in the literature.
+
+	For a short circuit, one would ideally expect a vertical line corresponding to
+
 \papersec{Conclusion}

### 2018-03-19 two_terminal/paper.tex
fixed... again
Commit
fixed... again... again
analysis

@@
 \input{header}
-\usepackage{tikz}
-\usetikzlibrary{optics}
-
-\usepackage{verbatim}
-
 \physics
@@
 
-	Introduction goes here
-
 \papersec{Observations}
@@
 
-	% \begin{comment}
+	% \comment{
 	\paperfig{ShortCircuit}{\pdf{char_curves/1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
@@
 	\paperfig{Thermistor}{\pdf{char_curves/10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
-	% \end{comment}
+	% \}
 
-	\begin{comment}
+	\comment{
 	\paperfig{ShortCircuit}{\pdf{char_curves\\1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
@@
 	\paperfig{Thermistor}{\pdf{char_curves\\10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
-	\end{comment}
+}
 
@@
 Here, slopes, intercepts, and points of bending of the curves were examined where applicable and compared to the results available in the literature.
+\textbf{TODO}: explain why couldn't fit data.
 
-	For a short circuit, one would ideally expect a vertical line corresponding to
+	An ideal short circuit offers no resistance to the moving electrons, and therefore one would expect to observe a vertical line on the I vs.
+V curve.
+In this lab, I was found to vary linearly as a function of V, but the resulting line was not vertical.
+Instead, the curve had a small positive slope that was approximated to be \( \pars{2.00 \pm 0.07} \times 10^-3 \).
+This is readily explained by the fact that in practice all wires have a nonzero resistance, and thus the I vs.
+V curve will never be truly vertical.
+
+	The shape of the I vs.
+V curve for a \( 47 \si{\ohm} \)  resistor is similar to that of the short circuit, with the exception of a change in the slope.
+This time, the inverse of the slope, which corresponds to the resistance of the circuit element, was approximated to be \( \pars{48 \pm 4} \si{\ohm} \).
+This value agrees with the measured resistance in \figResistances.
+
+	As expected, the familiar linear I vs.
+V curve reappeared again for the \( 1000 \si{\ohm} \)) resistor.
+The inverse of the slope in this case was found to be \( \pars{1.0 \pm 0.3} \times 10^4 \si{\ohm} \).
+\textbf{WHY DOESN'T THIS MATCH?}
+
+	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented \textbf{up???} was approximated to be \( \pars{550 \pm 40 } \).
+
+	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented \textbf{down???} was approximated to be \( \pars{510 \pm 20 } \).
+
+	\textbf{Need to do the thermistor slope + everything else}
 

### 2018-03-19 two_terminal/plot_master.py

@@ -39,7 +39,7 @@ for line in directories:
 	ch2_data = (ch2_data[:, 4] / R)
 
 	# Index of elements whose i vs. v is linear (can fit for slope)
-	need_slope = np.array(["1", "2", "2", "4a", "4b", "10"])
+	need_slope = np.array(["1", "2", "3", "4a", "4b", "10"])
 
 	print line
 	'''
@@ -76,4 +76,6 @@ for line in directories:
 	plt.ylabel("Device Current (I)")
 	plt.title(line[1])
 	plt.savefig("char_curves/" + line[0] + ".pdf")
+	if line[0][ : (line[0]).find("-") ] in need_slope:
+		plt.show()
 	plt.close()

### 2018-03-20 two_terminal/paper.tex
done

@@
 \begin{document}
-\papertitle{Two-Terminal Devices}
+\papertitle{Analysis of Various Two-Terminal Devices}
 \paperauth{A}{Khesin}{1002442029}
@@
 
-	Abstract goes here
+	This experiment analyzed the behaviours of various two-terminal devices.
+The devices were connected to a circuit and an oscilloscope which allowed for the I vs.
+V curves of the devices to be determined.
+From there, their behaviour was observed by changing the sign of the current, which was especially significant for four the two-terminal devices, which were diodes.
+The inverses of the slopes of the linear parts of the curves were determined and compared to the measured resistances of the devices.
 
@@
 	The operation of a two-terminal device may be completely described by providing a relationship between the current through the device and the voltage across it.
-In this lab, the latter relation was determined for a variety of circuit elements, including resistors, a resistor in series with a dry cell, several diodes, a thermistor, and a section of a rectifier.
+In this experiment, the latter relation was determined for a variety of circuit elements, including resistors, a resistor in series with a dry cell, several diodes, a thermistor, and a section of a rectifier.
 
@@
 
-	\paperfig{SetupMain}{\pdf{setup_main}}{Experimental setup used to determine I vs. V plots for a variety of provided circuit components, with the diode vacuum tube specifically investigated here.}
+	\paperfig{SetupMain}{\pdf{setup_main}\vspace{-1.5em}}{Experimental setup used to determine I vs.
+V plots for a variety of provided circuit components, with the diode vacuum tube specifically investigated here.}
 
@@
 
-	Additionally, I vs. V graphs of several capacitors, inductors, and a potentiometer were obtained. The same circuit as in \textbf{TODO} was used, resulting in the following setup.
+	Additionally, I vs. V graphs of several capacitors, inductors, and a potentiometer were obtained. The same circuit as in \figCircuit was used, resulting in the following setup.
 
-	\paperfig{SetupAdditional}{\pdf{setup_additional}}{Experimental setup used to determine I vs. V curves of additional circuit components, with a \( 100 \si{\kilo\ohm} \) connected here.}
+	\paperfig{SetupAdditional}{\pdf{setup_additional}\vspace{-1.5em}}{Experimental setup used to determine I vs.
+V curves of additional circuit components, with a \( 100 \si{\kilo\ohm} \) connected here.}
 
@@
 Dividing the channel two voltage by the resistance as described above, the desired plots were obtained.
-Note that \( R_1 \) in \textbf{TODO} varied for each circuit component.
+Note that \( R_1 \) in \figCircuit varied for each circuit component.
 
@@
 	\paperfig{CellUp}{\pdf{char_curves/4a-cell-up}}{I vs.
-V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{positive direction???}.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a \SI{1.5}{\volt} dry cell aligned positively with the circuit.
 Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
 	\paperfig{CellDown}{\pdf{char_curves/4b-cell-down}}{I vs.
-V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{negative direction???}.
+V curve for a \( 47 \si{\ohm} \) resistor in series with a \SI{1.5}{\volt}dry cell aligned negatively with the circuit.
 Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
@@
 }
+
+The ``resistances'' of all the devices were also measured in both possible directions.
+The results were included below.
 
@@
 Here, slopes, intercepts, and points of bending of the curves were examined where applicable and compared to the results available in the literature.
-\textbf{TODO}: explain why couldn't fit data.
+Due to the chaotic nature of the I vs.
+V curves and the sweep rate of the oscilloscope, it proved to be impossible to accurately fit the slopes of the I vs.
+V curves while making sure to account for the random noise in the data.
+The slopes were determined by determining the slopes of straight lines that would pass through the areas of the curves where the datapoints were concentrated most densely.
 
@@
 In this lab, I was found to vary linearly as a function of V, but the resulting line was not vertical.
-Instead, the curve had a small positive slope that was approximated to be \( \pars{2.00 \pm 0.07} \times 10^-3 \).
+Instead, the curve had a small positive slope that was approximated to be \( \pars{2.00 \pm 0.07} \times 10^\text{-3} \).
 This is readily explained by the fact that in practice all wires have a nonzero resistance, and thus the I vs.
@@
 	As expected, the familiar linear I vs.
-V curve reappeared again for the \( 1000 \si{\ohm} \)) resistor.
-The inverse of the slope in this case was found to be \( \pars{1.0 \pm 0.3} \times 10^4 \si{\ohm} \).
-\textbf{WHY DOESN'T THIS MATCH?}
+V curve reappeared again for the \( 1000 \si{\ohm} \) resistor.
+The inverse of the slope in this case was found to be \( \pars{1.0 \pm 0.3} \times 10^3 \si{\ohm} \), matching what was observed for the previous resistor.
 
-	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented \textbf{up???} was approximated to be \( \pars{550 \pm 40 } \).
+	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented positively aligned with the circuit was approximated to be \( \pars{550 \pm 40 } \), meaning that there was significantly less resistance, as the circuit looked more like a short circuit.
 
-	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented \textbf{down???} was approximated to be \( \pars{510 \pm 20 } \).
+	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented negatively aligned with the circuit was approximated to be \( \pars{510 \pm 20 } \) and the same result was observed as when it was oriented positively.
 
-	\textbf{Need to do the thermistor slope + everything else}
+	For each of the four diodes, it was observed that the current was consistently 0 when the potential was such that the flow was oriented against the diode.
+When this was not the case, the current flowed through the diode.
+As far as it is visible from the plots, the points of bending are all (0, 0).
+These are also the intercepts of the diode plots, consistent for all four diodes.
+The only exceptions to this are the silicon diode, which has point of bending (-7, 0) and the Zener diode, which has points of bending (-50, 0) and (7, 0).
+
+	The diodes have slopes $(6.6\pm.3)\SI{E-4}{}$ for the germanium diode, $(1.0\pm.1)\SI{E-2}{}$ for the silicon diode, $(7.3\pm.4)\SI{E-4}{}$ for the diode vacuum tube, and $(1.0\pm.2)\SI{E-2}{}$ for the Zener diode.
+These slopes are consistent with theory as we find lower resistances for diodes made out of materials with higher conductivities, such as silicon.
+
+	The two fixed potentials on the Zener diode were at \SI{-50}{\volt} and \SI{7}{\volt}.
+Additionally, we note that touching the glass bead of the thermistor increased the slope of the curve, thereby lowering its resistance.
+This was due to the fact that human skin is significantly warmer than air temperature, and the resistance of a thermistor decreases if it is heated.
+
+	When analyzing the resistances in \figResistances, we find that all components which are not diodes conduct just fine in both directions, but all the diodes only conduct in one direction.
+This is exactly what is to be expected, as the multimeter is effectively connecting a potential source to the circuit.
+As is clear from the I vs.
+V curves of the devices, there is no current going through the diodes if the circuit is oriented against the diode.
+Hence, the resistances of the diodes were infinite in one direction and reasonable in another.
+For most devices, we find that the inverses of the slopes of the I vs.
+V curves are very similar to the observed resistances, which is exactly what is to be expected from Ohm's law.
 
@@
 
-	Conclusion goes here
+	This experiment was succesful in determining the I vs.
+V curves of various two-terminal devices, but it was not free from sources of error.
+The first source of error was the uncertainties in measurements of the resistances of the components, which can be erratic if a device does not have a perfectly linear I vs.
+V curve as the multimeter will then just measure the inverse of the slope at a given point, determined by its internal potential.
+
+	The second source of error was in determining the slopes of the I vs.
+V curves from the plots.
+This was mostly unavoidable due to the chaotic nature of the oscilloscope.
+However, an attempt to cleanup the data and get as accurate of a reading as possible, it was impossible to do this without adding any error to the experiment.
+
+	Overall, the experiment was succesful in relating the measured resistances of various two-terminal devices to the inverses of the slopes of their I vs. V curves.
 

### 2018-03-20 two_terminal/plot_master.py

@@ -41,7 +41,7 @@ for line in directories:
 	# Index of elements whose i vs. v is linear (can fit for slope)
 	need_slope = np.array(["1", "2", "3", "4a", "4b", "10"])
 
-	print line
+	print(line)
 	'''
 	unc_ch1 = ch1_data * 0.04
 	unc_ch2 = ch2_data * 0.04

### 2018-03-20 two_terminal/paper.tex
Deleted additional

@@
 
-	Additionally, I vs. V graphs of several capacitors, inductors, and a potentiometer were obtained. The same circuit as in \figCircuit was used, resulting in the following setup.
-
-	\paperfig{SetupAdditional}{\pdf{setup_additional}\vspace{-1.5em}}{Experimental setup used to determine I vs.
-V curves of additional circuit components, with a \( 100 \si{\kilo\ohm} \) connected here.}
-
 \papersec{Observations}
@@
 \papertableindex\papertablecval{Zener (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{Thermistor}\papertableuval{1150}{10}\\\paperiline
-\papertableindex\papertablecval{\SI{68.6}{\milli\henry} Inductor}\papertableuval{0.3}{.3}\\\paperiline
-\papertableindex\papertablecval{\SI{1.68}{\milli\henry} Inductor}\papertableuval{0.0}{.3}\\\paperiline
-\papertableindex\papertablecval{\SI{1.0}{\micro\farad} Capacitor}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{\SI{22}{\nano\farad} Capacitor}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{\SI{0.1}{\micro\farad} Capacitor}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{5-\SI{50}{\ohm} Pot.}\papertableuval{5.0}{.3}\\\paperoline
+\papertableindex\papertablecval{Thermistor}\papertableuval{1150}{10}\\\paperoline
 \end{papertable}\vspace{-1.5em}}

### 2018-03-20 two_terminal/paper.tex
fixed table description

@@
 In cases where the resistance was so large that it could not be accurately measured by the multimeter, or in the cases where it was oscillating between large and small values and was not stabilising, $(\infty\pm?)$ was recorded.
-The entries in the table are for the following devices: a short circuit, a \SI{47}{\ohm} resistor, a \SI{1}{\kilo\ohm} resistor, a \SI{47}{\ohm} resistor in series with a \SI{1.5}{\volt} battery in both directions, a germanium diode, a silicon diode, one section of a selenium rectifier, a diode vacuum tube, a zener diode, a thermistor, a \SI{68.6}{\milli\henry} inductor, a \SI{1.68}{\milli\henry} inductor, a \SI{1.0}{\micro\farad} capacitor, a \SI{22}{\nano\farad} capacitor, a \SI{0.1}{\micro\farad} capacitor, and a a $5-\SI{50}{\ohm}$ potentiometer which was set to its lowest setting.}
+The entries in the table are for the following devices: a short circuit, a \SI{47}{\ohm} resistor, a \SI{1}{\kilo\ohm} resistor, a \SI{47}{\ohm} resistor in series with a \SI{1.5}{\volt} battery in both directions, a germanium diode, a silicon diode, one section of a selenium rectifier, a diode vacuum tube, a zener diode, and a thermistor.}
 

### 2018-03-21 franck-hertz/paper.tex
Franck-Hertz plots

--- 2018-03-20 two_terminal/paper.tex
@@
 \begin{document}
-\papertitle{Analysis of Various Two-Terminal Devices}
+\papertitle{The Franck-Hertz Experiment}
 \paperauth{A}{Khesin}{1002442029}
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{March 19, 2018, Completed March 13, 2018}
+\paperdate{March 121, 2018, Completed March 15, 2018}
 \begin{paperabs}
 
-	This experiment analyzed the behaviours of various two-terminal devices.
-The devices were connected to a circuit and an oscilloscope which allowed for the I vs.
-V curves of the devices to be determined.
-From there, their behaviour was observed by changing the sign of the current, which was especially significant for four the two-terminal devices, which were diodes.
-The inverses of the slopes of the linear parts of the curves were determined and compared to the measured resistances of the devices.
+	Abstract goes here
 
@@
 
-	The operation of a two-terminal device may be completely described by providing a relationship between the current through the device and the voltage across it.
-In this experiment, the latter relation was determined for a variety of circuit elements, including resistors, a resistor in series with a dry cell, several diodes, a thermistor, and a section of a rectifier.
-
-	\paperfig{Circuit}{\begin{center}
-			\begin{tikzpicture}
-			\draw
-			(2,2) rectangle (3,3)
-			(2.5,2) |- (5,1.5)
-			(2.5,1.5) to[resistor] (2.5,0)
-			(1,0) -- (5,0)
-			(2.5,3) |- (5,3.5)
-			(2.5,3.5) to[resistor] (1,3.5) -- (1,2.1)
-			(-0.05,2.1) node[transformer core]{}
-			(4,0) node[ground]{}
-			(5,0) node[above]{\small Ground}
-			(5,1.5) node[above]{\small Y Input}
-			(5,3.5) node[below]{\small X Input}
-			(2.5,2.5) node[]{\small Device}
-			(2.7,0.9) node[right]{\small $R_2$}
-			(2.7,0.6) node[right]{\small\SI{4.7}{\ohm}}
-			(1.75,3.4) node[below]{\small $R_1$}
-			(0.5,1.3) node[right]{\small \SI{6.3}{\volt}}
-			(0.5,1) node[right]{\small RMS}
-			(0.5,0.7) node[right]{\small A. C.}
-			(-0.5,0.85) node[left]{\small A. C.}
-			(-0.5,1.15) node[left]{\small \SI{60}{\hertz}}
-			;
-			\end{tikzpicture}\end{center}}
-	{The circuit used in the experiment.
-		The value of $R_1$ was varied depending on what was used for the Device.
-		The $X$ and $Y$ nodes were connected to an oscilloscope.}
-
-	Prior to wiring the circuit as displayed above, vertical and horizontal sensitivities of the oscilloscope along with its zeros were set.
-The desired I vs.
-V curves were displayed in the Y vs.
-X mode of the oscilloscope; to obtain current as opposed to potential on the dependent axes, the Y voltage was divided by \( R_2 = 4.7 \si{\ohm} \) before plotting.
-The final experimental setup looked as shown below.
-
-	\paperfig{SetupMain}{\pdf{setup_main}\vspace{-1.5em}}{Experimental setup used to determine I vs.
-V plots for a variety of provided circuit components, with the diode vacuum tube specifically investigated here.}
-
-	To further interpret the obtained I vs. V curves, a multimeter was used to measure the resistance of each component, with the connections made in both possible directions.
+	Introduction goes here
 
@@
 
-	To obtain I vs.
-V plots for the circuit components investigated, measurements were first saved using the \textit{Save} function of the oscilloscope.
-Dividing the channel two voltage by the resistance as described above, the desired plots were obtained.
-Note that \( R_1 \) in \figCircuit varied for each circuit component.
-
-	% \comment{
-	\paperfig{ShortCircuit}{\pdf{char_curves/1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
-	\paperfig{Resistor47}{\pdf{char_curves/2-47}}{I vs. V curve for a \( 47 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
-	\paperfig{Resistor1000}{\pdf{char_curves/3-1000}}{I vs. V curve for a \( 1000 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
-	\paperfig{CellUp}{\pdf{char_curves/4a-cell-up}}{I vs.
-V curve for a \( 47 \si{\ohm} \) resistor in series with a \SI{1.5}{\volt} dry cell aligned positively with the circuit.
-Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{CellDown}{\pdf{char_curves/4b-cell-down}}{I vs.
-V curve for a \( 47 \si{\ohm} \) resistor in series with a \SI{1.5}{\volt}dry cell aligned negatively with the circuit.
-Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Germanium}{\pdf{char_curves/5-germanium}}{I vs. V curve for a germanium diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Silicon}{\pdf{char_curves/6-silicon}}{I vs. V curve for a silicon diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Selenium}{\pdf{char_curves/7-selenium}}{I vs. V curve for a one section of a selenium rectifier. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Vacuum}{\pdf{char_curves/8-vacuum}}{I vs. V curve for a diode vacuum tube. Here, \( R_1 \) of \( 0 \si{\ohm} \) was used.}
-	\paperfig{Zener}{\pdf{char_curves/9-zener}}{I vs. V curve for a zener diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Thermistor}{\pdf{char_curves/10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
-	% \}
-
-	\comment{
-	\paperfig{ShortCircuit}{\pdf{char_curves\\1-short}}{I vs. V curve for a short circuit, with \( R_1 \) set to \( 100 \si{\ohm} \).}
-	\paperfig{ShortCircuit}{\pdf{char_curves\\2-47}}{I vs. V curve for a \( 47 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}
-	\paperfig{Resistor1000}{\pdf{char_curves\\3-1000}}{I vs. V curve for a \( 1000 \si{\ohm} \) resistor, with \( R_1 \) set to \( 100 \si{\ohm} \).}	
-	\paperfig{CellUp}{\pdf{char_curves\\4a-cell-up}}{I vs.
-V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{positive direction???}.
-Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{CellDown}{\pdf{char_curves\\4b-cell-down}}{I vs.
-V curve for a \( 47 \si{\ohm} \) resistor in series with a 1 1/2 volt dry cell in the \textbf{negative direction???}.
-Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Germanium}{\pdf{char_curves\\5-germanium}}{I vs. V curve for a germanium diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Silicon}{\pdf{char_curves\\6-silicon}}{I vs. V curve for a silicon diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	paperfig{Selenium}{\pdf{char_curves\\7-selenium}}{I vs. V curve for a one section of a selenium rectifier. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Vacuum}{\pdf{char_curves\\8-vacuum}}{I vs. V curve for a diode vacuum tube. Here, \( R_1 \) of \( 0 \si{\ohm} \) was used.}
-	\paperfig{Zener}{\pdf{char_curves\\9-zener}}{I vs. V curve for a zener diode. Here, \( R_1 \) of \( 100 \si{\ohm} \) was used.}
-	\paperfig{Thermistor}{\pdf{char_curves\\10-thermistor}}{I vs. V curve for a thermistor. Here, \( R_1 \) of \( 50 \si{\ohm} \) was used.}
-}
-
-The ``resistances'' of all the devices were also measured in both possible directions.
-The results were included below.
-
-\paperfig{Resistances}{\begin{papertable}{|[outer]I|[inner]C|[inner]U|[outer]}\paperoline
-\papertableindexheader&\multirow{2}{*}{\textsc{Device}}\papertableuheadersymbole{\textsc{Resistance}}\\
-&\papertableuheadersymbole{R$ $(\si{\ohm})}\\\paperiline
-\papertableindex\papertablecval{Short Circuit}\papertableuval{0.0}{.3}\\\paperiline
-\papertableindex\papertablecval{\SI{47}{\ohm} Resistor}\papertableuval{47.0}{.8}\\\paperiline
-\papertableindex\papertablecval{\SI{1}{\kilo\ohm} Resistor}\papertableuval{990}{10}\\\paperiline
-\papertableindex\papertablecval{With Cell (+/-)}\papertableuval{(5.21}{.04)\SI{E6}{}}\\\paperiline
-\papertableindex\papertablecval{Ge (+ Cathode)}\papertableuval{2830}{30}\\\paperiline
-\papertableindex\papertablecval{Ge (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{Si (+ Cathode)}\papertableuval{(3.33}{.03)\SI{E6}{}}\\\paperiline
-\papertableindex\papertablecval{Si (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{Se (+ Cathode)}\papertableuval{(18.4}{.2)\SI{E3}{}}\\\paperiline
-\papertableindex\papertablecval{Se (+ Anode)}\papertableuval{(61.4}{.5)\SI{E3}{}}\\\paperiline
-\papertableindex\papertablecval{Tube (+ Cathode)}\papertableuval{7020}{60}\\\paperiline
-\papertableindex\papertablecval{Tube (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{Zener (+ Cathode)}\papertableuval{(25.2}{.2)\SI{E6}{}}\\\paperiline
-\papertableindex\papertablecval{Zener (+ Anode)}\papertableuval{$\infty$}{?}\\\paperiline
-\papertableindex\papertablecval{Thermistor}\papertableuval{1150}{10}\\\paperoline
-\end{papertable}\vspace{-1.5em}}
-{A table of the resistances of various devices used in the experiment.
-For each device, the resistance was measured in both directions, if it was found to be the same, it was recorded in a single line,
-otherwise, it was recorded with a note indicating if the positive lead of the multimeter was at the cathode or the anode of the device.
-In cases where the resistance was so large that it could not be accurately measured by the multimeter, or in the cases where it was oscillating between large and small values and was not stabilising, $(\infty\pm?)$ was recorded.
-The entries in the table are for the following devices: a short circuit, a \SI{47}{\ohm} resistor, a \SI{1}{\kilo\ohm} resistor, a \SI{47}{\ohm} resistor in series with a \SI{1.5}{\volt} battery in both directions, a germanium diode, a silicon diode, one section of a selenium rectifier, a diode vacuum tube, a zener diode, and a thermistor.}
+	Observations go here
 
@@
 
-	As stated in the introduction, the I vs.
-V curve provides a complete description of the functionality of an electrical component.
-Here, slopes, intercepts, and points of bending of the curves were examined where applicable and compared to the results available in the literature.
-Due to the chaotic nature of the I vs.
-V curves and the sweep rate of the oscilloscope, it proved to be impossible to accurately fit the slopes of the I vs.
-V curves while making sure to account for the random noise in the data.
-The slopes were determined by determining the slopes of straight lines that would pass through the areas of the curves where the datapoints were concentrated most densely.
-
-	An ideal short circuit offers no resistance to the moving electrons, and therefore one would expect to observe a vertical line on the I vs.
-V curve.
-In this lab, I was found to vary linearly as a function of V, but the resulting line was not vertical.
-Instead, the curve had a small positive slope that was approximated to be \( \pars{2.00 \pm 0.07} \times 10^\text{-3} \).
-This is readily explained by the fact that in practice all wires have a nonzero resistance, and thus the I vs.
-V curve will never be truly vertical.
-
-	The shape of the I vs.
-V curve for a \( 47 \si{\ohm} \)  resistor is similar to that of the short circuit, with the exception of a change in the slope.
-This time, the inverse of the slope, which corresponds to the resistance of the circuit element, was approximated to be \( \pars{48 \pm 4} \si{\ohm} \).
-This value agrees with the measured resistance in \figResistances.
-
-	As expected, the familiar linear I vs.
-V curve reappeared again for the \( 1000 \si{\ohm} \) resistor.
-The inverse of the slope in this case was found to be \( \pars{1.0 \pm 0.3} \times 10^3 \si{\ohm} \), matching what was observed for the previous resistor.
-
-	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented positively aligned with the circuit was approximated to be \( \pars{550 \pm 40 } \), meaning that there was significantly less resistance, as the circuit looked more like a short circuit.
-
-	The inverse slope of the linear characteristic curve of the \( 47 \si{\ohm} \) resistor in series with a dry cell oriented negatively aligned with the circuit was approximated to be \( \pars{510 \pm 20 } \) and the same result was observed as when it was oriented positively.
-
-	For each of the four diodes, it was observed that the current was consistently 0 when the potential was such that the flow was oriented against the diode.
-When this was not the case, the current flowed through the diode.
-As far as it is visible from the plots, the points of bending are all (0, 0).
-These are also the intercepts of the diode plots, consistent for all four diodes.
-The only exceptions to this are the silicon diode, which has point of bending (-7, 0) and the Zener diode, which has points of bending (-50, 0) and (7, 0).
-
-	The diodes have slopes $(6.6\pm.3)\SI{E-4}{}$ for the germanium diode, $(1.0\pm.1)\SI{E-2}{}$ for the silicon diode, $(7.3\pm.4)\SI{E-4}{}$ for the diode vacuum tube, and $(1.0\pm.2)\SI{E-2}{}$ for the Zener diode.
-These slopes are consistent with theory as we find lower resistances for diodes made out of materials with higher conductivities, such as silicon.
-
-	The two fixed potentials on the Zener diode were at \SI{-50}{\volt} and \SI{7}{\volt}.
-Additionally, we note that touching the glass bead of the thermistor increased the slope of the curve, thereby lowering its resistance.
-This was due to the fact that human skin is significantly warmer than air temperature, and the resistance of a thermistor decreases if it is heated.
-
-	When analyzing the resistances in \figResistances, we find that all components which are not diodes conduct just fine in both directions, but all the diodes only conduct in one direction.
-This is exactly what is to be expected, as the multimeter is effectively connecting a potential source to the circuit.
-As is clear from the I vs.
-V curves of the devices, there is no current going through the diodes if the circuit is oriented against the diode.
-Hence, the resistances of the diodes were infinite in one direction and reasonable in another.
-For most devices, we find that the inverses of the slopes of the I vs.
-V curves are very similar to the observed resistances, which is exactly what is to be expected from Ohm's law.
+	Analysis goes here
 
@@
 
-	This experiment was succesful in determining the I vs.
-V curves of various two-terminal devices, but it was not free from sources of error.
-The first source of error was the uncertainties in measurements of the resistances of the components, which can be erratic if a device does not have a perfectly linear I vs.
-V curve as the multimeter will then just measure the inverse of the slope at a given point, determined by its internal potential.
-
-	The second source of error was in determining the slopes of the I vs.
-V curves from the plots.
-This was mostly unavoidable due to the chaotic nature of the oscilloscope.
-However, an attempt to cleanup the data and get as accurate of a reading as possible, it was impossible to do this without adding any error to the experiment.
-
-	Overall, the experiment was succesful in relating the measured resistances of various two-terminal devices to the inverses of the slopes of their I vs. V curves.
+	Conclusion goes here
 
@@
 
-	\papersource{J.V., R.M.S., Two-terminal devices, 2010}
+	\\papersource{Serbanescu, R.,The Franck-Hertz Experiment, 2017}
 

### 2018-03-21 franck-hertz/plot_master.py

@@ -1,0 +1,32 @@
+#!/bin/python
+# Plots Franck-Hertz dta & saves as a .pdf
+# Assumes text files to be read are in 'data' directory, same parent directory as this .py
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+
+# ---------- User-Defined Functions ----------
+
+# ---------- Main Code ----------
+
+# Set desired font
+plt.rc('font', family = 'Times New Roman')
+
+num_data_files = 17
+
+# Loop over all data files, plot & save collected curves
+for i in range(0, num_data_files):
+	path_to_file = "data/" + str(i + 1) + ".txt"
+	# path_to_file = "data\\" + str(i + 1) + ".txt"		# Windows	<===
+	
+	ch1_data, ch2_data = np.loadtxt(path_to_file, unpack = True)
+	
+	plt.plot(ch1_data, ch2_data, color = "black")
+	plt.xlabel("Channel 1 Potential (V)")
+	plt.ylabel("Channel 2 Potential (V)")
+	plt.title("Current vs. accelerating voltage")
+	plt.savefig(str(i + 1) + ".pdf")
+	plt.close()
+

### 2018-03-21 two_terminal/plot_master.py

@@ -1,3 +1,4 @@
+#!/bin/python
 # Reads .csv files (oscilloscope's) output for channels 1 and 2 and graphs the corresponding XY plot
 
 # ---------- Import Statements ----------

### 2018-03-21 franck-hertz/paper.tex
FH introduction

@@
 
-	Introduction goes here
+	The Franck-Hertz experiment is well-known as the one of the first experiments to provide empirical evidence for the quantum nature of atoms.
+In the course of the experiment, one may demonstrate that electrons lose discrete amounts of energy, supporting Bohr's propositions about the nature of an atom.
+This is achieved by bombarding mercury atoms with a beam of electrons and observing the relationship between current and accelerating voltage of the electrons.
+This paper outlines the setup and procedure required for reproducing the experiment as well as results and observations.
+
+	Primary components of the experimental setup include a filament used for emitting electrons, electron-accelerating grids and an anode collecting the electrons; all of these are contained in a mercury vapor filled tube.
+Additionally, power supplies for heating the filament and accelerating the electrons, an oven for heating the tube, an electrometer and a voltmeter were used.
+The required apparatus are shown below.
+
+	\paperfig{Setup}{\pdf{setup}}{Devices used in the experiment prior to wiring. The final apparatus was connected using the schematic circuit diagram further below.}
 
@@
 
-	\\papersource{Serbanescu, R.,The Franck-Hertz Experiment, 2017}
+	\papersource{Serbanescu, R.,The Franck-Hertz Experiment, 2017}
 

### 2018-03-21 franck-hertz/paper.tex
More intro

@@
 Additionally, power supplies for heating the filament and accelerating the electrons, an oven for heating the tube, an electrometer and a voltmeter were used.
-The required apparatus are shown below.
+The required devices are shown below.
 
-	\paperfig{Setup}{\pdf{setup}}{Devices used in the experiment prior to wiring. The final apparatus was connected using the schematic circuit diagram further below.}
+	\paperfig{Setup}{\vspace{-1em} \pdf{setup} \vspace{-3em}}{Apparatus used in the experiment prior to wiring.
+The final apparatus was connected using the schematic circuit diagram further below.
+The panel supports four DC voltages with functions explained below.}
 

### 2018-03-21 franck-hertz/paper.tex
Finished observations x2

@@
 \paperauth{P}{Zavyalova}{1002345036}
-\paperdate{March 121, 2018, Completed March 15, 2018}
+\paperdate{March 21, 2018, Completed March 15, 2018}
 \begin{paperabs}
@@
 The final apparatus was connected using the schematic circuit diagram further below.
-The panel supports four DC voltages with functions explained below.}
+The panel supports four DC voltages with functionality explained below.}
+
+	\textbf{Schematic circuit diagram + description}.
+
+	Prior to beginning data acquisition, the accelerating voltage was connected to the \textit{Manual} panel ports.
+The filament supply and the screen grid voltage were adjusted until the electrometer reflected smooth and regular raises and decreases as the accelerating voltage was slowly changed.
+
+	Throughout the course of the experiment, two voltages were recorded with the help of provided software: the accelerating voltage (X, channel 1) and the voltage recorded by the Keithley electrometer (Y, channel 2).
+All measurements were taken with the tube heated to \textbf{TODO: tube temperature}.
 
@@
 
-	Observations go here
+	The resulting collected data took form of Channel 2 (Keithley elecrometer reading) vs.
+Channel 1 (accelerating potential) curves.
+A total of 17 curves were obtained, with some taking the desired smooth periodic form, and some having sudden peaks that could be explained with deviations of the tube temperature from the optimal value.
+The latter data sets could still be used whenever the horizontal distance between minima was not affected by the peaks.
+Presented below are three sample runs of varying smoothness and periodicity that correspond to the primary types of data collected throughout the experiment.
+
+	\paperfig{DataClean}{\pdf{16}}{Keithley electrometer potential vs. accelerating potential data for a run exhibiting a smooth, periodic curve with no spikes due to temperature fluctuations.}
+
+	\paperfig{DataCleanNotSmooth}{\pdf{9}}{Keithley electrometer potential vs.
+accelerating potential data for a run exhibiting a periodic curve with no spikes due to temperature fluctuations.
+However, due to a consistently non-optimal temperature throughout this run, the curve is as smooth as desired, complicating locating the x-positions of the minima.}
+
+	\paperfig{DataSpike}{\pdf{17}}{Keithley electrometer potential vs.
+accelerating potential data for a run exhibiting a smooth, periodic curve with potential spikes that may be attributed to temperature fluctuations throughout the run.
+Periodicity of the data still allows this curve to be used to measure horizontal distance between spikes.}
+
+	The amount of energy transferred from an electron to a mercury atom in the vapor filling the tube in the course of an inelastic collision was inferred from the obtained curves by measuring the horizontal distances between the minima.
+The measured distances between peaks are shown below.
+\vspace{1em}
+
+	\paperfig{Doublet}{\begin{papertable}{|[outer]I|[inner]C|[outer]}\paperoline
+			\papertableindexheader&\textsc{Horizontal Distance Between Peaks (V)}\\
+			\papertablecheadersymbol{(\pm.3)}\\\paperiline
+			\papertableindex\papertablecval{5.2}\\\paperiline
+			\papertableindex\papertablecval{5.1}\\\paperiline
+			\papertableindex\papertablecval{5.4}\\\paperiline
+			\papertableindex\papertablecval{5.4}\\\paperiline
+			\papertableindex\papertablecval{5.1}\\\paperiline	
+			\papertableindex\papertablecval{5.1}\\\paperiline
+			\papertableindex\papertablecval{5.1}\\\paperiline
+			\papertableindex\papertablecval{5.3}\\\paperiline
+			\papertableindex\papertablecval{4.8}\\\paperiline
+			\papertableindex\papertablecval{5.2}\\\paperiline
+			\papertableindex\papertablecval{5.1}\\\paperiline
+			\papertableindex\papertablecval{5.2}\\\paperiline
+			\papertableindex\papertablecval{5.3}\\\paperiline
+			\papertableindex\papertablecval{5.3}\\\paperiline
+			\papertableindex\papertablecval{5.2}\\\paperiline
+			\papertableindex\papertablecval{5.4}\\\paperiline
+			\papertableindex\papertablecval{5.3}\\\paperoline
+		\end{papertable} \vspace{-1em} }{Horizontal distance between minima of the Keithley electrometer potential vs. accelerating voltage for several runs of the Franck-Hertz experiment. }
+
+	Since the distances were measured by selecting the position of the minima by eye, the uncertainty arises from the uncertainty of selection of the minimum point.
+Selecting the minimum point was made significantly more difficult due to the upward trend in the Channel 2 potential.
 

### 2018-03-21 franck-hertz/plot_master.py

@@ -26,7 +26,7 @@ for i in range(0, num_data_files):
 	plt.plot(ch1_data, ch2_data, color = "black")
 	plt.xlabel("Channel 1 Potential (V)")
 	plt.ylabel("Channel 2 Potential (V)")
-	plt.title("Current vs. accelerating voltage")
+	plt.title("Keithley electrometer reading vs. accelerating voltage")
 	plt.savefig(str(i + 1) + ".pdf")
 	plt.close()
 

### 2018-03-22 franck-hertz/paper.tex
done?

@@
 
-	Abstract goes here
+	The Franck-Hertz experiment hints at the quantum nature of atoms by showing that they lose energy in discrete chunks when bombarded with electrons.
+The energy they lose between two peaks was shown to be $(8.3\pm.3)\SI{E-19}{\joule}$. The associated wavelength of light that photons release was shown to be $(240\pm10)\si{\nano\meter}$.
 
@@
 
-	\textbf{Schematic circuit diagram + description}.
+	The circuit was setup according to the following diagram.
+
+	\paperfig{Circuit}{\pdf{images}\vspace{-3em}}{Citcuit diagram used in the experiment.
+Ports E1 through E4 are localed on the device and the other nodes are on the accompanying box.
+Source for diagram: Serbanescu, 2017.}\\
 
@@
 	Throughout the course of the experiment, two voltages were recorded with the help of provided software: the accelerating voltage (X, channel 1) and the voltage recorded by the Keithley electrometer (Y, channel 2).
-All measurements were taken with the tube heated to \textbf{TODO: tube temperature}.
+All measurements were taken with the tube heated to \SI{169}{\celsius}.
 
@@
 
-	Since the distances were measured by selecting the position of the minima by eye, the uncertainty arises from the uncertainty of selection of the minimum point.
+	Since the distances were measured by selecting the position of the minima by using the software cursors, the uncertainty arises from the uncertainty of selection of the minimum point.
 Selecting the minimum point was made significantly more difficult due to the upward trend in the Channel 2 potential.
@@
 
-	Analysis goes here
+The data in \figDoublet shows that the average potential difference between two peaks was $(5.2\pm.2)\si{\volt}$.
+This was used to find the transfered energy.
+The energy is related to the potential and the wavelength of the particles with the following equation.
+
+\papereq{E}{E=eV=\frac{hc}\lambda}{}
+\begin{paperwhere}
+\papervar{E}{energy}{\joule}
+\papervar{e}{fundamental charge}{\coulomb}
+\papervar{V}{potential}{\volt}
+\papervar{h}{Planck's constant}{\joule\second}
+\papervar{c}{speed of light}{\meter\per\second}
+\papervar{\lambda}{wavelength}{\meter}
+\end{paperwhere}
+
+The following values were used for fundamental constants.
+The value of $e$ was taken to be \SI{1.60217662E-19}{\coulomb}, the value of $h$ was taken to be \SI{6.62607004E-34}{\joule\second}, and the value of $c$ was taken to be \SI{299792458}{\meter\per\second}, the following results were obtained.
+
+The Energy transfered was calculated with \eqE to be $(8.3\pm.3)\SI{E-19}{\joule}$.
+The associated wavelength was calculated with \eqE to be $(240\pm10)\si{\nano\meter}$.
+
+The original experiment used mercury instead of hydrogen gas as the gas needs to be heavy in order for the collisions with the electrons to be inelastic.
+As hydrogen is much lighter than mercury, a collision of an electron with a hydrogen atom has a much lower chance of being inelastic.
+
+On the graphs of the data plots, the patterns showed smooth dips and not sharp sawtooth patterns.
+This was because the odds of an electron being absorbed by an atom increase at the corresponding potenials.
+However, these odds are never a certainty, they slowly increase due to the various energies present in the electrons, and they reach their peak when the means of the two distributions, those being those of the energies of the mercury atoms and the electrons, are at the optimal distance apart.
+This made the results less precise as the minimum of the distribution was harder to locate and was possibly shifted, making this harder to measure than if it had been a sawtooth pattern.
 
@@
 
-	Conclusion goes here
+Although this experiment was successful, it was not free from sources of error.
+The most important source of error was the ability to accurately record and measure the data.
+The software would frequently display large jumps and discontinuities as seen in \figDataSpike.
+This made it difficult to get an accurate value for the distance between two consecutive minima.
+This would have been reduced by collecting more data and aggregating all of the values.
+
+The final results of this experiment hint at the quantum nature of atoms by showing that they lose energy in discrete chunks when bombarded with electrons.
+The energy they lose between two peaks was shown to be $(8.3\pm.3)\SI{E-19}{\joule}$. The associated wavelength of light that photons release was shown to be $(240\pm10)\si{\nano\meter}$.
 

### 2018-03-27 air_gyroscope/paper.tex
Started gyroscope introduction

\input{header}
\physics
\begin{document}
\papertitle{Determination of \textit{g} through precession of an air gyroscope}
\paperauth{A}{Khesin}{1002442029}
\paperauth{P}{Zavyalova}{1002345036}
\paperdate{March 28, 2018, Completed March 22, 2018}
\begin{paperabs}

	Abstract goes here

\end{paperabs}

\begin{paper}

\papersec{Introduction}

	The value of \textit{g} may be accurately determined by examining the precession of a gyroscopic rotator, an accurately machined sphere with a flat region. The sphere is driven by a coil to rotate with the axis of rotational symmetry horizontal. The rotator ends up being magnetized along an equatorial diameter and therefore together with the coil constitutes a synchronous motor. Since the rotor is free, the angular momentum vector may freely change its direction.

	The change in the angular momentum vector of the rotor arises from a torque acting in the horizontal plane resulting from the imbalance from the truncated section of the sphere. A pure precession about a vertical axis arises due to the fact that the torque is at all times perpendicular to the angular momentum.

	In this experiment, the above setup was implemented with the goal of approximating \textit{g}. Constant torsion-free air suspension supported the sphere. The rotor was accelerated using a controllable air flow until a frequency of \( 3600 \) rpm was attained. The frequency of rotation was measured using a strobe light; as soon as the desired value was obtained, the accelerating air flow was shut off and the driving coil was switched on. The rotator was driven at \( \pars{60 \pm .1} \si{\hertz} \) by a coil connected to the A.C. mains. To determine the period of rotation of the sphere, a laser light was reflected from the surface of the sphere. By marking the position of a well-defined spot resulting from specular reflection from the flat section and measuring the time of a full revolution, the period was obtained. The complete experimental setup is shown below.

	\paperfig{Setup}{\pdf{setup} \vspace{-2.5em}}{Experimental setup used for determining the value of \textit{g} through precession of an air gyroscope. The driving coil was mounted in the platform supporting the truncated sphere, a laser was aligned with the flat surface, and a strobe light was used to ensure that the desired frequency is maintained.}

	Expressions for torque \( L \) and moment of inertia of the rotator may be calculated by assuming a uniform density of the sphere. The dimensions of the gyroscopic rotator were denoted as follows.

	\paperfig{Sphere}{\begin{tikzpicture}
		\draw (0, 0) circle (50pt);
		\draw[->] (-3, 0)--(3, 0);
		\draw[-] (1.2, -1.29)--(1.2, 1.29);
		\draw[<->] (0, 0)--(1.1, 1.37);
		\draw[-] (0, -0.4)--(0, 0.2);
		\draw[<->] (0, -0.2)--(1.2, -0.2);
		\draw[<->] (1.2, -0.2)--(1.75, -0.2);
		\draw (0.6, -0.2) node[below] {\( \xi \)};
		\draw (1.45, -0.2) node[below] {\( \delta \)};
		\draw (0.4, 0.6) node[above] {\( R \)};
		\draw (2.4, 0.3) node {\( I\vec{\omega} \)};
	\end{tikzpicture}}{A sphere of radius \( R \) truncated to obtain a minimum distance from the center of \( R - \delta = \xi \), constituting a gyroscopic rotator. The angular momentum vector lies in the horizontal plane at all times and has a magnitude of \( I\omega \)}.

\papersec{Observations}

	Observations go here

\papersec{Analysis}

	Analysis goes here

\papersec{Conclusion}

	Conclusion goes here

\papersec{Sources}

	\papersource{}

\end{paper}
\end{document}

### 2018-03-28 air_gyroscope/integration.py
integration script

@@ -1,0 +1,55 @@
+#!/bin/python
+# Integrates the volume of the truncated sphere
+
+# ---------- Import Statements ----------
+
+import numpy as np
+import matplotlib.pyplot as plt
+from scipy import integrate
+
+# ---------- User-Defined Functions ----------
+
+# Integrad for scipy.integrate.dblquad (1)
+def func1(y, x):
+	return 2 * np.pi * y ** 3
+	
+# Lower bound for integration in y (1)
+def gfun1(x):
+	return 0
+	
+# Upper bound for integration in y (1)
+# Radius R must be defined before calling the function
+def hfun1(x):
+	return np.sqrt(R ** 2 - x ** 2)
+	
+# Integrad for scipy.integrate.dblquad (2) (x component)
+def func2x(y, x):
+	return 2 * np.sqrt(R ** 2 - x ** 2 - y ** 2) * y
+	
+# Integrad for scipy.integrate.dblquad (2) (y component)
+def func2y(y, x):
+	return 2 * np.sqrt(R ** 2 - x ** 2 - y ** 2) * (-x)
+	
+# Lower bound for integration in y (2)
+def gfun2(x):
+	return -1 * np.sqrt(R ** 2 - x ** 2)
+	
+# Upper bound for integration in y (2)
+# Radius R must be defined before calling the function
+def hfun2(x):
+	return np.sqrt(R ** 2 - x ** 2)
+	
+# ---------- Main Code ----------
+
+R = 25.2625e-3		# m
+delta = 50.525e-3 - 48.620e-3		# m
+rho = 1
+g = 1
+
+val1 = integrate.dblquad(func1, R - delta, R, gfun1, hfun1)
+print "I:", rho * (8 * np.pi * R ** 5) / 15 - val1[0], "+-", val1[1]
+
+val2x = integrate.dblquad(func2x, - R, R - delta, gfun2, hfun2)
+val2y = integrate.dblquad(func2y, - R, R - delta, gfun2, hfun2)
+print "L, x:", rho * g * val2x[0], "+-", val2x[1]
+print "L, y:", rho * g * val2y[0], "+-", val2y[1]

### 2018-03-28 air_gyroscope/paper.tex

@@
 \begin{document}
-\papertitle{Determination of \textit{g} through precession of an air gyroscope}
+\papertitle{Analysis of an Air Gyroscope's Precession}
 \paperauth{A}{Khesin}{1002442029}
@@
 
-	Abstract goes here
+	HEY SORRY FOR CAPS COULD YOU PLEASE TRY TO KEEP ``OBSERVATIONS'' RIGHT AT THE TOP OF PAGE TWO? THANKS
 
@@
 
-	Expressions for torque \( L \) and moment of inertia of the rotator may be calculated by assuming a uniform density of the sphere. The dimensions of the gyroscopic rotator were denoted as follows.
+	Expressions for torque \( L \) and moment of inertia of the rotator may be calculated by assuming a uniform density of the sphere. The dimensions of the gyroscopic rotator were denoted as follows.\\
 
-	\paperfig{Sphere}{\begin{tikzpicture}
+	\paperfig{Sphere}{\hspace{4ex}\begin{tikzpicture}
 		\draw (0, 0) circle (50pt);
@@
 	\end{tikzpicture}}{A sphere of radius \( R \) truncated to obtain a minimum distance from the center of \( R - \delta = \xi \), constituting a gyroscopic rotator.
-The angular momentum vector lies in the horizontal plane at all times and has a magnitude of \( I\omega \)}.
+The angular momentum vector lies in the horizontal plane at all times and has a magnitude of \( I\omega \).}
 
@@
 
-	Observations go here
+Under the strobe light, the sphere came to a standstill, to the point where changing the strobe light frequency from 3600 flashes per minute by a few points would add noticable rotation to the sphere.
+Thus, the frequency of the sphere's rotation was determined to be $(60\pm.02)\si{\hertz}$.
+Additionally, this experiment does not work if the surface of rotation is not perfectly horizontal, the provided level was used to make sure that all areas of the surface were as level as possible.
+
+The diameter of the sphere was measured with a capliper in several places, resulting in a value of $(50.525\pm.005)\si{\milli\meter}$ for the diameter, or $R=(25.263\pm.003)\si{\milli\meter}$ for the radius.
+The ``diameter'' of the sphere measured along its axis of rotation was $(48.620\pm.005)\si{\milli\meter}$ resulting in a distance from the centre to the middle of the flat side of $\xi=(23.357\pm.006)\si{\milli\meter}$, meaning that the cutoff distance was measured to be $\delta=(1.905\pm.007)\si{\milli\meter}$.
+
+The periods of revolution of the sphere obtained by marking a point on the wall and waiting for a steady laser to pass over the same point were recorded below.\\
+
+\paperfig{T}{\begin{papertable}{|[outer]I|[inner]C|[outer]}\paperoline
+\papertableindexheader&\textsc{Period}\\
+\papertablecheadersymbol{T$ $(\pm\SI{1}{\second})}\\\paperiline
+\papertableindex\papertablecval{635}\\\paperiline
+\papertableindex\papertablecval{642}\\\paperiline
+\papertableindex\papertablecval{645}\\\paperiline
+\papertableindex\papertablecval{644}\\\paperiline
+\papertableindex\papertablecval{645}\\\paperiline
+\papertableindex\papertablecval{644}\\\paperiline
+\papertableindex\papertablecval{645}\\\paperiline
+\papertableindex\papertablecval{645}\\\paperiline
+\papertableindex\papertablecval{646}\\\paperiline
+\papertableindex\papertablecval{647}\\\paperoline
+\end{papertable}\vspace{-1.5em}}
+{The observed periods of rotation of the sphere.
+By discrading the first two measurements due to the fact that the sphere was still stabilising, yields an averarage period of $(645\pm1)\si{\second}$.}\\
+
+The results in \figT show that the average rate of rotation of the sphere was one rotation every $(645\pm1)\si{\second}$.
 
@@
 
-	Analysis goes here
+First, a placeholder value called $\epsilon$ was calculated, which was the ratio between $\delta$ and $R$.
+
+\papereq{E}{\epsilon=\frac\delta R}{gmg/gdl}
+\begin{paperwhere}
+\papervar{\epsilon}{fraction cut off}{}
+\papervar{\delta}{distance cut off}{\meter}
+\papervar{R}{radius of sphere}{\meter}
+\end{paperwhere}
+
+For the calculated values of $\delta$ and $R$, the value of $\epsilon$ was derived to be $(0.0754\pm.0003)$.
+Next, the torque was calculated using the following formula, which is an expansion of the $r\cross F$ formula using the knowledge of the sphere's shape and simplified using the fact that $(r+a\cdot F)\cross F=r\cross F$.
+
+\papereq{L}{\fontsize{9pt}{9pt}\selectfont\vec L=\rho g\int\limits_{\text-R}^{R-\delta}\int\limits_{\text-\sqrt{R^2-x^2}}^{\sqrt{R^2-x^2}}2\sqrt{R^2-x^2-y^2}(y,\text-x,0)\d y \d x}{}
+\begin{paperwhere}
+\papervar{\vec L}{torque}{\newton\metre}
+\papervar{\rho}{density}{\kilo\gram\per\meter\cubed}
+\papervar{g}{gravitational acceleration}{\meter\per\second\squared}
+\end{paperwhere}
+
+The resulting vector from \eqL is the vector (0,$(6.74\pm.02)\SI{E-9}{}\rho g$,0).
+This is sensible as there is no torque in the $x$ or $z$ component, but only torque in the $y$ component.
+Thus, $L=(3.37\pm.01)\SI{E-9}{}\rho g$.
+Without plugging in the values of $R$ and $\delta$, the $y$ component of the above integrates to $\frac{\pi\delta^2(2r-\delta)^2\rho g}{4}$, which can be rewritten as $\frac{g\rho\pi R^4\epsilon^2(2-\epsilon)^2}{4}$.
+
+For the moment of inertia of the sphere, the integral is done by subtracting the moment of intertia of the sliced off piece from that of a sphere, then integrating over expanding rings.
+The result is the following.
+
+\papereq{I}{\fontsize{9pt}{9pt}\selectfont I=\rho\left(\frac{8\pi R^5}{15}-\int\limits_{R-\delta}^{R}\int\limits_0^{\sqrt{R^2-x^2}}2\pi r^3\d r\d x\right)}{}
+\begin{paperwhere}
+\papervar{I}{moment of inertia}{\meter\square\kilo\gram}
+\end{paperwhere}
+
+The result from \eqI is $I=(1.72\pm.01)\SI{E-8}{}\rho$.
+Without plugging in the values of $R$ and $\delta$, the above integrates to $\rho\left(\frac{8\pi R^5}{15}-\frac{\delta^3\pi(3\delta^2-15\delta R+20R^2)}{30}\right)$, which can be rewritten as $\frac{\rho\pi R^5(2-\epsilon)^3(\epsilon^2+\epsilon+\frac23)}{10}$.
+
+It is known that the ratio of the torque and the product of the moment of inertia and the angular velocity about the sphere's axis is equal to the angular velocity of the precession in the plane.
+But the angular velocities are given by the ratio of $2\pi$ by the period, thus we get the following.
+
+\papereq{R}{\frac{2\pi}{T}\cdot\frac{2\pi}{\frac{1}{60}}=\frac{L}{I}}{}
+\begin{paperwhere}
+\papervar{T}{precession period}{\second}
+\end{paperwhere}
+
+Note that by taking the ratios of \eqL and \eqI, we can derive an expression equivalent to \eqR.
+
+\papereq{S}{\frac LI=\frac{5g\epsilon^2}{2R(2-\epsilon)(\epsilon^2+\epsilon+\frac23)}}{}
+
+By plugging in all the obtained values, and equating \eqR and \eqS, we get that
+$(3.67\pm0.08)\si{\per\second\squared}=(0.39\pm.02)\si{\per\metre}g$.
+Thus, we obtain the final result of $g=(9.79\pm.02)\si{\metre\per\second\squared}$.
 
@@
 
-	\papersource{}
+	\papersource{`g' Using Precession of an Air Gyroscope, gmg/gdl -- 1971, jbv 1990}
 

### 2018-03-28 air_gyroscope/paper.tex
Script + paper

@@
 
-	HEY SORRY FOR CAPS COULD YOU PLEASE TRY TO KEEP ``OBSERVATIONS'' RIGHT AT THE TOP OF PAGE TWO? THANKS
+	The precession of an air gyroscope is a simple yet an accurate way of approximating the value of \textit{g}, the acceleration due to gravity.
+This paper outlines the experimental setup as well as some necessary derivations.
+Upon implementing the procedure, \( g \) is determined to be \( \pars{9.79 \pm .02} \si{\metre\per\second\squared} \), agreeing with the actual value.
 
@@
 
-	The change in the angular momentum vector of the rotor arises from a torque acting in the horizontal plane resulting from the imbalance from the truncated section of the sphere.
+	The change in the angular momentum vector of the rotor arises from a torque acting in the horizontal plane result5ing from the imbalance from the truncated section of the sphere.
 A pure precession about a vertical axis arises due to the fact that the torque is at all times perpendicular to the angular momentum.
@@
 
-	Conclusion goes here
+	This experiment has shown that a simple setup designed to observe the precession of an air gyroscope could be used to accurately determine the value of \textit{g}.
+Specifically, acceleration due to gravity was determined to be \( \pars{9.79 \pm .02} \si{\metre\per\second\squared} \), agreeing with the actual value.
+
+	Various sources of possible error may arise as one implements the procedure outlined in this experiment.
+For instance, upon obtaining the desired frequency of rotation of the truncated sphere, the first few rotations could be affected by the still-significant transients in the motion.
+This could be reflected in measurements in the form of a shorter period of rotation.
+Additionally, one's control of air flow is limited and is assumed to remain constant throughout the course of the experiment.
+Finally, some error could arise from numerical approximations of integrals, but it remains nearly insignificant when compared to other sources.
 

### 2018-03-29 air_gyroscope/integration.py
done

@@ -1,4 +1,3 @@
-#!/bin/python
 # Integrates the volume of the truncated sphere
 
 # ---------- Import Statements ----------
@@ -47,9 +46,9 @@ rho = 1
 g = 1
 
 val1 = integrate.dblquad(func1, R - delta, R, gfun1, hfun1)
-print "I:", rho * (8 * np.pi * R ** 5) / 15 - val1[0], "+-", val1[1]
+print("I:", rho * (8 * np.pi * R ** 5) / 15 - val1[0], "+-", val1[1])
 
 val2x = integrate.dblquad(func2x, - R, R - delta, gfun2, hfun2)
 val2y = integrate.dblquad(func2y, - R, R - delta, gfun2, hfun2)
-print "L, x:", rho * g * val2x[0], "+-", val2x[1]
-print "L, y:", rho * g * val2y[0], "+-", val2y[1]
+print("L, x:", rho * g * val2x[0], "+-", val2x[1])
+print("L, y:", rho * g * val2y[0], "+-", val2y[1])
